### 2021-08-09 docs/09-09-21_three-category/three-category.Rmd
09-09-2021 slides beginning

---
title: A multinomial spatio-temporal model for sexual risk behaviour in adolescent girls and young women
subtitle: HIV Inference Lab Group Meeting
author: Adam Howes
institute: Imperial College London
date: August 2021
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

## Background

* Want to estimate the proportion $p_k$ of AGYW in $K = 4$ risk categories
  * $k = 1$: Not sexually active
  * $k = 2$: Cohabiting, single partner
  * $k = 3$: Non-regular partner(s)
  * $k = 4$: Key population, female sex worker
* Used as a step towards estimating total incidence by group
  * By district, age, sex, time
* Different policy responses depending on where new infections are

## Extent

* 13 AGYW Global Fund priority countries (but fitting individually)
  * Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Swaziland, Tanzania, Uganda, Zambia and Zimbabwe
* The available DHSs

## Goal

* Estimate proportions indexed by
  * District $i = 1, \ldots, n$
  * Survey $t = 1, \ldots, T$
  * Age $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
  * Category $k$
* e.g. in Lilongwe, in 2015, how many AGYW aged 20-24 are cohabiting with a single partner?

## Multinomial likelihood

* We have proportions $p_1, \ldots, p_4$ which are all $\in [0, 1]$ and $\sum_k p_k = 1$
* $\implies$ suggests using a multinomial likelihood $\mathbf{y}_{ita} \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{itaK})$
$$
p(\mathbf{y}_{ita} \, | \, m_{ita}, p_{ita1}, \ldots, p_{ita4}) = \frac{m_{ita}!}{y_{ita1}! \times \cdots \times y_{ita4}!} p_{ita1}^{y_{ita1}} \times \cdots p_{ita4}^{y_{ita4}}
$$

## Multivariate model

* Requires a multivariate model in that each observation depends on $K$ probabilities
  * Really $K - 1$ numbers, since they are constrained to sum to one
* Usually this is done by modelling the "contrasts" between categories
  * How much more likely to be in this category (or group of categories) than that category (or group of categories)
* These types of models are popular in economics to model choice
  * Treat the latent field like utilities of choices
* Some keywords: discrete choice model, multinomial logit model

## Baseline category

* Pick one of the $k \in \{1, \ldots, K\}$ as your baseline category, say $k = 2$
* Define log-odds for being in category $k \neq 2$ versus $k = 2$
$$
\log \left( \frac{p_{itak}}{p_{ita2}} \right)
$$
* Three of these: $\{2\}$ versus $\{1\}$, $\{2\}$ versus $\{3\}$ and $\{2\}$ versus $\{4\}$

## Nested

* Attractive when it is appropriate to model individuals as making choices sequentially
* $\{1\}$ versus $\{2, 3, 4\}$, $\{2\}$ versus $\{3, 4\}$ and $\{3\}$ versus $\{4\}$
* Choosing 1. whether or not to have sex, 2. conditional on having sex, whether to have one cohabiting partner or irregular partners seems reasonable
* Choosing 3. whether or not to be a FSW based upon choosing to have irregular partners is less reasonable
  * i.e. not like you first choose to have many partners then choose to be FSW, more like choose to be FSW based on economic factors say

## Workaround requried

* Want to fit this model quickly and easily using `R-INLA`
* Sadly `R-INLA` doesn't work for likelihoods which depend upon multiple elements of the latent field (like this multinomial model)
* There is a workaround, called the Poisson trick
  * A multinomial likelihood can be rewritten as a Poisson likelihood (with some additional nuisance parameters)
  * So this respecifies the model in terms of a Poisson likelihood for each category of the observation

## Poisson trick

* Based on the following fact
* Let $y_k \sim \text{Pois}(\lambda_k)$, $k = 1, \ldots, K$ then $\y \, | \, n \sim \text{Multinomial}(\y; n, p_1, \ldots, p_K)$
  * $m = \sum_k y_k$
  * $p_j = \lambda_j / \sum_{k = 1}^K \lambda_k$
* In words, given their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized]
  * In some some way you can obtain the multinomial likelihood (what we want) from Poisson likelihoods (what we have to work with)

## Poisson trick

* In the multinomial likelihood, the sample size is treated as fixed
* Instead treat $m = \sum_k y_k$ as random. Let $\Lambda = \sum_{k = 1}^K \lambda_k$ and suppose that $m \sim \text{Poisson}(\delta \Lambda)$ [@lee2017poisson]
\begin{align*}
P(\mathbf{y}, m) = P(m)P(\mathbf{y} \, | \, m) &= \exp(-\delta \Lambda) \frac{(\delta \Lambda)^m}{m!} \times \frac{m!}{\prod_k y_k!} \prod_k \left( \frac{\lambda_k}{\Lambda} \right)^{y_k} \\
&= \prod_k \left( \frac{\exp(-\delta \lambda_k) \left( \delta \lambda_k \right)^{y_k}}{y_k!} \right)
\end{align*}

## Poisson trick

* To find the marginal $P(\mathbf{y})$ sum over the possible values of $m$ (0 to $\infty$)
$$
P(\mathbf{y}) = \prod_k \left( \frac{\exp(-\delta \lambda_k) \left( \delta \lambda_k \right)^{y_k}}{y_k!} \right)
$$
* $\implies y_k \sim \text{Poisson}(\delta \lambda_k)$ independently

## Poisson log-linear model

* $y_{itak} \sim \text{Poisson}(\lambda_{itak})$
* $\log(\lambda_{itak}) = \eta_{itak}$ the linear predictor for district $i$, survey $t$, age-group $a$ and category $k$
* Including observation-specific random effects $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$ in the model $\eta_{itak} = \theta_{ita} + \cdots$ assures exact reproduction of the multinomial denominators
  * By "observation" I mean observation of the multinomial e.g. a vector `c(2, 5, 3, 0)`
* Then you put whatever mixed model things you'd like in

## No intercept

* Don't include an intercept, i.e. `-1` in the formula
* This is because we are interested in recovering probabilities from the model
$$
p_j = \frac{\lambda_j}{\sum_{k = 1}^K \lambda_k} = \frac{\exp{\eta_j}}{\sum_{k = 1}^K \exp{\eta_j}}
$$
* So adding a constant $\beta_0$ on to each of the $\eta_j$ does nothing (so I'd hope that if you did include a constant it would turn out to be zero if you fitted the model)
$$
\frac{\exp{(\eta_j + \beta_0)}}{\sum_{k = 1}^K \exp{(\eta_j + \beta_0)}} = \frac{\exp{\eta_j}}{\sum_{k = 1}^K \exp{\eta_j}}
$$
* Note that this `exp(x) / sum(exp(x))` function is called "softmax"

## Nine models

* Always use age-category random effects $\alpha_{ak} \sim \mathcal{N}(0, \tau_\alpha^{-1})$
  * I haven't been including category random effects, but based on my research for this presentation I think I should have been. I think because I have the age-category it's already mopping up the intercept
* Three choices for spatial-category random effects $\phi_{ik}$:
  * None
  * IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$
  * BYM2
* Three choices of time-category random effects $\gamma_{tk}$
  * None
  * IID $\gamma_{tk} \sim \mathcal{N}(0, \tau_\gamma^{-1})$
  * AR1
* Some amount of nuance / choice to defining the structured {spatial (BYM2), temporal (AR1)}-category interactions

## First way

* Let `area_idx` be an indicator the the area
* `area_idx.k = ifelse(category == k, area_idx, NA)` is that same indicator but just for the category `k`
* Then (say you want spatial) you can use `f(area_idx.k, model = "bym2", graph = adjM)` in your `R-INLA` formula
* This results in a set of $K$ independent spatial random effects
$$
\phi_{ik} = \sqrt{\tau_{\phi_{k}}^{-1}} \left(\sqrt{\pi_k} \cdot u_{ik} + \sqrt{1 - \pi_k} \cdot v_{ik} \right), \quad k = 1, \ldots, K
$$
* Key point is that you have different hyperparameters for each category $\{\tau_{\phi_k}, \pi_k\}$
  * Do we want this?
* Also have to define `area_idx.k` and write `f(...)` more times (annoying)

## Second way

* Alternative (in `R-INLA`) is to use the `group` option which lets you define "Gaussian Kronecker product Markov random fields"
  * Sounds fancy, isn't that fancy
* "Precison matrix" (probably it doesn't have full rank so it's not really a precision) defined by $\mathbf{Q} = \mathbf{Q}_1 \otimes \mathbf{Q}_2$
* In `R-INLA` it's more like the "structure matrix" is defined by $\mathbf{R} = \mathbf{R}_1 \otimes \mathbf{R}_2$
  * So that the precision is $\mathbf{Q} = \tau \mathbf{R}$

## Example of `group` option

* Let's say we're trying to define the time-category interaction random effects, using an AR1 on time
* If there are three surveys, and we suppose $\rho = 1$ then the precision matrix for this AR1 is
$$
\begin{pmatrix}
1 & -1 & 0 \\
-1 & 2 & -1 \\
0 & -1 & 1
\end{pmatrix}
$$
* To get the structure matrix $\mathbf{R_1}$ we'd divide by `exp(mean(log(diag(Q))))`

## Example of `group` option

* For the "category random effects" grouping variable we want IID structure, so that the precision (and structure matrix $\mathbf{R_2}$) are
$$
\begin{pmatrix}
1 & 0 & 0 \\
0 & 1 & 0 \\
0 & 0 & 1
\end{pmatrix}
$$
* The `R-INLA` call for this is `f(sur_idx, model = "ar1", group = cat_idx, control.group = list(model = "iid"), ...)`
* The new structure matrix looks like
$$
\mathbf{R} =
\begin{pmatrix}
\mathbf{R_1} & \mathbf{0} & \mathbf{0} \\
\mathbf{0} & \mathbf{R_1} & \mathbf{0} \\
\mathbf{0} & \mathbf{0} & \mathbf{R_1}
\end{pmatrix}
$$
* Important difference: just have one set of hyperparameters $\{\tau_\gamma, \rho\}$
  * i.e. there is pooling across categories doing it this way

## References {.allowframebreaks}

### 2021-08-09 docs/09-09-21_three-category/ar1.R

@@ -1,0 +1,16 @@
+#' From https://haakonbakkagit.github.io/btopic120.html
+precision_ar1 = function(N, rho){
+  Q <- matrix(0, N, N)
+  diag(Q) <- 1 + rho^2
+  for (i in 1:(N-1)) {
+    Q[i, i + 1] <- -rho
+    Q[i + 1, i] <- -rho
+  }
+  Q[1, 1] <- 1
+  Q[N, N] <- 1
+  return(Q)
+}
+
+Q <- precision_ar1(3, 1)
+
+exp(mean(log(diag(Q))))

### 2021-08-09 docs/09-09-21_three-category/three-category.Rmd
Slides up

@@
 ---
-title: A multinomial spatio-temporal model for sexual risk behaviour in adolescent girls and young women
+title: A multinomial spatio-temporal model for sexual risk behaviour in AGYW
 subtitle: HIV Inference Lab Group Meeting
@@
 * Want to estimate the proportion $p_k$ of AGYW in $K = 4$ risk categories
-  * $k = 1$: Not sexually active
-  * $k = 2$: Cohabiting, single partner
-  * $k = 3$: Non-regular partner(s)
-  * $k = 4$: Key population, female sex worker
+  * $k = 1$: Not sexually active `nosex12m`
+  * $k = 2$: Cohabiting, single partner `sexcohab`
+  * $k = 3$: Non-regular partner(s) `sexnonreg`
+  * $k = 4$: Key population, female sex worker `sexpaid12m`
 * Used as a step towards estimating total incidence by group
@@
 * Different policy responses depending on where new infections are
-
-## Extent
-
-* 13 AGYW Global Fund priority countries (but fitting individually)
-  * Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Swaziland, Tanzania, Uganda, Zambia and Zimbabwe
-* The available DHSs
 
@@
   * District $i = 1, \ldots, n$
+    * 13 AGYW Global Fund priority countries (but fitting individually): Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Swaziland, Tanzania, Uganda, Zambia and Zimbabwe
   * Survey $t = 1, \ldots, T$
+    * The available DHSs
   * Age $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
@@
 * e.g. in Lilongwe, in 2015, how many AGYW aged 20-24 are cohabiting with a single partner?
+
+## Why not just use the raw data
+
+1. Usual high variance from low counts problem, improved by spatio-temporal smoothing
+2. The raw proportions don't add up to one
+  * This is illustrated in the next slide
+
+##
+
+:::: columns
+
+::: column
+
+```{r echo=FALSE}
+knitr::include_graphics("page1-check100.pdf")
+```
+
+:::
+
+::: column
+
+```{r echo=FALSE}
+knitr::include_graphics("page2-check100.pdf")
+```
+
+:::
+
+::::
 
@@
   * How much more likely to be in this category (or group of categories) than that category (or group of categories)
+  * Different ways to do this
 * These types of models are popular in economics to model choice
-  * Treat the latent field like utilities of choices
+  * Treat the latent field like utility
 * Some keywords: discrete choice model, multinomial logit model
@@
 
+## Sidenote: ordinal
+
+* $\pi_{k} = \sum_{l \leq k} p_{l}$ be the cumulative probability of category $k$ where $\pi_{1} \leq \pi_{2} \leq \cdots \leq \pi_{K}$.
+* Ordinal logistic regression is based upon $K - 1$ cumulative logits $\text{logit} (\pi_{k}) = \eta_{k}$ where the linear predictors are ordered
+* One way to do this is to assume $\eta_k$ only differ in their intercept (also called cut-point)
+* I wonder if you can fit this with a single linear predictor and a category random effect?
+  * Possibly wouldn't need Poisson trick
+
 ## Poisson trick
@@
 
+## Poisson trick
+
+* "The Poisson surrogate model eliminates $m$ from the denominator of the multinomial probabilities.
+This makes sense intuitively, as we do not expect the multinomial sums to provide any useful information in estimating the fixed effects." [@lee2017poisson]
+* Example of a broader class of Poisson transformations where the theme is to consider the normalisation constant as another parameter [@barthelme2015poisson]
+* I guess that this must mean the normalisation constant is "estimated" exactly always
+
 ## Poisson log-linear model
@@
   * By "observation" I mean observation of the multinomial e.g. a vector `c(2, 5, 3, 0)`
+  * These variables correspond to $\log(\delta)$ from before. So we're just having a free parameter which can 
 * Then you put whatever mixed model things you'd like in
@@
 
+## Survey weights
+
+* Use survey weights to calculate effective observation `x_eff`
+* May not be integers i.e. `c(1.87, 5.32, 2.20, 0.15)`
+* Deal with this by using `xPoisson` (generalisation of the Poisson to non-integer data) rather than `Poisson`
+* Might be equivalent to weighted log-likelihood approach
+
+##
+
+:::: columns
+
+::: column
+
+```{r echo=FALSE}
+knitr::include_graphics("page-multinomial-smoothed-district-sexbehav.pdf")
+```
+
+:::
+
+::: column
+
+* A (difficult to see) example of what this looks like
+* Model 9 has BYM2 and AR1
+* Other notes
+  * Quantiles produced by manipulating `inla.posterior.sample`s
+  * Same samples used in combination with Naomi population data to produce aggregates (i.e. 15-24 age category)
+
+:::
+
+::::
+
+## Data issues for `sexpaid12m` category
+
+* Two different questions asked in the DHS, and answered very differently
+* Before 2015, asked about most recent three partners. One of the categories for these is paid
+  * Very rare to list one of these as paid, using this question often think there are essentially no FSW
+* After 2015, asked if have given or received gifts or money in exchange for sex
+  * Better answered but still has issues
+    * Missing some FSW from survey sampling frame
+    * Not all "gifts of money in exchange for sex" is sex work
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("../../archive/check_sexpaid-survey-question/20210720-120340-77026581/sexpaid-survey-question.pdf")
+```
+
+## Current approach
+
+* Can't fit a (meaningful) spatio-temporal model when the question asked / response is so different
+* Have been fitting single-survey spatial models to the most recent DHS
+* Otherwise have created a three-category model, moving all `sexpaid12m` into `sexnonreg` to create a new `sexnonregplus` category
+  * Haven't checked that some of the `sexpaid12m` shouldn't go into `sexcohab` rather than `sexnonreg` yet (sorry Katie!)
+* Challenge is what to do about the `sexpaid12m` category
+
+## What to do about the `sexpaid12m` category
+
+1. Ignore it
+2. Try to use other data sources to help
+  * Previous estimates from workbook are based upon national estimates of FSW population size (perhaps the UNAIDS Key Population Atlas)
+
+## Johnston et al. (2021, preprint)
+
+**Deriving and interpreting population size estimates for adolescent and young key populations at higher risk of HIV transmission: men who have sex with men, female sex workers and transgender persons**
+
+* Disaggregates the UNAIDS published population size estimates by age (nice, but not by district, which we'd also want) using proportion of sexually active adults
+* Kinh is a coauthor and warns that
+  * The estimates should (often) be seen as expert opinion rather than based on data
+  * Several countries had no data
+  * Rounding up when the number is too small
+
+## Laga et al. (2021, preprint)
+
+**Mapping female sex worker prevalence (aged 15-49 years) in sub-Saharan Africa**
+
+* Collates available FSW population size estimates
+* Small-area model with covariates used to extrapolate to district level
+* Has code available
+* Probably the best single source to rely on, done a lot of the work already
+
+## Hodgkins et al. (2021, preprint)
+
+**HIV prevalence, population sizes, and HIV prevention among men who paid for sex in sub-Saharan Africa: a meta-analysis of 82 population-based surveys (2000-2020)**
+
+* Proportion of men who pay for sex (CFSW) estimated from survey data
+* Could be linked to proportion FSW by some model e.g.
+$$
+p_{\text{CFSW}} = B \times p_{\text{FSW}}
+$$
+with a strongly informative prior $B \sim p(B)$ (around 10 say)
+  * Don't know if this is a good model, anyone have any ideas?
+  * Extract estimates from Hodgkins and plot versus estimates of FSW to see if it looks linear
+  * Of course the ratio is going to vary, but perhaps it's quite stable?
+* Fit a model on the good DHS `sexpaid12m` question, then use it where there isn't the question
+
+##
+
+\begin{align}
+\log(p_{\text{CFSW}}) - \log(p_{\text{FSW}}) &= \log(B) \\
+\log \left( \frac{p_{\text{CFSW}}}{p_{\text{FSW}}} \right) &= \log(B)
+\end{align}
+
 ## References {.allowframebreaks}

### 2021-09-22 docs/24-09-21_new-cohort/new-cohort.Rmd
Start presentation for new cohort

---
title: "Spatio-temporal statistics for HIV surveillance"
author: "Adam Howes"
date: "August 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
subtitle: StatML Kick-off Camp
bibliography: citations.bib
institute: Imperial College London
---

## Welcome!

* Welcome to the CDT!
* Congratulations for many of you on completing your previous studies under some non-ideal circumstances

## About me / my project

* Surveillance of HIV in sub-Saharan Africa in collaboration with UNAIDS
* Main interest is in methods and applications of Bayesian statistics towards policy-relevant questions

## Spatio-temporal

* Observations are indexed by space $s$ and time $t$
* For example, often we have a sequence of national surveys
* In social science it's natural that we observe people in space and time
* Key property of spatio-temporal data is correlation structure

## Bayesian statistics

* Bayesian statistics makes sense to me
* Perhaps more importantly, there isn't a lot to remember
  1. Write down a model for your process
  2. Some kind of algorithm to obtain the posterior
  3. Use the posterior for all decision theory

## Data and theory

* The data we work with is incomplete, biased, noisy
* Mainly concerned with getting roughly the right answer
* Happy to use informative priors or scientific knowledge of domain experts to help

## 1. Size of the sample

* Running a (household) survey is expensive
* We only get small-sample sizes, and a low coverage of space-time
* The field of "small-area" estimation should really be called "small-data" estimation
* We use the fact that spatio-temporal data is correlated to improve things with smoothing

## 2. Who is in the sample?

* The sample probably often isn't representative 
* Some people aren't on the sampling frame at all
* Example: for HIV, there are some key population groups (men who have sex with men, transgender people, injecting drug users, sex workers) who are hard to reach with surveys

## 3. Are the answers they give accurate?

* Survey questions can be ambiguous
* People may not be able to or want to answer questions
* Example: age at first sex is an important epidemiological parameter, but men and women (and old and young) give answers which are difficult to make line up

## Sexual risk categories model

* Some work in progress of mine, hopefully will make the above more concrete
* Young women are an important population for HIV prevention

## References {.allowframebreaks}

### 2021-09-24 docs/24-09-21_new-cohort/new-cohort.Rmd
Finish presentation for new cohort

@@
 ---
-title: "Spatio-temporal statistics for HIV surveillance"
+title: "Statistics for HIV surveillance"
 author: "Adam Howes"
@@
 * Congratulations for many of you on completing your previous studies under some non-ideal circumstances
+* PhDs can be challenging, learning process
+    * I hope I'm a better researcher than I was two years ago
+* Important to find the right work environment, draw on each other
 
@@
 
-* Some work in progress of mine, hopefully will make the above more concrete
+* Some work in progress of mine, to hopefully make the above concrete!
 * Young women are an important population for HIV prevention
+    * 10% of the population and 25% of all new infections [@unaids2021update]
+* Not enough resources to provide programs for all young women in high prevalence settings $\implies$ standardised method for accessing population at risk required
+
+##
+
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{lll}
+\toprule
+Category & HIV related risk & HIV risk ratio \\ 
+ \midrule
+None & Not sexually active & 0 \\
+Low & Sexually active, one cohabiting partner & 1 \\
+High & Non-regular sexual partner(s) & 1.72 \\
+Very high & Young women from key populations & 13 \\
+\bottomrule
+\end{tabularx}
+\caption{HIV risk categories and risk ratios.}
+\end{table}
+
+## Goal
+
+* Estimate proportion of young women in each risk category
+  * Districts $i = 1, \ldots, n$ in 13 AGYW Global Fund priority countries
+  * Survey $t = 1, \ldots, T$
+  * Age $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
+* e.g. in Lilongwe (Malawi), in 2015, how many AGYW aged 20-24 are cohabiting with a single partner?
+
+## Spatial random effects
+
+* Tried none, IID and the Besag model (most common structured spatial random effect model)
+
+$$
+b_i \, | \, \mathbf{b}_{-i} \sim \mathcal{N} \left(\frac{\sum_{j: j \sim i} b_j}{n_{\delta i}}, \frac{1}{n_{\delta i}}\right),
+$$
+
+## Temporal random effects
+
+* Tried none, IID and an AR1 model (most common structured spatial random effect model)
+
+\begin{align*}
+a_1 &\sim \left( 0, \frac{1}{1 - \rho^2} \right), \\
+a_t &= \rho a_{t - 1} + \epsilon_t, \quad t = 2, \ldots, T, 
+\end{align*}
+
+##
+
+\begin{table}[htb]
+\centering
+\begin{tabularx}{\textwidth}{llllllllll}
+Model ID & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+\midrule
+Spatial structure & S1 & S2 & S3 & S1 & S2 & S3 & S1 & S2 & S3 \\
+\midrule
+Temporal structure & T1 & T1 & T1 & T2 & T2 & T2 & T3 & T3 & T3 \\
+\end{tabularx}
+\caption{All of the models considered}
+\label{tab:models}
+\end{table}
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("../../archive/process_information-criteria/20210916-133107-9c7e6acd/all-dhs-rank-comparison.pdf")
+```
 

### 2021-09-29 docs/24-09-21_new-cohort/new-cohort.Rmd
This was in September not August

@@
 author: "Adam Howes"
-date: "August 2021"
+date: "September 2021"
 output:

### 2021-11-26 docs/30-11-21_coverage/coverage.Rmd
First half of slides about coverage for next Tuesdays lab meeting

---
title: Graphical tests for coverage
subtitle: HIV Inference Lab Group Meeting
author: "Adam Howes"
date: "November 2021"
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7
    fig_height: 3
    includes:
      in_header: preamble.tex
  slidy_presentation:
    highlight: haddock
bibliography: citations.bib
institute: Imperial College London
---

##

**Calibration** If I say something I mean it (in some weak probabilistic sense).

If I say "this event happens with probability $p$" then it does actually happen $p$ proportion of the time.

##

A **credible interval** is a Bayesian alternative to a confidence interval.

I think people often talk about them as if they are interchangeable, which is probably fine.

##

A $(1 - \alpha)100$% **confidence interval** $[L, U]$ for a parameter $\theta$ is intended to have the property that $(1 - \alpha)100$% of intervals calculated according to the procedure contain $\theta$.

(According to frequentist interpretation, the probability that $\theta \in [L, U]$ is either 0 or 1, it either is or it isn't covered.
It's the interval rather than the parameter which is random.)

##

On the other hand, a $(1 - \alpha)100$% **credible interval** $[L, U]$ for $\theta$ is intended to have the (more natural) property that
$$
\mathbb{P}(L \leq \theta \leq U) = 1 - \alpha.
$$

Now this is a probability statement! We can talk about if these claims about coverage are calibrated.

##

For example, in the Naomi app often when you hover over a number it comes up with an interval (I think these are 90%).

It would be good if 90% of the time the actual number was contained within that interval!

##

**Note** this means we also want it to be outside the interval 10% of the time.
Saying you're 90% sure and being right 100% of the time (under-confidence) is also an error.

##

**Also note** that this isn't the only thing we care about.
If I tell you that the probability HIV prevalence is within $[0, 1]$ (no one to everyone) then you can't really fault my coverage, but also I'm not very useful.
Other thing we might care about is sharpness (saying more precise things).
Proper scoring rules assess these together, but I don't think they can be decomposed.

##

How could you assess this?

As usual, we have the problem of not (and never being able to) know what the true value of the parameter is.

Workaround is to try to have the raw estimate (no model) be contained in the (modelled) interval instead.

##

Compare

* **nominal coverage**, probability we claimed that interval contains the number, to
* **empirical coverage**, proportion of intervals which actually contain the number.

Ideally they should be the same.

##

**Criticism**: intervals are defined based on a particular significance level $\alpha$.
The choice of this significance level is *arbitrary* (a bad word).

How do we assess the calibration of our credible intervals for all possible $\alpha$?

## References {.allowframebreaks}

### 2021-11-29 docs/30-11-21_coverage/coverage.Rmd
80% there on passable slides. Need to add the new plots. Perhaps some actual discussion of the paper's contribution as well.

@@
 ---
-title: Graphical tests for coverage
+title: Graphical tests for coverage [@sailynoja2021graphical]
 subtitle: HIV Inference Lab Group Meeting
@@
 
-##
+```{r echo = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
+
+## Caliration
 
@@
 
-##
+## Intervals
 
@@
 
-##
+## Confidence interval
 
@@
 
-##
+## Credible interval
 
@@
 
-##
+## Example of credible intervals
 
@@
 
-##
+## Expect to "be wrong" sometimes
 
@@
 
-##
+## Sharpness and SPSR
 
 **Also note** that this isn't the only thing we care about.
+
 If I tell you that the probability HIV prevalence is within $[0, 1]$ (no one to everyone) then you can't really fault my coverage, but also I'm not very useful.
+
 Other thing we might care about is sharpness (saying more precise things).
-Proper scoring rules assess these together, but I don't think they can be decomposed.
+Scoring rules assess these together.
+Defining feature of (strictly) proper scoring rules is that they can't be gamed.
 
-##
+It would be nice is there was some type of decomposition along the lines of
+$$
+\text{score(forecast)} = \text{calibration(forecast)} + \text{sharpness(forecast)},
+$$
+but AFAIK that doesn't exist.
 
-How could you assess this?
+## Using raw data rather than truth
+
+How can we assess the calibration of our credible intervals?
 
@@
 
-##
+## Nominal versus empirical
 
@@
 
+## Example
+
+Say that the nominal coverage is 90%:
+
+| Analyst   | $n$ | Inside the CrI | Empirical coverage | Diagnosis |
+| --------- | --- | -------------- | ------------------ | --------- |
+| Hai Kon   | 28  | 27             | 96%                | Overconfident |
+| Relan     | 28  | 21             | 75%                | Underconfident |
+
+*Any resemblance to real people living or dead is purely coincidental.*
+
 ##
@@
 
+##
+
+```{r}
+library(ggplot2)
+
+ggplot() + 
+  stat_function(fun = dnorm) +
+  xlim(c(-3, 3)) +
+  theme_void() +
+  labs(title = "Posterior predictive distribution")
+```
+
+##
+
+```{r}
+ggplot() + 
+  stat_function(fun = dnorm) +
+  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
+  xlim(c(-3, 3)) +
+  theme_void() +
+  labs(title = "Add a credible interval (equal-tailed)")
+```
+
+##
+
+```{r}
+ggplot() + 
+  stat_function(fun = dnorm) +
+  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
+  geom_point(data = data.frame(x = 0.75, y = 0), aes(x = x, y = y), size = 5) +
+  geom_label(data = data.frame(x = 0.75, y = 0.05, label = "Within interval"), aes(x = x, y = y, label = label)) +
+  xlim(c(-3, 3)) +
+  theme_void() +
+  labs(title = "Suppose that this is the observation we get")
+```
+
+##
+
+```{r}
+ggplot() + 
+  stat_function(fun = dnorm) +
+  stat_function(fun = dnorm, xlim = c(-1.96, 1.96), geom = "area", alpha = 0.2) +
+  geom_point(data = data.frame(x = 0.75, y = 0), aes(x = x, y = y), size = 5) +
+  geom_label(data = data.frame(x = 0.75, y = 0.05, label = "Quantile: 0.674"), aes(x = x, y = y, label = label)) +
+  xlim(c(-3, 3)) +
+  theme_void() +
+  labs(title = "Is it in the interval, yes or no, doesn't tell the full story.\nKnowing the quantile allows us to say if it's in any (equal-tailed) credible interval.")
+```
+
+##
+
+Given a collection of posterior predictive quantile results $q_1, \ldots, q_n$, what can we do?
+
+**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$.
+
+Hence "tests for discrete uniformity" [@sailynoja2021graphical].
+
+##
+
+Prior to seeing the paper, I was making some plots to check if the quantiles in my models looked uniform:
+
+##
+
+```{r}
+knitr::include_graphics("twitter1.png")
+```
+
+##
+
+```{r}
+knitr::include_graphics("twitter2.png")
+```
+
 ## References {.allowframebreaks}

### 2021-11-30 docs/30-11-21_coverage/coverage.Rmd
Slides up for lab meeting

@@
 
-## Caliration
+## Calibration
 
@@
 I think people often talk about them as if they are interchangeable, which is probably fine.
+The difference is mostly about philosophical interpretation, and I'd guess most people talking about confidence intervals have the credible interval interpretation in mind.
 
@@
 
-It would be good if 90% of the time the actual number was contained within that interval!
+It would be good if 90% of the time the actual number was contained within that interval! Then we can say that our app is **calibrated**.
 
@@
 **Note** this means we also want it to be outside the interval 10% of the time.
-Saying you're 90% sure and being right 100% of the time (under-confidence) is also an error.
+Saying you're 90% sure and being right 100% of the time is also an error.
+
+It helps to have sample size.
+For small sample size then if you're 90% sure then you'd hope you're right.
 
@@
 
+## Decomposition of SPSR
+
 It would be nice is there was some type of decomposition along the lines of
@@
 $$
-but AFAIK that doesn't exist.
+Wikipedia says that:
+
+> The expectation value of a proper scoring rule can be decomposed into the sum of three components, called uncertainty, reliability, and resolution.
 
@@
 
-Given a collection of posterior predictive quantile results $q_1, \ldots, q_n$, what can we do?
+Collection of posterior predictive quantile results $q_1, \ldots, q_n$, then what can we do?
 
-**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$.
+**Main point** if our forecast is calibrated then $q_i \sim \mathcal{U}[0, 1]$ because the truth is a draw from the posterior predictive.
+Sometimes called "Probability Integral Transform".
 
@@
 
-##
+## BP (before paper)
 
 Prior to seeing the paper, I was making some plots to check if the quantiles in my models looked uniform:
+
+1. **PIT-histograms** True value should lie in each decile 10% of the time so that the grey bars are level with the blue dashed line.
+2. **Nominal coverage versus actual coverage** If nominal coverage equals actual coverage then the grey line should be along the green line.
 
@@
 
+## AP (after paper)
+
+* That second plot is alright, but how far can we reasonably expect the empirical coverage to stray from the nominal coverage?
+Especially when we are considerince all the possible confidence levels $\alpha$ simultaneously
+* One answer provided by @sailynoja2021graphical who give "simultaneous confidence bands" which "jointly satisfy a desired coverage"
+* Code is available: github.com/TeemuSailynoja/simultaneous-confidence-bands
+
+##
+
+```{r}
+knitr::include_graphics("twitter_new1.png")
+```
+
+##
+
+```{r}
+knitr::include_graphics("twitter_new2.png")
+```
+
 ## References {.allowframebreaks}

### 2021-12-01 docs/30-11-21_coverage/coverage.Rmd
This is wrong way around as pointed out during presentation

@@
 | --------- | --- | -------------- | ------------------ | --------- |
-| Hai Kon   | 28  | 27             | 96%                | Overconfident |
-| Relan     | 28  | 21             | 75%                | Underconfident |
+| Hai Kon   | 28  | 27             | 96%                | Underconfident |
+| Relan     | 28  | 21             | 75%                | Overconfident |
 

### 2021-12-22 src/plot-tikz_category-flowchart/category-flowchart.tex
The structure for TikZ plot #54

\documentclass[tikz]{standalone}

\usepackage{tikz}

\begin{document}

\begin{tikzpicture}
\node[] at (-1, 1.5) {(i)};nonumber
\node[] at (-0.5, 0) {1};
\node[] at (0.5, 0) {2};
\node[] at (1.5, 0) {3};
\draw (-1,1) -- (2,1);
\draw (-1,-1) -- (2,-1);
\draw (-1,-1) -- (-1,1);
\draw (2,-1) -- (2,1);
\draw (0,-1) -- (0,1);
\draw (1,-1) -- (1,1);

\node[] at (3, 1.5) {(ii)};
\node[] at (4.5, 0) {1};
\node[] at (5.25, 0) {2};
\node[] at (5.75, 0) {3};
\draw (4.5,0) circle (.5);
\draw (4.5,0) circle (1);
\draw (4.5,0) circle (1.5);

\node[] at (-1, -2) {(iii)};
\node[] at (-0.5, -3.5) {1};
\node[] at (0.5, -3.5) {2};
\node[] at (1.5, -3.5) {3};
\draw (-1,-3) -- (2,-2);
\draw (-1,-4) -- (2,-5);
\draw (-1,-4) -- (-1,-3);
\draw (2,-5) -- (2,-2);
\draw (0,-0.8333 - 3.5) -- (0,0.8333 - 3.5);
\draw (1,-1.1666 - 3.5) -- (1,1.1666 - 3.5);

\node[] at (3, 1.5 - 3.5) {(iv)};nonumber
\node[] at (3.25, 0 - 3.5) {1};
\node[] at (4, 0 - 3.5) {2};
\node[] at (5.25, 0 - 3.5) {3};
\draw (3,1 - 3.5) -- (6,1 - 3.5);
\draw (3,-1 - 3.5) -- (6,-1 - 3.5);
\draw (3,-1 - 3.5) -- (3,1 - 3.5);
\draw (6,-1 - 3.5) -- (6,1 - 3.5);
\draw (3.5,-1 - 3.5) -- (3.5,1 - 3.5);
\draw (4.5,-1 - 3.5) -- (4.5,1 - 3.5);

\end{tikzpicture}

\end{document}

### 2021-12-22 src/plot-tikz_category-flowchart/script.R

@@ -1,0 +1,5 @@
+#' Uncomment and run the two line below to resume development of this script
+# orderly::orderly_develop_start("plot-tikz_category-flowchart")
+# setwd("src/plot-tikz_category-flowchart")
+
+system("lualatex category-flowchart.tex")

### 2021-12-31 src/docs_04-01-22-update/04-01-22-update.Rmd
As report is a better way to create slides (e.g. include most recent figures automatically using depends) #50

---
title: A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries
subtitle: HIV Inference Lab Group Meeting
author: Adam Howes
institute: Imperial College London
date: January 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

##

```{r echo=FALSE}
knitr::include_graphics("depends/available-surveys.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/3-rank-comparison.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/model-direct-benefits.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/continental-map.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/variance-proportions.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/within-between-country-variation.pdf")
```

##

```{r echo=FALSE}
knitr::include_graphics("depends/age-variation.pdf")
```

## References {.allowframebreaks}

### 2021-12-31 src/docs_04-01-22-update/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_04-01-22-update")
+# setwd("src/docs_04-01-22-update")
+
+rmarkdown::render("04-01-22-update.Rmd")

### 2021-12-31 src/plot-tikz_category-flowchart/category-flowchart.tex
Basic version of flowchart #54

@@
 \usepackage{tikz}
+\usetikzlibrary{shapes,arrows,positioning}
 
@@
 
-\begin{tikzpicture}
-\node[] at (-1, 1.5) {(i)};nonumber
-\node[] at (-0.5, 0) {1};
-\node[] at (0.5, 0) {2};
-\node[] at (1.5, 0) {3};
-\draw (-1,1) -- (2,1);
-\draw (-1,-1) -- (2,-1);
-\draw (-1,-1) -- (-1,1);
-\draw (2,-1) -- (2,1);
-\draw (0,-1) -- (0,1);
-\draw (1,-1) -- (1,1);
+\tikzstyle{question} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
+\tikzstyle{category} = [rectangle, draw, fill=gray!10, text width=10em, text centered, rounded corners, minimum height=4em]
+\tikzstyle{outerblock} = [rectangle, draw, text width=11em, text centered, rounded corners, minimum height=22em]
+\tikzstyle{line} = [draw, -latex']
 
-\node[] at (3, 1.5) {(ii)};
-\node[] at (4.5, 0) {1};
-\node[] at (5.25, 0) {2};
-\node[] at (5.75, 0) {3};
-\draw (4.5,0) circle (.5);
-\draw (4.5,0) circle (1);
-\draw (4.5,0) circle (1.5);
+\begin{tikzpicture}[node distance = 2cm, auto]
+    \node[category] at (0, 0) (1) {Not sexually active};
+    \node[category] at (0, -2) (2) {One cohabiting sexual partner};
+    \node[category] at (0, -4) (3) {Non-regular sexual partner(s)};
+    \node[category] at (0, -6) (4) {Key populations};
+    % \node[outerblock] at (0, -3) {};
 
-\node[] at (-1, -2) {(iii)};
-\node[] at (-0.5, -3.5) {1};
-\node[] at (0.5, -3.5) {2};
-\node[] at (1.5, -3.5) {3};
-\draw (-1,-3) -- (2,-2);
-\draw (-1,-4) -- (2,-5);
-\draw (-1,-4) -- (-1,-3);
-\draw (2,-5) -- (2,-2);
-\draw (0,-0.8333 - 3.5) -- (0,0.8333 - 3.5);
-\draw (1,-1.1666 - 3.5) -- (1,1.1666 - 3.5);
+    \node[question] at (-10, 0) (a) {Is the respondent sexually active in the past 12 months?};
+    \node[question] at (-10, -2) (b) {Number of partners of the respondent of the past 12 months?};
+    \node[question] at (-5, -2) (c) {Does that partner live in the same household as the respondent?};
+    \node[question] at (-10, -4) (d) {Has the respondent had transactional sex?};
 
-\node[] at (3, 1.5 - 3.5) {(iv)};nonumber
-\node[] at (3.25, 0 - 3.5) {1};
-\node[] at (4, 0 - 3.5) {2};
-\node[] at (5.25, 0 - 3.5) {3};
-\draw (3,1 - 3.5) -- (6,1 - 3.5);
-\draw (3,-1 - 3.5) -- (6,-1 - 3.5);
-\draw (3,-1 - 3.5) -- (3,1 - 3.5);
-\draw (6,-1 - 3.5) -- (6,1 - 3.5);
-\draw (3.5,-1 - 3.5) -- (3.5,1 - 3.5);
-\draw (4.5,-1 - 3.5) -- (4.5,1 - 3.5);
-
+    \path[line] (a) -- node {No}(1);
+    \path[line] (a) -- node {Yes}(b);
+    \path[line] (b) -- node {$1$}(c);
+    \path[line] (b) -- node {$>1$}(d);
+    \path[line] (c) -- node {Yes}(2);
+    \path[line] (c) |- node[near end] {No}(3);
+    \path[line] (d) |- node[near end] {Yes}(4);
+    \path[line] (d) -- (3);
 \end{tikzpicture}

### 2021-12-31 src/plot-tikz_category-flowchart/script.R

@@ -2,4 +2,4 @@
 # orderly::orderly_develop_start("plot-tikz_category-flowchart")
 # setwd("src/plot-tikz_category-flowchart")
 
-system("lualatex category-flowchart.tex")
+tools::texi2dvi("category-flowchart.tex", pdf = TRUE, clean = TRUE)

### 2022-01-03 src/docs_04-01-22-update/04-01-22-update.Rmd
Update slides for tomorrow #50

@@
 
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{lXlX}
+\toprule
+Category & Description & Risk ratio & Notes \\ 
+ \midrule
+None & Not sexually active & 0 & Ignores incidence from e.g. drug injection (assumed to be negligible). \\
+Low & One cohabiting sexual partner & 1 & Baseline category. \\
+High & Non-regular sexual partner(s) & 1.72 & From ALPHA network pooled analysis. Supported by Jia et al. \\
+Very high & Young women from key populations & 13 & Sabin et al. \\
+\bottomrule
+\end{tabularx}
+\caption{HIV risk categories and risk ratios.}
+\label{tab:risk-categories}
+\end{table}
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/category-flowchart.pdf")
+```
+
+##
+
 ```{r echo=FALSE}
@@
 ```
+
+##
+
+Final model selected:
+
+\begin{align}
+    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
+    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \theta_{iat}.
+\end{align}
+
+## Benefits of smoothing
+
+1. Get estimates even where there isn't direct data
+
+* Some people think of this as "making up data"
+* In some sense all estimates are "made up" though
+* Uncertainty should be higher in regions with infilling
+* Perhaps we do a bad job communicating uncertainty, or it's just hard
+
+## Benefits of smoothing
+
+2. Borrow information across space, surveys, categories
+
+* Space-category effects, survey-category effects, space-survey-category effects (using Kronecker products)
+* Fun to think about what models might be reasonable for this and whether structured category effects might be interesting
+  * e.g. some model for misclassification of individuals into categories could give a kind of structured category effect (currently it's IID always)
+* Wonder to what extent we're oversmoothing
+  * e.g. might expect to see discontunities in the data (e.g. urban centers) which we're smoothing away
 
@@
 ```
-
-## References {.allowframebreaks}

### 2022-01-03 src/docs_24-09-21-new-cohort/script.R
Port presentation for kick-off camp over to an orderly report

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_24-09-21-new-cohort")
+# setwd("src/docs_24-09-21-new-cohort")
+
+rmarkdown::render("24-09-21-new-cohort.Rmd")

### 2022-01-04 src/docs_04-01-22-update/04-01-22-update.Rmd
Finish off presentation for lab group #50

@@
 
+## Statistical model
+
+Fit 13 models of the form:
+
+\begin{align}
+    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
+    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \delta_{itk} + \theta_{ita}.
+\end{align}
+
+##
+
+\begin{table}[htb]
+\centering
+\begin{tabularx}{\textwidth}{llll}
+\midrule
+Model ID & Spatial structure & Temporal structure & Spatio-temporal interaction \\ 
+\midrule
+1 & None & None & \xmark \\
+2 & IID & None & \xmark \\
+3 & Besag & None & \xmark \\
+4 & None & IID & \xmark \\
+5 & IID & IID & \xmark \\
+5x & IID & IID & \cmark \\
+6 & Besag & IID & \xmark \\
+6x & Besag & IID  & \cmark \\
+7 & None & AR1 & \xmark \\
+8 & IID & AR1 & \xmark \\
+8x & IID & AR1 & \cmark \\
+9 & Besag & AR1 & \xmark \\
+9x & Besag & AR1 & \cmark \\
+\midrule
+\end{tabularx}
+\end{table}
+
 ##
@@
 
-Final model selected:
-
-\begin{align}
-    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
-    \log(\lambda_{itak}) &= \beta_k + \alpha_{ak} + \phi_{ik} + \gamma_{tk} + \theta_{iat}.
-\end{align}
+```{r echo=FALSE}
+knitr::include_graphics("depends/model-direct-benefits.pdf")
+```
 
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/model-direct-benefits.pdf")
+knitr::include_graphics("depends/continental-map.pdf")
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/continental-map.pdf")
+knitr::include_graphics("depends/within-between-country-variation.pdf")
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/within-between-country-variation.pdf")
+knitr::include_graphics("depends/age-variation.pdf")
 ```
 
-##
+## Next steps
 
-```{r echo=FALSE}
-knitr::include_graphics("depends/age-variation.pdf")
-```
+* Feedback on paper from people who know more about country contexts
+* Connect more to policy. For example by replicating Katie's "number of new infections by risk group" spreadsheet
+* Add logistic regression model for proportion of non-regular partner(s) who are KP

### 2022-01-04 docs/09-09-21_three-category/three-category.Rmd
Swaziland is now Eswatini everywhere (I hope) #56

@@
   * District $i = 1, \ldots, n$
-    * 13 AGYW Global Fund priority countries (but fitting individually): Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Swaziland, Tanzania, Uganda, Zambia and Zimbabwe
+    * 13 AGYW Global Fund priority countries (but fitting individually): Botswana, Cameroon, Eswatini, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Tanzania, Uganda, Zambia and Zimbabwe
   * Survey $t = 1, \ldots, T$

### 2022-01-04 src/check_surveys-stat-compiler/script.R

@@ -7,9 +7,7 @@
 stat_compiler <- read_xlsx("STATcompilerExport2021127_12313.xlsx", range = "A4:E110") %>%
   rename(country = Country,
          survey =  Survey) %>%
-  select(country, survey) %>%
-  mutate(country = ifelse(country == "Eswatini", "Swaziland", country))
-
+  select(country, survey)
 
 #' iso3 codes from https://gist.github.com/tadast/8827699
 country_codes <- read_csv("countries_codes_and_coordinates.csv") %>%

### 2022-01-04 src/plot_available-surveys/script.R

@@ -46,7 +46,7 @@ df <- df %>%
       "Mozambique" = "MOZ",
       "Malawi" = "MWI",
       "Namibia" = "NAM",
-      "Swaziland" = "SWZ",
+      "Eswatini" = "SWZ",
       "Tanzania" = "TZA",
       "Uganda" = "UGA",
       "South Africa" = "ZAF",

### 2022-01-04 src/plot_continental-map/script.R

@@ -35,7 +35,7 @@ df <- df %>%
                  "Mozambique" = "MOZ",
                  "Malawi" = "MWI",
                  "Namibia" = "NAM",
-                 "Swaziland" = "SWZ",
+                 "Eswatini" = "SWZ",
                  "Tanzania" = "TZA",
                  "Uganda" = "UGA",
                  "South Africa" = "ZAF",

### 2022-01-04 src/plot_within-between-country-variation/script.R

@@ -34,7 +34,7 @@ df <- df %>%
         "Mozambique" = "MOZ",
         "Malawi" = "MWI",
         "Namibia" = "NAM",
-        "Swaziland" = "SWZ",
+        "Eswatini" = "SWZ",
         "Tanzania" = "TZA",
         "Uganda" = "UGA",
         "South Africa" = "ZAF",
@@ -87,7 +87,7 @@ region_key <- c(
   "Mozambique" = "South",
   "Malawi" = "South",
   "Namibia" = "South",
-  "Swaziland" = "South",
+  "Eswatini" = "South",
   "Tanzania" = "East",
   "Uganda" = "East",
   "South Africa" = "South",

### 2022-01-04 src/process_information-criteria/functions.R

@@ -18,7 +18,7 @@ update_naming <- function(df) {
         "Mozambique" = "MOZ",
         "Malawi" = "MWI",
         "Namibia" = "NAM",
-        "Swaziland" = "SWZ",
+        "Eswatini" = "SWZ",
         "Tanzania" = "TZA",
         "Uganda" = "UGA",
         "South Africa" = "ZAF",

### 2022-01-06 src/docs_09-09-21-three-category/script.R
Port three-category and coverage presentations over to being orderly reports too

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_09-09-21-three-category")
+# setwd("src/docs_09-09-21-three-category")
+
+rmarkdown::render("09-09-21-three-category.Rmd")

### 2022-01-06 src/docs_30-11-21-coverage/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_30-11-21-coverage")
+# setwd("src/docs_30-11-21-coverage")
+
+rmarkdown::render("30-11-21-coverage.Rmd")

### 2022-01-19 src/docs_19-01-22-seth-sam/19-01-22-seth-sam.Rmd
Presentation for Seth / Sam's lab group

--- 2022-01-04 src/docs_04-01-22-update/04-01-22-update.Rmd
@@
 title: A multinomial spatio-temporal model for sexual risk behaviour with application to adolescent girls and young women in 13 sub-Saharan African countries
-subtitle: HIV Inference Lab Group Meeting
+subtitle: Statistics and Epidemiology Group Meeting
 author: Adam Howes
@@
 
-* Feedback on paper from people who know more about country contexts
-* Connect more to policy. For example by replicating Katie's "number of new infections by risk group" spreadsheet
-* Add logistic regression model for proportion of non-regular partner(s) who are KP
+* Have sent to Elona in Cape Town to get feedback
+* Connecting more to policy, recently produced "new infections by risk group"
+* Adding logistic regression model for proportion of non-regular partner(s) who are KP

### 2022-01-19 src/docs_19-01-22-seth-sam/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_19-01-22-seth-sam")
+# setwd("src/docs_19-01-22-seth-sam")
+
+rmarkdown::render("19-01-22-seth-sam.Rmd")

### 2022-01-27 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Start of talk for EA society next Thursday

---
title: How it's been doing a statistics PhD plus some research
subtitle: EA Imperial
author: Adam Howes
institute: Imperial College London
date: February 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

## Academic background

* Maths undergraduate at Durham, no real ideas about career
  * Worked in a pub first year, Cranfield second year, and Basque Center for Applied Mathematics third year
  * Dissertation about Bayesian optimisation 
* Not enough statistics courses at Durham, so did a masters at Warwick
  * Dissertation about Bayesian models for combining sources of evidence
* StatML CDT (Imperial / Oxford) started the year I was applying
  * Somewhat successor to OxWaSP (Oxford / Warwick)

## EA background

* Heard about 80,000 Hours in 3rd year from a friend
* Listened to a few podcasts, found them compelling, first time anything career related really resonated with me
* Read a few books over summer, then started going to the EA society at Warwick
  * Events like retreats, more people in the community, helped to add depth
* First EAG I went to was the year I started at Imperial
  * Volunteering can be a good way to get a place

## Any tips about applying for PhDs

* Find (and call if possible) any previous students of the supervisor
  * What are they doing now?
* Assess the vibe among current graduate students
* Be interested in things, read papers, attend reading groups
  * "List of things you don't need permission to do"
* Doing research as an undergraduate is a good test

## Reflections on PhD experience

* Many (all?) of my friends doing PhDs have had periods where it has negatively effected them
  * "The well-being costs of graduate school versus STIs"
* Little structure, often sporadic feedback, uncertainty about research direction and progress, making a narrow contribution (that perhaps few people care about) to a large field
* Different to undergraduate: not learning material then passing test for another 3/4 years

## What's my PhD about

* HIV/AIDS is an infectious disease which is endemic in sub-Saharan Africa
* Epidemic indicators can be used to guide policy response
* My area of research is Bayesian spatio-temporal statistics, the method we use to perform small-area estimation
  * I'll explain what these terms mean

## Bayesian statistics

## Spatio-temporal statistics

## Career plans going forward

### 2022-01-27 src/docs_03-02-22-ea-talk/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_03-02-22-ea-talk")
+# setwd("src/docs_03-02-22-ea-talk")
+
+rmarkdown::render("03-02-22-ea-talk.Rmd")

### 2022-01-29 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Progressing EA talk more

@@
 * My area of research is Bayesian spatio-temporal statistics, the method we use to perform small-area estimation
-  * I'll explain what these terms mean
+  * (I'll explain what these terms mean)
 
@@
 
+* First step in Bayesian statistics is to write a probabilistic model for the data
+  * Focus is on understanding and modelling scientific phenomenon, rather than e.g. remembering arcane statistical tests
+* Second step is to perform inference (which is usually done with an algorithm)
+  * Given we observed certain data, what can we learn about the parameters of the model?
+* Things might go wrong with the above two steps with the data, probabilistic model, algorithm
+  * Should also perform checks, following a "Bayesian workflow"
+
 ## Spatio-temporal statistics
 
+* Say that you have a collection of people who have taken a HIV test, and their results are either positive or negative
+* If have the location for these people, this might be important information to include in our probabilistic model
+* Similarly, the time that they took the test might also be important
+* Spatio-temporal statistics is just when we think these two features of the data are important to take into account
+* It allows us to answer spatio-temporal questions
+  * What's the situation at time $t$ and location $s$?
+  * Often important for policy
+
+## My work
+
+* I'm interested in applied and methodological work
+  * Applied: focus is on answering a question about the world
+  * Methodological: focus is on developing techniques which can be used to answer questions about the world
+* The deliniation between these might not be clear sometimes
+  * To answer questions about the world you'll often have to develop new methods
+  * To develop new (relevant) methods that you should be thinking about which questions they will allow you to answer to think
+* Some examples of my work
+  * Applied: estimating numbers of young women at risk
+  * Methodological: investigating models for spatial smoothing
+
+## Applied example
+
+* Women 15-29 are disproportionately at risk of HIV
+* To efficiently target programs and resources to the most at risk women, we're working on small-area estimates of the number of women in different risk groups
+
+##
+
+\begin{table}
+\centering
+\begin{tabularx}{\textwidth}{lXlX}
+\toprule
+Category & Description & Risk ratio \\ 
+ \midrule
+None & Not sexually active & 0 \\
+Low & One cohabiting sexual partner & 1 \\
+High & Non-regular sexual partner(s) & 1.72  \\
+Very high & Young women from key populations & 13 \\
+\bottomrule
+\end{tabularx}
+\caption{HIV risk categories and risk ratios.}
+\label{tab:risk-categories}
+\end{table}
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/category-flowchart.pdf")
+```
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/available-surveys.pdf")
+```
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/aids-abstract-A.pdf")
+```
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/aids-abstract-B.pdf")
+```
+
+## Methods example
+
+* TO-DO: Create annotated equations version of the Besag model
+
 ## Career plans going forward
+
+* Global health
+* Biosecurity
+  * Reading group this term, Fridays at St Mary's 12-1!
+
+## Thanks!

### 2022-01-30 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Progressing presentation some more based on comments

@@
 
+## Is it worth doing a PhD?
+
+* Skills or talent gap for many causes in EA
+  * Rather than funding gap
+* Independent research skills developed during a PhD important for many causes
+  * AI, biorisk, global priorities, global health and development
+* Can be useful for signalling expertise
+  * Then transfer into e.g. policy
+* 3/4+ years, possibly large opportunity cost
+
 ## Any tips about applying for PhDs
@@
 
-## Reflections on PhD experience
+## Some negative reflections on PhD experience
 
-* Many (all?) of my friends doing PhDs have had periods where it has negatively effected them
-  * "The well-being costs of graduate school versus STIs"
-* Little structure, often sporadic feedback, uncertainty about research direction and progress, making a narrow contribution (that perhaps few people care about) to a large field
+* I, along with many (all?) of my friends doing PhDs, have had periods where it has negatively effected wellbeing
+  * "Grad school is worse for public health than STDs" https://www.benkuhn.net/grad/
+* Little structure, often sporadic feedback, uncertainty about research direction and progress, narrow contribution (that perhaps few people care about) to a large field, low pay, alignment with supervisor and program, (in some fields) somewhat pyramid scheme-y
 * Different to undergraduate: not learning material then passing test for another 3/4 years
@@
 * Epidemic indicators can be used to guide policy response
+  * Prevalence (how many people are infected)
+  * Incidence (how many people newly infected)
+  * Coverage of treatments (how many people have (don't have) treatment)
 * My area of research is Bayesian spatio-temporal statistics, the method we use to perform small-area estimation
@@
 
+## How impactful is this work
+
+* Could be used to guide HIV interventions for women 15-29
+  * Interventions suggested include STI-screening and treatment, economic empowerment, comprehensive sexuality education, PrEP, PEP
+* Neglectedness, tractability, scale?
+* TO-DO: Add the latest versions of infections averted graph
+
 ## Methods example
@@
 
-## Career plans going forward
+## Some possible routes for the future
 
-* Global health
-* Biosecurity
-  * Reading group this term, Fridays at St Mary's 12-1!
+* Small-area estimation of health and development indicators
+* Outbreak disease surveillance
+* Monitoring of the environment (e.g. sea-ice for climate, air-pollution for global health)
+* Statistical ecology (as it relates to animal welfare)
+* AI safety (likely the more applied FAT-style work than theoretical)
+* Predicting (or helping to win) elections
+* Meta EA
+
+## Current plan
+
+* Outbreak disease surveillance for reducing GCBRs
+* Longtermist issues likely score better on neglectedness and scope
+* Biorisk cause area "competitive" with AI risk
+  * Better personal fit to biorisk
+* Biosecurity reading group this term, Fridays at St Mary's 12-1!
 

### 2022-02-01 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
Finish draft of these slides

@@
   * Applied: estimating numbers of young women at risk
-  * Methodological: investigating models for spatial smoothing
+  * Methodological: investigating models for spatial structure
 
-## Applied example
+## Estimating numbers of young women at risk
 
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/category-flowchart.pdf")
-```
-
-##
-
-```{r echo=FALSE}
 knitr::include_graphics("depends/available-surveys.pdf")
@@
 
-## How impactful is this work
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("depends/model-direct-benefits-h.pdf")
+```
+
+## The Besag model
+
+$$
+\phi_i \, | \, \bphi_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} \phi_j}{n_{\delta i}}, \frac{1}{n_{\delta i}\tau_\phi}\right)
+$$
+
+Mean of $\phi_i$ average of adjacent units and precision is proportional to $n_{\delta i}$
+
+##
+
+```{r echo=FALSE}
+knitr::include_graphics("geometry-graph-zwe.pdf")
+```
+
+## Impact of this work
 
 * Could be used to guide HIV interventions for women 15-29
-  * Interventions suggested include STI-screening and treatment, economic empowerment, comprehensive sexuality education, PrEP, PEP
-* Neglectedness, tractability, scale?
-* TO-DO: Add the latest versions of infections averted graph
+* Interventions suggested include 
+  * STI-screening and treatment
+  * Economic empowerment,
+  * Comprehensive sexuality education
+  * PrEP
+  * PEP
 
-## Methods example
+##
 
-* TO-DO: Create annotated equations version of the Besag model
+```{r echo=FALSE}
+knitr::include_graphics("depends/infections-averted-country.pdf")
+```
 

### 2022-02-25 src/docs_amazon-poster/amazon-poster.Rmd
Template for poster (still can't install posterdown, probably because of Rcpp) #77

---
title: A Better Reproducible Poster Title
author:
  - name: Brent Thorne
    affil: 1
    twitter: brentthorne18
    email: brentthorne18@gmail.com
    orcid: 0000-0002-1099-3857
    main: true
affiliation:
  - num: 1
    address: Department of Earth Sceicnes, Brock University
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**."
  - '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main_pic}'
logoleft_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png){.main-img-left}'
logoright_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main-img-right}'
output: 
  posterdown::posterdown_betterland:
    self_contained: false
    pandoc_args: --mathjax
    highlight: haddock
    number_sections: false
link-citations: true
bibliography: citations.bib
---

```{r, include=FALSE}
knitr::opts_chunk$set(results = 'asis',
                      echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

```{r myplot, include=FALSE}
svg('myplot.svg')
plot(iris$Sepal.Length, iris$Sepal.Width)
dev.off()
```

# Introduction

This is the `posterdown_betterland` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

<br>

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=FALSE,collapse=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=3.5, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:8,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# References

### 2022-02-25 src/docs_amazon-poster/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_amazon-poster")
+# setwd("src/docs_amazon-poster")
+
+rmarkdown::render("amazon-poster.Rmd")

### 2022-02-28 src/docs_09-09-21-three-category/09-09-21-three-category.Rmd
Port three-category and coverage presentations over to being orderly reports too
Replace "multinomial-smoothed-district-sexbehav" with "multi-sexbehav-sae"

--- 2022-01-04 docs/09-09-21_three-category/three-category.Rmd
@@
 ```{r echo=FALSE}
-knitr::include_graphics("page-multinomial-smoothed-district-sexbehav.pdf")
+knitr::include_graphics("page-multi-sexbehav-sae.pdf")
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("../../archive/check_sexpaid-survey-question/20210720-120340-77026581/sexpaid-survey-question.pdf")
+knitr::include_graphics("depends/sexpaid-survey-question.pdf")
 ```

### 2022-02-28 make/_make.R

@@ -8,10 +8,10 @@ src("make/pull_oli_population.R")
 src("make/run_data_prep.R")
 
 #' 4. Run the four category models for applicable countries
-src("make/run_aaa_fit_4-multi-sexbehav-sae.R")
+src("make/run_aaa_fit_4-multinomial-smoothed-district-sexbehav.R")
 
 #' 5. Run the three category models for all countries
-src("make/run_aaa_fit_3-multi-sexbehav-sae.R")
+src("make/run_aaa_fit_3-multinomial-smoothed-district-sexbehav.R")
 
 #' TODO: Run the three category models for all countries jointly
 # src("make/run_fit_3-multisexbehav-sae.R")

### 2022-02-28 make/post_process.R

@@ -1,6 +1,6 @@
 source("make/utils.R")
 
-run_commit_push("process_multi-sexbehav-sae")
+run_commit_push("process_multinomial-smoothed-district-sexbehav")
 run_commit_push("process_information-criteria")
 run_commit_push("process_variance-proportions")
 run_commit_push("process_coverage")

### 2022-02-28 make/run_aaa_fit_3-multi-sexbehav-sae.R

@@ -1,8 +1,10 @@
-#' Run aaa_fit_3-multi-sexbehav-sae in bulk
+#' Run aaa_fit_3-multinomial-smoothed-district-sexbehav in bulk
 #' For all 13 countries
 
-report <- "aaa_fit_3-multi-sexbehav-sae"
+report <- "aaa_fit_3-multinomial-smoothed-district-sexbehav"
 iso3 <- c("BWA", "CMR", "KEN", "LSO", "MOZ", "MWI", "NAM", "SWZ", "TZA", "UGA", "ZAF", "ZMB", "ZWE")
+#' TZA failed
+iso3 <- c("TZA")
 
 # #' With all data and interactions
 # params <- data.frame(iso3 = iso3, include_interactions = TRUE, include_phia = TRUE)

### 2022-02-28 make/run_aaa_fit_4-multi-sexbehav-sae.R

@@ -1,6 +1,6 @@
-#' Run aaa_fit_4-multi-sexbehav-sae in bulk
+#' Run aaa_fit_4-multinomial-smoothed-district-sexbehav in bulk
 
-report <- "aaa_fit_4-multi-sexbehav-sae"
+report <- "aaa_fit_4-multinomial-smoothed-district-sexbehav"
 
 #' Only those countries which have any surveys with a dedicated sex paid question
 recent <- orderly::orderly_latest(name = "plot_available-surveys")

### 2022-02-28 src/aaa_fit_multi-sexbehav-sae/script.R

@@ -432,7 +432,7 @@ res_df <- res_df %>%
   mutate(iso3 = iso3, .before = indicator) %>%
   relocate(model, .before = estimate_smoothed)
 
-write_csv(res_df, "multinomial-smoothed-district-sexbehav.csv", na = "")
+write_csv(res_df, "multi-sexbehav-sae.csv", na = "")
 
 #' Create plotting data
 res_plot <- res_df %>%
@@ -450,7 +450,7 @@ res_plot <- res_df %>%
 
 #' Artefact: Cloropleths
 
-pdf("multinomial-smoothed-district-sexbehav.pdf", h = 8.25, w = 11.75)
+pdf("multi-sexbehav-sae.pdf", h = 8.25, w = 11.75)
 
 res_plot %>%
   split(~indicator + model) %>%

### 2022-02-28 src/check_national-fsw-comparison/script.R

@@ -102,7 +102,7 @@ cowplot::plot_grid(plotA, plotB, ncol = 1)
 dev.off()
 
 #' The proportion estimates from the sexpaid12m category of our model
-est <- read_csv("depends/human-best-3p1-multinomial-smoothed-district-sexbehav.csv") %>%
+est <- read_csv("depends/human-best-3p1-multi-sexbehav-sae.csv") %>%
   filter(
     indicator == "YWKP",
     age_group %in% c("15-19", "20-24", "25-29", "15-24")

### 2022-02-28 src/fit_multi-sexbehav-sae/script.R

@@ -313,4 +313,4 @@ res_df <- res_df %>%
   mutate(iso3 = iso3, .before = indicator) %>%
   relocate(model, .before = estimate_smoothed)
 
-write_csv(res_df, "multinomial-smoothed-district-sexbehav.csv", na = "")
+write_csv(res_df, "multi-sexbehav-sae.csv", na = "")

### 2022-02-28 src/plot_age-variation/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("plot_age-variation")
 # setwd("src/plot_age-variation")
 
-df <- read_csv("depends/human-best-3-multinomial-smoothed-district-sexbehav.csv") %>%
+df <- read_csv("depends/human-best-3-multi-sexbehav-sae.csv") %>%
   filter(age_group != "15-24")
 
 df_age_country <- df %>%

### 2022-02-28 src/plot_aids-abstract/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("plot_aids-abstract")
 # setwd("src/plot_plot_aids-abstract")
 
-df <- read_csv("depends/human-best-3-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/human-best-3-multi-sexbehav-sae.csv")
 
 #' The following section is copied mostly from plot_within-between-country-variation
 

### 2022-02-28 src/plot_continental-map/script.R

@@ -2,8 +2,8 @@
 # orderly::orderly_develop_start("plot_continental-map")
 # setwd("src/plot_continental-map")
 
-df_3 <- read_csv("depends/human-best-3-multinomial-smoothed-district-sexbehav.csv")
-df_3p1 <- read_csv("depends/human-best-3p1-multinomial-smoothed-district-sexbehav.csv")
+df_3 <- read_csv("depends/human-best-3-multi-sexbehav-sae.csv")
+df_3p1 <- read_csv("depends/human-best-3p1-multi-sexbehav-sae.csv")
 areas <- readRDS("depends/areas.rds")
 national_areas <- readRDS("depends/national_areas.rds")
 

### 2022-02-28 src/plot_model-direct-benefits/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("plot_model-direct-benefits")
 # setwd("src/plot_model-direct-benefits")
 
-df <- read_csv("depends/tza_multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/tza_multi-sexbehav-sae.csv")
 areas <- read_sf(paste0("depends/tza_areas.geojson"))
 
 df <- df %>%

### 2022-02-28 src/plot_temporal-variation/script.R

@@ -2,8 +2,8 @@
 # orderly::orderly_develop_start("plot_temporal-variation")
 # setwd("src/plot_temporal-variation")
 
-df_3 <- read_csv("depends/human-best-3-multinomial-smoothed-district-sexbehav.csv")
-df_3p1 <- read_csv("depends/human-best-3p1-multinomial-smoothed-district-sexbehav.csv")
+df_3 <- read_csv("depends/human-best-3-multi-sexbehav-sae.csv")
+df_3p1 <- read_csv("depends/human-best-3p1-multi-sexbehav-sae.csv")
 
 pdf("3-temporal-interpolation.pdf", h = 4, w = 6.25)
 

### 2022-02-28 src/plot_within-between-country-variation/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("plot_within-between-country-variation")
 # setwd("src/plot_within-between-country-variation")
 
-df <- read_csv("depends/human-best-3p1-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/human-best-3p1-multi-sexbehav-sae.csv")
 
 df <- df %>%
   filter(age_group != "15-24") %>%

### 2022-02-28 src/process_coverage/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("process_coverage")
 # setwd("src/process_coverage")
 
-df <- read_csv("depends/best-3-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/best-3-multi-sexbehav-sae.csv")
 
 df <- df %>%
   filter(

### 2022-02-28 src/process_differentiate-high-risk/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("process_differentiate-high-risk")
 # setwd("src/process_differentiate-high-risk")
 
-df <- read_csv("depends/best-3-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/best-3-multi-sexbehav-sae.csv")
 
 #' Just the most recent surveys (this isn't a good solution)
 prop <- read_csv("depends/best-fsw-logit-smoothed-district-sexbehav.csv") %>%
@@ -42,5 +42,5 @@ df <- bind_rows(
   df_sexpaid12m
 )
 
-write_csv(df, "best-3p1-multinomial-smoothed-district-sexbehav.csv", na = "")
-write_csv(multi.utils::update_naming(df), "human-best-3p1-multinomial-smoothed-district-sexbehav.csv", na = "")
+write_csv(df, "best-3p1-multi-sexbehav-sae.csv", na = "")
+write_csv(multi.utils::update_naming(df), "human-best-3p1-multi-sexbehav-sae.csv", na = "")

### 2022-02-28 src/process_incidence/script.R

@@ -4,7 +4,7 @@
 
 analysis_level <- multi.utils::analysis_level()
 
-df <- read_csv("depends/best-3p1-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/best-3p1-multi-sexbehav-sae.csv")
 areas <- readRDS("depends/areas.rds")
 
 #' Confusing file names here, but I believe they are all the same thing

### 2022-02-28 src/process_johnston-adjustment/script.R

@@ -2,7 +2,7 @@
 # orderly::orderly_develop_start("process_johnston-adjustment")
 # setwd("src/process_johnston-adjustment")
 
-df <- read_csv("depends/best-3p1-multinomial-smoothed-district-sexbehav.csv")
+df <- read_csv("depends/best-3p1-multi-sexbehav-sae.csv")
 johnston <- read_csv("depends/johnston-fsw-comparison.csv")
 
 #' Some NAs in here: sad reacts
@@ -47,4 +47,4 @@ df <- df %>%
     values_to = "estimate_smoothed"
   )
 
-write_csv(df, "adjust-best-3p1-multinomial-smoothed-district-sexbehav.csv")
+write_csv(df, "adjust-best-3p1-multi-sexbehav-sae.csv")

### 2022-02-28 src/process_subset-maps/script.R

@@ -5,10 +5,10 @@
 #' Want to create .pdf files containing only the results from particular models
 #' (Probably the final model chosen)
 iso3 <- multi.utils::priority_iso3()
-pdfs <- paste0("depends/", tolower(iso3), "_all-dhs-multinomial-smoothed-district-sexbehav.pdf")
+pdfs <- paste0("depends/", tolower(iso3), "_all-dhs-multi-sexbehav-sae.pdf")
 
 if (!dir.exists("tmp")) dir.create("tmp")
-pdfs_output <- paste0("tmp/", tolower(iso3), "_all-dhs-multinomial-smoothed-district-sexbehav.pdf")
+pdfs_output <- paste0("tmp/", tolower(iso3), "_all-dhs-multi-sexbehav-sae.pdf")
 
 #' Get the page numbers of all maps corresponding the chosen model
 pages <- map(pdfs,
@@ -24,7 +24,7 @@ pmap(
 )
 
 #' Combine them into one output artefact
-pdftools::pdf_combine(input = pdfs_output, output = paste0("all-dhs-multinomial-smoothed-district-sexbehav.pdf"))
+pdftools::pdf_combine(input = pdfs_output, output = paste0("all-dhs-multi-sexbehav-sae.pdf"))
 
 #' Delete the temporary directory
 unlink("tmp", recursive = TRUE)

### 2022-03-12 src/docs_amazon-poster/amazon-poster.Rmd
Start working on poster #77

@@
 ---
-title: A Better Reproducible Poster Title
+main_topsize: 0.2
+main_bottomsize: 0.1
+poster_height: "48in"
+poster_width: "36in"
+font_family: "Open Sans"
+#ESSENTIALS
+title: Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
 author:
-  - name: Brent Thorne
+  - name: '**Adam Howes**'
     affil: 1
-    twitter: brentthorne18
-    email: brentthorne18@gmail.com
-    orcid: 0000-0002-1099-3857
     main: true
+    twitter: adamhowes
+    email: ath19@ic.ac.uk
 affiliation:
   - num: 1
-    address: Department of Earth Sceicnes, Brock University
+    address: Department of Mathematics, Imperial College London
 main_findings:
-  - "Make **better posters** with RMarkdown + **posterdown**."
-  - '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main_pic}'
-logoleft_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png){.main-img-left}'
-logoright_name: '![](https://raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png){.main-img-right}'
+  - "**Large efficiency gains** possible by targeting HIV programming using **risk behaviour**."
+# Style & formatting
+title_textsize: "60pt"
+author_textsize: "1.17em"
+authorextra_textsize: "35px"
+affiliation_textsize: "25px"
+affiliation_textcol: '#00000080'
+caption_fontsize: "20pt"
+# Main
+main_fontfamily: "Open Sans"
+# Poster body options
+primary_colour: '#38761C'
+secondary_colour: '#3b77D8'
+accent_colour: "#5d19c4"
+body_bgcol: "#ffffff"
+body_textsize: "45px"
+body_textcol: "#000000"
+reference_textsize: "23px"
+# Standard options
 output: 
-  posterdown::posterdown_betterland:
+  posterdown::posterdown_betterport:
     self_contained: false
     pandoc_args: --mathjax
-    highlight: haddock
-    number_sections: false
-link-citations: true
-bibliography: citations.bib
+    highlight: espresso
+    number_sections: true
 ---
-
-```{r, include=FALSE}
-knitr::opts_chunk$set(results = 'asis',
-                      echo = FALSE,
-                      warning = FALSE,
-                      tidy = FALSE,
-                      message = FALSE,
-                      fig.align = 'center',
-                      out.width = "100%")
-options(knitr.table.format = "html") 
-```
-
-```{r myplot, include=FALSE}
-svg('myplot.svg')
-plot(iris$Sepal.Length, iris$Sepal.Width)
-dev.off()
-```
 
@@
 
-This is the `posterdown_betterland` template for the {posterdown} package!
-I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown].
-If you're not an R user don't sweat as you do **NOT** need to use it at all!
-Feel free to use only the Markdown functionality of this package :)
-
-```{r, include=FALSE}
-knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
-```
-
-## Objectives
-
-1. Pick a template layout.
-2. Write/ create your poster content distraction free.
-3. Let posterdown do its thing!
+* Adolescent girls and young women (15-29) face higher risk of HIV, and have been identified as a priority population for prevention efforts
+* The UNAIDS Global AIDS Strategy recommends differentiating services based on local HIV incidence and individual risk behaviours
 
@@
 
-I will show here how to include poster elements that may be useful, such as an equation using mathjax:
-
-$$
-E = mc^2
-$$
-
-To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file.
-For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].
-
-To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).
-
-**_Now on to the results!_**
-
-<br>
-
-# Results
-
-Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).
-
-```{r, irisfigure, fig.cap='Here is a caption for the figure.
-This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
-par(mar=c(2,2,0,1))
-plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
-     col = iris$Species, pch = 19, xlab = "Sepal Length",
-     ylab = "Sepal Width")
-```
-
-Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too!
-Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!
-
-```{r myprettycode, echo=FALSE,collapse=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=3.5, out.width="80%"}
-#trim whitespace
-par(mar=c(2,2,0,0))
-#plot boxplots
-boxplot(iris$Sepal.Width~iris$Species,
-        col = "#008080", 
-        border = "#0b4545",
-        ylab = "Sepal Width (cm)",
-        xlab = "Species")
-```
-
-How about a neat table of data? See, Table \@ref(tab:iristable):
-
-```{r, iristable}
-knitr::kable(
-  iris[1:8,1:5], format = "html",
-  caption = "A table made with the **knitr::kable** function.",
-  align = "c", col.names = c("Sepal <br> Length",
-                             "Sepal <br> Width",
-                             "Petal <br> Length",
-                             "Petal <br> Width",
-                             "Species"),
-  escape = FALSE)
-```
-
-# References
+1. Fit multinomial model to $k = 1, 2, 3^{+}$
+2. Fit logistic regression model $k = 3, 4$
+3. Differentiate $k = 3^{+}$ into $k = 3$ and $k = 4$
+4. Adjust national-level FSW estimates

### 2022-03-13 src/docs_amazon-poster/amazon-poster.Rmd
Poster progress including models, logos, consulting Pinar on headline #77

@@
 main_topsize: 0.2
-main_bottomsize: 0.1
+main_bottomsize: 0.05
 poster_height: "48in"
@@
     email: ath19@ic.ac.uk
+  - name: "Kathryn A. Risher"
+    affil: 3
+  - name: "Van Kinh Nguyen"
+    affil: 3
+  - name: "Oliver Stevens"
+    affil: 3
+  - name: "Katherine M. Jia"
+    affil: 4
+  - name: "Tim M. Wolock"
+    affil: 1
+  - name: "Lycias Zembe"
+    affil: 5
+  - name: "Ian Wanyeki"
+    affil: 5
+  - name: "Mary Mahy"
+    affil: 5
+  - name: "Clemens Benedikt"
+    affil: 5
+  - name: "Seth R. Flaxman"
+    affil: 6
+  - name: "Jeffrey W. Eaton"
+    affil: 2
 affiliation:
@@
     address: Department of Mathematics, Imperial College London
+  - num: 2
+    address: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London
+  - num: 3
+    address: Department of Medical Social Sciences, Feinberg School of Medicine, Northwestern University
+  - num: 4
+    address: Harvard T. H. Chan School of Public Health, Harvard University
+  - num: 5
+    address: Joint United Nations Programme on HIV/AIDS, Geneva, Switzerland
+  - num: 6
+    address: Department of Computer Science, University of Oxford
 main_findings:
-  - "**Large efficiency gains** possible by targeting HIV programming using **risk behaviour**."
+  - "Targeting HIV programming based on risk behaviour would **greatly increase** resource allocation efficiency."
+logoleft_name: "IMP_ML_W_N.png"
+logoright_name: "UNAIDS-reverse-EN.gif"
 # Style & formatting
-title_textsize: "60pt"
+title_textsize: "60px"
 author_textsize: "1.17em"
@@
 affiliation_textcol: '#00000080'
-caption_fontsize: "20pt"
+caption_fontsize: "20px"
 # Main
@@
 body_bgcol: "#ffffff"
-body_textsize: "45px"
+body_textsize: "40px"
 body_textcol: "#000000"
-reference_textsize: "23px"
+reference_textsize: "20px"
 # Standard options
@@
     highlight: espresso
-    number_sections: true
+    number_sections: false
 ---
@@
 
-* Adolescent girls and young women (15-29) face higher risk of HIV, and have been identified as a priority population for prevention efforts
-* The UNAIDS Global AIDS Strategy recommends differentiating services based on local HIV incidence and individual risk behaviours
+* Adolescent girls and young women (AGYW) 15-29 continue to **face higher risk** of HIV, and have been identified as a **priority population** for prevention efforts
+* The UNAIDS Global AIDS Strategy **recommends differentiating services** for AGYW geographically based on individual risk behaviours
+* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** in 13 priority countries at a district level in the years 1999-2020
 
@@
 
-1. Fit multinomial model to $k = 1, 2, 3^{+}$
-2. Fit logistic regression model $k = 3, 4$
-3. Differentiate $k = 3^{+}$ into $k = 3$ and $k = 4$
-4. Adjust national-level FSW estimates
+* We used 48 household surveys (including AIS, BAIS, DHS and PHIA) but only 13 included a specific question about paid sex
+* For the categories $k \in \{1, 2, 3^{+}\}$ we specified a multinomial logistic regression via the multinomial-Poisson transformation
+\begin{align}
+    &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
+    &\log(\kappa_{itak}) = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk},
+\end{align}
+where $p_{itak} = \text{softmax}(\kappa_{ita})_k$.
+
+* To differentiate $3^{+}$ we used a logistic regression
+\begin{align}
+    &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
+    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4})) = \beta_0 + \alpha_a + \zeta_c + \phi_i + \beta_\texttt{cfswever}.  
+\end{align}

### 2022-03-14 src/docs_amazon-poster/amazon-poster.Rmd
Add figure and discussion to poster #77

@@
 main_topsize: 0.2
-main_bottomsize: 0.05
+main_bottomsize: 0.1
 poster_height: "48in"
@@
 main_findings:
-  - "Targeting HIV programming based on risk behaviour would **greatly increase** resource allocation efficiency."
+  - "Successful **targeting** of HIV programming using **risk behaviour** would **greatly increase** resource allocation efficiency."
 logoleft_name: "IMP_ML_W_N.png"
@@
 # Style & formatting
+column_numbers: 3
 title_textsize: "60px"
@@
 
-* Adolescent girls and young women (AGYW) 15-29 continue to **face higher risk** of HIV, and have been identified as a **priority population** for prevention efforts
-* The UNAIDS Global AIDS Strategy **recommends differentiating services** for AGYW geographically based on individual risk behaviours
-* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** in 13 priority countries at a district level in the years 1999-2020
+* Adolescent girls and young women (AGYW) 15-29 continue to **face higher risk** of HIV, and have been identified as a **priority population** for prevention
+* The UNAIDS Global AIDS Strategy **recommends differentiating services** for AGYW geographically based on individual risk behaviour
+* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** $k = 1:4$ in 13 priority countries at a district level in the years 1999-2020
+
+|$k$|Category               | Risk ratio|
+|:--|:----------------------|----------:|
+|  1|Not sexually active    |          0|
+|  2|One cohabiting partner |          1|
+|  3|Non-regular partner(s) |       1.72|
+|  4|Female sex workers     |         13|
 
@@
 
-* We used 48 household surveys (including AIS, BAIS, DHS and PHIA) but only 13 included a specific question about paid sex
-* For the categories $k \in \{1, 2, 3^{+}\}$ we specified a multinomial logistic regression via the multinomial-Poisson transformation
+* We used 48 household surveys (AIS, BAIS, DHS, PHIA)
+* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fits a multinomial logistic regression via the multinomial-Poisson transformation
 \begin{align}
@@
 
-* To differentiate $3^{+}$ we used a logistic regression
+* To differentiate $3^{+}$ we used only the 13 surveys with a specific paid sex question to fit a logistic regression
 \begin{align}
@@
 \end{align}
+
+# Results
+
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}
+knitr::include_graphics("depends/infections-averted.png")
+```
+
+# Discussion
+
+* Our model uses a **modular approach** to integrate all relevant data and **spatio-temporal smoothing** to overcome small-area sample sizes
+* Individual behaviour is a key determinant of HIV risk and providing prevention services according to behavior would allow many more new infections to be reached, especially among female sex workers
+
+## Limitations
+
+* No assessment **practical difficulties and costs** of strategies
+* No adjustment for **reporting bias**
+* **Risk category definitions** could be disputed
+
+## Future work
+
+* Inclusion of **more surveys** e.g. VACS
+* Extension to **general population** of adults 15-49

### 2022-03-14 make/docs.R

@@ -1,0 +1,3 @@
+source("make/utils.R")
+
+run_commit_push("docs_amazon-poster")

### 2022-03-14 src/docs_amazon-poster/script.R

@@ -2,3 +2,4 @@
 # setwd("src/docs_amazon-poster")
 
 rmarkdown::render("amazon-poster.Rmd")
+pagedown::chrome_print("amazon-poster.html")

### 2022-03-14 src/plot_infections-averted/script.R

@@ -53,7 +53,7 @@ inc_age_behav <- compute_infections_averted(df_age_behav, stratification_name = 
 inc_area <- compute_infections_averted(df_area, stratification_name = "Area")
 inc_age <- compute_infections_averted(df_age, stratification_name = "Age")
 inc_behav <- compute_infections_averted(df_behav, stratification_name = "Behaviour")
-inc_none <- compute_infections_averted(df_none, stratification_name = "Baseline (no targeting)")
+inc_none <- compute_infections_averted(df_none, stratification_name = "Baseline")
 
 inc <- bind_rows(
   inc_area_age_behav,
@@ -68,7 +68,7 @@ inc <- bind_rows(
 
 #' Add "improvement over no targetting" column
 infections_averted_per_population_baseline <- inc %>%
-  filter(stratification == "Baseline (no targeting)") %>%
+  filter(stratification == "Baseline") %>%
   #' Just the end of the line
   filter(population_cumulative == max(population_cumulative)) %>%
   mutate(infections_averted_per_population_baseline = infections_averted_cumulative / population_cumulative) %>%
@@ -84,35 +84,44 @@ inc <- inc %>%
     prop_population_cumulative = population_cumulative / max(population_cumulative, na.rm = TRUE),
     stratification = factor(
       stratification,
-      levels = c("Area, age, behaviour", "Area, age", "Area, behaviour", "Age, behaviour", "Area", "Age", "Behaviour", "Baseline (no targeting)")
+      levels = c("Area, age, behaviour", "Area, age", "Area, behaviour", "Age, behaviour", "Area", "Age", "Behaviour", "Baseline")
     )
   )
 
 pdf("infections-averted.pdf", h = 3, w = 6.25)
 
-ggplot(inc, aes(x = prop_population_cumulative, y = prop_infections_averted_cumulative_improvement, col = stratification)) +
-  geom_line(alpha = 0.8, size = 0.7) +
+plotA <- ggplot(inc, aes(x = prop_population_cumulative, y = prop_infections_averted_cumulative_improvement, col = stratification)) +
+  geom_line(alpha = 0.8, size = 1) +
   scale_color_manual(values = multi.utils::cbpalette()) +
   scale_x_continuous(labels = scales::percent) +
   scale_y_continuous(labels = scales::label_percent(accuracy = 1L)) +
   labs(
-    x = "Percentage of at risk population reached",
[…]

### 2022-03-14 src/docs_amazon-poster/amazon-poster.Rmd
Underbraces, citations #77

@@
 body_textcol: "#000000"
-reference_textsize: "20px"
+reference_textsize: "25px"
 # Standard options
+bibliography: citations.bib
 output: 
@@
 |$k$|Category                 | Risk ratio|
-|:--|:----------------------|----------:|
+|:--|:------------------------|----------:|
 |  1|Not sexually active      |          0|
@@
 |  3|Non-regular partner(s)   |       1.72|
-|  4|Female sex workers     |         13|
+|  4|Female sex workers (FSW) |         13|
 
@@
 * We used 48 household surveys (AIS, BAIS, DHS, PHIA)
-* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fits a multinomial logistic regression via the multinomial-Poisson transformation
+* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
 \begin{align}
     &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
-    &\log(\kappa_{itak}) = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk},
+    &\log(\kappa_{itak}) 
+    = \underbrace{\theta_{ita}}_{\text{Observation (IID)}}
+    + \underbrace{\beta_k}_{\text{Category (IID)}}
+    + \underbrace{\alpha_{ak}}_{\text{Age (IID)}} \\
+    &+ \underbrace{\zeta_{ck}}_{\text{Country (IID)}} 
+    + \underbrace{\phi_{ik}}_{\text{Spatial (Besag)}} 
+    + \underbrace{\gamma_{tk}}_{\text{Temporal (AR1)}}
 \end{align}
-where $p_{itak} = \text{softmax}(\kappa_{ita})_k$.
-
-* To differentiate $3^{+}$ we used only the 13 surveys with a specific paid sex question to fit a logistic regression
+where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
+* To differentiate $3^{+}$ we used the 13 surveys with a paid sex question to fit a survey-weighted logistic regression
 \begin{align}
     &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
-    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4})) = \beta_0 + \alpha_a + \zeta_c + \phi_i + \beta_\texttt{cfswever}.  
+    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4}))
+    = \beta_0
+    + \beta_\texttt{cfswever} x_c \\
+    &+ \underbrace{\alpha_a}_{\text{Age (IID)}}
+    + \underbrace{\zeta_c}_{\text{Country (IID)}}
+    + \underbrace{\phi_i}_{\text{Spatial (Besag)}}
 \end{align}
+where $x_c$ is the proportion of men in each country who are clients of FSW [@hodgins2021cfsw]
+* We align our estimates for FSW to the UNAIDS Key Populations Atlas at the national-level [@johnston2022deriving]
 
@@
 * Our model uses a **modular approach** to integrate all relevant data and **spatio-temporal smoothing** to overcome small-area sample sizes
-* Individual behaviour is a key determinant of HIV risk and providing prevention services according to behavior would allow many more new infections to be reached, especially among female sex workers
+* Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more new infections to be reached, **especially among FSW**
 
@@
 
-* No assessment **practical difficulties and costs** of strategies
+* No assessment **practicalities or costs** of strategies
 * No adjustment for **reporting bias**
@@
 * Extension to **general population** of adults 15-49
+
+# References
+
+<div id="refs" class="references"></div>

### 2022-03-15 src/docs_amazon-poster/amazon-poster.Rmd
Small changes to poster after meeting #77

@@
 main_topsize: 0.2
-main_bottomsize: 0.1
+main_bottomsize: 0.075
 poster_height: "48in"
@@
 main_findings:
-  - "Successful **targeting** of HIV programming using **risk behaviour** would **greatly increase** resource allocation efficiency."
+  - "Successfully **targeting** HIV programming using **risk behaviour** would **greatly increase** new infections reached."
 logoleft_name: "IMP_ML_W_N.png"
@@
 |:--|:------------------------|----------:|
-|  1|Not sexually active      |          0|
-|  2|One cohabiting partner   |          1|
-|  3|Non-regular partner(s)   |       1.72|
-|  4|Female sex workers (FSW) |         13|
+|1  |Not sexually active      |          0|
+|2  |One cohabiting partner   |          1|
+|3  |Non-regular partner(s)   |       1.72|
+|4  |Female sex workers (FSW) |         13|
 
@@
 * We align our estimates for FSW to the UNAIDS Key Populations Atlas at the national-level [@johnston2022deriving]
+* Inference performed with integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
 
@@
 
-* Our model uses a **modular approach** to integrate all relevant data and **spatio-temporal smoothing** to overcome small-area sample sizes
+* Using a **modular approach** allowed integration of all relevant data
+* **Spatio-temporal smoothing** overcame high variance from small sample sizes
 * Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more new infections to be reached, **especially among FSW**
+* Geographic delineation: cohabiting more common in the east and non-regular partner(s) more common in the south
+* Large numbers of 15-19 in Mozambique already cohabiting
 
@@
 
-* No assessment **practicalities or costs** of strategies
 * No adjustment for **reporting bias**
 * **Risk category definitions** could be disputed
+* No assessment **practicalities or costs** of strategies
 

### 2022-03-16 src/plot-tikz_category-flowchart/category-flowchart.tex
Fix the category flowchart logic

@@
 \tikzstyle{question} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
-\tikzstyle{category} = [rectangle, draw, fill=gray!10, text width=10em, text centered, rounded corners, minimum height=4em]
+\tikzstyle{category} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
 \tikzstyle{outerblock} = [rectangle, draw, text width=11em, text centered, rounded corners, minimum height=22em]
@@
 \begin{tikzpicture}[node distance = 2cm, auto]
-    \node[category] at (0, 0) (1) {Not sexually active};
-    \node[category] at (0, -2) (2) {One cohabiting sexual partner};
-    \node[category] at (0, -4) (3) {Non-regular sexual partner(s)};
-    \node[category] at (0, -6) (4) {Key populations};
+    \node[category] at (0, 0) (1) {$k = 1$:\\Not sexually active};
+    \node[category] at (0, -2) (2) {$k = 4$:\\Female sex worker};
+    \node[category] at (0, -4) (3) {$k = 2$:\\One cohabiting sexual partner};
+    \node[category] at (0, -6) (4) {$k = 3$:\\Non-regular sexual partner(s)};
     % \node[outerblock] at (0, -3) {};
@@
     \node[question] at (-10, 0) (a) {Is the respondent sexually active in the past 12 months?};
-    \node[question] at (-10, -2) (b) {Number of partners of the respondent of the past 12 months?};
-    \node[question] at (-5, -2) (c) {Does that partner live in the same household as the respondent?};
-    \node[question] at (-10, -4) (d) {Has the respondent had transactional sex?};
+    \node[question] at (-10, -2) (b) {Has the respondent been given gifts or money for sex?};
+    \node[question] at (-5, -4) (c) {Does that partner live in the same household as the respondent?};
+    \node[question] at (-10, -4) (d) {Number of partners of the respondent of the past 12 months?};
 
@@
     \path[line] (a) -- node {Yes}(b);
-    \path[line] (b) -- node {$1$}(c);
-    \path[line] (b) -- node {$>1$}(d);
-    \path[line] (c) -- node {Yes}(2);
-    \path[line] (c) |- node[near end] {No}(3);
-    \path[line] (d) |- node[near end] {Yes}(4);
-    \path[line] (d) -- (3);
+    \path[line] (b) -- node {Yes}(2);
+    \path[line] (b) -- node {No}(d);
+    \path[line] (c) -- node {Yes}(3);
+    \path[line] (d) -- node {$1$}(c);
+    \path[line] (d) |- node[near start] {$>1$}(4);
+    \path[line] (c) |- node[near start] {No}(4);
 \end{tikzpicture}

### 2022-03-17 src/docs_amazon-poster/amazon-poster.Rmd
Renamed dependency

@@
 ```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}
-knitr::include_graphics("depends/infections-averted.png")
+knitr::include_graphics("depends/infections-reached.png")
 ```

### 2022-03-17 src/docs_amazon-poster/amazon-poster.Rmd
Test AIDS abstract in poster. I think a 2 row version of dotplot and cloropleth would work well here #77

@@
 main_findings:
-  - "Successfully **targeting** HIV programming using **risk behaviour** would **greatly increase** new infections reached."
+  - "Successfully **targeting** HIV programs using **risk behaviour** would **greatly increase** new infections reached."
 logoleft_name: "IMP_ML_W_N.png"
@@
 
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Results for two of the risk categories'}
+knitr::include_graphics("depends/aids-abstract.png")
+```
+
 ```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}

### 2022-03-23 src/docs_amazon-poster/amazon-poster.Rmd
Close #96

--- 2022-03-17 src/docs_amazon-poster/amazon-poster.Rmd
@@
 font_family: "Open Sans"
-#ESSENTIALS
+# Essentials
 title: Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
@@
 
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Dotplots showing the posterior mean of our district level estimates (in colour) and national estimates (in white) in 2018.'}
+knitr::include_graphics("depends/3p1-within-between-country-variation.png")
+```
+
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Cloropleths showing the posterior mean of our district level estimates in 2018.'}
+knitr::include_graphics("depends/3p1-continental-map.png")
+```
+
 ```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}

### 2022-03-23 src/plot_continental-map/script.R

@@ -19,13 +19,13 @@ df_3p1 <- read_csv("depends/adjust-best-3p1-multi-sexbehav-sae.csv") %>%
 areas <- readRDS("depends/areas.rds")
 national_areas <- readRDS("depends/national_areas.rds")
 
-pdf("3-aaa-continental-map.pdf", h = 8, w = 6.25)
+pdf("3-aaa-continental-map.pdf", h = 7, w = 6.25)
 
 continental_map(df_3_aaa, areas, national_areas)
 
 dev.off()
 
-pdf("3p1-aaa-continental-map.pdf", h = 8, w = 6.75)
+pdf("3p1-aaa-continental-map.pdf", h = 7, w = 6.25)
 
 df_3p1_aaa %>%
   mutate(iso3 = substr(survey_id, 1, 3)) %>%
@@ -33,17 +33,25 @@ df_3p1_aaa %>%
 
 dev.off()
 
-pdf("3-continental-map.pdf", h = 8, w = 6.75)
+pdf("3-continental-map.pdf", h = 7, w = 6.25)
 
 df_3 %>%
   continental_map(areas, national_areas)
 
 dev.off()
 
-pdf("3p1-continental-map.pdf", h = 8, w = 6.75)
+pdf("3p1-continental-map.pdf", h = 7, w = 6.25)
 
-df_3p1 %>%
+plotA <- df_3p1 %>%
   mutate(iso3 = substr(survey_id, 1, 3)) %>%
   continental_map(areas, national_areas)
 
+plotA
+
 dev.off()
+
+ggsave(
+  "3p1-continental-map.png",
+  plotA,
+  width = 6.25, height = 7, units = "in", dpi = 300
+)

### 2022-03-23 src/plot_within-between-country-variation/script.R

@@ -20,7 +20,7 @@ df_3p1_national <- temp_3p1$df_national
 
 pdf("3p1-within-between-country-variation.pdf", h = 7, w = 6.25)
 
-df_3p1_subnational %>%
+plotA <- df_3p1_subnational %>%
   mutate(iso3 = reorder(iso3, iso3_sort_order)) %>%
   ggplot(aes(x = fct_rev(iso3), y = estimate_smoothed, col = region)) +
     geom_jitter(width = 0.1, alpha = 0.6, shape = 20) +
@@ -41,7 +41,16 @@ df_3p1_subnational %>%
       legend.text = element_text(size = 9),
     )
 
+plotA
+
 dev.off()
+
+#' Save version for poster
+ggsave(
+  "3p1-within-between-country-variation.png",
+  plotA,
+  width = 6.25, height = 7, units = "in", dpi = 300
+)
 
 #' Have a closer look at the FSW estimates and check that the Johnston adjustment has worked
 df_3p1_unadjusted <- read_csv("depends/best-3p1-multi-sexbehav-sae.csv")

### 2022-03-24 src/docs_amazon-poster/amazon-poster.Rmd
Full draft of Amazon poster #77

@@
 main_findings:
-  - "Successfully **targeting** HIV programming using **risk behaviour** would **greatly increase** new infections reached."
+  - "Successful **targeting of HIV programming** using **risk behaviour** would **greatly increase** new infections reached."
 logoleft_name: "IMP_ML_W_N.png"
@@
 reference_textsize: "25px"
+sectitle_textsize: "40px"
 # Standard options
@@
 
-# Introduction
+<!-- Using LaTeX to create spacing -->
+$$\\[0.2in]$$
 
-* Adolescent girls and young women (AGYW) 15-29 continue to **face higher risk** of HIV, and have been identified as a **priority population** for prevention
-* The UNAIDS Global AIDS Strategy **recommends differentiating services** for AGYW geographically based on individual risk behaviour
-* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** $k = 1:4$ in 13 priority countries at a district level in the years 1999-2020
+## Introduction
+
+* Adolescent girls and young women (AGYW) 15-29 continue to **face disproportionately high risk** of HIV, and have been identified as a **priority population** for prevention efforts
+* The UNAIDS Global AIDS Strategy 2021-2026 **recommends differentiating services** for AGYW geographically based both on individual risk behaviour and epidemic indicators
+* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** $k = 1:4$ in 13 priority countries at a district level in the years 1999-2018
 
@@
 
-# Methods
+$$\\[0.2in]$$
+
+## Methods
 
@@
 where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
-* To differentiate $3^{+}$ we used the 13 surveys with a paid sex question to fit a survey-weighted logistic regression
+* To differentiate $3^{+}$ we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
 \begin{align}
@@
 where $x_c$ is the proportion of men in each country who are clients of FSW [@hodgins2021cfsw]
-* We align our estimates for FSW to the UNAIDS Key Populations Atlas at the national-level [@johnston2022deriving]
-* Inference performed with integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
+* We aligned our FSW estimates to the national-level UNAIDS Key Populations Atlas [@johnston2022deriving]
+* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
+* We estimated incidence and number of new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates
 
-# Results
+$$\\[0.2in]$$
+
+## Results
 
@@
 
+* There is **significant variation** in risk group proportions **within and between countries**, as well as **between age groups** (but close to no change over time)
+* We found a geographic delineation, with **cohabiting more common in the east** and **non-regular partner(s) more common in the south**
+* Large numbers of 15-19 in Mozambique have early sexual debut and are already cohabiting
+
 ```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}
@@
 
-# Discussion
+* Using area, age and behavioural risk stratification **25% of new infections can be found by reaching 3% of the population**, as compared with 8% of the population when behaviour is excluded
 
-* Using a **modular approach** allowed integration of all relevant data
-* **Spatio-temporal smoothing** overcame high variance from small sample sizes
+$$\\[0.2in]$$
+
+## Discussion
+
+* Using a **modular approach** allowed us to integrate all data from non-conformable surveys
+* **Spatio-temporal smoothing** can be used to overcome high variance from the small sample sizes that result when further stratifying districts
 * Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more new infections to be reached, **especially among FSW**
-* Geographic delineation: cohabiting more common in the east and non-regular partner(s) more common in the south
-* Large numbers of 15-19 in Mozambique already cohabiting
 
-## Limitations
+### Limitations
 
@@
 * **Risk category definitions** could be disputed
-* No assessment **practicalities or costs** of strategies
+* No assessment of **practicalities or costs** of risk stratification approaches, or efficacy of available interventions
 
-## Future work
+### Future work
 
@@
 
-# References
+$$\\[0.2in]$$
+
+## References
 

### 2022-03-24 src/docs_amazon-poster/amazon-poster.Rmd
Update # of surveys

@@
 
-* We used 48 household surveys (AIS, BAIS, DHS, PHIA)
+* We used 47 household surveys (AIS, BAIS, DHS, PHIA)
 * For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation

### 2022-03-28 src/docs_amazon-poster/amazon-poster.Rmd
Update poster based on Jeff's suggestions

@@
 # Essentials
-title: Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
+title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
 author:
   - name: '**Adam Howes**'
-    affil: 1
+    affil: 1, 2
     main: true
@@
   - name: "Kathryn A. Risher"
-    affil: 3
+    affil: 2, 3
   - name: "Van Kinh Nguyen"
-    affil: 3
+    affil: 2
   - name: "Oliver Stevens"
-    affil: 3
+    affil: 2
   - name: "Katherine M. Jia"
@@
   - name: "Tim M. Wolock"
-    affil: 1
+    affil: 1, 2
   - name: "Lycias Zembe"
@@
 main_findings:
-  - "Successful **targeting of HIV programming** using **risk behaviour** would **greatly increase** new infections reached."
+  - "Successful **targeting of HIV prevention** using **risk behaviour** would **greatly increase** expected new infections preemptively reached."
 logoleft_name: "IMP_ML_W_N.png"
-logoright_name: "UNAIDS-reverse-EN.gif"
+# logoright_name: "UNAIDS-reverse-EN.gif"
 # Style & formatting
@@
 <!-- Using LaTeX to create spacing -->
-$$\\[0.2in]$$
+$$\\[0.15in]$$
 
@@
 
-* Adolescent girls and young women (AGYW) 15-29 continue to **face disproportionately high risk** of HIV, and have been identified as a **priority population** for prevention efforts
+* Adolescent girls and young women (AGYW) 15-29 **face disproportionately high risk** of HIV infection, and have been identified as a **priority population** for prevention efforts
 * The UNAIDS Global AIDS Strategy 2021-2026 **recommends differentiating services** for AGYW geographically based both on individual risk behaviour and epidemic indicators
@@
 
-$$\\[0.2in]$$
+<!-- Using LaTeX to create spacing -->
+$$\\[0.05in]$$
 
@@
 
-* We used 47 household surveys (AIS, BAIS, DHS, PHIA)
-* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
+* We analyzed 47 national household surveys (AIS, BAIS, DHS, PHIA)
+* For the categories $k \in \{1, 2, 3^{+}\}$ we fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
 \begin{align}
-    &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
+    &y_{itak}^\star \sim \text{Poisson}(\kappa_{itak}), \\
     &\log(\kappa_{itak}) 
@@
 where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
-* To differentiate $3^{+}$ we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
+* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
+* To estimate the FSW proportion we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
 \begin{align}
-    &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
+    &y_{ia4}^\star \sim \text{Binomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
     &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4}))
@@
 * We aligned our FSW estimates to the national-level UNAIDS Key Populations Atlas [@johnston2022deriving]
-* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
-* We estimated incidence and number of new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates
-
-$$\\[0.2in]$$
+* We estimated incidence and number of expected new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates
 
@@
 
-* Using area, age and behavioural risk stratification **25% of new infections can be found by reaching 3% of the population**, as compared with 8% of the population when behaviour is excluded
-
-$$\\[0.2in]$$
+* Using location, age and behavioral risk stratification, **25% of expected new infections can be found by reaching 3% of the population**, compared with 8% of the population when behaviour is excluded
+* Majority of this benefit comes from reaching FSW, who are **3.5% of the at risk population but 21.0% of all expected new infections**
 
@@
 * **Spatio-temporal smoothing** can be used to overcome high variance from the small sample sizes that result when further stratifying districts
-* Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more new infections to be reached, **especially among FSW**
+* Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more expected new infections to be reached, **especially among FSW**
 
@@
 
+* No assessment of **practicalities or costs** of risk stratification approaches, or efficacy of available interventions
 * No adjustment for **reporting bias**
 * **Risk category definitions** could be disputed
-* No assessment of **practicalities or costs** of risk stratification approaches, or efficacy of available interventions
+  * What constitutes sex work?
+  * Is within-group risk heterogeneity small enough?
 
@@
 * Inclusion of **more surveys** e.g. VACS
-* Extension to **general population** of adults 15-49
+* Extension to **general population**: men and women 15-49
 
-$$\\[0.2in]$$
+<font size="6"> **Funding** AH was supported by the EPSRC and Bill & Melinda Gates Foundation. This research was supported by the MRC Centre for Global Infectious Disease Analysis. </font>
 

### 2022-04-14 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
Good part of the way there with slides for #112

---
title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
subtitle: MRC Centre for Global Infectious Disease Analysis Seminars
author: Adam Howes
institute: Imperial College London
date: May 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

## Background

* In sub-Saharan Africa, adolescent girls and young women (AGYW) are XX.X\% of the population but XX.X\% of all new HIV infections
* Reasons for this disparity include:
  1. Younger age at first sex
  2. Age patterns of sexual mixing
  3. Structural vulnerabilities and power imbalances
  4. Increased susceptibility to HIV infection

## Stratified prevention

* To have the greatest impact with available prevention resources, interventions should be prioritised to those at highest risk
* The Global AIDS Strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
  1. Population-level HIV incidence in the local population
  2. Individual-level sexual risk behaviour

## Scope for our work

### Goals

1. Enable countries to implement prevention approaches stratified by incidence and behaviour
2. Assess the extent to which this would be beneficial

### Approach

1. Estimate the proportion of AGYW in four sexual risk behaviour groups at a district level (in 13 countries identified as priority by The Global Fund)
2. Analyze the number of new infections reached by stratified prevention strategies

## Data

* We used sexual behaviour data from household surveys (see next slide)
* District-level HIV incidence estimates from the Naomi model [@eaton2021naomi]
* District boundaries

##

```{r echo=FALSE, out.width = "400px"}
knitr::include_graphics("depends/available-surveys.png")
```

## Two-stage model for risk group proportions

### Stage 1.

* Multinomial logistic regression model for the proportion of AGYW in the None, Low and {High, Very High} risk groups, using all 47 surveys
* Selected model included:
  * Age effects (IID)
  * Country effects (IID)
  * Correlated spatial effects (ICAR)
  * Correlated temporal effects (AR1) 
* Multinomial-Poisson transformation allowed use of `R-INLA` for inference

## Two-stage model for risk group proportions

### Stage 2.

* Logistic regression model for the proportion of {High, Very High} who are in the Very High risk group, using only the 13 surveys with a specific transactional sex question
* Selected model included:
  * Age effects (IID)
  * Country effects (IID)
  * Correlated spatial effects (ICAR)
  * Clients of FSW covariates
* Used `R-INLA` for inference

## Two-stage model for risk group proportions

### Combination and FSW adjustment

* Take 1000 samples from each model, then suitably multiply to generate estimates for all four risk groups
* We adjusted the Very High risk group to match national FSW estimates from @johnston2022deriving

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
$\implies$ estimates of risk group proportions $\rho_{itak}$ by district, year and age group
\end{tcolorbox}
\end{center}

<!-- ## -->

<!-- ```{r echo=FALSE, out.width = "400px"} -->
<!-- knitr::include_graphics("depends/3p1-continental-map.png") -->
<!-- ``` -->

##

```{r echo=FALSE, out.width = "400px"}
knitr::include_graphics("depends/3p1-within-between-country-variation.png")
```

## Benefits of our modelled risk group estimates

1. Estimates even where there isn't direct data
    * Although some people think of this as "making up data", the data almost never "speak for themselves"
    * Uncertainty should be higher in regions with infilling: important to clearly communicate this
2. Borrow information across space, between countries, over multiple surveys, (weakly) between risk groups
    * See next slide for illustration of why this is important

##

```{r echo=FALSE, out.width = "400px"}
knitr::include_graphics("depends/model-direct-benefits.png")
```

## HIV incidence by risk group

* We used our risk group proportion estimates and relative risk ratio estimates from the literature to disaggregate Naomi general population HIV incidence estimates
\begin{align*}
I_{ia} &= \sum_k \lambda_{iak} N_{iak} \\
&= \sum_k \lambda_{ia2} \text{RR}_k N_{iak}.
\end{align*}

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
$\implies$ estimates of HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ by district, age group and risk group
\end{tcolorbox}
\end{center}

## Prioritisation with risk group information

* Suppose we have all of the information (district, age, and risk group)
* Which are the strata with highest incidence?

```{r include=FALSE}
df <- readr::read_csv("depends/incidence-district-sexbehav.csv")

df_area_age_behav <- df %>%
  select(iso3, area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>%
  pivot_longer(
    cols = starts_with("population") | starts_with("incidence"),
    names_to = c("indicator", "category"),
    names_sep = "_"
  ) %>%
  pivot_wider(
    id_cols = c("iso3", "area_id", "age_group", "indicator", "category"),
    names_from = "indicator",
    values_from = "value"
  )
```

```{r echo=FALSE}
df_area_age_behav %>%
  arrange(desc(incidence)) %>%
  head() %>%
  knitr::kable()
```

## Prioritisation without risk group information

* What about if we lost the risk group information? Now what are the strata with the highest incidence?

```{r include=FALSE}
df_area_age <- df_area_age_behav %>%
  group_by(iso3, area_id, age_group) %>%
  summarise(
    incidence = sum(incidence * population, na.rm = TRUE) / sum(population, na.rm = TRUE),
    population = sum(population, na.rm = TRUE)
  ) %>%
  ungroup()
```

```{r echo=FALSE}
df_area_age %>%
  select(iso3, area_id, age_group, population, incidence) %>%
  arrange(desc(incidence)) %>%
  head() %>%
  knitr::kable()
```

##

```{r echo=FALSE, out.width = "400px"}
knitr::include_graphics("depends/infections-reached.png")
```

## Policy takeaways

* ?

## Limitations

* Infections reached analysis simplistic, doesn't account for e.g. difficulty in reaching each strata, variable intervention effectiveness, change in strata membership
* High risk sexual behaviours are under-reported, and likely varyingly so by age (foremost) and location (less so)
* Risk group definitions didn't consider other important characteristics that may determine risk e.g. condom usage
* Our analysis only focused on AGYW 15-29, and could be extended to adults of both sexes aged 15-49

## Methods takeaways

* `R-INLA` and the multinomial-Poisson trick are a relatively good choice for spatio-temporal multinomial models
  * Make good use of the `group` and `replicate` feature to define sufficiently complex Kronecker product effects
  * Can run into limitations on model complexity: I might be moving to something more flexible e.g. `tmb`, `aghq` to continue development of this project

## Thanks for listening!

* \faEnvelope $\,$ `ath19@ic.ac.uk`
* \faHome $\,$ `athowes.github.io`

## Bibliography {-}

### 2022-04-14 src/docs_12-05-22-mrc-gida/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_12-05-22-mrc-gida")
+# setwd("src/docs_12-05-22-mrc-gida")
+
+rmarkdown::render("12-05-22-mrc-gida.Rmd")

### 2022-04-14 src/docs_aids22-poster/aids22-poster.Rmd
Basic version of #111

--- 2022-03-28 src/docs_amazon-poster/amazon-poster.Rmd
@@
 logoleft_name: "IMP_ML_W_N.png"
-# logoright_name: "UNAIDS-reverse-EN.gif"
+logoright_name: "UNAIDS-reverse-EN.gif"
 # Style & formatting

### 2022-04-14 src/docs_aids22-poster/script.R

@@ -1,0 +1,5 @@
+# orderly::orderly_develop_start("docs_aids22-poster")
+# setwd("src/docs_aids22-poster")
+
+rmarkdown::render("aids22-poster.Rmd")
+pagedown::chrome_print("aids22-poster.html")

### 2022-04-19 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
Minimal viable version of these slides #112

@@
 
-1. Enable countries to implement prevention approaches stratified by incidence and behaviour
-2. Assess the extent to which this would be beneficial
+1. Enable implementation of prevention strategies stratified by incidence and behaviour
+2. Assess the benefits of such approaches
 
@@
 1. Estimate the proportion of AGYW in four sexual risk behaviour groups at a district level (in 13 countries identified as priority by The Global Fund)
-2. Analyze the number of new infections reached by stratified prevention strategies
+2. Analyze numbers of new infections reached by stratified prevention strategies
 
@@
 
-* We used sexual behaviour data from household surveys (see next slide)
-* District-level HIV incidence estimates from the Naomi model [@eaton2021naomi]
-* District boundaries
+* Sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys (see next slide)
+* Later, we used district-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
 
@@
 
-### Stage 1.
+### Stage 1: $k = 1, 2, 3^{+}$
 
-* Multinomial logistic regression model for the proportion of AGYW in the None, Low and {High, Very High} risk groups, using all 47 surveys
+* Multinomial logistic regression model for the proportion of AGYW in the none, low and {high, very high} risk groups, using all 47 surveys
 * Selected model included:
@@
   * Correlated temporal effects (AR1) 
-* Multinomial-Poisson transformation allowed use of `R-INLA` for inference
+* Multinomial-Poisson transformation allowed us to use `R-INLA` for inference
 
@@
 
-### Stage 2.
+### Stage 2: $k = 3, 4$
 
-* Logistic regression model for the proportion of {High, Very High} who are in the Very High risk group, using only the 13 surveys with a specific transactional sex question
+* Logistic regression model for the proportion of those in the {high, very high} risk groups who are in the very high risk group, using only the 13 surveys with a specific transactional sex question
 * Selected model included:
@@
   * Correlated spatial effects (ICAR)
-  * Clients of FSW covariates
-* Used `R-INLA` for inference
+  * Clients of FSW covariates [@hodgins2022population]
+* Also used `R-INLA` for inference here
 
@@
 
-* Take 1000 samples from each model, then suitably multiply to generate estimates for all four risk groups
-* We adjusted the Very High risk group to match national FSW estimates from @johnston2022deriving
+* Take 1000 samples from each model, then multiply suitably to generate estimates for all four risk groups
+* We adjusted the very high risk group to match national FSW estimates from @johnston2022deriving
 
@@
 \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ estimates of risk group proportions $\rho_{itak}$ by district, year and age group
+$\implies$ Estimates of risk group proportions $\rho_{itak}$ by district, year and age group
 \end{tcolorbox}
 \end{center}
+
+##
+
+```{r echo=FALSE, out.width = "400px"}
+knitr::include_graphics("depends/aids-abstract-A.pdf")
+```
+
+##
+
+```{r echo=FALSE, out.width = "400px"}
+knitr::include_graphics("depends/aids-abstract-B.pdf")
+```
 
@@
 
-##
+<!-- ## -->
 
-```{r echo=FALSE, out.width = "400px"}
-knitr::include_graphics("depends/3p1-within-between-country-variation.png")
-```
+<!-- ```{r echo=FALSE, out.width = "400px"} -->
+<!-- knitr::include_graphics("depends/3p1-within-between-country-variation.png") -->
+<!-- ``` -->
 
@@
 
-1. Estimates even where there isn't direct data
-    * Although some people think of this as "making up data", the data almost never "speak for themselves"
-    * Uncertainty should be higher in regions with infilling: important to clearly communicate this
-2. Borrow information across space, between countries, over multiple surveys, (weakly) between risk groups
-    * See next slide for illustration of why this is important
+### Integration of all relevant surveys
+
+* Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question
+
+## Benefits of our modelled risk group estimates
+
+### Alleivating small-sample sizes
+
+* Direct estimates display large variance
+* We borrowed information across space, between countries and over surveys
+* Our estimates more plausibly reflect spatial heterogeneity
 
@@
 ```
+
+## Benefits of our modelled risk group estimates
+
+### Estimates even where there isn't direct data
+
+* Although some people think of this as "making up data", the data almost never "speak for themselves"
+* Uncertainty should be higher in regions with infilling: important to clearly communicate this
 
@@
 \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ estimates of HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ by district, age group and risk group
+$\implies$ Estimates of HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ by district, age group and risk group
 \end{tcolorbox}
@@
 df_area_age_behav <- df %>%
-  select(iso3, area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>%
+  select(area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>%
   pivot_longer(
@@
   pivot_wider(
-    id_cols = c("iso3", "area_id", "age_group", "indicator", "category"),
+    id_cols = c("area_id", "age_group", "indicator", "category"),
     names_from = "indicator",
@@
   head() %>%
-  knitr::kable()
+  knitr::kable(digits = 2)
 ```
@@
 df_area_age <- df_area_age_behav %>%
-  group_by(iso3, area_id, age_group) %>%
+  group_by(area_id, age_group) %>%
   summarise(
@@
 df_area_age %>%
-  select(iso3, area_id, age_group, population, incidence) %>%
+  select(area_id, age_group, population, incidence) %>%
   arrange(desc(incidence)) %>%
   head() %>%
-  knitr::kable()
+  knitr::kable(digits = 2)
 ```
@@
 
+## Limitations
+
+* Simplistic infections reached analysis
+  * No accounting for difficulty in reaching each strata
+  * Variable intervention effectiveness
+  * Change in strata membership
+* Under-reporting of high risk sexual behaviours
+  * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning
+* Simple risk groups, not clearly linked to data
+  * Didn't consider other important characteristics that may determine risk e.g. condom usage
+* Only focused on AGYW 15-29
+  * Could be extended to adults of both sexes aged 15-49
+
 ## Policy takeaways
 
-* ?
-
-## Limitations
-
-* Infections reached analysis simplistic, doesn't account for e.g. difficulty in reaching each strata, variable intervention effectiveness, change in strata membership
-* High risk sexual behaviours are under-reported, and likely varyingly so by age (foremost) and location (less so)
-* Risk group definitions didn't consider other important characteristics that may determine risk e.g. condom usage
-* Our analysis only focused on AGYW 15-29, and could be extended to adults of both sexes aged 15-49
+* We hope that our risk group estimates will help countries to implement the Global AIDS Strategy
+  * (User guide currently under development)
+* It's very important to reach FSW!
+* Countries have different epidemic profiles
 

### 2022-05-06 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
Presentable version of slides incase laptop dies again. Close #112

@@
 bibliography: citations.bib
+header-includes:
+  - \widowpenalties 1 150
 output:
@@
 
-* In sub-Saharan Africa, adolescent girls and young women (AGYW) are XX.X\% of the population but XX.X\% of all new HIV infections
-* Reasons for this disparity include:
+* In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are disproportionately at risk of HIV infection
+* This disparity is because of:
   1. Younger age at first sex
@@
 
-* To have the greatest impact with available prevention resources, interventions should be prioritised to those at highest risk
+* Prevention packages are made up of a core package, available to everyone, and more intensified interventions
+* To have the greatest impact, it's important to priorisite intensified interventions to those at highest risk
 * The Global AIDS Strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
@@
 
-1. Estimate the proportion of AGYW in four sexual risk behaviour groups at a district level (in 13 countries identified as priority by The Global Fund)
+1. Estimate the proportion of AGYW in four behavioural risk groups at a district level (in 13 countries identified as priority by The Global Fund)
 2. Analyze numbers of new infections reached by stratified prevention strategies
@@
 
-* Sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys (see next slide)
-* Later, we used district-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
+* We used sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys to place respondents into four risk groups:
+  1. $k = 1$: Not sexually active
+  2. $k = 2$: One cohabiting sexual partner
+  3. $k = 3$: Non-regular sexual partner(s)
+  4. $k = 4$: Female sex workers
+* District-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
+* Risk ratios from ALPHA network analysis [@slaymaker2020croi] and UNAIDS analysis led by Keith Sabin
+
+##
+
+```{r echo=FALSE, out.width = "400px"}
+knitr::include_graphics("depends/category-flowchart.pdf")
+```
 
@@
 
-* Multinomial logistic regression model for the proportion of AGYW in the none, low and {high, very high} risk groups, using all 47 surveys
+* Multinomial logistic regression model for the proportion of AGYW in the $k = 1, 2, 3^{+}$ risk groups, using all 47 surveys
 * Selected model included:
-  * Age effects (IID)
+  * Age country effects (IID)
   * Country effects (IID)
@@
 
-* Logistic regression model for the proportion of those in the {high, very high} risk groups who are in the very high risk group, using only the 13 surveys with a specific transactional sex question
+* Logistic regression model for the proportion of those in the $k = 3^{+} = \{3, 4\}$ risk groups who are in the $k = 4$ risk group, using only the 13 surveys with a specific transactional sex question
 * Selected model included:
-  * Age effects (IID)
+  * Age country effects (IID)
   * Country effects (IID)
@@
 * Take 1000 samples from each model, then multiply suitably to generate estimates for all four risk groups
-* We adjusted the very high risk group to match national FSW estimates from @johnston2022deriving
+* We adjusted the $k = 4$ risk group to match national FSW estimates from @johnston2022deriving
 
@@
 
-```{r echo=FALSE, out.width = "400px"}
+```{r echo=FALSE, out.width="350px", fig.cap = "We found a geographic discontinuity in behaviour between Southern and Eastern Africa."}
 knitr::include_graphics("depends/aids-abstract-A.pdf")
@@
 
-```{r echo=FALSE, out.width = "400px"}
+```{r echo=FALSE, out.width="350px", fig.cap = "Here is another view of the discontinuity."}
 knitr::include_graphics("depends/aids-abstract-B.pdf")
-```
-
-<!-- ## -->
-
-<!-- ```{r echo=FALSE, out.width = "400px"} -->
-<!-- knitr::include_graphics("depends/3p1-continental-map.png") -->
-<!-- ``` -->
-
-<!-- ## -->
-
-<!-- ```{r echo=FALSE, out.width = "400px"} -->
-<!-- knitr::include_graphics("depends/3p1-within-between-country-variation.png") -->
-<!-- ``` -->
-
-## Benefits of our modelled risk group estimates
-
-### Integration of all relevant surveys
-
-* Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question
-
-## Benefits of our modelled risk group estimates
-
-### Alleivating small-sample sizes
-
-* Direct estimates display large variance
-* We borrowed information across space, between countries and over surveys
-* Our estimates more plausibly reflect spatial heterogeneity
-
-##
-
-```{r echo=FALSE, out.width = "400px"}
-knitr::include_graphics("depends/model-direct-benefits.png")
 ```
@@
 
-### Estimates even where there isn't direct data
+* Integration of all relevant surveys
+  * Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question
+* Alleivating small-sample sizes (that caused direct estimates to display large variance)
+  * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity
+* Estimates where there isn't direct data
+  * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model)
+  * Uncertainty should be higher in regions with infilling: important to transparently communicate this
 
-* Although some people think of this as "making up data", the data almost never "speak for themselves"
-* Uncertainty should be higher in regions with infilling: important to clearly communicate this
+##
+
+```{r echo=FALSE, out.width = "350px", fig.cap = "Illustration of the problem with direct survey estimates."}
+knitr::include_graphics("depends/model-direct-benefits.png")
+```
 
@@
 
-* We hope that our risk group estimates will help countries to implement the Global AIDS Strategy
-  * (User guide currently under development)
-* It's very important to reach FSW!
+* Our risk group estimates can be used to help countries implement the Global AIDS Strategy (user guide currently under development)
+* It's important to reach FSW (not a new message!)
 * Countries have different epidemic profiles
@@
 
-* `R-INLA` and the multinomial-Poisson trick are a relatively good choice for spatio-temporal multinomial models
-  * Make good use of the `group` and `replicate` feature to define sufficiently complex Kronecker product effects
-  * Can run into limitations on model complexity: I might be moving to something more flexible e.g. `tmb`, `aghq` to continue development of this project
+* `R-INLA` and the multinomial-Poisson trick are a good choice for spatio-temporal multinomial models
+  * The `group` and `replicate` features can be used to define quite complex Kronecker product effects
+  * However, can run into limitations on model complexity and I might be moving to something more flexible e.g. `tmb`, `aghq` to continue development of this project
 
@@
 
+* This project was joint work with members of the HIV inference group, particularly Katie Risher and Jeff Eaton
+  * \faHome $\,$ `hiv-inference.org`
+* You can find me via
   * \faEnvelope $\,$ `ath19@ic.ac.uk`
@@
 
-## Bibliography {-}
+## Bibliography {.allowframebreaks}

### 2022-05-12 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
Final updates to MRC presentation, including a plot highlighting girls cohabiting in MOZ

@@
 
+## Prevention packages
+
+* Prevention
+  * Core package
+  * Intensified interventions
+* It's important to priorisite intensified interventions to those at highest risk
+
 ## Stratified prevention
 
-* Prevention packages are made up of a core package, available to everyone, and more intensified interventions
-* To have the greatest impact, it's important to priorisite intensified interventions to those at highest risk
-* The Global AIDS Strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
-  1. Population-level HIV incidence in the local population
+::: columns
+
+:::: column
+
+The Global AIDS strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
+
+1. Population-level HIV incidence
 2. Individual-level sexual risk behaviour
+
+::::
+
+:::: column
+
+```{r echo=FALSE, out.width = "125px", fig.cap="Global AIDS strategy"}
+knitr::include_graphics("global-aids-strategy.png")
+```
+
+::::
+
+:::
 
@@
 
-1. Enable implementation of prevention strategies stratified by incidence and behaviour
+1. Enable implementation of prevention stratified by incidence and behaviour
 2. Assess the benefits of such approaches
@@
 * We used sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys to place respondents into four risk groups:
-  1. $k = 1$: Not sexually active
-  2. $k = 2$: One cohabiting sexual partner
-  3. $k = 3$: Non-regular sexual partner(s)
-  4. $k = 4$: Female sex workers
+  1. Not sexually active
+  2. One cohabiting sexual partner
+  3. Non-regular sexual partner(s)
+  4. Female sex workers
 * District-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
@@
 * Multinomial logistic regression model for the proportion of AGYW in the $k = 1, 2, 3^{+}$ risk groups, using all 47 surveys
-* Selected model included:
+* Selected model (by CPO) included:
   * Age country effects (IID)
@@
   * Correlated temporal effects (AR1) 
-* Multinomial-Poisson transformation allowed us to use `R-INLA` for inference
+* Multinomial-Poisson transformation allowed use of `R-INLA` for inference
 
@@
 * Logistic regression model for the proportion of those in the $k = 3^{+} = \{3, 4\}$ risk groups who are in the $k = 4$ risk group, using only the 13 surveys with a specific transactional sex question
-* Selected model included:
+* Selected model (by CPO) included:
   * Age country effects (IID)
@@
   * Clients of FSW covariates [@hodgins2022population]
-* Also used `R-INLA` for inference here
+* Used `R-INLA` for inference
 
@@
 * Integration of all relevant surveys
-  * Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question
-* Alleivating small-sample sizes (that caused direct estimates to display large variance)
-  * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity
+  <!-- * Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question -->
+* Alleivating small-sample sizes by borrowing information
+  <!-- * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity -->
 * Estimates where there isn't direct data
-  * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model)
-  * Uncertainty should be higher in regions with infilling: important to transparently communicate this
+  <!-- * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model) -->
+  <!-- * Uncertainty should be higher in regions with infilling: important to transparently communicate this -->
 
@@
 
-* We used our risk group proportion estimates and relative risk ratio estimates from the literature to disaggregate Naomi general population HIV incidence estimates
+* Risk group proportion estimates plus relative risk ratio estimates to disaggregate general population HIV incidence estimates
 \begin{align*}
@@
 
-```{r echo=FALSE, out.width = "400px"}
+```{r echo=FALSE, out.width = "350px", fig.cap = "New infections reached prioritising according to different stratifications."}
 knitr::include_graphics("depends/infections-reached.png")
+```
+
+##
+
+```{r echo=FALSE, out.width = "350px", fig.cap = "As previous slide but specific to Mozambique."}
+knitr::include_graphics("depends/infections-reached-moz.png")
+```
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.cap = "Mozambique stands out."}
+knitr::include_graphics("depends/cohabiting-girls.pdf")
 ```
@@
 * Simplistic infections reached analysis
-  * No accounting for difficulty in reaching each strata
-  * Variable intervention effectiveness
-  * Change in strata membership
+  <!-- * No accounting for difficulty in reaching each strata -->
+  <!-- * Variable intervention effectiveness -->
+  <!-- * Change in strata membership -->
 * Under-reporting of high risk sexual behaviours
-  * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning
-* Simple risk groups, not clearly linked to data
-  * Didn't consider other important characteristics that may determine risk e.g. condom usage
+  <!-- * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning -->
+* Risk groups definition justification not clear
+  <!-- * Didn't consider other important characteristics that may determine risk e.g. condom usage -->
 * Only focused on AGYW 15-29
-  * Could be extended to adults of both sexes aged 15-49
+  <!-- * Could be extended to adults of both sexes aged 15-49 -->
 
-## Policy takeaways
+## Takeaways
 
-* Our risk group estimates can be used to help countries implement the Global AIDS Strategy (user guide currently under development)
-* It's important to reach FSW (not a new message!)
+* Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being prepared!
+* Importance of reaching FSW
 * Countries have different epidemic profiles
-
-## Methods takeaways
-
-* `R-INLA` and the multinomial-Poisson trick are a good choice for spatio-temporal multinomial models
-  * The `group` and `replicate` features can be used to define quite complex Kronecker product effects
-  * However, can run into limitations on model complexity and I might be moving to something more flexible e.g. `tmb`, `aghq` to continue development of this project
 
@@
 
-* This project was joint work with members of the HIV inference group, particularly Katie Risher and Jeff Eaton
-  * \faHome $\,$ `hiv-inference.org`
-* You can find me via
-  * \faEnvelope $\,$ `ath19@ic.ac.uk`
-  * \faHome $\,$ `athowes.github.io`
+* Joint work with members of the HIV inference group (`hiv-inference.org`) particularly Katie Risher and Jeff Eaton
+* The code for this project is at `github.com/athowes/multi-agyw`
+* You can find me online at `athowes.github.io`
 

### 2022-05-12 src/plot_within-between-country-variation/script.R

@@ -2,7 +2,8 @@
 # orderly::orderly_develop_start("plot_within-between-country-variation")
 # setwd("src/plot_within-between-country-variation")
 
-df_3p1 <- read_csv("depends/adjust-best-3p1-multi-sexbehav-sae.csv")
+df_3p1 <- read_csv("depends/adjust-best-3p1-multi-sexbehav-sae.csv") %>%
+  filter(indicator != "sexnonregplus")
 pop <- read_csv("depends/interpolated_population.csv")
 
 #' Add population and updating naming
@@ -51,6 +52,40 @@ ggsave(
   plotA,
   width = 6.25, height = 7, units = "in", dpi = 300
 )
+
+#' Version showing cohabiting numbers for 15-19
+
+pdf("cohabiting-girls.pdf", h = 4, w = 6.25)
+
+df_3p1_subnational %>%
+  mutate(iso3 = reorder(iso3, iso3_sort_order)) %>%
+  filter(
+    age_group == "15-19",
+    indicator == "Cohabiting partner"
+  ) %>%
+  mutate(
+    moz_indicator = factor(ifelse(iso3 == "Mozambique", 1, 0))
+  ) %>%
+  ggplot(aes(x = fct_rev(iso3), y = estimate_smoothed, col = moz_indicator)) +
+  geom_jitter(width = 0.1, shape = 20) +
+  geom_point(data = filter(df_3p1_national, age_group == "15-19", indicator == "Cohabiting partner"),
+             aes(x = fct_rev(iso3), y = estimate_smoothed), shape = 21, size = 2, fill = "white",
+             col = "black", alpha = 0.9) +
+  scale_color_manual(values = c("#D3D3D3", multi.utils::cbpalette()[2])) +
+  scale_y_continuous(labels = function(x) paste0(100 * x, "%")) +
+  coord_flip() +
+  labs(x = "", y = "Proportion of girls 15-19 cohabiting", col = "") +
+  guides(colour = FALSE) +
+  theme_minimal() +
+  theme(
+    panel.spacing = unit(0.5, "lines"),
+    legend.position = "bottom",
+    strip.text = element_text(face = "bold"),
+    legend.title = element_text(size = 9),
+    legend.text = element_text(size = 9),
+  )
+
+dev.off()
 
 #' Have a closer look at the FSW estimates and check that the Johnston adjustment has worked
 df_3p1_unadjusted <- read_csv("depends/best-3p1-multi-sexbehav-sae.csv")

### 2022-06-04 src/docs_paper/appendix.Rmd
Infrastructure for writing paper and abstract in markdown #128

---
title: Appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent
  girls and young women across 13 priority countries in sub-Saharan Africa"
output: pdf_document

---

### 2022-06-04 src/docs_paper/paper.Rmd
Infrastructure for writing paper and abstract in markdown #128

---
title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
author:
  - name: Adam Howes
    email: ath19@ic.ac.uk
    affiliation: Imperial College London
    corresponding: ath19@ic.ac.uk
address:
  - code: Imperial College London
    address: Department of Mathematics
abstract: |
  Abstract

author_summary: |
  Author summary

bibliography: citations.bib
output: rticles::plos_article
# plos.csl can be download and used locally
csl: http://www.zotero.org/styles/plos
---

# Introduction

In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are XX.X\% of the population but XX.X\% of new HIV infections [@unaids2021update].
HIV incidence amongst AGYW is X.X times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
AGYW have therefore been identified as a priority population for HIV primary prevention, and significant investments have been made in prevention programming [@saul2018dreams; @global2018measurement].

HIV prevention for AGYW is typically comprised of basic programming which is made available to all, together with additional, more intensified, programming which is differentiated on the basis of risk [@joint2016hiv, birdthistle2018evaluating].
To maximize the impact of additional programming, often comprised of more costly interventions, delivery should be prioritised towards those at the highest risk level.
As both community-level epidemic indicators and individual-level behaviours determine risk of acquiring HIV, it is important to consider both of these factors in tandem to enable more efficient prioritisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].

The Global AIDS Strategy 2021-2016 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying provision of HIV prevention to AGYW based on both population-level HIV incidence in the local population and individual-level sexual risk behaviour.
Four prioritisation strata (Table) are defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1\% and >3\%), and (2) self-reported high-risk behaviour or recent STI infection.
The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table) based upon this prioritisation strata [@unaids2021global].
These interventions may include STI screening and treatment, access to pre-exposure prophylaxis (PrEP), access to post-exposure prophylaxis (PEP), comprehensive sexuality education, and economic empowerment.

Implementation of the strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group, age group, and district to determine prioritisation for stratified HIV prevention.
We developed a multivariate Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
We focused on 13 countries in sub-Saharan Africa which have been identified by by the Global Fund to Fight AIDS, TB, and Malaria [@global2018measurement] as priority countries for implementation of AGYW HIV prevention.
Our methodology is standardised across countries, allowing prioritisation both within and between countries.
We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
Using our estimates, we calculated the number of new infections in each risk, age, and district strata using population size data, incidence rate ratios, and expected incidence projections.
Finally, we quantified the increased efficiency in terms of the expected number of new infections that could be preemptively reached by stratified prioritisation of interventions.

# Methodology

## Data

We analysed nationally-representative household survey data from 13 countries: Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Eswatini, Tanzania, Uganda, Zambia and Zimbabwe.
We included surveys conducted in these countries in the years 1999-2018 in which women were interviewed about their sexual behaviour and sufficient geographic information was available to locate survey clusters to districts.
Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS), Population-based HIV Impact Assessment (PHIA) surveys, and the Botswana HIV/AIDS Impact Survey 2013 (BAIS) were included.

For each survey, we classified respondents into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table, Figure).
In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
Exact survey questions varied to a limited extent between surveys, as described in Appendix.
Questions captured information about if the respondent had been sexually active in the past twelve months, and if so how with many partners.
For their three most recent partners, respondents were also asked about the type of partnership (spouse, cohabiting partner, partner not cohabiting with respondent, friend, sex worker, sex work client, and other).

Some surveys included a specific question asking if the respondent had received or given payment for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
In surveys without that question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
For this reason, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who were FSW or engaged in transactional sex.

We used estimates of population, people living with HIV (PLHIV) and new HIV infections stratified by district and age group from outputs of the Naomi model [@eaton2021naomi].
The model synthesises data from multiple sources to produce consistent subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi.
In Cameroon and Kenya we used an analysis level one higher than used in Naomi.

## Two-stage risk group proportion model

To estimate the proportion of AGYW in each risk group we took a two-stage modelling approach, further details of which are provided in Appendix.
First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24 and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) cohabiting, and (3) either non-regular partner(s) or transactional sex.
Combining the two highest risk groups in this way allowed data from all 47 surveys to be included in this first stage model.
Second, we fit a spatial logistic regression model separating those who have non-regular parnter(s) from those who have had transactional sex, stratified by district, and five-year age group, and using only data from the 13 surveys with a specific transaction sex question.
As these surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in at least the high risk group was constant over time.
We combined the two models using 1000 samples from each posterior distribution to produce samples from all four risk groups.
Finally, we adjusted the samples from the transactional sex category to match age-country specific FSW population size estimates, modifying the samples from the non-regular partner(s) category such that the proportions sum to one.
To do so, we disaggregated national 15-49 FSW population size estimates from @stevens2022estimating using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions from @kinh2021trends.

<!-- \text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution -->

We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Table).
All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
Alternative models varied the specification for the spatial effect between independent spatial effects versus spatially correlated effects and independent temporal effects versus first-order auto-regressive temporal effects.
Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts.
To understand the importance of each part of the model we undertook a variance-based sensitivity analysis using the random effect variance parameters.

For the logistic regression model for the proportion engaging in transactional sex among those with non-regular partner(s), we considered six specifications (Table).
Each included an intercept, age and country effects, and a spatial effect allowing district level variation.
Both independent and spatially correlated spatial effects were considered.
To improve estimation with sparse data, we considered model alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months, available from @hodgins2022population.

We performed inference using integrated nested Laplace approximation [@rue2009approximate] via the `R-INLA` package [@martins2013bayesian].
The best performing model was selected according to the conditional predictive ordinate (CPO) criteria, a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
The \textsc{R} [@r] code used to implement the models and produce  results is available from `github.com/athowes/multi-agyw`.
We used the `orderly` package [@orderly] for reproducible research.

\subsection{Prevalence, incidence and new infections}

We used the risk group proportion estimates to calculate HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified according to district, age group and risk group by disaggregating estimates from the Naomi model (further details are provided in Appendix).

We disaggregated HIV prevalence estimates by risk group on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
Logit scaling was preferred to linear scaling, as linear scaling resulted in some strata having prevalence above 100\%.
PLHIV were calculated by multiplying HIV prevalence by risk group population size.

HIV incidence estimates were disaggregated by risk group on the linear scale using the HIV infection risk ratios given in Table.
Number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size. 
We then calculated the number of new infections that would be found per person reached when prioritising according to incidence under each possible risk stratification.
In doing so, we implicitly assumed it is possible to reach all members of a strata.

# References {#references .unnumbered}

### 2022-06-04 src/docs_paper/appendix.Rmd
Progress moving paper and appendix to markdown (this will be a fun plan activity!) #128

@@
   girls and young women across 13 priority countries in sub-Saharan Africa"
-output: pdf_document
+output:
+  pdf_document:
+    keep_tex: true
+    includes:
+      in_header: preamble.tex
+bibliography: citations.bib
+---
 
----
+\newpage
+
+# Statistical modelling of risk group proportions
+
+## Overview
+
+We index the four risk groups given in Table by $k \in \{1, 2, 3, 4\}$ and we denote being in either the third or fourth risk group by $k = 3^{+}$.
+Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts.
+For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider a multinomial random vector
+\begin{equation}
+    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}).
+\end{equation}
+The number of women in risk group $k$ is $y_{itak}$ and the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, where $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
+To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial; @lee2017poisson]
+\begin{align}
+    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
+    \log(\kappa_{itak}) &= \eta_{itak}, \label{eq:linearpredictor}
+\end{align}
+for particular choice of the linear predictor $\eta_{itak}$, described in more detail in Section.
+
+To estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
+\begin{align}
+    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \\
+    q_{ia} &= p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}, \\
+    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
+\end{align}
+for choice of the linear predictor $\eta_{ia}$, described in more detail in Section.
+This approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
+As all such surveys occurred in 2013-2018, $q_{ia}$ was assumed to be constant over time.
+
+To quantify uncertainty from our model, we took posterior samples $s = 1, \ldots, 1000$ from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via
+\begin{align*}
+    p_{ita3}^s &= (1 - q_{ia}^s)p_{ita{3^+}^s}, \\
+    p_{ita4}^s &= q_{ia}^s p_{ita{3^+}}^s.
+\end{align*}
+As transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that the population size estimates for FSW aggregated to a national level matched those of @stevens2022estimating.
+In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
+We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using these adjusted samples.
+To produce aggregated estimates, such as the age category 15-24 and national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].
+
+## Multinomial regression model
+
+### The multinomial-Poisson transformation
+
+The multinomial-Poisson transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
+\begin{align}
+    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
+    \log(\kappa_{itak}) &= \eta_{itak},
+\end{align}
+for suitable choice of linear predictor $\eta_{itak}$.
+Category probabilities are then obtained by applying the softmax function to the linear predictor as follows
+\begin{equation}
+    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}}.
+\end{equation}
+In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random rather than fixed as they would be in the multinomial logistic regression model.
+In particular, following Equation, the sample sizes follow a Poisson distribution
+\begin{equation}
+    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right),
+\end{equation}
+where the intensity $\kappa_{ita} = \sum_k \kappa_{itak}$ is given by a sum of intensities over each category.
+The basis of the Poisson trick is that, conditional on their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized]
+\begin{equation}
+    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{itaK}}{\kappa_{ita}} \right).
+\end{equation}
+As such, the joint distribution of $p(\mathbf{y}_{ita}, m_{ita})$ is
+\begin{align}
+p(m_{ita}) p(\mathbf{y}_{ita} \, | \, m_{ita}) 
+&= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
+&= \prod_k \left( \frac{\exp(-\kappa_{itak}) \left( \kappa_{itak} \right)^{y_{itak}}}{y_{itak}!} \right) \\
+&= \prod_k \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right). \label{eq:prodpoisson}
+\end{align}
+Equation corresponds to the product of $K$ independent Poisson likelihoods, and the joint distribution over all the data $\{\mathbf{y}_{ita}, m_{ita}\}_{i, t, a}$ is given by $\prod_{i, t, a, k} \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right)$.
+The Poisson log-linear model, which vicariously includes the sample sizes as random, is equivalent only when these normalisation constants are recovered exactly by the model.
+To ensure that this is the case, we included observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor in every model we considered.
+Multiplying each of $\{\kappa_{itak}\}_{k = 1}^K$ by $\exp(\theta_{ita})$ has no effect on the multinomial probabilities, but does provide the flexibility required for $\kappa_{ita}$ to exactly recover $m_{ita}$ as desired.
+Although in theory an improper prior $\theta_{ita} \propto 1$ should be used, in practise, by keeping $\eta_{ita}$ small so that arbitrarily large values of the observation-specific random effects $\theta_{ita}$ are not required, it is sufficient (and practically preferable for inference) to instead use a vague prior.
+As such, we set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
+
+### Model specifications
+
+We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form $\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}$.
+Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for the Poisson log-linear model to be equivalent to the multinomial logistic regression.
+To capture age-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and age-category random effects $\alpha_{ak} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
+Owing to country-level heterogeneity in the data, we also included country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects, as well as separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure.
+All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$
+where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
+
+To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the age-category, country-category, space-category and year-category random effects did not alter overall category probabilities.
+For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
+Together, these were\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.}:
+\begin{enumerate}
+    \item Category $\sum_k \beta_k = 0$
+    \item Age $\sum_a \alpha_{ak} = 0, \, \forall \, k$
+    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
+    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
+    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
+    \item Spatio-temporal $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
+\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
+\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
+\end{enumerate}
+
+#### Spatial random effects \label{sec:spatial-random-effects}
+
+The specifications we considered for the space-category random effects were IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and Besag grouped by category
+$$
+\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{1K}, \ldots \phi_{nK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
+$$
+where the scaled structure matrix $\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}$ is given by the Kronecker product of the scaled Besag structure matrix $\mathbf{R}^\star_b$ and the identity matrix $\mathbf{I}$.
+Scaling of the structure matrix to have generalised variance one ensures interpretable priors may be placed on the precision parameter [@sorbye2014scaling].
+We follow the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
+The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with the full conditionals
+\begin{equation}
+b_i \, | \, \mathbf{b}_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} b_j}{n_{\delta i}}, \frac{1}{n_{\delta i}}\right),
+\end{equation}
+where $j \sim i$ if the districts $A_i$ and $A_j$ are adjacent, and $n_{\delta i}$ is the number of districts adjacent to $A_i$.
+
+In preliminary testing, we tried excluding spatial random effects from the model, but found that this negatively effected performance.
+We also tried using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one.
+For simplicity and to avoid numerical issues, by instead using Besag random effects we decided to fix this proportion to one, rather than learn it.
+
+#### Temporal random effects \label{sec:temporal-random-effects}
+
+The specifications we considered for the survey-category random effects were IID $\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and AR1 grouped by category
+$$
+\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{1K}, \ldots, \gamma_{T1}, \ldots, \gamma_{TK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
+$$
+where the scaled structure matrix $\mathbf{R}^\star_\gamma = \mathbf{R}^\star_r \otimes \mathbf{I}$ is given by the Kronecker product of a scaled AR1 structure matrix $\mathbf{R}^\star_r$ and the identity matrix $\mathbf{I}$.
+The AR1 structure matrix $\mathbf{R}_r$ is obtained by precision matrix of the random effects $\mathbf{r} = (r_1, \ldots, r_T)^\top$ specified by
+\begin{align}
+r_1 &\sim \left( 0, \frac{1}{1 - \rho^2} \right), \\
+r_t &= \rho r_{t - 1} + \epsilon_t, \quad t = 2, \ldots, T, 
+\end{align}
+where $\epsilon_t \sim \mathcal{N}(0, 1)$ and $|\rho| < 1$.
+For the lag-one correlation parameter $\rho$, we used the PC prior, as derived by @sorbye2017penalised, with base model $\rho = 1$ and condition $\mathbb{P}(\rho > 0 = 0.75)$.
+We chose a base model corresponding to no change in behaviour over time, rather than the alternative $\rho = 0$ corresponding to no correlation in behaviour over time, as we judged the former to be more plausible a priori.
+
+#### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}
+
+For each model including spatio-temporal random effects we used the specification
+\begin{equation}
+    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nTK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
+\end{equation}
+where $\mathbf{R}^\star_\delta$ is a Kronecker product of the relevant space, time and category structure matrices.
+In particular, for each of the four models including spatio-temporal interactions, these matrices are
+\begin{itemize}
+\item
+1x: No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
+\item
+2x: Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
+\item
+3x: Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
+\item
+4x: Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
+\\
+\end{itemize}
+where the first, second and third elements of the product represent space, time and category respectively, and the interaction type provided in brackets is given according to the @knorr2000bayesian framework.
+
+### Survey weighted likelihood
+
+<!-- To account for the complex survey design, in which individuals have unequal sampling probabilities, we replaced the observed counts $\{y_{itak}\}$ in each risk group with weighted counts $\{y_{itak}^\star\}$ and used a pseudo-likelihood to extend the Poisson distribution to non-integer weighted counts.
+-->
+
+The surveys we used utilise a complex design, in which each individual has an unequal probability of being included in the sample.
+For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
+To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y_{itak}$ are replaced by effective counts $y^\star_{itak}$ calculated using survey weights $w_{itak}$.
+We multiplied direct estimates produced using the `survey` package \citep{JSSv009i08} by the Kish effective sample size \citep{kish1965survey}
+\begin{equation}
+    m^\star_{itak} = \left(\sum_{itak} w_{itak} \right)^2 / \sum_{itak} {w_{itak}}^2
+\end{equation}
+to obtain $y^\star_{itak}$.
+As these counts may not be integers, the Poisson likelihood in Equation~\eqref{eq:poisson} is inappropriate.
+Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, as implemented by `family = "xPoisson"` in `R-INLA`, given by
+\begin{equation}
+    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right).
+\end{equation}
+
+\subsection{Logistic regression model} \label{app:logistic-model}
+
+\begin{table}[htb]
+\small
+\centering
+\begin{tabularx}{\textwidth}{llllll}
+\midrule
+Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_c$) & Spatial ($\phi_i$) & Covariates \\ 
+\midrule
+L1 & Constant & IID & IID & IID & None \\
+L2 & Constant & IID & IID & Besag & None \\
+L3 & Constant & IID & IID & IID & \texttt{cfswever} \\
+L4 & Constant & IID & IID & Besag & \texttt{cfswever} \\
+L5 & Constant & IID & IID & IID & \texttt{cfswrecent} \\
+L6 & Constant & IID & IID & Besag & \texttt{cfswrecent} \\
+\midrule
+\end{tabularx}
+\caption{The logistic regression models that were considered.
+\texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months \citep{hodgins2022population}.}
+\label{tab:logistic-models}
+\small
+\end{table}
+
+We considered six logistic regression models (Table~\ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.
+To aid estimation with sparse data, we also considered national-level covariates for the proportion of men who have paid for sex ever \texttt{cfswever} or in the last twelve months \texttt{cfswrecent}, available from \citet{hodgins2022population}.
+For both random effect precision parameters $\tau \in \{\tau_\alpha, \tau_\zeta\}$ as before we use the PC prior with base model $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$.
+For the regression parameters $\beta \in \{\beta_\texttt{cfswever}, \beta_\texttt{cfswrecent}\}$ we used the prior $\beta \sim \mathcal{N}(0, 2.5^2)$.
+
+\subsubsection{Survey weighted likelihood}
+
+As with the multinomial regression model, we used survey weighted counts $\{y_{itak}^\star\}$ and sample sizes $\{m_{itak}^\star\}$.
+We used a used a generalised binomial pseudo-likelihood $y^\star \sim \text{xBinomial}(y^\star, m^\star)$, as implemented by \texttt{family = "xBinomial"} in \texttt{R-INLA}, given by
+\begin{equation}
+    p(y^\star \, | \, m^\star) =  \binom{\lfloor m^\star \rfloor}{\lfloor y^\star \rfloor} q^{y^\star} (1 - q)^{m^\star - y^\star}.
+\end{equation}
+to extend the binomial distribution to non-integer weighted counts and sample sizes.
+
+\subsubsection{Model selection}
+
+\begin{footnotesize}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{0.82\textwidth}{lllllll}
+\toprule
+ & Model 1 & Model 2 & Model 3 & Model 4 & Model 5 & Model 6 \\ 
+\midrule
+DIC & 4662 (110) & 4605 (111) & 4662 (110) & 4605 (111) & 4662 (110) & 4605 (111) \\ 
+WAIC & 4692 (115) & 4624 (115) & 4692 (115) & 4624 (115) & 4692 (115) & 4624 (115) \\ 
+CPO & 950 (15) & 969 (15) & 951 (15) & 970 (15) & 950 (15) & 970 (15) \\ 
+\bottomrule
+\end{tabularx}
+\caption{Logistic regression model performance.}
+\label{tab:logistic-model-performance}
+\end{table}
+
+\end{footnotesize}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics{figures/fsw-logit-information-criteria.pdf}}
+    \caption{Logistic regression model performance.}
+    \label{fig:logistic-model-performance}
+\end{figure}
+
+\newpage
+
+# Prevalence, incidence and new infections reached analysis
+
+## Calculation of prevalence and PLHIV
+
+We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak} = \rho_{iak} N_{iak}$ stratified according to district, age group and risk group by disaggregation
+\begin{align}
+    H_{ia} &= \sum_k H_{iak} = \sum_k \rho_{iak} N_{iak} \\
+    &= \rho_{ia1} N_{ia1} + \rho_{ia1} \text{PR}_2 N_{ia2} + \rho_{ia1} \text{PR}_3 N_{ia3} + \rho_{ia1} \text{PR}_4 N_{ia4} \\
+    &= \rho_{ia1} \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right).
+\end{align}
+Risk group specific prevalence estimates are then given by
+\begin{align}
+    \rho_{ia1} &= H_{ia} / \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right), \\
+    \rho_{ia2} &= \rho_{ia1} \text{PR}_2,\\
+    \rho_{ia3} &= \rho_{ia1} \text{PR}_3,\\
+    \rho_{ia4} &= \rho_{ia1} \text{PR}_4,
+\end{align}
+which we evaluated using Naomi model estimates of PLHIV $H_{ia} = \rho_{ia} N_{ia}$, prevalence ratios $\{\text{PR}_k\}$ as described below, and risk group population sizes $N_{iak} = p_{iak} N_{ia}$ based on our 2018 risk group estimates together with population size estimates from the Naomi model.
+To obtain the prevalence ratios, we...
+
+## Calculation of incidence and number of new infections
+
+Similarly, we calculated HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ stratified according to district, age group and risk group by disaggregation
+\begin{align}
+    I_{ia} &= \sum_k I_{iak} = \sum_k \lambda_{iak}N_{iak} \\
+    &= 0 + \lambda_{ia2} N_{ia2} + \lambda_{ia3} N_{ia3} + \lambda_{ia4} N_{ia4} \\
+    &= \lambda_{ia2} \left(N_{ia2}  + \text{RR}_{3} N_{ia3} + \text{RR}_4(\lambda_{ia}) N_{ia4}  \right).
+\end{align}
+Risk group specific incidence estimates are then given by
+\begin{align}
+    \lambda_{ia1} &= 0, \\
+    \lambda_{ia2} &= I_{ia} / \left(N_{ia2} + \text{RR}_{3} N_{ia3} + \text{RR}_4(\lambda_{ia}) N_{ia4}\right), \\
+    \lambda_{ia3} &= \text{RR}_{3} \lambda_{ia2}, \\
+    \lambda_{ia4} &= \text{RR}_4(\lambda_{ia}) \lambda_{ia2}.
+\end{align}
+which we evaluated using Naomi model estimates of the number of new HIV infections $I_{ia} = \lambda_{ia} N_{ia}$, HIV infection risk ratios $\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}$ as given in Table~\ref{tab:risk-categories}, and 2018 risk group population sizes as above.
+The risk ratio $\text{RR}_4(\lambda_{ia})$ is defined as a function of general population incidence.
+Using these estimates $\{\lambda_{iak}\}$, the number of new HIV infections is then $I_{iak} = \lambda_{iak} N_{iak}$.
+
+## Analysis of new infections reached
+
+We calculated the number of new infections that would be reached prioritising according to each possible stratification of the population.
+As an illustration, for stratification by age, we aggregated the number of new HIV infections and HIV incidence as such 
+\begin{align}
+    I_a &= \sum_{ik} I_{iak}, \\
+    \lambda_a &= I_a / \sum_{ik} N_{iak}.
+\end{align}
+Under this stratification, individuals in each age group $a$ would be prioritised according to the highest HIV incidence $\lambda_a$.
+We repeated this analysis for all $2^3 = 8$ possible combinations of stratification by location, age, and risk group.
+
+\newpage
+
+# The Global AIDS Strategy 2021-2016
+
+\begin{footnotesize}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Prioritisation strata & Criterion \\ 
+ \midrule
+Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
+Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
+High & 1-3\% incidence AND high-risk behaviour \\
+Very high & $>$3\% incidence \\
+\bottomrule
+\end{tabularx}
+\caption{Prioritisation strata.}
+\label{tab:unaids-strategy-prioritisation}
+\end{table}
+
+\end{footnotesize}
+
+\begin{footnotesize}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Intervention & Details \\ 
+ \midrule
+STI screening and treatment & (Remain to be filled in: describe targets and commitments in terms of each prioritisation strata) \\
+PrEP use & (As above) \\
+Access to PEP & (As above) \\
+Comprehensive sexuality education & (As above) \\
+Economic empowerment & (As above) \\
+\bottomrule
+\end{tabularx}
+\caption{Targets and commitments.}
+\label{tab:unaids-strategy-targets}
+\end{table}
+
+\end{footnotesize}
+
+\newpage
+
+# Survey questions and risk group classification
+
+## Survey questions
+
+\begin{footnotesize}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Variable(s) & Description \\ 
+ \midrule
+\texttt{v501} & Current marital status of the respondent. \\
+\texttt{v529} & Computed time since last sexual intercourse. \\
+\texttt{v531} & Age at first sexual intercourse--imputed. \\
+\texttt{v766b} & Number of sexual partners during the last 12 months (including husband). \\
+\texttt{v767[a, b, c]} & Relationship with last three sexual partners.
+Options are: spouse, boyfriend not living with respondent, other friend, casual acquaintance, relative, commercial sex worker, live-in partner, other.
+\\
+\texttt{v791a} & Had sex in return for gifts, cash or anything else in the past 12 months. Asked only to women 15-24 who are not in a union. \\
+\bottomrule
+\end{tabularx}
+\caption{AIS, BAIS and DHS survey questions.}
+\end{table}
+
+\end{footnotesize}
+
+\begin{footnotesize}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Variable(s) & Description \\ 
+ \midrule
+\texttt{part12monum} & Number of sexual partners during the last 12 months (including husband). \\
+\texttt{part12modkr} & Reason for leaving \texttt{part12monum} blank. \\
+\texttt{partlivew[1, 2, 3]} & Does the person you had sex with live in this household? \\
+\texttt{partrelation[1, 2, 3]} & Relationship with last three sexual partners.
+Options are: husband, live-in partner, partner (not living with), ex-spouse/partner, friend/acquaintance, sex worker, sex worker client, stranger, other, don't know, refused.
+\\
+\texttt{sellsx12mo} & Had sex for money and/or gifts in the last 12 months. \\
+\texttt{buysx12mo} & Paid money or given gifts for sex in the last 12 months. \\
+\bottomrule
+\end{tabularx}
+\caption{PHIA survey questions.}
+\end{table}
+
+\end{footnotesize}
+
+\newpage
+
+\subsection{Risk group classification based on survey questions}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics{depends/category-flowchart.pdf}
+    \caption{Flowchart describing allocation of respondents to risk groups.}
+    \label{fig:category-flowchart}
+\end{figure}
+
+\newpage
+
+# Supplementary figures
+
+\newpage
+
+# Supplementary tables
+
+\newpage
+
+# References {#references .unnumbered}

### 2022-06-04 src/docs_paper/appendix.tex
Progress moving paper and appendix to markdown (this will be a fun plan activity!) #128

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix to ``Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa''},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage[authoryear]{natbib}
\RequirePackage{bm}
\RequirePackage{enumerate}
\RequirePackage{enumitem}
\RequirePackage{tabularx}
\RequirePackage{adjustbox}
\RequirePackage{tikz}
\RequirePackage{bbm}
\RequirePackage{lscape}
\RequirePackage{booktabs}
\RequirePackage{longtable}
\RequirePackage{lscape}
\RequirePackage{pifont}
\usepackage{footnote}

\newcommand{\Sc}{\mathcal{S}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\bv}{\mathbf{v}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\bb}{\mathbf{b}}
\newcommand{\brho}{\bm{\rho}}
\newcommand{\bphi}{\bm{\phi}}
\newcommand{\btheta}{\bm{\theta}}
\newcommand{\bpsi}{\bm{\psi}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Appendix to ``Spatio-temporal estimates of HIV risk group
proportions for adolescent girls and young women across 13 priority
countries in sub-Saharan Africa''}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\newpage

\hypertarget{statistical-modelling-of-risk-group-proportions}{%
\section{Statistical modelling of risk group
proportions}\label{statistical-modelling-of-risk-group-proportions}}

\hypertarget{overview}{%
\subsection{Overview}\label{overview}}

We index the four risk groups given in Table by \(k \in \{1, 2, 3, 4\}\)
and we denote being in either the third or fourth risk group by
\(k = 3^{+}\). Let \(c \in \{1, \ldots, 13\}\) denote the 13 studied
AGYW priority countries, each partitioned into districts. For each
district \(i \in \{1, \ldots, n\}\), year
\(t \in \{1999, \ldots, 2018\}\), age category
\(a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}\), and risk
group \(k \in \{1, 2, 3^{+}\}\) we consider a multinomial random vector
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}).
\end{equation} The number of women in risk group \(k\) is \(y_{itak}\)
and the sample size is \(m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}\),
where \(p_{itak} > 0\) is the probability of membership of the \(k\)th
risk group with \(\sum_{k = 1}^{3^{+}} p_{itak} = 1\). To efficiently
model this data we used the multinomial-Poisson transformation, which
allows multinomial logistic regression models to be cast as equivalent
Poisson log-linear models (Baker 1994; Lee, Green, and Ryan 2017)
\begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
    \log(\kappa_{itak}) &= \eta_{itak}, \label{eq:linearpredictor}
\end{align} for particular choice of the linear predictor
\(\eta_{itak}\), described in more detail in Section.

To estimate the proportion of those in the \(k = 3^{+}\) risk group that
were respectively in the \(k = 3\) and \(k = 4\) risk groups, we fit a
separate logistic regression model of the form \begin{align}
    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \\
    q_{ia} &= p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}, \\
    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
\end{align} for choice of the linear predictor \(\eta_{ia}\), described
in more detail in Section. This approach allowed us to include all
surveys in the multinomial regression model, but only those surveys with
a specific transactional sex question to estimate the proportions
\(\{p_{ia4}\}\). As all such surveys occurred in 2013-2018, \(q_{ia}\)
was assumed to be constant over time.

To quantify uncertainty from our model, we took posterior samples
\(s = 1, \ldots, 1000\) from each of the multinomial \(\{p_{itak}^s\}\)
and logistic regression \(\{q_{ia}^s\}\) models. Samples \(p_{ita3}^s\)
and \(p_{ita4}^s\) were then generated by splitting samples from the
\(k = 3^{+}\) category of the multinomial model via \begin{align*}
    p_{ita3}^s &= (1 - q_{ia}^s)p_{ita{3^+}^s}, \\
    p_{ita4}^s &= q_{ia}^s p_{ita{3^+}}^s.
\end{align*} As transactional sex is too inclusive to directly
correspond to sex work (Wamoyi et al. 2016), we adjusted our samples so
that the population size estimates for FSW aggregated to a national
level matched those of Stevens et al. (2022). In making this adjustment,
we assumed that subnational variation in the FSW proportion corresponds
to that of the transactional sex proportion. We calculated the mean,
median, 2.5\% and 97.5\% quantiles for the risk group probabilities
empirically using these adjusted samples. To produce aggregated
estimates, such as the age category 15-24 and national estimates, we
weighted the adjusted samples by population sizes
\(N_{ita} = \sum_k N_{itak}\) obtained from the Naomi model (Eaton et
al. 2021).

\hypertarget{multinomial-regression-model}{%
\subsection{Multinomial regression
model}\label{multinomial-regression-model}}

\hypertarget{the-multinomial-poisson-transformation}{%
\subsubsection{The multinomial-Poisson
transformation}\label{the-multinomial-poisson-transformation}}

The multinomial-Poisson transformation reframes a given multinomial
logisitic regression model as an equivalent Poisson log-linear model of
the form \begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
    \log(\kappa_{itak}) &= \eta_{itak},
\end{align} for suitable choice of linear predictor \(\eta_{itak}\).
Category probabilities are then obtained by applying the softmax
function to the linear predictor as follows \begin{equation}
    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}}.
\end{equation} In the equivalent model, the sample sizes
\(m_{ita} = \sum_k y_{itak}\) are treated as random rather than fixed as
they would be in the multinomial logistic regression model. In
particular, following Equation, the sample sizes follow a Poisson
distribution \begin{equation}
    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right),
\end{equation} where the intensity
\(\kappa_{ita} = \sum_k \kappa_{itak}\) is given by a sum of intensities
over each category. The basis of the Poisson trick is that, conditional
on their sum, Poisson counts are jointly multinomially distributed
(McCullagh and Nelder 1989) \begin{equation}
    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{itaK}}{\kappa_{ita}} \right).
\end{equation} As such, the joint distribution of
\(p(\mathbf{y}_{ita}, m_{ita})\) is \begin{align}
p(m_{ita}) p(\mathbf{y}_{ita} \, | \, m_{ita}) 
&= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
&= \prod_k \left( \frac{\exp(-\kappa_{itak}) \left( \kappa_{itak} \right)^{y_{itak}}}{y_{itak}!} \right) \\
&= \prod_k \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right). \label{eq:prodpoisson}
\end{align} Equation corresponds to the product of \(K\) independent
Poisson likelihoods, and the joint distribution over all the data
\(\{\mathbf{y}_{ita}, m_{ita}\}_{i, t, a}\) is given by
\(\prod_{i, t, a, k} \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right)\).
The Poisson log-linear model, which vicariously includes the sample
sizes as random, is equivalent only when these normalisation constants
are recovered exactly by the model. To ensure that this is the case, we
included observation-specific random effects \(\theta_{ita}\) in the
equation for the linear predictor in every model we considered.
Multiplying each of \(\{\kappa_{itak}\}_{k = 1}^K\) by
\(\exp(\theta_{ita})\) has no effect on the multinomial probabilities,
but does provide the flexibility required for \(\kappa_{ita}\) to
exactly recover \(m_{ita}\) as desired. Although in theory an improper
prior \(\theta_{ita} \propto 1\) should be used, in practise, by keeping
\(\eta_{ita}\) small so that arbitrarily large values of the
observation-specific random effects \(\theta_{ita}\) are not required,
it is sufficient (and practically preferable for inference) to instead
use a vague prior. As such, we set
\(\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})\), with fixed
precision \(\tau_\theta = 0.000001\) (or a standard deviation of
\(\sigma_\theta = 1000\)).

\hypertarget{model-specifications}{%
\subsubsection{Model specifications}\label{model-specifications}}

We considered eight models
(Table\textasciitilde{}\ref{tab:multinomial-models}) for \(\eta_{ita}\)
of the form
\(\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}\).
Observation random effects \(\theta_{ita}\) with a diffuse prior,
\(\mathcal{N}(0, 1000^2)\), were included in every model to ensure the
sample sizes \(m_{ita}\) were recovered exactly, as required for the
Poisson log-linear model to be equivalent to the multinomial logistic
regression. To capture age-specific proportion estimates for each
category \(k = 1, 2, 3^{+}\), we included category random effects
\(\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})\) and age-category random
effects \(\alpha_{ak} \sim \mathcal{N}(0, \tau_\alpha^{-1})\). Owing to
country-level heterogeneity in the data, we also included
country-category random effects
\(\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})\). We considered two
specifications, independent and identically distributed (IID) and Besag,
for the space-category \(\phi_{ik}\) random effects and two
specifications, IID and first order autoregressive (AR1), for the
year-category \(\gamma_{tk}\) random effects, as well as separable
space-year-category interactions \(\delta_{itk}\) with corresponding
Kronecker product structure. All random effect precision parameters
\(\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}\)
were given independent penalised complexity (PC) priors (Simpson et al.
2017) with base model \(\sigma = 0\) given by
\(p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)\)
where \(\nu = - \ln(0.01) / 2.5\) such that
\(\mathbb{P}(\sigma > 2.5) = 0.01\).

To ensure interpretable posterior inferences of random effect
contribution, we applied sum-to-zero constraints such that the
age-category, country-category, space-category and year-category random
effects did not alter overall category probabilities. For the
space-year-category random effects, we analogously applied sum-to-zero
constraints to maintain roles of the space-category and year-category
random effects. Together, these
were\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.}:

\begin{enumerate}
    \item Category $\sum_k \beta_k = 0$
    \item Age $\sum_a \alpha_{ak} = 0, \, \forall \, k$
    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
    \item Spatio-temporal $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
\end{enumerate}

\hypertarget{spatial-random-effects}{%
\paragraph{\texorpdfstring{Spatial random effects
\label{sec:spatial-random-effects}}{Spatial random effects }}\label{spatial-random-effects}}

The specifications we considered for the space-category random effects
were IID \(\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})\) and Besag
grouped by category \[
\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{1K}, \ldots \phi_{nK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
\] where the scaled structure matrix
\(\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}\) is
given by the Kronecker product of the scaled Besag structure matrix
\(\mathbf{R}^\star_b\) and the identity matrix \(\mathbf{I}\). Scaling
of the structure matrix to have generalised variance one ensures
interpretable priors may be placed on the precision parameter (Sørbye
and Rue 2014). We follow the further recommendations of
Freni-Sterrantino, Ventrucci, and Rue (2018) with regard to disconnected
adjacency graphs, singletons and constraints. The Besag structure matrix
\(\mathbf{R}_b\) is obtained by the precision matrix of the random
effects \(\mathbf{b} = (b_1, \ldots, b_n)^\top\) with the full
conditionals \begin{equation}
b_i \, | \, \mathbf{b}_{-i} \sim \N\left(\frac{\sum_{j: j \sim i} b_j}{n_{\delta i}}, \frac{1}{n_{\delta i}}\right),
\end{equation} where \(j \sim i\) if the districts \(A_i\) and \(A_j\)
are adjacent, and \(n_{\delta i}\) is the number of districts adjacent
to \(A_i\).

In preliminary testing, we tried excluding spatial random effects from
the model, but found that this negatively effected performance. We also
tried using the BYM2 model (Simpson et al. 2017) in place of the Besag,
but found that the proportion parameter posteriors tended to be highly
peaked at the value one. For simplicity and to avoid numerical issues,
by instead using Besag random effects we decided to fix this proportion
to one, rather than learn it.

\hypertarget{temporal-random-effects}{%
\paragraph{\texorpdfstring{Temporal random effects
\label{sec:temporal-random-effects}}{Temporal random effects }}\label{temporal-random-effects}}

The specifications we considered for the survey-category random effects
were IID \(\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})\) and AR1
grouped by category \[
\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{1K}, \ldots, \gamma_{T1}, \ldots, \gamma_{TK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
\] where the scaled structure matrix
\(\mathbf{R}^\star_\gamma = \mathbf{R}^\star_r \otimes \mathbf{I}\) is
given by the Kronecker product of a scaled AR1 structure matrix
\(\mathbf{R}^\star_r\) and the identity matrix \(\mathbf{I}\). The AR1
structure matrix \(\mathbf{R}_r\) is obtained by precision matrix of the
random effects \(\mathbf{r} = (r_1, \ldots, r_T)^\top\) specified by
\begin{align}
r_1 &\sim \left( 0, \frac{1}{1 - \rho^2} \right), \\
r_t &= \rho r_{t - 1} + \epsilon_t, \quad t = 2, \ldots, T, 
\end{align} where \(\epsilon_t \sim \mathcal{N}(0, 1)\) and
\(|\rho| < 1\). For the lag-one correlation parameter \(\rho\), we used
the PC prior, as derived by Sørbye and Rue (2017), with base model
\(\rho = 1\) and condition \(\mathbb{P}(\rho > 0 = 0.75)\). We chose a
base model corresponding to no change in behaviour over time, rather
than the alternative \(\rho = 0\) corresponding to no correlation in
behaviour over time, as we judged the former to be more plausible a
priori.

\hypertarget{spatio-temporal-random-effects}{%
\paragraph{\texorpdfstring{Spatio-temporal random effects
\label{sec:spatio-temporal-random-effects}}{Spatio-temporal random effects }}\label{spatio-temporal-random-effects}}

For each model including spatio-temporal random effects we used the
specification \begin{equation}
    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nTK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
\end{equation} where \(\mathbf{R}^\star_\delta\) is a Kronecker product
of the relevant space, time and category structure matrices. In
particular, for each of the four models including spatio-temporal
interactions, these matrices are

\begin{itemize}
\item
1x: No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
\item
2x: Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
\item
3x: Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
\item
4x: Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
\\
\end{itemize}

where the first, second and third elements of the product represent
space, time and category respectively, and the interaction type provided
in brackets is given according to the Knorr-Held (2000) framework.

\hypertarget{survey-weighted-likelihood}{%
\subsubsection{Survey weighted
likelihood}\label{survey-weighted-likelihood}}

The surveys we used utilise a complex design, in which each individual
has an unequal probability of being included in the sample. For example,
the DHS often employs a two-stage cluster design, first taking an urban
rural stratified sample of ennumeration areas, before selecting
households from each ennumeration area using systematic sampling. To
account for the survey design, we use a weighted pseudo-likelihood where
the observed counts \(y_{itak}\) are replaced by effective counts
\(y^\star_{itak}\) calculated using survey weights \(w_{itak}\). We
multiplied direct estimates produced using the \texttt{survey} package
\citep{JSSv009i08} by the Kish effective sample size
\citep{kish1965survey} \begin{equation}
    m^\star_{itak} = \left(\sum_{itak} w_{itak} \right)^2 / \sum_{itak} {w_{itak}}^2
\end{equation} to obtain \(y^\star_{itak}\). As these counts may not be
integers, the Poisson likelihood in
Equation\textasciitilde{}\eqref{eq:poisson} is inappropriate. Instead,
we used a generalised Poisson pseudo-likelihood
\(y^\star \sim \text{xPoisson}(\kappa)\), as implemented by
\texttt{family\ =\ "xPoisson"} in \texttt{R-INLA}, given by
\begin{equation}
    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right).
\end{equation}

\newpage

\hypertarget{prevalence-incidence-and-new-infections-reached-analysis}{%
\section{\texorpdfstring{Prevalence, incidence and new infections
reached analysis
\label{app:inc-inf}}{Prevalence, incidence and new infections reached analysis }}\label{prevalence-incidence-and-new-infections-reached-analysis}}

\hypertarget{calculation-of-prevalence-and-plhiv}{%
\subsection{Calculation of prevalence and
PLHIV}\label{calculation-of-prevalence-and-plhiv}}

We calculated HIV prevalence \(\rho_{iak}\) and number of people living
with HIV (PLHIV) \(H_{iak} = \rho_{iak} N_{iak}\) stratified according
to district, age group and risk group by disaggregation \begin{align}
    H_{ia} &= \sum_k H_{iak} = \sum_k \rho_{iak} N_{iak} \\
    &= \rho_{ia1} N_{ia1} + \rho_{ia1} \text{PR}_2 N_{ia2} + \rho_{ia1} \text{PR}_3 N_{ia3} + \rho_{ia1} \text{PR}_4 N_{ia4} \\
    &= \rho_{ia1} \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right).
\end{align} Risk group specific prevalence estimates are then given by
\begin{align}
    \rho_{ia1} &= H_{ia} / \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right), \\
    \rho_{ia2} &= \rho_{ia1} \text{PR}_2,\\
    \rho_{ia3} &= \rho_{ia1} \text{PR}_3,\\
    \rho_{ia4} &= \rho_{ia1} \text{PR}_4,
\end{align} which we evaluated using Naomi model estimates of PLHIV
\(H_{ia} = \rho_{ia} N_{ia}\), prevalence ratios \(\{\text{PR}_k\}\) as
described below, and risk group population sizes
\(N_{iak} = p_{iak} N_{ia}\) based on our 2018 risk group estimates
together with population size estimates from the Naomi model. To obtain
the prevalence ratios, we\ldots{}

\hypertarget{calculation-of-incidence-and-number-of-new-infections}{%
\subsection{Calculation of incidence and number of new
infections}\label{calculation-of-incidence-and-number-of-new-infections}}

Similarly, we calculated HIV incidence \(\lambda_{iak}\) and number of
new HIV infections \(I_{iak}\) stratified according to district, age
group and risk group by disaggregation \begin{align}
    I_{ia} &= \sum_k I_{iak} = \sum_k \lambda_{iak}N_{iak} \\
    &= 0 + \lambda_{ia2} N_{ia2} + \lambda_{ia3} N_{ia3} + \lambda_{ia4} N_{ia4} \\
    &= \lambda_{ia2} \left(N_{ia2}  + \text{RR}_{3} N_{ia3} + \text{RR}_4(\lambda_{ia}) N_{ia4}  \right).
\end{align} Risk group specific incidence estimates are then given by
\begin{align}
    \lambda_{ia1} &= 0, \\
    \lambda_{ia2} &= I_{ia} / \left(N_{ia2} + \text{RR}_{3} N_{ia3} + \text{RR}_4(\lambda_{ia}) N_{ia4}\right), \\
    \lambda_{ia3} &= \text{RR}_{3} \lambda_{ia2}, \\
    \lambda_{ia4} &= \text{RR}_4(\lambda_{ia}) \lambda_{ia2}.
\end{align} which we evaluated using Naomi model estimates of the number
of new HIV infections \(I_{ia} = \lambda_{ia} N_{ia}\), HIV infection
risk ratios \(\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}\) as given in
Table\textasciitilde{}\ref{tab:risk-categories}, and 2018 risk group
population sizes as above. The risk ratio \(\text{RR}_4(\lambda_{ia})\)
is defined as a function of general population incidence. Using these
estimates \(\{\lambda_{iak}\}\), the number of new HIV infections is
then \(I_{iak} = \lambda_{iak} N_{iak}\).

\hypertarget{analysis-of-new-infections-reached}{%
\subsection{Analysis of new infections
reached}\label{analysis-of-new-infections-reached}}

We calculated the number of new infections that would be reached
prioritising according to each possible stratification of the
population. As an illustration, for stratification by age, we aggregated
the number of new HIV infections and HIV incidence as such \begin{align}
    I_a &= \sum_{ik} I_{iak}, \\
    \lambda_a &= I_a / \sum_{ik} N_{iak}.
\end{align} Under this stratification, individuals in each age group
\(a\) would be prioritised according to the highest HIV incidence
\(\lambda_a\). We repeated this analysis for all \(2^3 = 8\) possible
combinations of stratification by location, age, and risk group.

\newpage

\hypertarget{the-global-aids-strategy-2021-2016-as-it-relates-to-agyw}{%
\section{The Global AIDS Strategy 2021-2016 as it relates to
AGYW}\label{the-global-aids-strategy-2021-2016-as-it-relates-to-agyw}}

\begin{footnotesize}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Prioritisation strata & Criterion \\ 
 \midrule
Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
High & 1-3\% incidence AND high-risk behaviour \\
Very high & $>$3\% incidence \\
\bottomrule
\end{tabularx}
\caption{Prioritisation strata.}
\label{tab:unaids-strategy-prioritisation}
\end{table}

\end{footnotesize}

\begin{footnotesize}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Intervention & Details \\ 
 \midrule
STI screening and treatment & (Remain to be filled in: describe targets and commitments in terms of each prioritisation strata) \\
PrEP use & (As above) \\
Access to PEP & (As above) \\
Comprehensive sexuality education & (As above) \\
Economic empowerment & (As above) \\
\bottomrule
\end{tabularx}
\caption{Targets and commitments.}
\label{tab:unaids-strategy-targets}
\end{table}

\end{footnotesize}

\newpage

\hypertarget{survey-questions-and-risk-group-classification}{%
\section{Survey questions and risk group
classification}\label{survey-questions-and-risk-group-classification}}

\hypertarget{survey-questions}{%
\subsection{Survey questions}\label{survey-questions}}

\begin{footnotesize}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Variable(s) & Description \\ 
 \midrule
\texttt{v501} & Current marital status of the respondent. \\
\texttt{v529} & Computed time since last sexual intercourse. \\
\texttt{v531} & Age at first sexual intercourse--imputed. \\
\texttt{v766b} & Number of sexual partners during the last 12 months (including husband). \\
\texttt{v767[a, b, c]} & Relationship with last three sexual partners. Options are: spouse, boyfriend not living with respondent, other friend, casual acquaintance, relative, commercial sex worker, live-in partner, other. \\
\texttt{v791a} & Had sex in return for gifts, cash or anything else in the past 12 months. Asked only to women 15-24 who are not in a union. \\
\bottomrule
\end{tabularx}
\caption{AIS, BAIS and DHS survey questions.}
\end{table}

\end{footnotesize}

\begin{footnotesize}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Variable(s) & Description \\ 
 \midrule
\texttt{part12monum} & Number of sexual partners during the last 12 months (including husband). \\
\texttt{part12modkr} & Reason for leaving \texttt{part12monum} blank. \\
\texttt{partlivew[1, 2, 3]} & Does the person you had sex with live in this household? \\
\texttt{partrelation[1, 2, 3]} & Relationship with last three sexual partners. Options are: husband, live-in partner, partner (not living with), ex-spouse/partner, friend/acquaintance, sex worker, sex worker client, stranger, other, don't know, refused. \\
\texttt{sellsx12mo} & Had sex for money and/or gifts in the last 12 months. \\
\texttt{buysx12mo} & Paid money or given gifts for sex in the last 12 months. \\
\bottomrule
\end{tabularx}
\caption{PHIA survey questions.}
\end{table}

\end{footnotesize}

\newpage

\subsection{Risk group classification based on survey questions}

\begin{figure}[h!]
    \centering
    \includegraphics{depends/category-flowchart.pdf}
    \caption{Flowchart describing allocation of respondents to risk groups.}
    \label{fig:category-flowchart}
\end{figure}

\newpage

\hypertarget{supplementary-figures}{%
\section{Supplementary figures}\label{supplementary-figures}}

\newpage

\hypertarget{supplementary-tables}{%
\section{Supplementary tables}\label{supplementary-tables}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-baker1994multinomial}{}}%
Baker, Stuart G. 1994. {``{The multinomial-Poisson transformation}.''}
\emph{Journal of the Royal Statistical Society: Series D (The
Statistician)} 43 (4): 495--504.

\leavevmode\vadjust pre{\hypertarget{ref-eaton2021naomi}{}}%
Eaton, Jeffrey W., Laura Dwyer-Lindgren, Steve Gutreuter, Megan
O'Driscoll, Oliver Stevens, Sumali Bajaj, Rob Ashton, et al. 2021.
{``{Naomi: a new modelling tool for estimating HIV epidemic indicators
at the district level in sub-Saharan Africa}.''} \emph{Journal of the
International AIDS Society} 24 (S5): e25788.

\leavevmode\vadjust pre{\hypertarget{ref-freni2018note}{}}%
Freni-Sterrantino, Anna, Massimo Ventrucci, and Håvard Rue. 2018. {``A
Note on Intrinsic Conditional Autoregressive Models for Disconnected
Graphs.''} \emph{Spatial and Spatio-Temporal Epidemiology} 26: 25--34.

\leavevmode\vadjust pre{\hypertarget{ref-knorr2000bayesian}{}}%
Knorr-Held, Leonhard. 2000. {``Bayesian Modelling of Inseparable
Space-Time Variation in Disease Risk.''} \emph{Statistics in Medicine}
19 (17-18): 2555--67.

\leavevmode\vadjust pre{\hypertarget{ref-lee2017poisson}{}}%
Lee, Jarod YL, Peter J Green, and Louise M Ryan. 2017. {``{On the
{`Poisson Trick'} and its Extensions for Fitting Multinomial Regression
Models}.''} \emph{arXiv Preprint arXiv:1707.08538}.

\leavevmode\vadjust pre{\hypertarget{ref-mccullagh1989generalized}{}}%
McCullagh, Peter, and John A Nelder. 1989. \emph{Generalized Linear
Models}. Routledge.

\leavevmode\vadjust pre{\hypertarget{ref-simpson2017penalising}{}}%
Simpson, Daniel, Håvard Rue, Andrea Riebler, Thiago G Martins, and
Sigrunn H Sørbye. 2017. {``Penalising Model Component Complexity: A
Principled, Practical Approach to Constructing Priors.''}
\emph{Statistical Science} 32 (1): 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-sorbye2014scaling}{}}%
Sørbye, Sigrunn Holbek, and Håvard Rue. 2014. {``{Scaling intrinsic
Gaussian Markov random field priors in spatial modelling}.''}
\emph{Spatial Statistics} 8: 39--51.

\leavevmode\vadjust pre{\hypertarget{ref-sorbye2017penalised}{}}%
---------. 2017. {``Penalised Complexity Priors for Stationary
Autoregressive Processes.''} \emph{Journal of Time Series Analysis} 38
(6): 923--35.

\leavevmode\vadjust pre{\hypertarget{ref-stevens2022estimating}{}}%
Stevens, Oliver, Keith Sabin, Sonia Arias Garcia, Kalai Willis, Abu
Abdul-Quader, Anne McIntyre, Frances Cowan, et al. 2022. {``{Estimating
key population size, HIV prevalence, and ART coverage for sub-Saharan
Africa at the national level}.''}

\leavevmode\vadjust pre{\hypertarget{ref-wamoyi2016transactional}{}}%
Wamoyi, Joyce, Kirsten Stobeanau, Natalia Bobrova, Tanya Abramsky, and
Charlotte Watts. 2016. {``{Transactional sex and risk for HIV infection
in sub-Saharan Africa: a systematic review and meta-analysis}.''}
\emph{Journal of the International AIDS Society} 19 (1): 20992.

\end{CSLReferences}

\end{document}

### 2022-06-04 src/docs_paper/paper.Rmd
Progress moving paper and appendix to markdown (this will be a fun plan activity!) #128

@@
     email: ath19@ic.ac.uk
-    affiliation: Imperial College London
+    affiliation: A
     corresponding: ath19@ic.ac.uk
 address:
-  - code: Imperial College London
-    address: Department of Mathematics
+  - code: A
+    address: Department of Mathematics, Imperial College London
+  - code: B
+    address: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London
+  - code: C
+    address: Department of Medical Social Sciences, Feinberg School of Medicine, Northwestern University
+  - code: D
+    address: Harvard T. H. Chan School of Public Health, Harvard University
+  - code: E
+    address: Joint United Nations Programme on HIV/AIDS, Geneva, Switzerland
+  - code: F
+    address: Department of Computer Science, University of Oxford
 abstract: |
   Abstract
-
 author_summary: |
@@
 output: rticles::plos_article
+header-includes:
+- \usepackage{tabularx}
 # plos.csl can be download and used locally
@@
 
-\subsection{Prevalence, incidence and new infections}
+## Prevalence, incidence and new infections
 
@@
 
+# Results
+
+## Data
+
+We included 47 surveys in our analysis (Figure, Table), with a total sample size of 284,168 women aged 15-29 years (106,397 aged 15-19 years, 95,253 aged 20-24 years, and 82,518 aged 25-29 years).
+Of these, 13 surveys included a specific transactional sex question, with corresponding sample size 85,760 (31,752 aged 15-19 years, 29,167 aged 20-24 years, and 24,841 aged 25-29 years).
+The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Figures).
+
+## Model selection
+
+The best fitting multinomial regression model included correlated spatial effects and first-order autoregressive temporal effects, but not spatio-temporal interactions.
+The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
+Model performance according to the CPO criteria for each of the considered models is provided in the appendix (Figures, Tables).
+
+Posterior mean estimates for our final model in the most recent year, 2018, are shown as choropleths (Figure) and dotplots (Figure).
+In the following results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
+Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
+
+# Discussion
+
+We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with pressing HIV prevention requirements.
+Our estimates will enable country and district-level planners to differentiate prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
+
+<!-- Comment about how novel this would be if implemented -->
+
+By considering all possible risk stratification strategies, we showed that successful implementation of a risk-stratified approach would allow substantially more new infections to be found before they occur.
+A considerable proportion of these new infections are among FSW, supporting the case for HIV programming efforts focused on key population groups [@baral2012burden].
+We showed that there is substantial variation in the importance of prioritisation by age, location and behaviour within each country.
+This highlights the importance of understanding and tailoring HIV prevention efforts to country-specific contexts.
+By standardising our analysis across all 13 countries, we showed the additional efficiency benefits of resource allocation between countries.
+
+We found a geographic delineation in the proportion of women cohabiting between southern and eastern Africa, calling attention to a divide attributable to many cultural, social and economic factors.
+The delineation does not represent a boundary between predominately Christian and Muslim populations, which is further north.
+We also note that the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique, reflecting existing concerns [@unicef].
+
+Our modelled estimates improve upon direct survey results for three reasons.
+First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Figure).
+Third, we provide estimates in all settings, including districts without any survey clusters as well as years without surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
+
+To the best of our knowledge, the only previous research to geographically map AGYW HIV risk groups is @brugh2021characterizing, who use biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups.
+
+This work serves as a case-study in how to use the multinomial-Poisson transformation to efficiently specify and fit multinomial spatio-temporal models in `R-INLA`.
+We used Kronecker products over Gaussian Markov random fields to define appropriate category-specific spatio-temporal random effects.
+
+<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@kinh2021trends]. -->
+
+## Limitations
+
+Our analysis of the number of infections that could be reached by each risk stratification strategy was based on simplifying assumptions and should be interpreted as illustrating the potentially obtainable benefits, rather than benefits that would be accrued from any specific intervention strategy.
+Factors we did not consider include the greater administrative burden of more complex strategies, variation in difficulty or feasibility of reaching individuals in each strata, variation in the range or effectiveness of interventions by strata, and changes in strata membership that may occur during the course of a year.
+
+<!-- Dependence of FSW on clustering and migration. -->
+
+Under-reporting of higher risk sexual behaviours amongst AGYW could affect the validity of our estimates.
+Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive} or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @kinh2021trends].
+For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
+Furthermore, our FSW estimates do not overcome the difficulties of sampling hard to reach groups; in particular, the possibility of being excluded from household sampling frames.
+
+<!-- I think the Nnko 2004 is a good cite. For biases in age at first sex as folks age: -->
+<!-- https://pubmed.ncbi.nlm.nih.gov/15572637/ -->
+<!-- https://pubmed.ncbi.nlm.nih.gov/19307342/ -->
+<!-- Then these are all about how methodological approaches can result in different estimates (I think): -->
+<!-- Hewett PC, Mensch BS, Erulkar AS.
+Consistency in the reporting of sexual behaviour by adolescent girls in Kenya: a comparison of interviewing methods.
+Sex Transm Infect.
+2004;80 Suppl 2:ii43-8.
+-->
+<!-- Cleland J, Boerma JT, Carael M, Weir SS. Monitoring sexual behaviour in general populations: a synthesis of lessons of the past decade. Sex Transm Infect. 2004;80 Suppl 2:ii1-7. -->
+<!-- Helleringer S, Kohler HP, Kalilani-Phiri L, Mkandawire J, Armbruster B.
+The reliability of sexual partnership histories: implications for the measurement of partnership concurrency during surveys.
+AIDS.
+2011;25(4):503-11.Mensch BS, Hewett PC, Erulkar AS.
+The reporting of sensitive behavior by adolescents: a methodological experiment in Kenya.
+Demography.
+2003;40(2):247-68.
+-->
+<!-- Then there’s the option of discussing validity of self-reported sexual behaviour based on biomarker validation (e.g.
+https://academic.oup.com/ofid/article/6/2/ofz010/5285444, there are more like this) but I’m not super familiar with this literature to pull a reference that would be appropriate.
+-->
+
+The risk groups we analysed did not consider other important characteristics, such as condom usage or partner-specific risk, which contribute to heterogeneity within each risk group.
+Although the number of risk groups considered could be increased, capturing more of this heterogeneity, this inclination must be balanced with the benefits of parsimony.
+Our approach assumed that within risk group heterogeneity is small enough that the categories are meaningfully consistent across contexts.
+Additionally, the categories we used are not immediately actionable.
+For example, a program is designed to reach AGYW who are cohabiting, then it is not clear how to find these individuals within a community.
+As such it may be preferable to select risk groups based more amenable attributes, such as attendance of a particular service or facility.
+% e.g. school, healthcare
+
+Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the wider population of all adults of both sexes.
+By limiting our consideration to this group we didn't account for XX.X\% of all new infections [CITE: Katie, others].
+% Obtaining population size estimates for sexual risk behaviour in the general population is a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
+
+<!-- Likely over-reporting of never having had sex in the past year by young women, if we apply an RR of 0 to this group, to balance out the overall incidence rate, might be over-attributing risk to the other groups.
+-->
+<!-- Defining condom usage is challenging, particularly for those with multiple partners, and reporting is likely biased due to social desirability. -->
+<!-- Additionally, consistent condom usage is rare amongst those cohabiting, and as such likely only relevant for those with non-regular sexual partners.  -->
+
+## Conclusion
+
+We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk categories at a district-level in 13 priority countries.
+Using these estimates, we performed an analysis of the number of infections that could be reached by prioritisation based upon location, age and behaviour.
+Though subject to limitations, our results quantify the crucial importance of reaching the AGYW at highest risk.
+
+## Funding
+
+AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).
+AH, VKN, KAR, JWE were supported by the Bill and Melinda Gates Foundation (OPP1190661, OPP1164897).
+TMW was supported by Imperial College London (President's PhD Scholarship).
+SF was supported by the EPSRC (EP/V002910/1).
+JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664).
+
+This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
+
+## Disclaimer
+
+The findings and conclusions in this manuscript are those of the authors and do not necessarily represent the official position of the funding agencies.
+
 # References {#references .unnumbered}

### 2022-06-05 src/docs_paper/appendix.Rmd
Work on the manuscript #128

@@
 
-# Statistical modelling of risk group proportions
+# Modelling of risk group proportions
 
@@
 
-We index the four risk groups given in Table by $k \in \{1, 2, 3, 4\}$ and we denote being in either the third or fourth risk group by $k = 3^{+}$.
-Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts.
-For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider a multinomial random vector
+We index the four risk groups given in Table X by $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
+Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts according to Table X.
+For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider the multinomial random vector
 \begin{equation}
-    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}).
+    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
 \end{equation}
-The number of women in risk group $k$ is $y_{itak}$ and the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, where $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
-To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial; @lee2017poisson]
+where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
+
+To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial] of the form
 \begin{align}
@@
 \end{align}
-for particular choice of the linear predictor $\eta_{itak}$, described in more detail in Section.
-
-To estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
+for suitable choice of the linear predictor $\eta_{itak}$, which we describe in more detail in Section.
+Then, to estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
 \begin{align}
@@
 \end{align}
-for choice of the linear predictor $\eta_{ia}$, described in more detail in Section.
+again for suitable choice of the linear predictor $\eta_{ia}$, which we describe in more detail in Section.
 This approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
-As all such surveys occurred in 2013-2018, $q_{ia}$ was assumed to be constant over time.
+As all such surveys occurred in 2013-2018, in the logistic regresion model $q_{ia}$ was assumed to be constant over time.
 
-To quantify uncertainty from our model, we took posterior samples $s = 1, \ldots, 1000$ from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
-Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via
+To quantify uncertainty from our model, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via the equations
 \begin{align*}
@@
 \end{align*}
-As transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that the population size estimates for FSW aggregated to a national level matched those of @stevens2022estimating.
+Next, as transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match externally produced age-country specific FSW population size estimates, which we calculate in Section.
 In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
@@
 
-The multinomial-Poisson transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
+The transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
 \begin{align}
     y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
-    \log(\kappa_{itak}) &= \eta_{itak},
+    \log(\kappa_{itak}) &= \eta_{itak}.
 \end{align}
-for suitable choice of linear predictor $\eta_{itak}$.
-Category probabilities are then obtained by applying the softmax function to the linear predictor as follows
+Category probabilities are obtained by applying the softmax function to the linear predictor as follows
 \begin{equation}
@@
 \end{equation}
-In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random rather than fixed as they would be in the multinomial logistic regression model.
-In particular, following Equation, the sample sizes follow a Poisson distribution
+In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random, rather than fixed as they would be in the multinomial logistic regression model, and follow a Poisson distribution
 \begin{equation}
@@
 
-We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form $\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}$.
-Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for the Poisson log-linear model to be equivalent to the multinomial logistic regression.
-To capture age-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and age-category random effects $\alpha_{ak} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
-Owing to country-level heterogeneity in the data, we also included country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+\begin{table}[htb]
+\small
+\centering
+\begin{tabularx}{\textwidth}{lllllll}
+\midrule
+Model ID & Category ($\beta_k$) & Age ($\alpha_{ak}$) & Country ($\zeta_{ck}$) & Spatial ($\phi_{ik}$) & Temporal ($\gamma_{tk}$) & Spatio-temporal ($\delta{itk}$) \\
+\midrule
+M1 & IID & IID & IID & IID & IID & \xmark \\
+M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\
+M2 & IID & IID & IID & Besag & IID & \xmark \\
+M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\
+M3 & IID & IID & IID & IID & AR1 & \xmark \\
+M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\
+M4 & IID & IID & IID & Besag & AR1 & \xmark \\
+M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\
+\midrule
+\end{tabularx}
+\caption{The multinomial regression models that we considered. Observation random effects $\theta_{ita}$ are omitted from this table.}
+\label{tab:multinomial-models}
+\small
+\end{table}
+
+We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
+$$
+\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
+$$
+Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for equivalency of the models.
+To capture country-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We allowed heterogeneity in risk group proportions by age by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
 We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects, as well as separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure.
@@
 
-To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the age-category, country-category, space-category and year-category random effects did not alter overall category probabilities.
+To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
 For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
@@
     \item Category $\sum_k \beta_k = 0$
-    \item Age $\sum_a \alpha_{ak} = 0, \, \forall \, k$
     \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
+    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, k \quad \text{TODO}$,
     \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
@@
 To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y_{itak}$ are replaced by effective counts $y^\star_{itak}$ calculated using survey weights $w_{itak}$.
-We multiplied direct estimates produced using the `survey` package \citep{JSSv009i08} by the Kish effective sample size \citep{kish1965survey}
+We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
 \begin{equation}
@@
 \midrule
-L1 & Constant & IID & IID & IID & None \\
-L2 & Constant & IID & IID & Besag & None \\
+L1 & Constant & IID & IID & IID & \xmark \\
+L2 & Constant & IID & IID & Besag & \xmark \\
 L3 & Constant & IID & IID & IID & \texttt{cfswever} \\
@@
 \caption{The logistic regression models that were considered.
-\texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months \citep{hodgins2022population}.}
+\texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months.}
 \label{tab:logistic-models}
@@
 We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.
-To aid estimation with sparse data, we also considered national-level covariates for the proportion of men who have paid for sex ever \texttt{cfswever} or in the last twelve months \texttt{cfswrecent}, available from \citet{hodgins2022population}.
-For both random effect precision parameters $\tau \in \{\tau_\alpha, \tau_\zeta\}$ as before we use the PC prior with base model $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$.
+To aid estimation with sparse data, we also considered national-level covariates for the proportion of men who have paid for sex ever \texttt{cfswever} or in the last twelve months \texttt{cfswrecent}, available from @hodgins2022population.
+For both random effect precision parameters $\tau \in \{\tau_\alpha, \tau_\zeta\}$ we used the PC prior with base model $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$.
 For the regression parameters $\beta \in \{\beta_\texttt{cfswever}, \beta_\texttt{cfswrecent}\}$ we used the prior $\beta \sim \mathcal{N}(0, 2.5^2)$.
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{figures/fsw-logit-information-criteria.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.pdf}}
     \caption{Logistic regression model performance.}
@@
 \newpage
+
+# Age-country FSW population size estimates
+
+We obtained estimates of adult (15-49) FSW population size from @stevens2022estimating.
 
@@
 
-# Supplementary figures
-
-\newpage
-
-# Supplementary tables
-
-\newpage
-
 # References {#references .unnumbered}

### 2022-06-05 src/docs_paper/paper.Rmd
Work on the manuscript #128

@@
     email: ath19@ic.ac.uk
-    affiliation: A
+    affiliation: [A, B]
     corresponding: ath19@ic.ac.uk
+  - name: Kathryn A. Risher 
+    affiliation: [C, B]
+  - name: Van Kính Nguyen
+    affiliation: B
+  - name: Oliver Stevens
+    affiliation: B
+  - name: Katherine M. Jia
+    affiliation: D
+  - name: Timothy M. Wolock
+    affiliation: [A, B]
+  - name: Lycias Zembe
+    affiliation: E
+  - name: Ian Wanyeki
+    affiliation: E
+  - name:  Mary Mahy
+    affiliation: E
+  - name: Clemens Benedikt
+    affiliation: E
+  - name: Seth R. Flaxman
+    affiliation: F
+  - name: Jeff W. Eaton
+    affiliation: B
 address:
@@
 abstract: |
-  Abstract
+  **Background:**
+  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for   HIV prevention and recommends differentiating intervention portfolios geographically based on local HIV incidence   and individual risk behaviours.
+
+  **Methods:**
+  We analysed 47 geospatially referenced national household surveys conducted between 1999-2018 across 13 Global   Fund priority countries in sub-Saharan Africa.
+  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual partnerships.
+  We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year and five-year age group.
+  We then assessed the efficiency of prioritising interventions according to these risk groups.
+
+  **Results:**
+  Data consisted of $291,465$ female survey respondents aged 15-29.
+  Risk group proportions varied substantially across age groups (44.6\% of variation), countries (28.7\%), and between districts within each country (20.6\%), but changed little over time (1.6\%).
+  Among women aged 20-29, we found a geographic delineation, north of which in eastern Africa, cohabiting (69.5\%) is more common than non-regular partner(s) (13.3\%), and south of which, non-regular partner(s) (52.6\%) are more common than cohabiting (27.9\%).
+  Prioritisation based on behavioural risk, on top of location and age based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from 20.1\% to 10.4\%.
+  Female sex workers were 2.4\% of the at risk population but 15.9\% of all new infections.
+
+  **Conclusions:**
+  Our risk group estimates provide data for HIV programmes to implement a differentiated prevention approach and set targets according to the Global AIDS Strategy.
+  Successfully implementing this approach would result in finding substantially more infections, particularly among female sex workers.
 author_summary: |
@@
 - \usepackage{tabularx}
-# plos.csl can be download and used locally
-csl: http://www.zotero.org/styles/plos
+# # plos.csl can be download and used locally
+# csl: http://www.zotero.org/styles/plos
 ---
@@
 
-In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are XX.X\% of the population but XX.X\% of new HIV infections [@unaids2021update].
-HIV incidence amongst AGYW is X.X times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
+In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r "num"`\% of the population but `r "num"`\% of new HIV infections [@unaids2021update].
+HIV incidence amongst AGYW is `r "num"` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
 AGYW have therefore been identified as a priority population for HIV primary prevention, and significant investments have been made in prevention programming [@saul2018dreams; @global2018measurement].
@@
 
-We included 47 surveys in our analysis (Figure, Table), with a total sample size of 284,168 women aged 15-29 years (106,397 aged 15-19 years, 95,253 aged 20-24 years, and 82,518 aged 25-29 years).
-Of these, 13 surveys included a specific transactional sex question, with corresponding sample size 85,760 (31,752 aged 15-19 years, 29,167 aged 20-24 years, and 24,841 aged 25-29 years).
+We included 47 surveys in our analysis (Figure, Table), with a total sample size of `r "num"` women aged 15-29 years (`r "num"` aged 15-19 years, `r "num"` aged 20-24 years, and `r "num"` aged 25-29 years).
+Of these, 13 surveys included a specific transactional sex question, with corresponding sample size `r "num"` (`r "num"` aged 15-19 years, `r "num"` aged 20-24 years, and `r "num"` aged 25-29 years).
 The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
@@
 Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
+
+## Spatial, temporal and age trends
+
+In most districts (`r "num"`\%; 95\% credible interval [CI] `r "num"`--`r "num"`\%) adolescent girls aged 15-19 were not sexually active.
+The exception was Mozambique, where the majority (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) were sexually active in the past year and close to a third (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) were cohabiting with a partner.
+
+In the 20-24 and 25-29 year age groups, the majority (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) of women were either cohabiting or had non-regular partner(s).
+Countries in east and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r "num"`\%, as compared with `r "num"`\% with non-regular partner[s]) and countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular partner(s) (`r "num"`\%, as compared with `r "num"`\% cohabiting).
+There was a clear geographic delineation along the border of Mozambique, through the interior of Zimbabwe and along the border of Zambia.
+
+The median proportion of FSW nationally was `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) for the 15-19 age group, compared with $2.4\%$ (95\% CI `r "num"`--`r "num"`\%) and `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) for the 20-24 and 25-29 age groups respectively.
+This age pattern, reflecting the lower proportion sexually active among those aged 15-19 years, was the foremost effect of adjusting our estimates to match [@johnston2022deriving]; in contrast, our initial estimates of transactional sex were close to constant by age (Figure~\ref{fig:fsw-within-between-country-variation}).
+
+##
+
+Age explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) of the variation in risk group proportions, country explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%), and district explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%).
+The temporal effects only explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) of variation, indicating very little change in risk group proportions over time, with the remaining `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) attributable to the category random effects.
+We observed similar variance decomposition results fitting each country individually (Figure~\ref{fig:aaa-variance-proportions}) or using other model specifications.
+
+<!-- Can you please write another paragraph here calling out some examples of the amount of variation? -->
+<!-- Awaiting additional results: https://github.com/athowes/multi-agyw/issues/95 -->
+
+## Infections reached
+
+For any given fraction of AGYW prioritised, substantially more new infections were reached by strategies that included behavioural risk stratification.
+Reaching half of all new infections required reaching 20.1\% of the population when stratifying by area and age, but only 10.4\% when behavioural stratification was included (Figure~\ref{fig:infections-reached}).
+The majority of this benefit came from reaching FSW, who were 2.4\% of the population but 15.9\% of all new infections.
+
+Efficiency was reduced if prioritisation was done separately by country.
+On average, reaching half of new infections in a country required reaching 15.7\% (range 7.8-23.4\%) of the population when stratifying by area and age, reducing to 5.1\% (range 1.3-9.2\%) when behaviour was included.
+The importance of stratifying risk upon age, location and behaviour within a country varied (Figure~\ref{fig:infections-reached-country-1}--Figure~\ref{fig:infections-reached-country-13}), analogous to the varying contribution of each to the total variance (Section~\ref{sec:variance-decomp}).
+For example, FSW in Tanzania were estimated to be 5.3\% of the population and close to half (41.4\%) of all new infections, whereas FSW in Namibia were just 0.3\% of the population and 2.7\% of all new infections.
 
@@
 Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the wider population of all adults of both sexes.
-By limiting our consideration to this group we didn't account for XX.X\% of all new infections [CITE: Katie, others].
+By limiting our consideration to this group we didn't account for `r "num"`\% of all new infections [CITE: Katie, others].
 % Obtaining population size estimates for sexual risk behaviour in the general population is a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.

### 2022-06-05 src/docs_paper/tables-figures.Rmd
Work on the manuscript #128

---
title: Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent
  girls and young women across 13 priority countries in sub-Saharan Africa"
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: preamble.tex
bibliography: citations.bib
---

\newpage

# Data

\begin{longtable}{rlrcrrrr}
\toprule
\multicolumn{1}{l}{} &  &  &  & \multicolumn{4}{c}{Sample size} \\ 
\cmidrule(lr){5-8}
\multicolumn{1}{l}{} & Type & Year & Transactional sex question & 15-19 & 20-24 & 25-29 & Total \\ 
\midrule
\multicolumn{1}{l}{Botswana} \\ 
\midrule
 & BAIS & 2013 & \cmark & 557 & 588 & 649 & 1794 \\ 
Total &  &  &  & $557$ & $588$ & $649$ & $1794$ \\ 
\midrule
\multicolumn{1}{l}{Cameroon} \\ 
\midrule
 & DHS & 2004 & \xmark & 2675 & 2207 & 1732 & 6614 \\ 
 & DHS & 2011 & \xmark & 3588 & 3115 & 2655 & 9358 \\ 
 & PHIA & 2017 & \xmark & 2620 & 2339 & 2259 & 7218 \\ 
 & DHS & 2018 & \cmark & 3349 & 2463 & 2345 & 8157 \\ 
Total &  &  &  & $12232$ & $10124$ & $8991$ & $31347$ \\ 
\midrule
\multicolumn{1}{l}{Kenya} \\ 
\midrule
 & DHS & 2003 & \xmark & 1819 & 1709 & 1391 & 4919 \\ 
 & DHS & 2008 & \xmark & 1767 & 1743 & 1419 & 4929 \\ 
 & DHS & 2014 & \xmark & 2861 & 2534 & 2858 & 8253 \\ 
Total &  &  &  & $6447$ & $5986$ & $5668$ & $18101$ \\ 
\midrule
\multicolumn{1}{l}{Lesotho} \\ 
\midrule
 & DHS & 2004 & \xmark & 1761 & 1455 & 1026 & 4242 \\ 
 & DHS & 2009 & \xmark & 1833 & 1543 & 1194 & 4570 \\ 
 & DHS & 2014 & \xmark & 1537 & 1292 & 1067 & 3896 \\ 
 & PHIA & 2017 & \cmark & 1156 & 1202 & 1054 & 3412 \\ 
Total &  &  &  & $6287$ & $5492$ & $4341$ & $16120$ \\ 
\midrule
\multicolumn{1}{l}{Mozambique} \\ 
\midrule
 & AIS & 2009 & \xmark & 1031 & 1106 & 987 & 3124 \\ 
 & DHS & 2011 & \xmark & 2932 & 2299 & 2206 & 7437 \\ 
 & AIS & 2015 & \xmark & 1552 & 1389 & 1080 & 4021 \\ 
Total &  &  &  & $5515$ & $4794$ & $4273$ & $14582$ \\ 
\midrule
\multicolumn{1}{l}{Malawi} \\ 
\midrule
 & DHS & 2000 & \xmark & 2914 & 2998 & 2358 & 8270 \\ 
 & DHS & 2004 & \xmark & 2407 & 2823 & 2135 & 7365 \\ 
 & DHS & 2010 & \xmark & 5031 & 4387 & 4309 & 13727 \\ 
 & DHS & 2015 & \cmark & 5273 & 5094 & 3976 & 14343 \\ 
 & PHIA & 2016 & \cmark & 1646 & 1934 & 1511 & 5091 \\ 
Total &  &  &  & $17271$ & $17236$ & $14289$ & $48796$ \\ 
\midrule
\multicolumn{1}{l}{Namibia} \\ 
\midrule
 & DHS & 2000 & \xmark & 1427 & 1313 & 1098 & 3838 \\ 
 & DHS & 2006 & \xmark & 2203 & 1869 & 1544 & 5616 \\ 
 & DHS & 2013 & \xmark & 1852 & 1709 & 1481 & 5042 \\ 
 & PHIA & 2017 & \cmark & 1491 & 1525 & 1370 & 4386 \\ 
Total &  &  &  & $6973$ & $6416$ & $5493$ & $18882$ \\ 
\midrule
\multicolumn{1}{l}{Eswatini} \\ 
\midrule
 & DHS & 2006 & \xmark & 1265 & 1027 & 731 & 3023 \\ 
 & PHIA & 2017 & \xmark & 1031 & 895 & 811 & 2737 \\ 
Total &  &  &  & $2296$ & $1922$ & $1542$ & $5760$ \\ 
\midrule
\multicolumn{1}{l}{Tanzania} \\ 
\midrule
 & AIS & 2003 & \xmark & 1466 & 1377 & 1270 & 4113 \\ 
 & AIS & 2007 & \xmark & 2137 & 1676 & 1509 & 5322 \\ 
 & DHS & 2010 & \xmark & 2221 & 1860 & 1613 & 5694 \\ 
 & AIS & 2012 & \xmark & 2474 & 1923 & 1815 & 6212 \\ 
 & PHIA & 2016 & \cmark & 2999 & 2845 & 2521 & 8365 \\ 
Total &  &  &  & $11297$ & $9681$ & $8728$ & $29706$ \\ 
\midrule
\multicolumn{1}{l}{Uganda} \\ 
\midrule
 & DHS & 2000 & \xmark & 1687 & 1541 & 1326 & 4554 \\ 
 & DHS & 2006 & \xmark & 1948 & 1660 & 1404 & 5012 \\ 
 & AIS & 2011 & \xmark & 2451 & 2164 & 1921 & 6536 \\ 
 & DHS & 2011 & \xmark & 2025 & 1664 & 1614 & 5303 \\ 
 & DHS & 2016 & \cmark & 4276 & 3782 & 3014 & 11072 \\ 
 & PHIA & 2016 & \xmark & 3289 & 3059 & 2574 & 8922 \\ 
\midrule 
Total &  &  &  & $15676$ & $13870$ & $11853$ & $41399$ \\ 
\midrule
\multicolumn{1}{l}{South Africa} \\ 
\midrule
 & DHS & 2016 & \cmark & 1505 & 1408 & 1397 & 4310 \\ 
Total &  &  &  & $1505$ & $1408$ & $1397$ & $4310$ \\ 
\midrule
\multicolumn{1}{l}{Zambia} \\ 
\midrule
 & DHS & 2007 & \xmark & 1598 & 1405 & 1373 & 4376 \\ 
 & DHS & 2013 & \xmark & 3685 & 3036 & 2789 & 9510 \\ 
 & PHIA & 2016 & \cmark & 2120 & 2045 & 1619 & 5784 \\ 
 & DHS & 2018 & \cmark & 3112 & 2687 & 2166 & 7965 \\ 
Total &  &  &  & $10515$ & $9173$ & $7947$ & $27635$ \\ 
\midrule
\multicolumn{1}{l}{Zimbabwe} \\ 
\midrule
 & DHS & 1999 & \xmark & 1467 & 1230 & 1011 & 3708 \\ 
 & DHS & 2005 & \xmark & 2128 & 1943 & 1438 & 5509 \\ 
 & DHS & 2010 & \xmark & 1963 & 1796 & 1679 & 5438 \\ 
 & DHS & 2015 & \cmark & 2154 & 1777 & 1646 & 5577 \\ 
 & PHIA & 2016 & \cmark & 2114 & 1817 & 1573 & 5504 \\ 
Total &  &  &  & $9826$ & $8563$ & $7347$ & $25736$ \\ 
\midrule 
\midrule 
Total &  &  &  & $106397$ & $95253$ & $82518$ & $284168$ \\ 
\bottomrule
\caption{All surveys that we used in our analysis.}
\label{tab:surveys-used}
\end{longtable}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{lX}
\toprule
Survey & Exclusion reason \\ 
 \midrule
MOZ2003DHS & No GPS coordinates available to place survey clusters within districts. \\
TZA2015DHS & Insufficient sexual behaviour questions. \\
UGA2004AIS & Unable to download region boundaries. \\
ZMB2002DHS & No GPS coordinates available to place survey clusters within districts. \\
\bottomrule
\end{tabularx}
\label{tab:surveys-excluded}
\caption{All surveys excluded from our analysis.}
\end{table}

\clearpage

# HIV incidence

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Botswana.}
    \label{fig:incidence-district-sexbehav-1}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Cameroon.}
    \label{fig:incidence-district-sexbehav-2}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Kenya.}
    \label{fig:incidence-district-sexbehav-3}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Lesotho.}
    \label{fig:incidence-district-sexbehav-4}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Mozambique.}
    \label{fig:incidence-district-sexbehav-5}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Malawi.}
    \label{fig:incidence-district-sexbehav-6}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Namibia.}
    \label{fig:incidence-district-sexbehav-7}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Eswatini.}
    \label{fig:incidence-district-sexbehav-8}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Tanzania.}
    \label{fig:incidence-district-sexbehav-9}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Uganda.}
    \label{fig:incidence-district-sexbehav-10}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in South Africa.}
    \label{fig:incidence-district-sexbehav-11}
\end{figure}

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/incidence-district-sexbehav.pdf}}
    \caption{District level incidence for each of the risk groups in 2018 in Zambia.}
    \label{fig:incidence-district-sexbehav-12}
\end{figure}

<!-- \begin{figure}[h] -->
<!--     \centering -->
<!--     \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}} -->
<!--     \caption{District level incidence for each of the risk groups in 2018 in Zimbabwe.} -->
<!--     \label{fig:incidence-district-sexbehav-13} -->
<!-- \end{figure} -->

\clearpage

# References {#references .unnumbered}

### 2022-06-05 src/docs_paper/script.R

@@ -3,3 +3,4 @@
 
 rmarkdown::render("paper.Rmd")
 rmarkdown::render("appendix.Rmd")
+rmarkdown::render("tables-figures.Rmd")

### 2022-06-05 src/docs_paper/tables-figures.Rmd
Include gt in .yml and add table to .Rmd #128

@@
 \bottomrule
-\caption{All surveys that we used in our analysis.}
+\caption{All surveys that we used in our analysis and their sample sizes.}
 \label{tab:surveys-used}
@@
 \end{table}
+
+\newpage
+
+\begin{longtable}{lrr}
+\toprule
+Country & Number of areas & Analysis level \\ 
+\midrule
+Botswana & 27 & 3 \\ 
+Cameroon & 58 & 2 \\ 
+Kenya & 47 & 2 \\ 
+Lesotho & 10 & 1 \\ 
+Mozambique & 161 & 3 \\ 
+Malawi & 33 & 5 \\ 
+Namibia & 38 & 2 \\ 
+Eswatini & 4 & 1 \\ 
+Tanzania & 195 & 4 \\ 
+Uganda & 136 & 3 \\ 
+South Africa & 52 & 2 \\ 
+Zambia & 116 & 2 \\ 
+Zimbabwe & 63 & 2 \\ 
+\bottomrule
+\end{longtable}
 

### 2022-06-05 src/process_all-data/script.R

@@ -50,8 +50,12 @@ areas_df <- areas %>%
 
 areas_df %>%
   select(Country = country, "Number of areas" = n, "Analysis level" = analysis_level) %>%
-  gt() %>%
-  as_latex() %>%
+  gt::gt() %>%
+  gt::cols_align(
+    align = "left",
+    columns = Country
+  ) %>%
+  gt::as_latex() %>%
   as.character() %>%
   cat(file = "area-levels.txt")
 

### 2022-06-06 src/docs_paper/tables-figures.Rmd
Add temporal interpolation plots to extra figures #128

@@
 
+# National direct and modelled estimates comparison
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=1]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Botswana.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-1}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=2]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Cameroon.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-2}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=3]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Kenya.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-3}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=4]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Lesotho.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-4}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=5]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Mozambique.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-5}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=6]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Malawi.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-6}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=7]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Namibia.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-7}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=8]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Eswatini.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-8}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=9]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Tanzania.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-9}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=10]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Uganda.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-10}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=11]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in South Africa.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-11}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=12]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zambia.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-12}
+\end{figure}
+
+<!-- \begin{figure}[h] -->
+<!-- \centering -->
+<!-- \makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}} -->
+<!-- \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.} -->
+<!-- \label{fig:temporal-interpolation-ribbon-13} -->
+<!-- \end{figure} -->
+
+\clearpage
+
 # HIV incidence
@@
 \clearpage
-
-# References {#references .unnumbered}

### 2022-06-06 src/plot_temporal-variation/script.R

@@ -3,9 +3,10 @@
 # setwd("src/plot_temporal-variation")
 
 df_3p1 <- read_csv("depends/best-3p1-multi-sexbehav-sae.csv") %>%
+  filter(indicator != "sexnonregplus") %>%
   multi.utils::update_naming()
 
-pdf("3p1-temporal-interpolation.pdf", h = 4, w = 6.25)
+pdf("temporal-interpolation.pdf", h = 4, w = 6.25)
 
 df_3p1 %>%
   split(.$iso3) %>%
@@ -16,7 +17,7 @@ df_3p1 %>%
 
 dev.off()
 
-pdf("3p1-temporal-interpolation-ribbon.pdf", h = 3.5, w = 6.25)
+pdf("temporal-interpolation-ribbon.pdf", h = 3.5, w = 6.25)
 
 df_3p1_ribbon <- df_3p1 %>%
   group_by(indicator, iso3, year, age_group) %>%
@@ -86,13 +87,13 @@ dev.off()
 
 #' Sadly multi-page .png don't exist
 #' This is a bit clunky but unsure if there is a better option
-lapply(1:length(plotsA), function(i) {
-  ggsave(
-    paste0("3p1-temporal-interpolation-ribbon-", i, ".png"),
-    plotsA[[i]],
-    width = 6.25, height = 3.5, units = "in", dpi = 300
-  )
-})
+# lapply(1:length(plotsA), function(i) {
+#   ggsave(
+#     paste0("temporal-interpolation-ribbon-", i, ".png"),
+#     plotsA[[i]],
+#     width = 6.25, height = 3.5, units = "in", dpi = 300
+#   )
+# })
 
 #' Checking estimates for one country (UGA)
 pdf("uga-check.pdf", h = 7, w = 6.25)

### 2022-06-06 src/docs_paper/paper.Rmd
Close #118 by obtaining data from Juliana and computing the relevant statistics in the document

@@
   **Results:**
-  Data consisted of $291,465$ female survey respondents aged 15-29.
-  Risk group proportions varied substantially across age groups (44.6\% of variation), countries (28.7\%), and between districts within each country (20.6\%), but changed little over time (1.6\%).
-  Among women aged 20-29, we found a geographic delineation, north of which in eastern Africa, cohabiting (69.5\%) is more common than non-regular partner(s) (13.3\%), and south of which, non-regular partner(s) (52.6\%) are more common than cohabiting (27.9\%).
-  Prioritisation based on behavioural risk, on top of location and age based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from 20.1\% to 10.4\%.
-  Female sex workers were 2.4\% of the at risk population but 15.9\% of all new infections.
+  Data consisted of `r "num"` female survey respondents aged 15-29.
+  Risk group proportions varied substantially across age groups (`r "num"`\% of variation), countries (`r "num"`\%), and between districts within each country (`r "num"`\%), but changed little over time (`r "num"`\%).
+  Among women aged 20-29, we found a geographic delineation, north of which in eastern Africa, cohabiting (`r "num"`\%) is more common than non-regular partner(s) (`r "num"`\%), and south of which, non-regular partner(s) (`r "num"`\%) are more common than cohabiting (`r "num"`\%).
+  Prioritisation based on behavioural risk, in combiniation with location and age based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r "num"`\% to `r "num"`\%.
+  Female sex workers were `r "num"`\% of the at risk population but `r "num"`\% of all new infections.
 
@@
 - \usepackage{tabularx}
-# # plos.csl can be download and used locally
-# csl: http://www.zotero.org/styles/plos
+# plos.csl can be download and used locally
+csl: http://www.zotero.org/styles/plos
 ---
+
+```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+library(tidyverse)
+
+priority_iso3 <- multi.utils::priority_iso3()
+analysis_level <- multi.utils::analysis_level()
+admin1_level <- multi.utils::admin1_level()
+
+hiv_estimates <- readxl::read_excel(
+  "HIV2021Estimates_Global_PLWHV-NI-Pop_6June2022.xlsx", 
+  sheet = "Table"
+) %>%
+  filter(ISO3 %in% priority_iso3) %>%
+  select(-c(`...1`, "UN", "ISO2", `...5`, "Region"))
+
+population_comparison <- hiv_estimates %>%
+  select(
+    "ISO3",
+    "L- Population by age and sex 15-19 ; Female", 
+    "L- Population by age and sex 20-24 ; Female", 
+    "L- Population by age and sex 25-29 ; Female",
+    "L- Population aged 15-49 Male+Female"
+  ) %>%
+  mutate(pop_female_Y015_029 = `L- Population by age and sex 15-19 ; Female` +
+    `L- Population by age and sex 20-24 ; Female` + 
+    `L- Population by age and sex 25-29 ; Female`
+  ) %>%
+  summarise(
+    total = sum(`L- Population aged 15-49 Male+Female`),
+    subset = sum(pop_female_Y015_029)
+  )
+
+population_percent <- 100 * round(population_comparison$subset / population_comparison$total, digits = 2)
+
+infections_comparison <- hiv_estimates %>%
+  select(
+    "ISO3",
+    "L- New infections by age 15-19 ; Female", 
+    "L- New infections by age 20-24 ; Female", 
+    "L- New infections by age 25-29 ; Female",
+    "L- New HIV infections (15-49) Male+Female"
+  ) %>%
+  mutate(inf_female_Y015_029 = `L- New infections by age 15-19 ; Female` +
+    `L- New infections by age 20-24 ; Female` + 
+    `L- New infections by age 25-29 ; Female`
+  ) %>%
+  summarise(
+    total = sum(`L- New HIV infections (15-49) Male+Female`),
+    subset = sum(inf_female_Y015_029)
+  )
+
+infections_percent <- 100 * round(infections_comparison$subset / infections_comparison$total, digits = 2)
+
+inc_comparison <- hiv_estimates %>%
+  select(
+    "ISO3",
+    "L- New infections by age 15-19 ; Female", 
+    "L- New infections by age 20-24 ; Female", 
+    "L- New infections by age 25-29 ; Female",
+    "L- New infections by age 15-19 ; Male", 
+    "L- New infections by age 20-24 ; Male", 
+    "L- New infections by age 25-29 ; Male",
+    "L- Population by age and sex 15-19 ; Female", 
+    "L- Population by age and sex 20-24 ; Female", 
+    "L- Population by age and sex 25-29 ; Female",
+    "L- Population by age and sex 15-19 ; Male", 
+    "L- Population by age and sex 20-24 ; Male", 
+    "L- Population by age and sex 25-29 ; Male",
+  ) %>%
+  mutate(
+    inf_female_Y015_029 = `L- New infections by age 15-19 ; Female` +
+    `L- New infections by age 20-24 ; Female` + 
+    `L- New infections by age 25-29 ; Female`,
+    inf_male_Y015_029 = `L- New infections by age 15-19 ; Male` +
+    `L- New infections by age 20-24 ; Male` + 
+    `L- New infections by age 25-29 ; Male`,
+    pop_female_Y015_029 = `L- Population by age and sex 15-19 ; Female` +
+    `L- Population by age and sex 20-24 ; Female` + 
+    `L- Population by age and sex 25-29 ; Female`,
+    pop_male_Y015_029 = `L- Population by age and sex 15-19 ; Male` +
+    `L- Population by age and sex 20-24 ; Male` + 
+    `L- Population by age and sex 25-29 ; Male`
+  ) %>%
+  summarise(
+    inc_female_Y015_029 = sum(inf_female_Y015_029) / sum(pop_female_Y015_029),
+    inc_male_Y015_029 = sum(inf_male_Y015_029) / sum(pop_male_Y015_029)
+  )
+
+inc_ratio <- round(inc_comparison$inc_female_Y015_029 / inc_comparison$inc_male_Y015_029, digits = 1)
+```
 
@@
 
-In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r "num"`\% of the population but `r "num"`\% of new HIV infections [@unaids2021update].
-HIV incidence amongst AGYW is `r "num"` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
+In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r population_percent`\% of the population but `r infections_percent`\% of new HIV infections [@unaids2021update].
+HIV incidence amongst AGYW is `r inc_ratio` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
 AGYW have therefore been identified as a priority population for HIV primary prevention, and significant investments have been made in prevention programming [@saul2018dreams; @global2018measurement].
@@
 
+## Supporting information
+
+**S1**: Appendix
+**S2**: Supplementary tables and figures
+
 ## Funding
@@
 
+# Tables
+
+# Figures
+
 # References {#references .unnumbered}

### 2022-06-09 src/docs_paper/paper.Rmd
Move available surveys analysis to reactive code in the manuscript #128

@@
 HIV incidence amongst AGYW is `r inc_ratio` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
-AGYW have therefore been identified as a priority population for HIV primary prevention, and significant investments have been made in prevention programming [@saul2018dreams; @global2018measurement].
+AGYW have therefore been identified as a priority population for HIV primary prevention, with significant investments being been made in prevention programming [@saul2018dreams; @global2018measurement].
 
-HIV prevention for AGYW is typically comprised of basic programming which is made available to all, together with additional, more intensified, programming which is differentiated on the basis of risk [@joint2016hiv, birdthistle2018evaluating].
-To maximize the impact of additional programming, often comprised of more costly interventions, delivery should be prioritised towards those at the highest risk level.
+HIV prevention for AGYW is typically comprised of: (1) basic programming which is made available to all (2) more intensified programming which is differentiated on the basis of risk [@joint2016hiv; @birdthistle2018evaluating].
+To maximize the impact of intensified programming delivery should be prioritised towards those at the highest risk level.
 As both community-level epidemic indicators and individual-level behaviours determine risk of acquiring HIV, it is important to consider both of these factors in tandem to enable more efficient prioritisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
 
-The Global AIDS Strategy 2021-2016 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying provision of HIV prevention to AGYW based on both population-level HIV incidence in the local population and individual-level sexual risk behaviour.
+The Global AIDS Strategy 2021-2016 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying provision of HIV prevention to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour.
 Four prioritisation strata (Table) are defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1\% and >3\%), and (2) self-reported high-risk behaviour or recent STI infection.
@@
 
-Implementation of the strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group, age group, and district to determine prioritisation for stratified HIV prevention.
+Implementation of the strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group by location to determine prioritisation for stratified HIV prevention.
 We developed a multivariate Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
@@
 We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
-Using our estimates, we calculated the number of new infections in each risk, age, and district strata using population size data, incidence rate ratios, and expected incidence projections.
-Finally, we quantified the increased efficiency in terms of the expected number of new infections that could be preemptively reached by stratified prioritisation of interventions.
+Using our estimates, we calculated the HIV prevalence, people living with HIV (PLHIV), HIV incidence, and number of new HIV infections in each risk, age, and district strata by disaggregating estimates from the Naomi model [@eaton2021naomi].
+Finally, we quantified the increased efficiency of HIV prevention, in terms of the expected number of new infections that could be preemptively reached, by stratified prioritisation of interventions.
 
@@
 The model synthesises data from multiple sources to produce consistent subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
-The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi.
-In Cameroon and Kenya we used an analysis level one higher than used in Naomi.
+The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi, with the exception of Cameroon and Kenya where we used an analysis level one higher.
 
@@
 
-## Prevalence, incidence and new infections
+## HIV indicators and prevention prioritisation
 
-We used the risk group proportion estimates to calculate HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified according to district, age group and risk group by disaggregating estimates from the Naomi model (further details are provided in Appendix).
+We used the risk group proportion estimates to calculate HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified according to district, age group and risk group by disaggregating estimates from the Naomi model.
 
-We disaggregated HIV prevalence estimates by risk group on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
-Logit scaling was preferred to linear scaling, as linear scaling resulted in some strata having prevalence above 100\%.
+### Prevalence and PLHIV
+
+To calculate HIV prevalence by risk group we disaggregated on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
+Logit scaling was used because linear scaling resulted in some strata having prevalence above 100\%.
 PLHIV were calculated by multiplying HIV prevalence by risk group population size.
 
-HIV incidence estimates were disaggregated by risk group on the linear scale using the HIV infection risk ratios given in Table.
+### Incidence and new infection
+
+We disaggregated HIV incidence by risk group linearly using the HIV infection risk ratios given in Table.
 Number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size.
-We then calculated the number of new infections that would be found per person reached when prioritising according to incidence under each possible risk stratification.
-In doing so, we implicitly assumed it is possible to reach all members of a strata.
+
+### Infections reached
+
+For each possible stratification of risk, we calculated the number of new infections that would be found per person reached when prioritising according to incidence.
+We assumed all members of every strata can be reached.
 
@@
 
-We included 47 surveys in our analysis (Figure, Table), with a total sample size of `r "num"` women aged 15-29 years (`r "num"` aged 15-19 years, `r "num"` aged 20-24 years, and `r "num"` aged 25-29 years).
-Of these, 13 surveys included a specific transactional sex question, with corresponding sample size `r "num"` (`r "num"` aged 15-19 years, `r "num"` aged 20-24 years, and `r "num"` aged 25-29 years).
+```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+available_surveys <- read_csv("depends/available-surveys.csv")
+
+#' What was the total number of surveys?
+total_surveys <- available_surveys %>%
+  pull(survey_id) %>%
+  unique() %>%
+  length()
+
+#' How many AGYW, in total, were surveyed?
+agyw_surveyd <- available_surveys %>%
+  pull(Y015_029) %>%
+  sum()
+
+#' What about disaggregating these AGYW by age?
+agyw_surveyed_age <- available_surveys %>%
+  summarise(
+    Y015_019 = sum(Y015_019),
+    Y020_024 = sum(Y020_024),
+    Y025_029 = sum(Y025_029)
+  )
+
+#' What was the total number of surveys including a transactional question?
+giftsvar_surveys <- available_surveys %>%
+  filter(giftsvar == 1) %>%
+  pull(survey_id)
+
+length(giftsvar_surveys)
+
+#' How many AGYW were sampled in these surveys?
+agyw_surveyed_giftsvar <- available_surveys %>%
+  filter(survey_id %in% giftsvar_surveys) %>%
+  pull(Y015_029) %>%
+  sum()
+
+#' Disaggregated by age
+#' TODO: This isn't quite right because some 25-29 are not asked FSW question in DHS surveys
+agyw_surveyed_giftsvar_age <- available_surveys %>%
+  filter(survey_id %in% giftsvar_surveys) %>%
+  summarise(
+    Y015_019 = sum(Y015_019),
+    Y020_024 = sum(Y020_024),
+    Y025_029 = sum(Y025_029)
+  )
+
+#' What was the median number of surveys by country, and the range?
+number_of_surveys <- available_surveys %>%
+  group_by(iso3) %>%
+  summarise(
+    count = length(unique(survey_id))
+  )
+
+number_of_surveys %>%
+  summarise(
+    min = min(count),
+    median = median(count),
+    max = max(count)
+  )
+```
+
+We included `r total_surveys` surveys in our analysis (Figure, Table), with a total sample size of `r agyw_surveyd` women aged 15-29 years (`r agyw_surveyed_age$Y015_019` aged 15-19 years, `r agyw_surveyed_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with corresponding sample size `r agyw_surveyed_giftsvar` (`r agyw_surveyed_giftsvar_age$Y015_019` aged 15-19 years, `r agyw_surveyed_giftsvar_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_giftsvar_age$Y025_029` aged 25-29 years).
 The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Figures).
 
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria for each of the considered models is provided in the appendix (Figures, Tables).
+Model performance according to the CPO criteria is provided in the appendix (Figures, Tables) for all considered models.
+
+## Risk group estimates
 
 Posterior mean estimates for our final model in the most recent year, 2018, are shown as choropleths (Figure) and dotplots (Figure).
-In the following results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Figures).
 Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
+In the sections to follow, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
 
-## Spatial, temporal and age trends
+### Spatial, temporal and age trends
 
@@
 
-##
+### Analysis of variance
 

### 2022-06-09 src/plot_available-surveys/script.R

@@ -157,55 +157,6 @@ df %>%
   as.character() %>%
   cat(file = "available-surveys.txt")
 
-#' What was the total number of surveys?
-df %>%
-  pull(survey_id) %>%
-  unique() %>%
-  length()
-
-#' How many AGYW, in total, were surveyed?
-df %>%
-  pull(Y015_029) %>%
-  sum()
-
-#' What was the total number of surveys including a transactional question?
-giftsvar_surveys <- df %>%
-  filter(giftsvar == 1) %>%
-  pull(survey_id)
-
-length(giftsvar_surveys)
-
-#' How many AGYW were sampled in these surveys?
-df %>%
-  filter(survey_id %in% giftsvar_surveys) %>%
-  pull(Y015_029) %>%
-  sum()
-
-#' What about disaggregating these AGYW by age?
-#' TODO: This isn't quite right because some 25-29 are not asked FSW question in DHS surveys
-#' Might fix this manually
-df %>%
-  filter(survey_id %in% giftsvar_surveys) %>%
-  summarise(
-    Y015_019 = sum(Y015_019),
-    Y020_024 = sum(Y020_024),
-    Y025_029 = sum(Y025_029)
-  )
-
-#' What was the median number of surveys by country, and the range?
-(number_of_surveys <- df %>%
-  group_by(iso3) %>%
-  summarise(
-    count = length(unique(survey_id))
-  ))
-
-number_of_surveys %>%
-  summarise(
-    min = min(count),
-    median = median(count),
-    max = max(count)
-  )
-
 #' What was the raw FSW proportion in surveys with and without a specific transactional question?
 lapply(files, function(file) {
   read_csv(file)

### 2022-06-10 src/docs_paper/paper.Rmd
Add two plots to paper.Rmd #128

@@
 
+<!-- \begin{table}[htb] -->
+<!-- \small -->
+<!-- \centering -->
+<!-- \begin{tabularx}{\textwidth}{llX} -->
+<!-- \toprule -->
+<!-- Risk group & Description & Risk ratio \\  -->
+<!-- \midrule -->
+<!-- None & Not sexually active & 0 (Excludes incidence from non-sexual transmission, e.g. unsafe injection, which is negligible in these populations.) \\ -->
+<!-- Low & One cohabiting sexual partner & 1 (Baseline group.) \\ -->
+<!-- High & Non-regular sexual partner(s) & 1.72 (Based upon analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by \citet{slaymaker2020croi} and \citet{jia2022risk}.) \\ -->
+<!-- Very high & Female sex workers & { -->
+<!-- \begin{tabularx}{\cellwidth}{ll} -->
+<!-- \hline -->
+<!-- District-level HIV incidence & Risk ratio \Top{}\\ -->
+<!-- $>$3.0\% & 3 \\ -->
+<!-- 1.0-3.0\% & 6 \\ -->
+<!-- 0.3-1.0\% & 9 \\ -->
+<!-- 0.1-0.3\% & 13 \\ -->
+<!-- $<$0.1\% & 25 \Bot{}\\ -->
+<!-- \hline -->
+<!-- \end{tabularx} -->
+<!-- }\\ -->
+<!-- \bottomrule -->
+<!-- \end{tabularx} -->
+<!-- \caption{HIV risk groups and risk ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group.
+Risk ratios for the highest risk group vary based upon general population HIV incidence and are based upon a UNAIDS analysis led by Keith Sabin.} -->
+<!-- \label{tab:risk-categories} -->
+<!-- \small -->
+<!-- \end{table} -->
+
 ## Data
@@
 ## Data
+
+```{r echo=FALSE, fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question."}
+knitr::include_graphics("depends/available-surveys.pdf")
+```
 
@@
 ## Infections reached
+
+```{r echo=FALSE, fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached."}
+knitr::include_graphics("depends/infections-reached.pdf")
+```
 
@@
 
-# Tables
-
-# Figures
-
 # References {#references .unnumbered}

### 2022-06-10 src/plot_infections-reached/script.R

@@ -16,7 +16,7 @@ df_area_age_behav <- df %>%
     names_sep = "_"
   ) %>%
   pivot_wider(
-    id_cols = c("iso3", "area_id", "age_group", "indicator", "category"),
+    id_cols = c("iso3", "area_id", "age_group", "category"),
     names_from = "indicator",
     values_from = "value"
   )
@@ -103,13 +103,13 @@ dev.off()
 
 #' Sadly multi-page .png don't exist
 #' This is a bit clunky but unsure if there is a better option
-lapply(1:length(plotsA), function(i) {
-  ggsave(
-    paste0("infections-reached-country-", i, ".png"),
-    plotsA[[i]],
-    width = 6.25, height = 3.5, units = "in", dpi = 300
-  )
-})
+# lapply(1:length(plotsA), function(i) {
+#   ggsave(
+#     paste0("infections-reached-country-", i, ".png"),
+#     plotsA[[i]],
+#     width = 6.25, height = 3.5, units = "in", dpi = 300
+#   )
+# })
 
 #' Quantification of points discussed
 

### 2022-06-11 src/docs_paper/paper.Rmd
A lot of progress with manuscript -- almost there! #128

--- 2022-06-09 src/docs_paper/paper.Rmd
@@
 author_summary: |
-  Author summary
-
+  The risk HIV poses to adolescent girls and young women depends on the extent of HIV in the local community and their individual sexual behaviour.
+  To help policy makers identify and provide services to those at highest risk, we geographically mapped HIV risk using behavioural data from household surveys.
 bibliography: citations.bib
-output: rticles::plos_article
-header-includes:
-- \usepackage{tabularx}
+output:
+  rticles::plos_article:
+    includes:
+      in_header: preamble.tex
 # plos.csl can be download and used locally
@@
 
-```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+```{r echo = FALSE}
+options(scipen = 100)
+
+knitr::opts_chunk$set(
+  echo = FALSE,
+  warning = FALSE,
+  message = FALSE,
+  dpi = 320,
+  cache = TRUE,
+  out.width = "95%",
+  fig.align = 'center'
+)
+```
+
+```{r}
 library(tidyverse)
@@
 We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
-Using our estimates, we calculated the HIV prevalence, people living with HIV (PLHIV), HIV incidence, and number of new HIV infections in each risk, age, and district strata by disaggregating estimates from the Naomi model [@eaton2021naomi].
+Using our estimates, we calculated the HIV prevalence, people living with HIV (PLHIV), HIV incidence, and number of new HIV infections in each risk group by disaggregating district-level estimates from the Naomi model [@eaton2021naomi].
 Finally, we quantified the increased efficiency of HIV prevention, in terms of the expected number of new infections that could be preemptively reached, by stratified prioritisation of interventions.
@@
 # Methodology
+
+\begin{table}[htb]
+\small
+\centering
+\begin{tabularx}{\textwidth}{llX}
+\toprule
+Risk group & Description & Risk ratio \\
+\midrule
+None & Not sexually active & 0 \\
+Low & One cohabiting sexual partner & 1 \\
+High & Non-regular sexual partner(s) & 1.72 \\
+Very high & Female sex workers & {
+\begin{tabularx}{\linewidth}{ll}
+\hline
+District-level HIV incidence & Risk ratio\\
+$>$3.0\% & 3 \\
+1.0-3.0\% & 6 \\
+0.3-1.0\% & 9 \\
+0.1-0.3\% & 13 \\
+$<$0.1\% & 25 \\
+\hline
+\end{tabularx}
+} \\
+\bottomrule
+\end{tabularx}
+\caption{HIV risk groups and incidence risk ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group.}
+\label{tab:risk-groups}
+\small
+\end{table}
 
@@
 For each survey, we classified respondents into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
-These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table, Figure).
+These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table, Fig).
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
@@
 
-We disaggregated HIV incidence by risk group linearly using the HIV infection risk ratios given in Table.
+We disaggregated HIV incidence by risk group linearly using the HIV infection risk ratios given in Table \ref{tab:risk-groups}.
+The risk ratio used for the not sexually active risk group was zero, reflecting exclusion of incidence from non-sexual transmission, e.g. unsafe injection, which is negligible in these populations.
+For the non-regular partner(s) risk group, the risk ratio was based upon analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by @slaymaker2020croi and supported by the review of @jia2022risk.
+Risk ratios for the highest risk group vary based upon general population HIV incidence and are based upon a UNAIDS analysis led by Keith Sabin.
 Number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size.
@@
 ## Data
+
+```{r echo=FALSE, fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question. \\label{fig:available-surveys}"}
+knitr::include_graphics("depends/available-surveys.pdf")
+```
 
@@
 
-We included `r total_surveys` surveys in our analysis (Figure, Table), with a total sample size of `r agyw_surveyd` women aged 15-29 years (`r agyw_surveyed_age$Y015_019` aged 15-19 years, `r agyw_surveyed_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
-Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with corresponding sample size `r agyw_surveyed_giftsvar` (`r agyw_surveyed_giftsvar_age$Y015_019` aged 15-19 years, `r agyw_surveyed_giftsvar_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_giftsvar_age$Y025_029` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table), with a total sample size of `r agyw_surveyd` women aged 15-29 years (`r agyw_surveyed_age$Y015_019` aged 15-19 years, `r agyw_surveyed_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size in these surveys of `r agyw_surveyed_giftsvar` (`r agyw_surveyed_giftsvar_age$Y015_019` aged 15-19 years, `r agyw_surveyed_giftsvar_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_giftsvar_age$Y025_029` aged 25-29 years).
 The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria is provided in the appendix (Figures, Tables) for all considered models.
+Model performance according to the CPO criteria is provided in the appendix (Figs, Tables) for all considered models.
 
@@
 
-Posterior mean estimates for our final model in the most recent year, 2018, are shown as choropleths (Figure) and dotplots (Figure).
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Figures).
+```{r continental-map, echo=FALSE, fig.cap="Choropleths of the posterior mean proportion of AGYW in each risk group in 2018.
+Countries in grey are included to show Cameroon (upper left) in relation to the other twelve spatially-contiguous countries (lower right).
+\\label{fig:continental-map}"}
+knitr::include_graphics("depends/3p1-continental-map.pdf")
+```
+
+```{r within-between-country-variation, echo=FALSE, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions.
+We used regions of sub-Saharan Africa defined according to the UN geocode (M49).
+\\ref{fig:within-between-country-variation}"}
+knitr::include_graphics("depends/3p1-within-between-country-variation.pdf")
+```
+
+Posterior mean estimates from our final model are shown as choropleths (Fig \ref{fig:continental-map}) and dotplots (Fig \ref{fig:within-between-country-variation}).
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level.
 Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
@@
 
-In most districts (`r "num"`\%; 95\% credible interval [CI] `r "num"`--`r "num"`\%) adolescent girls aged 15-19 were not sexually active.
-The exception was Mozambique, where the majority (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) were sexually active in the past year and close to a third (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) were cohabiting with a partner.
+```{r}
+df_3p1_subnational <- read_csv("depends/df_3p1_subnational.csv")
+df_3p1_national <- read_csv("depends/df_3p1_national.csv")
 
-In the 20-24 and 25-29 year age groups, the majority (`r "num"`\%; 95\% CI `r "num"`--`r "num"`\%) of women were either cohabiting or had non-regular partner(s).
-Countries in east and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r "num"`\%, as compared with `r "num"`\% with non-regular partner[s]) and countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular partner(s) (`r "num"`\%, as compared with `r "num"`\% cohabiting).
-There was a clear geographic delineation along the border of Mozambique, through the interior of Zimbabwe and along the border of Zambia.
+#' Quantification of points discussed
+#' District level quantile information (age disaggregated)
+district_age_quantiles <- df_3p1_subnational %>%
+  select(iso3, indicator, age_group, estimate_smoothed) %>%
+  group_by(indicator, age_group) %>%
+  summarise(
+    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+    median = 100 * median(estimate_smoothed, na.rm = TRUE),
+    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+  )
 
-The median proportion of FSW nationally was `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) for the 15-19 age group, compared with $2.4\%$ (95\% CI `r "num"`--`r "num"`\%) and `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) for the 20-24 and 25-29 age groups respectively.
-This age pattern, reflecting the lower proportion sexually active among those aged 15-19 years, was the foremost effect of adjusting our estimates to match [@johnston2022deriving]; in contrast, our initial estimates of transactional sex were close to constant by age (Figure~\ref{fig:fsw-within-between-country-variation}).
+district_Y015_019_nosex12m_quantiles <- filter(district_age_quantiles, indicator == "No sex", age_group == "15-19")
 
-### Analysis of variance
+#' District level quantile information aggregated by age (population weighted)
+district_quantiles <- df_3p1_subnational %>%
+  select(iso3, area_id, indicator, age_group, estimate_smoothed, population_mean) %>%
+  group_by(area_id, indicator) %>%
+  summarise(
+    estimate_smoothed = sum(estimate_smoothed * population_mean) / sum(population_mean)
+  ) %>%
+  ungroup() %>%
+  group_by(indicator) %>%
+  summarise(
+    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+    median = 100 * median(estimate_smoothed, na.rm = TRUE),
+    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+  )
 
-Age explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) of the variation in risk group proportions, country explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%), and district explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%).
-The temporal effects only explained `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) of variation, indicating very little change in risk group proportions over time, with the remaining `r "num"`\% (95\% CI `r "num"`--`r "num"`\%) attributable to the category random effects.
-We observed similar variance decomposition results fitting each country individually (Figure~\ref{fig:aaa-variance-proportions}) or using other model specifications.
+#' What proportion of 15-19 year-olds are cohabiting (or other indicators) in MOZ?
+moz_Y015_019 <- df_3p1_national %>%
+  filter(
+    age_group == "15-19",
+    iso3 == "Mozambique"
+  ) %>%
+  mutate(estimate_smoothed = 100 * estimate_smoothed)
 
-<!-- Can you please write another paragraph here calling out some examples of the amount of variation? -->
+moz_Y015_019_nosex12m <- filter(moz_Y015_019, indicator == "No sex")
+moz_Y015_019_sexcohab <- filter(moz_Y015_019, indicator == "Cohabiting partner")
+moz_Y015_019_sexnonreg <- filter(moz_Y015_019, indicator == "Non regular partner(s)")
+
+# #' In which countries are the majority of 15-19 year-olds not sexually active?
+# #' (Just MOZ!)
+# df_3p1_national %>%
+#   filter(
+#     age_group == "15-19",
+#     indicator == "No sex"
+#   ) %>%
+#   mutate(estimate_smoothed = 100 * estimate_smoothed) %>%
+#   filter(estimate_smoothed < 50)
+# 
+# #' What proportion of 20-29 year-olds are cohabiting versus with nonregular partner(s),
+# #' above and below the south / east dividing border (UN geoscheme)?
+# df_3p1_subnational %>%
+#   mutate(
+#     border = ifelse(region %in% c("East", "Middle"), "Above", "Below")
+#   ) %>%
+#   select(iso3, area_id, indicator, age_group, border, estimate_smoothed, population_mean) %>%
+#   filter(
+#     indicator %in% c("Cohabiting partner", "Nonregular partner(s)"),
+#     age_group %in% c("20-24", "25-29")
+#   ) %>%
+#   group_by(area_id, indicator) %>%
+#   summarise(
+#     estimate_smoothed = sum(estimate_smoothed * population_mean) / sum(population_mean),
+#     border = max(border) #' Should just be a way to keep border column
+#   ) %>%
+#   ungroup() %>%
+#   group_by(border, indicator) %>%
+#   summarise(
+#     lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+#     median = 100 * median(estimate_smoothed, na.rm = TRUE),
+#     upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+#   ) %>%
+#   ungroup() %>%
+#   mutate(across(lower:upper, ~signif(.x, digits = 3)))
+# 
+# #' What's the average FSW proportion by age?
+# fsw_age <- df_3p1_subnational %>%
+#   filter(indicator == "FSW") %>%
+#   group_by(iso3, age_group) %>%
+#   summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE)) %>%
+#   group_by(age_group) %>%
+#   summarise(
+#     lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+#     median = 100 * median(estimate_smoothed, na.rm = TRUE),
+#     upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+#   ) %>%
+#   mutate(across(lower:upper, ~signif(.x, digits = 3)))
+# 
+# #' What about by country?
+# fsw_iso3 <- df_3p1_subnational %>%
+#   filter(indicator == "FSW") %>%
+#   group_by(iso3) %>%
+#   summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE))
+```
+
+In most districts (`r round(district_Y015_019_nosex12m_quantiles$median, 1)`\%; 95\% credible interval [CI] `r round(district_Y015_019_nosex12m_quantiles$lower, 1)`--`r round(district_Y015_019_nosex12m_quantiles$upper, 1)`\%) adolescent girls aged 15-19 were not sexually active.
+The exception was Mozambique, where the majority (`r 100 - round(moz_Y015_019_nosex12m$estimate_smoothed, 2)`\%; 95\% CI `r "num"`--`r "num"`\%) were sexually active in the past year and close to a third (`r round(moz_Y015_019_sexcohab$estimate_smoothed, 2)`\%; 95\% CI `r "num"`--`r "num"`\%) were cohabiting with a partner.
+
+### Analysis of variance {#sec:analysis-of-variance}
+
+```{r}
+variance_proportions <- read_csv("depends/variance-proportions-uncertainty.csv")
+variance_proportions_age <- 100 * filter(variance_proportions, variable == "age") %>% select(-variable) %>% round(digits = 3)
+variance_proportions_iso3 <- 100 * filter(variance_proportions, variable == "iso3") %>% select(-variable) %>% round(digits = 3)
+variance_proportions_area <- 100 * filter(variance_proportions, variable == "area") %>% select(-variable) %>% round(digits = 3)
+variance_proportions_year <- 100 * filter(variance_proportions, variable == "year") %>% select(-variable) %>% round(digits = 3)
+variance_proportions_cat <- 100 * filter(variance_proportions, variable == "cat") %>% select(-variable) %>% round(digits = 3)
+```
+
+Age explained `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`\%) of the variation in risk group proportions.
+Variance explained by location may be broken down into `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`\%) explained by country and `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`\%) explained by district.
+The temporal effects only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`\%) of variation, indicating very little change in risk group proportions over time.
+We observed similar variance decomposition results fitting each country individually, and using other model specifications.
+
+<!-- Write another paragraph here calling out some examples of the amount of variation -->
 <!-- Awaiting additional results: https://github.com/athowes/multi-agyw/issues/95 -->
@@
 
+```{r echo=FALSE, fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached.
+\\ref{fig:infections-reached}"}
+knitr::include_graphics("depends/infections-reached.pdf")
+```
+
 For any given fraction of AGYW prioritised, substantially more new infections were reached by strategies that included behavioural risk stratification.
-Reaching half of all new infections required reaching 20.1\% of the population when stratifying by area and age, but only 10.4\% when behavioural stratification was included (Figure~\ref{fig:infections-reached}).
-The majority of this benefit came from reaching FSW, who were 2.4\% of the population but 15.9\% of all new infections.
+Reaching half of all new infections required reaching `r "num"`\% of the population when stratifying by area and age, but only `r "num"`\% when behavioural stratification was included (Fig \ref{fig:infections-reached}).
+The majority of this benefit came from reaching FSW, who were `r "num"`\% of the population but `r "num"`\% of all new infections.
 
 Efficiency was reduced if prioritisation was done separately by country.
-On average, reaching half of new infections in a country required reaching 15.7\% (range 7.8-23.4\%) of the population when stratifying by area and age, reducing to 5.1\% (range 1.3-9.2\%) when behaviour was included.
-The importance of stratifying risk upon age, location and behaviour within a country varied (Figure~\ref{fig:infections-reached-country-1}--Figure~\ref{fig:infections-reached-country-13}), analogous to the varying contribution of each to the total variance (Section~\ref{sec:variance-decomp}).
-For example, FSW in Tanzania were estimated to be 5.3\% of the population and close to half (41.4\%) of all new infections, whereas FSW in Namibia were just 0.3\% of the population and 2.7\% of all new infections.
+On average, reaching half of new infections in a country required reaching `r "num"`\% (range `r "num"`-`r "num"`\%) of the population when stratifying by area and age, reducing to `r "num"`\% (range `r "num"`-`r "num"`\%) when behaviour was included.
+The importance of stratifying risk upon age, location and behaviour within a country varied, analogous to the varying contribution of each to the total variance (Sec \@ref(analysis-of-variance)).
+For example, FSW in Tanzania were estimated to be `r "num"`\% of the population and close to half (`r "num"`\%) of all new infections, whereas FSW in Namibia were just `r "num"`\% of the population and `r "num"`\% of all new infections.
 
@@
 Our estimates will enable country and district-level planners to differentiate prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
-
-<!-- Comment about how novel this would be if implemented -->
+<!-- Some type of comment about how novel this would be if implemented -->
 
@@
 First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
-Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Figure).
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig).
 Third, we provide estimates in all settings, including districts without any survey clusters as well as years without surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
@@
 
-Our analysis of the number of infections that could be reached by each risk stratification strategy was based on simplifying assumptions and should be interpreted as illustrating the potentially obtainable benefits, rather than benefits that would be accrued from any specific intervention strategy.
-Factors we did not consider include the greater administrative burden of more complex strategies, variation in difficulty or feasibility of reaching individuals in each strata, variation in the range or effectiveness of interventions by strata, and changes in strata membership that may occur during the course of a year.
+The risk groups we analysed did not consider other important characteristics, such as condom usage or partner-specific risk, which contribute to heterogeneity within each risk group.
+Although the number of risk groups considered could be increased, capturing more of this heterogeneity, this inclination must be balanced with the benefits of parsimony.
+Our approach assumed that within risk group heterogeneity is small enough that the categories are meaningfully consistent across contexts.
+Additionally, the categories we used are not immediately actionable.
+For example, a program is designed to reach AGYW who are cohabiting, then it is not clear how to find these individuals within a community.
+It may be preferable to select risk groups based more amenable attributes, such as attendance of a particular service or facility.
+<!-- e.g. school, healthcare -->
 
-<!-- Dependence of FSW on clustering and migration. -->
-
-Under-reporting of higher risk sexual behaviours amongst AGYW could affect the validity of our estimates.
+Under-reporting of higher risk sexual behaviours amongst AGYW could affect the validity of our risk group proportion estimates.
 Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive} or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @kinh2021trends].
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
-Furthermore, our FSW estimates do not overcome the difficulties of sampling hard to reach groups; in particular, the possibility of being excluded from household sampling frames.
+
+Our FSW estimates do not overcome the difficulties of sampling hard to reach groups, specifically the possibility of being excluded from household sampling frames.
+As well, we did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
+
+Our analysis of the number of infections that could be reached by each risk stratification strategy was based on simplifying assumptions and should therefore be interpreted as illustrating the potentially obtainable benefits, rather than benefits that would be accrued from any specific intervention strategy.
+Factors we did not consider include the greater administrative burden of more complex strategies, variation in difficulty or feasibility of reaching individuals in each strata, variation in the range or effectiveness of interventions by strata, and changes in strata membership that may occur during the course of a year.
 
@@
 
-The risk groups we analysed did not consider other important characteristics, such as condom usage or partner-specific risk, which contribute to heterogeneity within each risk group.
-Although the number of risk groups considered could be increased, capturing more of this heterogeneity, this inclination must be balanced with the benefits of parsimony.
-Our approach assumed that within risk group heterogeneity is small enough that the categories are meaningfully consistent across contexts.
-Additionally, the categories we used are not immediately actionable.
-For example, a program is designed to reach AGYW who are cohabiting, then it is not clear how to find these individuals within a community.
-As such it may be preferable to select risk groups based more amenable attributes, such as attendance of a particular service or facility.
-% e.g. school, healthcare
-
 Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the wider population of all adults of both sexes.
 By limiting our consideration to this group we didn't account for `r "num"`\% of all new infections [CITE: Katie, others].
-% Obtaining population size estimates for sexual risk behaviour in the general population is a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
+Furthermore, obtaining population size estimates for sexual risk behaviour in the general population is a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
 

### 2022-06-11 src/plot_within-between-country-variation/script.R

@@ -22,6 +22,9 @@ temp_3p1 <- prepare_estimates(df_3p1)
 df_3p1_subnational <- temp_3p1$df_subnational
 df_3p1_national <- temp_3p1$df_national
 
+write_csv(df_3p1_subnational, "df_3p1_subnational.csv")
+write_csv(df_3p1_national, "df_3p1_national.csv")
+
 pdf("3p1-within-between-country-variation.pdf", h = 7, w = 6.25)
 
 plotA <- df_3p1_subnational %>%
@@ -151,92 +154,3 @@ ggsave(
   plotB,
   width = 6.25, height = 6, units = "in", dpi = 300
 )
-
-#' Quantification of points discussed
-#' District level quantile information (age disaggregated)
-df_3p1_subnational %>%
-  select(iso3, indicator, age_group, estimate_smoothed) %>%
-  group_by(indicator, age_group) %>%
-  summarise(
-    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
-    median = 100 * median(estimate_smoothed, na.rm = TRUE),
-    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
-  )
-
-#' District level quantile information aggregated by age (population weighted)
-df_3p1_subnational %>%
-  select(iso3, area_id, indicator, age_group, estimate_smoothed, population_mean) %>%
-  group_by(area_id, indicator) %>%
-  summarise(
-    estimate_smoothed = sum(estimate_smoothed * population_mean) / sum(population_mean)
-  ) %>%
-  ungroup() %>%
-  group_by(indicator) %>%
-  summarise(
-    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
-    median = 100 * median(estimate_smoothed, na.rm = TRUE),
-    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
-  )
-
-#' What proportion of 15-19 year-olds are cohabiting (or other indicators) in MOZ?
-df_3p1_national %>%
-  filter(
-    age_group == "15-19",
-    iso3 == "Mozambique"
-  ) %>%
-  mutate(estimate_smoothed = 100 * estimate_smoothed)
-
-#' In which countries are the majority of 15-19 year-olds not sexually active?
-#' Just MOZ!
-df_3p1_national %>%
-  filter(
-    age_group == "15-19",
-    indicator == "No sex"
-  ) %>%
[…]

### 2022-06-11 src/docs_paper/tables-figures.Rmd
Add Global AIDS Strategy, survey questions, infections reached by country to tables and figures appendix #128

@@
   pdf_document:
+    toc: true
     keep_tex: true
@@
 
-# Data
+# The Global AIDS Strategy
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Prioritisation strata & Criterion \\
+\midrule
+Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
+Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
+High & 1-3\% incidence AND high-risk behaviour \\
+Very high & $>$3\% incidence \\
+\bottomrule
+\end{tabularx}
+\caption{Prioritisation strata.}
+\label{tab:unaids-strategy-prioritisation}
+\end{table}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Intervention & Details \\
+\midrule
+STI screening and treatment & (Remain to be filled in: describe targets and commitments in terms of each prioritisation strata) \\
+PrEP use & (As above) \\
+Access to PEP & (As above) \\
+Comprehensive sexuality education & (As above) \\
+Economic empowerment & (As above) \\
+\bottomrule
+\end{tabularx}
+\caption{Targets and commitments.}
+\label{tab:unaids-strategy-targets}
+\end{table}
+
+\clearpage
+
+# Survey data
 
@@
 
-\newpage
-
-\begin{longtable}{lrr}
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lXX}
 \toprule
@@
 \bottomrule
-\end{longtable}
+\end{tabularx}
+\label{tab:area-levels}
+\caption{The numer of areas and analysis levels used in our analysis.}
+\end{table}
+
+\clearpage
+
+# Survey questions and risk group allocation
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Variable(s) & Description \\
+\midrule
+\texttt{v501} & Current marital status of the respondent. \\
+\texttt{v529} & Computed time since last sexual intercourse. \\
+\texttt{v531} & Age at first sexual intercourse--imputed. \\
+\texttt{v766b} & Number of sexual partners during the last 12 months (including husband). \\
+\texttt{v767[a, b, c]} & Relationship with last three sexual partners.
+Options are: spouse, boyfriend not living with respondent, other friend, casual acquaintance, relative, commercial sex worker, live-in partner, other.
+\\
+\texttt{v791a} & Had sex in return for gifts, cash or anything else in the past 12 months. Asked only to women 15-24 who are not in a union. \\
+\bottomrule
+\end{tabularx}
+\caption{AIS, BAIS and DHS survey questions.}
+\end{table}
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{lX}
+\toprule
+Variable(s) & Description \\
+\midrule
+\texttt{part12monum} & Number of sexual partners during the last 12 months (including husband). \\
+\texttt{part12modkr} & Reason for leaving \texttt{part12monum} blank. \\
+\texttt{partlivew[1, 2, 3]} & Does the person you had sex with live in this household? \\
+\texttt{partrelation[1, 2, 3]} & Relationship with last three sexual partners.
+Options are: husband, live-in partner, partner (not living with), ex-spouse/partner, friend/acquaintance, sex worker, sex worker client, stranger, other, don't know, refused.
+\\
+\texttt{sellsx12mo} & Had sex for money and/or gifts in the last 12 months. \\
+\texttt{buysx12mo} & Paid money or given gifts for sex in the last 12 months. \\
+\bottomrule
+\end{tabularx}
+\caption{PHIA survey questions.}
+\end{table}
+
+\newpage
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics{depends/category-flowchart.pdf}
+    \caption{Flowchart describing allocation of respondents to risk groups.}
+    \label{fig:category-flowchart}
+\end{figure}
 
@@
 
-# HIV incidence
+# Cloropleths
+
+## HIV prevalence
+
+## HIV incidence
 
@@
 
-<!-- \begin{figure}[h] -->
-<!--     \centering -->
-<!--     \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}} -->
-<!--     \caption{District level incidence for each of the risk groups in 2018 in Zimbabwe.} -->
-<!--     \label{fig:incidence-district-sexbehav-13} -->
-<!-- \end{figure} -->
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}}
+    \caption{District level incidence for each of the risk groups in 2018 in Zimbabwe.}
+    \label{fig:incidence-district-sexbehav-13}
+\end{figure}
 
 \clearpage
+
+# Infections reached
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=1]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
+\label{fig:infections-reached-country-1}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=2]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
+\label{fig:infections-reached-country-2}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=3]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
+\label{fig:infections-reached-country-3}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=4]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
+\label{fig:infections-reached-country-4}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=5]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
+\label{fig:infections-reached-country-5}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=6]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
+\label{fig:infections-reached-country-6}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=7]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
+\label{fig:infections-reached-country-7}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=8]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
+\label{fig:infections-reached-country-8}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=9]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
+\label{fig:infections-reached-country-9}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=10]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
+\label{fig:infections-reached-country-10}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=11]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
+\label{fig:infections-reached-country-11}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=12]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
+\label{fig:infections-reached-country-12}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=13]{depends/infections-reached-country.pdf}}
+\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}
+\label{fig:infections-reached-country-13}
+\end{figure}

### 2022-06-12 src/docs_paper/appendix.Rmd
Alterations to mathematical appendix #128

@@
 ---
-title: Appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent
+title: Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent
   girls and young women across 13 priority countries in sub-Saharan Africa"
@@
   pdf_document:
+    toc: true
+    number_sections: true
     keep_tex: true
@@
 
-# Modelling of risk group proportions
+# Modelling of risk group proportions {#modelling-of-risk-group-proportions}
 
@@
 
-We index the four risk groups given in Table X by $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
-Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts according to Table X.
+We index the four risk groups by $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
+Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts according to Table A.
 For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider the multinomial random vector
@@
 
-To quantify uncertainty from our model, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
-Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via the equations
-\begin{align*}
-    p_{ita3}^s &= (1 - q_{ia}^s)p_{ita{3^+}^s}, \\
-    p_{ita4}^s &= q_{ia}^s p_{ita{3^+}}^s.
-\end{align*}
-Next, as transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match externally produced age-country specific FSW population size estimates, which we calculate in Section.
+To allow uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.
+
+As transactional sex does not directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match FSW population size estimates at a national level by age.
+Our methodology for producing these estimates is described in Section \ref{fsw-population-size-estimation}.
 In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
-We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using these adjusted samples.
-To produce aggregated estimates, such as the age category 15-24 and national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].
+
+We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using the adjusted samples.
+To produce aggregated estimates, such as the age category 15-24 or any national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].
 
@@
 
-We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
+We considered eight models (Table \ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
 $$
@@
 $$
-Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for equivalency of the models.
+Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to allow the sample sizes $m_{ita}$ to be recovered exactly, as required for equivalency of the models.
 To capture country-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
@@
 
-\subsection{Logistic regression model} \label{app:logistic-model}
+## Logistic regression model
 
@@
 
-\subsubsection{Survey weighted likelihood}
+### Survey weighted likelihood
 
@@
 
-\subsubsection{Model selection}
-
-\begin{footnotesize}
+### Model selection
 
@@
 
-\end{footnotesize}
-
 \begin{figure}[h]
@@
 
-\newpage
+\clearpage
 
-# Age-country FSW population size estimates
+# FSW population size estimation {#fsw-population-size-estimation}
 
@@
 
-# Prevalence, incidence and new infections reached analysis
+\clearpage
+
+# Prevalence, incidence and new infections reached analysis {#hiv-indicators}
 
@@
 
-We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak} = \rho_{iak} N_{iak}$ stratified according to district, age group and risk group by disaggregation
+We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak} = \rho_{iak} N_{iak}$ stratified according to district, age group and risk group by disaggregation on the logit scale.
 \begin{align}
@@
 
-Similarly, we calculated HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ stratified according to district, age group and risk group by disaggregation
+We calculated HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ stratified according to district, age group and risk group by linear disaggregation
 \begin{align}
@@
 \end{align}
-which we evaluated using Naomi model estimates of the number of new HIV infections $I_{ia} = \lambda_{ia} N_{ia}$, HIV infection risk ratios $\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}$ as given in Table~\ref{tab:risk-categories}, and 2018 risk group population sizes as above.
+which we evaluated using Naomi model estimates of the number of new HIV infections $I_{ia} = \lambda_{ia} N_{ia}$, HIV infection risk ratios $\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}$, and 2018 risk group population sizes as above.
 The risk ratio $\text{RR}_4(\lambda_{ia})$ is defined as a function of general population incidence.
@@
 
-We calculated the number of new infections that would be reached prioritising according to each possible stratification of the population.
-As an illustration, for stratification by age, we aggregated the number of new HIV infections and HIV incidence as such 
+We calculated the number of new infections that would be reached prioritising according to each possible stratification of the population--that is for all $2^3 = 8$ possible combinations of stratification by location, age, and risk group.
+As an illustration, for stratification just by age, we aggregated the number of new HIV infections and HIV incidence as such 
 \begin{align}
@@
 \end{align}
-Under this stratification, individuals in each age group $a$ would be prioritised according to the highest HIV incidence $\lambda_a$.
-We repeated this analysis for all $2^3 = 8$ possible combinations of stratification by location, age, and risk group.
-
-\newpage
-
-# The Global AIDS Strategy 2021-2016
-
-\begin{footnotesize}
-
-\begin{table}[h]
-\centering
-\begin{tabularx}{\textwidth}{lX}
-\toprule
-Prioritisation strata & Criterion \\ 
- \midrule
-Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
-Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
-High & 1-3\% incidence AND high-risk behaviour \\
-Very high & $>$3\% incidence \\
-\bottomrule
-\end{tabularx}
-\caption{Prioritisation strata.}
-\label{tab:unaids-strategy-prioritisation}
-\end{table}
-
-\end{footnotesize}
-
-\begin{footnotesize}
-
-\begin{table}[h]
-\centering
-\begin{tabularx}{\textwidth}{lX}
-\toprule
-Intervention & Details \\ 
- \midrule
-STI screening and treatment & (Remain to be filled in: describe targets and commitments in terms of each prioritisation strata) \\
-PrEP use & (As above) \\
-Access to PEP & (As above) \\
-Comprehensive sexuality education & (As above) \\
-Economic empowerment & (As above) \\
-\bottomrule
-\end{tabularx}
-\caption{Targets and commitments.}
-\label{tab:unaids-strategy-targets}
-\end{table}
-
-\end{footnotesize}
-
-\newpage
-
-# Survey questions and risk group classification
-
-## Survey questions
-
-\begin{footnotesize}
-
-\begin{table}[h]
-\centering
-\begin{tabularx}{\textwidth}{lX}
-\toprule
-Variable(s) & Description \\ 
- \midrule
-\texttt{v501} & Current marital status of the respondent. \\
-\texttt{v529} & Computed time since last sexual intercourse. \\
-\texttt{v531} & Age at first sexual intercourse--imputed. \\
-\texttt{v766b} & Number of sexual partners during the last 12 months (including husband). \\
-\texttt{v767[a, b, c]} & Relationship with last three sexual partners.
-Options are: spouse, boyfriend not living with respondent, other friend, casual acquaintance, relative, commercial sex worker, live-in partner, other.
-\\
-\texttt{v791a} & Had sex in return for gifts, cash or anything else in the past 12 months. Asked only to women 15-24 who are not in a union. \\
-\bottomrule
-\end{tabularx}
-\caption{AIS, BAIS and DHS survey questions.}
-\end{table}
-
-\end{footnotesize}
-
-\begin{footnotesize}
-
-\begin{table}[h]
-\centering
-\begin{tabularx}{\textwidth}{lX}
-\toprule
-Variable(s) & Description \\ 
- \midrule
-\texttt{part12monum} & Number of sexual partners during the last 12 months (including husband). \\
-\texttt{part12modkr} & Reason for leaving \texttt{part12monum} blank. \\
-\texttt{partlivew[1, 2, 3]} & Does the person you had sex with live in this household? \\
-\texttt{partrelation[1, 2, 3]} & Relationship with last three sexual partners.
-Options are: husband, live-in partner, partner (not living with), ex-spouse/partner, friend/acquaintance, sex worker, sex worker client, stranger, other, don't know, refused.
-\\
-\texttt{sellsx12mo} & Had sex for money and/or gifts in the last 12 months. \\
-\texttt{buysx12mo} & Paid money or given gifts for sex in the last 12 months. \\
-\bottomrule
-\end{tabularx}
-\caption{PHIA survey questions.}
-\end{table}
-
-\end{footnotesize}
-
-\newpage
-
-\subsection{Risk group classification based on survey questions}
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics{depends/category-flowchart.pdf}
-    \caption{Flowchart describing allocation of respondents to risk groups.}
-    \label{fig:category-flowchart}
-\end{figure}
+Under this stratification, individuals in each age group $a$ are prioritised according to the highest HIV incidence $\lambda_a$.
+By cumulatively summing the expected infections, we calculated for each fraction of the total population reached, the fraction of total new infections that would be reached.
+This analysis was relatively simple: more involved analyses might consider prioritisation of a hypothetical interventions which has some, possibly varying, probability of preventing HIV acquistion together with the costs associated to its roll-out.
 

### 2022-06-12 make/7_post_process.R
Add model direct benefits plot #128

@@ -14,7 +14,7 @@ run_commit_push("plot_continental-map") #' [x]
 run_commit_push("plot_aids-abstract") #' [x]
 
 #' Choropleth contrasting direct estimates with modeled estimates, and illustrating benefits of the later
-run_commit_push("plot_model-direct-benefits") #' [ ]
+run_commit_push("plot_model-direct-benefits") #' [x]
 
 #' Barplot of the information criteria (DIC, WAIC, CPO) for each model
 run_commit_push("process_information-criteria") #' [/]

### 2022-06-12 src/plot_model-direct-benefits/script.R

@@ -9,7 +9,7 @@ df <- df %>%
   filter(
     survey_id == "TZA2010DHS",
     age_group == "Y020_024",
-    model == "Model 6",
+    model == "Model 4",
     area_id != "TZA",
     indicator == "sexcohab"
   ) %>%
@@ -25,7 +25,7 @@ df <- df %>%
   mutate(
     source = fct_recode(source,
       "Direct" = "raw",
-      "Modeled" = "smoothed"
+      "Modelled" = "smoothed"
     )
   ) %>%
   left_join( #' Use this to make it an sf again

### 2022-06-13 src/docs_paper/paper.Rmd
Include more figures into the results section #128

@@
 author_summary: |
-  The risk HIV poses to adolescent girls and young women depends on the extent of HIV in the local community and their individual sexual behaviour.
-  To help policy makers identify and provide services to those at highest risk, we geographically mapped HIV risk using behavioural data from household surveys.
+  The risk HIV poses to adolescent girls and young women depends on the extent of HIV in the local community as well as individual sexual behaviour.
+  To help policy makers identify and provide services to those at highest risk, we geographically mapped HIV risk groups using behavioural data from household surveys.
+  Doing so also allowed us to estimate the the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
 bibliography: citations.bib
@@
 \begin{tabularx}{\linewidth}{ll}
-\hline
 District-level HIV incidence & Risk ratio\\
@@
 $<$0.1\% & 25 \\
-\hline
 \end{tabularx}
@@
 For each survey, we classified respondents into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
-These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table, Fig).
+These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table \ref{tab:risk-groups}).
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
-Exact survey questions varied to a limited extent between surveys, as described in Appendix.
+Exact survey questions varied to a limited extent between surveys (Appendix B).
 Questions captured information about if the respondent had been sexually active in the past twelve months, and if so how with many partners.
@@
 The model synthesises data from multiple sources to produce consistent subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
-The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi, with the exception of Cameroon and Kenya where we used an analysis level one higher.
+The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi, with the exception of Cameroon and Kenya where we used an analysis level one higher (Appendix B).
 
@@
 
-We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Table).
+We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A).
 All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
@@
 
-For the logistic regression model for the proportion engaging in transactional sex among those with non-regular partner(s), we considered six specifications (Table).
+For the logistic regression model for the proportion engaging in transactional sex among those with non-regular partner(s), we considered six specifications (Appendix A).
 Each included an intercept, age and country effects, and a spatial effect allowing district level variation.
@@
 We used the risk group proportion estimates to calculate HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified according to district, age group and risk group by disaggregating estimates from the Naomi model.
+Further details are provided in Appendix A.
 
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria is provided in the appendix (Figs, Tables) for all considered models.
+Model performance according to the CPO criteria is provided in Appendix A for all considered models.
 
@@
 Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
-In the sections to follow, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
+In the writing to follow, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
 
-### Spatial, temporal and age trends
-
-```{r}
+```{r echo=FALSE}
 df_3p1_subnational <- read_csv("depends/df_3p1_subnational.csv")
@@
 
-# #' In which countries are the majority of 15-19 year-olds not sexually active?
-# #' (Just MOZ!)
-# df_3p1_national %>%
-#   filter(
-#     age_group == "15-19",
-#     indicator == "No sex"
-#   ) %>%
-#   mutate(estimate_smoothed = 100 * estimate_smoothed) %>%
-#   filter(estimate_smoothed < 50)
-# 
-# #' What proportion of 20-29 year-olds are cohabiting versus with nonregular partner(s),
-# #' above and below the south / east dividing border (UN geoscheme)?
-# df_3p1_subnational %>%
-#   mutate(
-#     border = ifelse(region %in% c("East", "Middle"), "Above", "Below")
-#   ) %>%
-#   select(iso3, area_id, indicator, age_group, border, estimate_smoothed, population_mean) %>%
-#   filter(
-#     indicator %in% c("Cohabiting partner", "Nonregular partner(s)"),
-#     age_group %in% c("20-24", "25-29")
-#   ) %>%
-#   group_by(area_id, indicator) %>%
-#   summarise(
-#     estimate_smoothed = sum(estimate_smoothed * population_mean) / sum(population_mean),
-#     border = max(border) #' Should just be a way to keep border column
-#   ) %>%
-#   ungroup() %>%
-#   group_by(border, indicator) %>%
-#   summarise(
-#     lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
-#     median = 100 * median(estimate_smoothed, na.rm = TRUE),
-#     upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
-#   ) %>%
-#   ungroup() %>%
-#   mutate(across(lower:upper, ~signif(.x, digits = 3)))
-# 
-# #' What's the average FSW proportion by age?
-# fsw_age <- df_3p1_subnational %>%
-#   filter(indicator == "FSW") %>%
-#   group_by(iso3, age_group) %>%
-#   summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE)) %>%
-#   group_by(age_group) %>%
-#   summarise(
-#     lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
-#     median = 100 * median(estimate_smoothed, na.rm = TRUE),
-#     upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
-#   ) %>%
-#   mutate(across(lower:upper, ~signif(.x, digits = 3)))
-# 
-# #' What about by country?
-# fsw_iso3 <- df_3p1_subnational %>%
-#   filter(indicator == "FSW") %>%
-#   group_by(iso3) %>%
-#   summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE))
+#' In which countries are the majority of 15-19 year-olds not sexually active?
+#' (Just MOZ!)
+df_3p1_national %>%
+  filter(
+    age_group == "15-19",
+    indicator == "No sex"
+  ) %>%
+  mutate(estimate_smoothed = 100 * estimate_smoothed) %>%
+  filter(estimate_smoothed < 50)
+
+#' What proportion of 20-29 year-olds are cohabiting versus with nonregular partner(s),
+#' above and below the south / east dividing border (UN geoscheme)?
+dividing_border <- df_3p1_subnational %>%
+  mutate(
+    border = ifelse(region %in% c("Eastern", "Central"), "Above", "Below")
+  ) %>%
+  select(iso3, area_id, indicator, age_group, border, estimate_smoothed, population_mean) %>%
+  filter(
+    indicator %in% c("Cohabiting partner", "Nonregular partner(s)"),
+    age_group %in% c("20-24", "25-29")
+  ) %>%
+  group_by(area_id, indicator) %>%
+  summarise(
+    estimate_smoothed = sum(estimate_smoothed * population_mean) / sum(population_mean),
+    border = max(border) #' Should just be a way to keep border column
+  ) %>%
+  ungroup() %>%
+  group_by(border, indicator) %>%
+  summarise(
+    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+    median = 100 * median(estimate_smoothed, na.rm = TRUE),
+    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+  ) %>%
+  ungroup() %>%
+  mutate(across(lower:upper, ~signif(.x, digits = 3)))
+
+dividing_border_above_sexcohab <- filter(dividing_border, border == "Above", indicator == "Cohabiting partner")
+dividing_border_above_sexnonreg <- filter(dividing_border, border == "Above", indicator == "Nonregular partner(s)")
+dividing_border_below_sexcohab <- filter(dividing_border, border == "Below", indicator == "Cohabiting partner")
+dividing_border_below_sexnonreg <- filter(dividing_border, border == "Below", indicator == "Nonregular partner(s)")
+
+#' What's the average FSW proportion by age?
+fsw_age <- df_3p1_subnational %>%
+  filter(indicator == "FSW") %>%
+  group_by(iso3, age_group) %>%
+  summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE)) %>%
+  group_by(age_group) %>%
+  summarise(
+    lower = 100 * quantile(estimate_smoothed, probs = 0.025, na.rm = TRUE),
+    median = 100 * median(estimate_smoothed, na.rm = TRUE),
+    upper = 100 * quantile(estimate_smoothed, probs = 0.975, na.rm = TRUE)
+  ) %>%
+  mutate(across(lower:upper, ~signif(.x, digits = 3)))
+
+fsw_age_Y015_019 <- filter(fsw_age, age_group == "15-19")
+fsw_age_Y020_024 <- filter(fsw_age, age_group == "20-24")
+fsw_age_Y025_029 <- filter(fsw_age, age_group == "25-29")
+
+#' What about by country?
+fsw_iso3 <- df_3p1_subnational %>%
+  filter(indicator == "FSW") %>%
+  group_by(iso3) %>%
+  summarise(estimate_smoothed = sum(estimate_smoothed * population_mean, na.rm = TRUE) / sum(population_mean, na.rm = TRUE))
 ```
 
+The median proportion of FSW nationally was `r fsw_age_Y015_019$median`\% (95\% CI `r fsw_age_Y015_019$lower`--`r fsw_age_Y015_019$upper`\%) for the 15-19 age group, `r fsw_age_Y020_024$median`\% (95\% CI `r fsw_age_Y020_024$lower`--`r fsw_age_Y020_024$upper`\%) for the 20-24 age group and `r fsw_age_Y025_029$median`\% (95\% CI `r fsw_age_Y025_029$lower`--`r fsw_age_Y025_029$upper`\%) for the 25-29 age group.
+
+In the 20-24 and 25-29 year age groups, the majority of women were either cohabiting or had non-regular partner(s).
+Countries in eastern and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r dividing_border_above_sexcohab$median`\% [95\% CI `r dividing_border_above_sexcohab$lower`--`r dividing_border_above_sexcohab$upper`\%] as compared with `r dividing_border_above_sexnonreg$median`\% [95\% CI `r dividing_border_above_sexnonreg$lower`--`r dividing_border_above_sexnonreg$upper`\%] with non-regular partner[s]) and countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular partner(s) (`r dividing_border_below_sexnonreg$median`\% [95\% CI `r dividing_border_below_sexnonreg$lower`--`r dividing_border_below_sexnonreg$upper`\%], as compared with `r dividing_border_below_sexcohab$median`\% [95\% CI `r dividing_border_below_sexcohab$lower`--`r dividing_border_below_sexcohab$upper`\%] cohabiting).
+This clear geographic delineation passes along the border of Mozambique, through the interior of Zimbabwe and along the border of Zambia (Fig \ref{fig:continental-map}).
+
 In most districts (`r round(district_Y015_019_nosex12m_quantiles$median, 1)`\%; 95\% credible interval [CI] `r round(district_Y015_019_nosex12m_quantiles$lower, 1)`--`r round(district_Y015_019_nosex12m_quantiles$upper, 1)`\%) adolescent girls aged 15-19 were not sexually active.
-The exception was Mozambique, where the majority (`r 100 - round(moz_Y015_019_nosex12m$estimate_smoothed, 2)`\%; 95\% CI `r "num"`--`r "num"`\%) were sexually active in the past year and close to a third (`r round(moz_Y015_019_sexcohab$estimate_smoothed, 2)`\%; 95\% CI `r "num"`--`r "num"`\%) were cohabiting with a partner.
-
-### Analysis of variance {#sec:analysis-of-variance}
+The exception was Mozambique, where the majority (`r 100 - round(moz_Y015_019_nosex12m$estimate_smoothed, 2)`\%) were sexually active in the past year and close to a third (`r round(moz_Y015_019_sexcohab$estimate_smoothed, 2)`\%) were cohabiting with a partner.
 
@@
 
-**S1**: Appendix
-**S2**: Supplementary tables and figures
+**Appendix A**: Statistical modelling
+**Appendix B**: Supplementary tables and figures
 

### 2022-06-15 src/docs_paper/paper.Rmd
Ran docs_paper to send to Imperial coauthors, added Katie's feedback on abstract #128

@@
   **Background:**
-  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for   HIV prevention and recommends differentiating intervention portfolios geographically based on local HIV incidence   and individual risk behaviours.
+  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
+  We aimed to estimate occurance of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
 
@@
   We analysed 47 geospatially referenced national household surveys conducted between 1999-2018 across 13 Global   Fund priority countries in sub-Saharan Africa.
-  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual partnerships.
-  We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year and five-year age group.
-  We then assessed the efficiency of prioritising interventions according to these risk groups.
+  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual behaviour.
+  We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
+  Using the UNAIDS Naomi modelled district-level estimates of HIV prevalence and incidence, we then estimated new HIV infections and incidence in each risk group and assessed the efficiency of prioritising interventions according to risk group.
 
@@
   Risk group proportions varied substantially across age groups (`r "num"`\% of variation), countries (`r "num"`\%), and between districts within each country (`r "num"`\%), but changed little over time (`r "num"`\%).
-  Among women aged 20-29, we found a geographic delineation, north of which in eastern Africa, cohabiting (`r "num"`\%) is more common than non-regular partner(s) (`r "num"`\%), and south of which, non-regular partner(s) (`r "num"`\%) are more common than cohabiting (`r "num"`\%).
-  Prioritisation based on behavioural risk, in combiniation with location and age based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r "num"`\% to `r "num"`\%.
+  Among women aged 20-29, we found a geographic delineation, north of which, in eastern Africa, cohabiting (`r "num"`\%) is more common than non-regular partner(s) (`r "num"`\%), and south of which, non-regular partner(s) (`r "num"`\%) are more common than cohabiting (`r "num"`\%).
+  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r "num"`\% to `r "num"`\%.
   Female sex workers were `r "num"`\% of the at risk population but `r "num"`\% of all new infections.
@@
 author_summary: |
-  The risk HIV poses to adolescent girls and young women depends on the extent of HIV in the local community as well as individual sexual behaviour.
+  The risk HIV poses to adolescent girls and young women depends on individual sexual behaviour as well as the extent of HIV in the local community.
+  The same sexual behaviour is more or less likely to result in HIV acquisiton depending on the scale of the epidemic in the community.
   To help policy makers identify and provide services to those at highest risk, we geographically mapped HIV risk groups using behavioural data from household surveys.
@@
 
-```{r echo=FALSE, fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question. \\label{fig:available-surveys}"}
+```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question. \\label{fig:available-surveys}"}
 knitr::include_graphics("depends/available-surveys.pdf")
@@
 
-```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
+```{r results='hide', warning=FALSE, message=FALSE}
 available_surveys <- read_csv("depends/available-surveys.csv")
@@
 
-```{r continental-map, echo=FALSE, fig.cap="Choropleths of the posterior mean proportion of AGYW in each risk group in 2018.
+```{r continental-map, fig.cap="Choropleths of the posterior mean proportion of AGYW in each risk group in 2018.
 Countries in grey are included to show Cameroon (upper left) in relation to the other twelve spatially-contiguous countries (lower right).
 \\label{fig:continental-map}"}
-knitr::include_graphics("depends/3p1-continental-map.pdf")
+knitr::include_graphics("depends/3p1-continental-map.png")
 ```
 
-```{r within-between-country-variation, echo=FALSE, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions.
+```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions.
 We used regions of sub-Saharan Africa defined according to the UN geocode (M49).
-\\ref{fig:within-between-country-variation}"}
+\\label{fig:within-between-country-variation}"}
 knitr::include_graphics("depends/3p1-within-between-country-variation.pdf")
@@
 
-```{r echo=FALSE}
+```{r results=FALSE}
 df_3p1_subnational <- read_csv("depends/df_3p1_subnational.csv")
@@
 #' (Just MOZ!)
-df_3p1_national %>%
+majority_claim_moz <- df_3p1_national %>%
   filter(
@@
 
-```{r echo=FALSE, fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached.
-\\ref{fig:infections-reached}"}
+```{r fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached.
+\\label{fig:infections-reached}"}
 knitr::include_graphics("depends/infections-reached.pdf")
@@
 
+```{r results=FALSE}
+inf <- read_csv("depends/infections-reached.csv")
+inf_country <- readRDS("depends/infections-reached-country.rds")
+
+#' What is the minimum proportion of the population to reach in order to
+#' achieve reaching over q \in [0, 1] proportion of the new infections?
+min_pop_reached <- function(inf, q) {
+  inf %>%
+    filter(prop_infections_averted_cumulative > q) %>%
+    group_by(stratification) %>%
+    filter(prop_population_cumulative == min(prop_population_cumulative)) %>%
+    select(stratification, prop_infections_averted_cumulative, prop_population_cumulative)
+}
+
+inf_quarter <- min_pop_reached(inf, 0.25)
+inf_half <- min_pop_reached(inf, 0.5)
+
+inf_half_with_behaviour <- round(100 * filter(inf_half, stratification == "Area, age, behaviour")$prop_population_cumulative, 1)
+inf_half_without_behaviour <- round(100 * filter(inf_half, stratification == "Area, age")$prop_population_cumulative, 1)
+
+#' At a national level
+country_min_pop <- lapply(inf_country, function(x) min_pop_reached(x, q = 0.25)) %>%
+  bind_rows(.id = "country") %>%
+  filter(stratification %in% c("Area, age, behaviour", "Area, age"))
+
+inf_country_half <- country_min_pop %>%
+  group_by(stratification) %>%
+  summarise(
+    max = 100 * round(max(prop_population_cumulative), 3),
+    median = 100 * round(median(prop_population_cumulative), 3),
+    min = 100 * round(min(prop_population_cumulative), 3)
+  )
+
+inf_country_half_with_behaviour <- filter(inf_country_half, stratification == "Area, age, behaviour")
+inf_country_half_without_behaviour <- filter(inf_country_half, stratification == "Area, age")
+
+#' What proportion of new infections are among FSW as compared with the proportion the population that are FSW?
+inf_fsw <- inf %>%
+  filter(
+    stratification == "Behaviour",
+    category == "sexpaid12m"
+  ) %>%
+  select(prop_infections_averted_cumulative, prop_population_cumulative) %>%
+  mutate(across(everything(), ~ 100 * signif(.x, digits = 3)))
+
+#' What about by country?
+inf_fsw_country <- lapply(inf_country, function(x)
+  x %>%
+    filter(stratification == "Behaviour", category == "sexpaid12m") %>%
+    select(prop_infections_averted_cumulative, prop_population_cumulative) %>%
+      mutate(across(prop_infections_averted_cumulative:prop_population_cumulative, ~ 100 * signif(.x, digits = 3)))
+) %>%
+  bind_rows(.id = "country")
+
+inf_fsw_kenya <- filter(inf_fsw_country, country == "Kenya")
+inf_fsw_tanzania <- filter(inf_fsw_country, country == "Tanzania")
+```
+
 For any given fraction of AGYW prioritised, substantially more new infections were reached by strategies that included behavioural risk stratification.
-Reaching half of all new infections required reaching `r "num"`\% of the population when stratifying by area and age, but only `r "num"`\% when behavioural stratification was included (Fig \ref{fig:infections-reached}).
-The majority of this benefit came from reaching FSW, who were `r "num"`\% of the population but `r "num"`\% of all new infections.
+Reaching half of all new infections required reaching `r inf_half_without_behaviour`\% of the population when stratifying by area and age, but only `r inf_half_with_behaviour`\% when behavioural stratification was included (Fig \ref{fig:infections-reached}).
+The majority of this benefit came from reaching FSW, who were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all new infections.
 
-Efficiency was reduced if prioritisation was done separately by country.
-On average, reaching half of new infections in a country required reaching `r "num"`\% (range `r "num"`-`r "num"`\%) of the population when stratifying by area and age, reducing to `r "num"`\% (range `r "num"`-`r "num"`\%) when behaviour was included.
-The importance of stratifying risk upon age, location and behaviour within a country varied, analogous to the varying contribution of each to the total variance (Sec \@ref(analysis-of-variance)).
-For example, FSW in Tanzania were estimated to be `r "num"`\% of the population and close to half (`r "num"`\%) of all new infections, whereas FSW in Namibia were just `r "num"`\% of the population and `r "num"`\% of all new infections.
+Considering each country separately, on average, reaching half of new infections required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
+The importance of stratifying risk upon age, location and behaviour within a country varied, analogous to the varying contribution of each to the total variance (Appendix B).
+For example, FSW in Kenya were estimated to be `r inf_fsw_kenya$prop_population_cumulative`\% of the population and close to a third (`r inf_fsw_kenya$prop_infections_averted_cumulative`\%) of all new infections, whereas FSW in Tanzania were just `r inf_fsw_tanzania$prop_population_cumulative`\% of the population and `r inf_fsw_tanzania$prop_infections_averted_cumulative`\% of all new infections.
 
@@
 
-To the best of our knowledge, the only previous research to geographically map AGYW HIV risk groups is @brugh2021characterizing, who use biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups.
+To the best of our knowledge, the only previous research to geographically map AGYW HIV risk groups is @brugh2021characterizing, who use biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups using a range of machine learning techniques.
+Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform policy.
 
-This work serves as a case-study in how to use the multinomial-Poisson transformation to efficiently specify and fit multinomial spatio-temporal models in `R-INLA`.
-We used Kronecker products over Gaussian Markov random fields to define appropriate category-specific spatio-temporal random effects.
+As well, this work serves as a case-study in how to use the multinomial-Poisson transformation to efficiently specify and fit multinomial spatio-temporal models in `R-INLA`.
+Specifically, we used Kronecker products over Gaussian Markov random fields to define appropriate category-specific spatio-temporal random effects.
 
@@
 
-**Appendix A**: Statistical modelling
+**Appendix A**: Statistical modelling \newline
 **Appendix B**: Supplementary tables and figures
@@
 JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664). 
-
 This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.

### 2022-06-15 make/8_docs.R

@@ -1,2 +1,10 @@
 run_commit_push("plot-tikz_category-flowchart")
+
+#' Presentations
+run_commit_push("docs_12-05-22-mrc-gida")
+
+#' Posters
 run_commit_push("docs_amazon-poster")
+
+#' Paper and appendices
+run_commit_push("docs_paper")

### 2022-06-16 src/docs_paper/paper.Rmd
Some edits from Jeff and Katie plus making the abstract use proper numbers #128

@@
     affiliation: [A, B]
+  - name: Rachel Esra
+    affiliation: B    
   - name: Lycias Zembe
@@
     affiliation: F
-  - name: Jeff W. Eaton
+  - name: Jeffrey W. Eaton
     affiliation: B
@@
     address: Department of Computer Science, University of Oxford
-abstract: |
-  **Background:**
-  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
-  We aimed to estimate occurance of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
-
-  **Methods:**
-  We analysed 47 geospatially referenced national household surveys conducted between 1999-2018 across 13 Global   Fund priority countries in sub-Saharan Africa.
-  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual behaviour.
-  We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
-  Using the UNAIDS Naomi modelled district-level estimates of HIV prevalence and incidence, we then estimated new HIV infections and incidence in each risk group and assessed the efficiency of prioritising interventions according to risk group.
-
-  **Results:**
-  Data consisted of `r "num"` female survey respondents aged 15-29.
-  Risk group proportions varied substantially across age groups (`r "num"`\% of variation), countries (`r "num"`\%), and between districts within each country (`r "num"`\%), but changed little over time (`r "num"`\%).
-  Among women aged 20-29, we found a geographic delineation, north of which, in eastern Africa, cohabiting (`r "num"`\%) is more common than non-regular partner(s) (`r "num"`\%), and south of which, non-regular partner(s) (`r "num"`\%) are more common than cohabiting (`r "num"`\%).
-  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r "num"`\% to `r "num"`\%.
-  Female sex workers were `r "num"`\% of the at risk population but `r "num"`\% of all new infections.
-
-  **Conclusions:**
-  Our risk group estimates provide data for HIV programmes to implement a differentiated prevention approach and set targets according to the Global AIDS Strategy.
-  Successfully implementing this approach would result in finding substantially more infections, particularly among female sex workers.
-author_summary: |
-  The risk HIV poses to adolescent girls and young women depends on individual sexual behaviour as well as the extent of HIV in the local community.
-  The same sexual behaviour is more or less likely to result in HIV acquisiton depending on the scale of the epidemic in the community.
-  To help policy makers identify and provide services to those at highest risk, we geographically mapped HIV risk groups using behavioural data from household surveys.
-  Doing so also allowed us to estimate the the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
 bibliography: citations.bib
@@
 )
+
+comma <- function(x) formatC(x, format = "d", big.mark = ",")
 ```
@@
 
+\clearpage
+
 # Introduction
@@
 
-HIV prevention for AGYW is typically comprised of: (1) basic programming which is made available to all (2) more intensified programming which is differentiated on the basis of risk [@joint2016hiv; @birdthistle2018evaluating].
-To maximize the impact of intensified programming delivery should be prioritised towards those at the highest risk level.
-As both community-level epidemic indicators and individual-level behaviours determine risk of acquiring HIV, it is important to consider both of these factors in tandem to enable more efficient prioritisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+<!-- HIV prevention for AGYW is typically comprised of: (1) basic programming which is made available to all (2) more intensified programming which is differentiated on the basis of risk [@joint2016hiv; @birdthistle2018evaluating].
+-->
+<!-- To maximize the impact of intensified programming delivery should be prioritised towards those at the highest risk level. -->
+<!-- As both community-level epidemic indicators and individual-level behaviours determine risk of acquiring HIV, it is important to consider both of these factors in tandem to enable more efficient prioritisation of prevention services.
+-->
 
-The Global AIDS Strategy 2021-2016 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying provision of HIV prevention to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour.
-Four prioritisation strata (Table) are defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1\% and >3\%), and (2) self-reported high-risk behaviour or recent STI infection.
+The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+Four prioritisation strata (Table) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
 The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table) based upon this prioritisation strata [@unaids2021global].
@@
 Implementation of the strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group by location to determine prioritisation for stratified HIV prevention.
-We developed a multivariate Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
+We developed a multinomial Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
 We focused on 13 countries in sub-Saharan Africa which have been identified by by the Global Fund to Fight AIDS, TB, and Malaria [@global2018measurement] as priority countries for implementation of AGYW HIV prevention.
@@
 \centering
-\begin{tabularx}{\textwidth}{llX}
+\begin{tabularx}{\textwidth}{llcc}
 \toprule
-Risk group & Description & Risk ratio \\
+Risk group & Description & Local HIV incidence & Incidence ratio \\
 \midrule
-None & Not sexually active & 0 \\
-Low & One cohabiting sexual partner & 1 \\
-High & Non-regular sexual partner(s) & 1.72 \\
-Very high & Female sex workers & {
-\begin{tabularx}{\linewidth}{ll}
-District-level HIV incidence & Risk ratio\\
-$>$3.0\% & 3 \\
-1.0-3.0\% & 6 \\
-0.3-1.0\% & 9 \\
-0.1-0.3\% & 13 \\
-$<$0.1\% & 25 \\
-\end{tabularx}
-} \\
+None & Not sexually active & -- & 0.0 \\
+Low & One cohabiting sexual partner & -- & 1.0 (Baseline) \\
+High & Non-regular sexual partner(s) & -- & 1.72 \\
+Very high & Female sex workers & $<$0.1\% & 25.0 \\
+ & & 0.1-0.3\% & 13.0 \\
+ & & 0.3-1.0\% & 9.0 \\
+ & & 1.0-3.0\% & 6.0 \\
+ & & $>$3.0\% & 3.0 \\
 \bottomrule
 \end{tabularx}
-\caption{HIV risk groups and incidence risk ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group.}
+\caption{HIV risk groups and assumed HIV incidence rate ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group.}
 \label{tab:risk-groups}
@@
 
-For each survey, we classified respondents into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
-These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who are female sex workers (FSW) (Table \ref{tab:risk-groups}).
+For each survey, we classified female respondents aged 15-29 years into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
+These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who report transactional sex (Table \ref{tab:risk-groups}).
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
-Exact survey questions varied to a limited extent between surveys (Appendix B).
+Exact survey questions varied slightly between surveys (Appendix B).
 Questions captured information about if the respondent had been sexually active in the past twelve months, and if so how with many partners.
@@
 
-Some surveys included a specific question asking if the respondent had received or given payment for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
+Some surveys included a specific question asking if the respondent had received money or gifts for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
 In surveys without that question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
-For this reason, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who were FSW or engaged in transactional sex.
+Because of this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who were FSW or engaged in transactional sex.
+We focused on estimating the proportion of women who reported transactional sex at a district level, and subsequently adjsuted these proportions to align to national estimates for the number of female sex workers.
 
-We used estimates of population, people living with HIV (PLHIV) and new HIV infections stratified by district and age group from outputs of the Naomi model [@eaton2021naomi].
-The model synthesises data from multiple sources to produce consistent subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
-The administrative area hierarchy and geographic boundaries we used correspond to those used in Naomi, with the exception of Cameroon and Kenya where we used an analysis level one higher (Appendix B).
+We used estimates of population, people living with HIV (PLHIV) and new HIV infections stratified by district and age group from HIV estimates published by UNAIDS that were developed using the Naomi model [@eaton2021naomi].
+The model synthesises data from multiple sources to produce subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
+The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning in UNAIDS Naomi estimates, except for Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Appendix B).
 
-## Two-stage risk group proportion model
+## Two-stage model for sexual risk group proportions
 
-To estimate the proportion of AGYW in each risk group we took a two-stage modelling approach, further details of which are provided in Appendix.
+To estimate the proportion of AGYW in each risk group we took a two-stage modelling approach.
 First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24 and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) cohabiting, and (3) either non-regular partner(s) or transactional sex.
@@
 Second, we fit a spatial logistic regression model separating those who have non-regular parnter(s) from those who have had transactional sex, stratified by district, and five-year age group, and using only data from the 13 surveys with a specific transaction sex question.
-As these surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in at least the high risk group was constant over time.
+As surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in at least the high risk group was constant over time.
 We combined the two models using 1000 samples from each posterior distribution to produce samples from all four risk groups.
@@
 To do so, we disaggregated national 15-49 FSW population size estimates from @stevens2022estimating using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions from @kinh2021trends.
+Technical details of the model are in Appendix A.
 
@@
 
-To calculate HIV prevalence by risk group we disaggregated on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
+To calculate HIV prevalence by risk group, we disaggregated on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
 Logit scaling was used because linear scaling resulted in some strata having prevalence above 100\%.
@@
 
-We disaggregated HIV incidence by risk group linearly using the HIV infection risk ratios given in Table \ref{tab:risk-groups}.
-The risk ratio used for the not sexually active risk group was zero, reflecting exclusion of incidence from non-sexual transmission, e.g. unsafe injection, which is negligible in these populations.
-For the non-regular partner(s) risk group, the risk ratio was based upon analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by @slaymaker2020croi and supported by the review of @jia2022risk.
-Risk ratios for the highest risk group vary based upon general population HIV incidence and are based upon a UNAIDS analysis led by Keith Sabin.
-Number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size.
+We disaggregated HIV incidence by risk group using the HIV infection risk ratios given in Table \ref{tab:risk-groups}.
+The risk ratio used for the not sexually active risk group was zero, excluding incidence from non-sexual transmission which is negligible in these populations.
+For the non-regular partner(s) risk group, the risk ratio was based on analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by @slaymaker2020croi and supported by the review of @jia2022risk.
+Risk ratios for the highest risk group vary based upon general population HIV incidence and are based on a UNAIDS analysis led by Keith Sabin.
+The number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size.
 
@@
 
-For each possible stratification of risk, we calculated the number of new infections that would be found per person reached when prioritising according to incidence.
-We assumed all members of every strata can be reached.
+For each possible stratification of risk, we calculated the expected number of new infections that would be found per person reached when prioritising according to incidence.
+To do so, we ordered the strata by descending incidence before cumulatively summing the expected incidence and population.
+We assumed it was possible to reach all members of every strata.
 
@@
 
-```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a transactional sex question. \\label{fig:available-surveys}"}
+```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
 knitr::include_graphics("depends/available-surveys.pdf")
@@
 #' How many AGYW, in total, were surveyed?
-agyw_surveyd <- available_surveys %>%
+agyw_surveyed <- available_surveys %>%
   pull(Y015_029) %>%
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table), with a total sample size of `r agyw_surveyd` women aged 15-29 years (`r agyw_surveyed_age$Y015_019` aged 15-19 years, `r agyw_surveyed_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
-Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size in these surveys of `r agyw_surveyed_giftsvar` (`r agyw_surveyed_giftsvar_age$Y015_019` aged 15-19 years, `r agyw_surveyed_giftsvar_age$Y020_024` aged 20-24 years, and `r agyw_surveyed_giftsvar_age$Y025_029` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size in these surveys of `r comma(agyw_surveyed_giftsvar)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029)` aged 25-29 years).
 The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
@@
 
+---
+abstract: |
+  **Background:**
+  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiated intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
+  We aimed to estimate occurance of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
+
+  **Methods:**
+  We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 Global Fund priority countries in sub-Saharan Africa.
+  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual behaviour.
+  We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
+  Using the UNAIDS district-level estimates of HIV prevalence and incidence, we estimated new HIV infections in each risk group by district and age group.
+  We then assessed the efficiency of prioritising interventions according to risk group.
+
+  **Results:**
+  Data consisted of `r comma(agyw_surveyed)` female survey respondents aged 15-29.
+  Risk group proportions varied substantially across age groups (`r variance_proportions_age$mean`\% of total variation), countries (`r variance_proportions_iso3$mean`\%), and between districts within each country (`r variance_proportions_area$mean`\%), but changed little over time (`r variance_proportions_year$mean`\%).
+  Among women aged 20-29, cohabiting (`r dividing_border_above_sexcohab$median`\%) was more common in eastern Africa than non-regular partner(s) (`r dividing_border_above_sexnonreg$median`\%), while in southern countries non-regular partner(s) (`r dividing_border_below_sexnonreg$median`\%) were more common than cohabiting (`r dividing_border_below_sexcohab$median`\%).
+  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
+  Female sex workers were `r inf_fsw$prop_population_cumulative`\% of the at risk population but `r inf_fsw$prop_infections_averted_cumulative`\% of all new infections.
+
+  **Conclusions:**
+  Our risk group estimates provide data for HIV programmes to set targets and implement differentiated prevention strategies outlined in the Global AIDS Strategy.
+  Successfully implementing this approach would result in more efficiently reaching substantially more at risk for infections.
+
+author_summary: |
+  Exposure to HIV among adolescent girls and young women depends on individual sexual behaviour and the level of HIV in the local community among potential sexual partners.
+  To support HIV programmes in identifying and providing services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
+  Doing so also allowed us to estimate the the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
+---
+
 # Discussion

### 2022-06-17 src/docs_paper/paper.Rmd
Updating main text based on Katie and Jeff's comments (again) #128

@@
 
+<!-- TODO: Follow up with Clemens r.e. FSW group name: -->
+<!-- There are a couple of options: female sex workers, young women from key populations (and clarify in the text that you mean sex work), AGYW who sell sex.
+Many people who do this work all the time use "FSW" so likely fine, but there's also a move away from defining someone by their job making "who sell sex" possibly the preferred option.
+-->
+
 In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r population_percent`\% of the population but `r infections_percent`\% of new HIV infections [@unaids2021update].
@@
 
-<!-- HIV prevention for AGYW is typically comprised of: (1) basic programming which is made available to all (2) more intensified programming which is differentiated on the basis of risk [@joint2016hiv; @birdthistle2018evaluating].
--->
-<!-- To maximize the impact of intensified programming delivery should be prioritised towards those at the highest risk level. -->
-<!-- As both community-level epidemic indicators and individual-level behaviours determine risk of acquiring HIV, it is important to consider both of these factors in tandem to enable more efficient prioritisation of prevention services.
--->
-
 The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
-Four prioritisation strata (Table) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
-The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table) based upon this prioritisation strata [@unaids2021global].
+Four prioritisation strata (Table B.X) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
+The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table B.X) based upon this prioritisation strata [@unaids2021global].
+All AGYW are recommended to have access to a basic package of HIV prevention, while those with with high risk behaviours in moderate incidence settings and all AGYW in very high incidence settings are recommended to have access to enhanced intervention packages [@joint2016hiv; @birdthistle2018evaluating].
+<!-- TODO: Add "basic package of HIV prevention consisting of... -->
 These interventions may include STI screening and treatment, access to pre-exposure prophylaxis (PrEP), access to post-exposure prophylaxis (PEP), comprehensive sexuality education, and economic empowerment.
@@
 We developed a multinomial Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
-We focused on 13 countries in sub-Saharan Africa which have been identified by by the Global Fund to Fight AIDS, TB, and Malaria [@global2018measurement] as priority countries for implementation of AGYW HIV prevention.
+We focused on 13 countries in sub-Saharan Africa which have been identified by the Global Fund to Fight AIDS, TB, and Malaria [@global2018measurement] as priority countries for implementation of AGYW HIV prevention.
 Our methodology is standardised across countries, allowing prioritisation both within and between countries.
@@
 \centering
-\begin{tabularx}{\textwidth}{llcc}
+\begin{tabularx}{\textwidth}{llll}
 \toprule
@@
 None & Not sexually active & -- & 0.0 \\
-Low & One cohabiting sexual partner & -- & 1.0 (Baseline) \\
-High & Non-regular sexual partner(s) & -- & 1.72 \\
+Low & One cohabiting partner & -- & 1.0 (Baseline) \\
+High & Non-regular or multiple partner(s) & -- & 1.72 \\
 Very high & Female sex workers & $<$0.1\% & 25.0 \\
@@
 \end{tabularx}
-\caption{HIV risk groups and assumed HIV incidence rate ratios giving the ratio of probabilities of being sexually infected with HIV in the next year relative to the baseline group.}
+\caption{HIV risk groups and assumed HIV incidence rate ratio for each risk group relative to AGYW with one cohabiting sexual partner.
+Among FSW, the incidence rate ratio depended on the level of HIV incidence among the general population.
+The incidence rate ratio for women with non-regular or multiple sexual partner(s) was derived from analysis of ALPHA network data.
+The incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.}
 \label{tab:risk-groups}
@@
 We included surveys conducted in these countries in the years 1999-2018 in which women were interviewed about their sexual behaviour and sufficient geographic information was available to locate survey clusters to districts.
-Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS), Population-based HIV Impact Assessment (PHIA) surveys, and the Botswana HIV/AIDS Impact Survey 2013 (BAIS) were included.
+Demographic and Health Surveys (DHS) [@measure2012sampling], AIDS Indicator Surveys (AIS) [@ais], Population-based HIV Impact Assessment (PHIA) [@phia] surveys, and the Botswana AIDS Impact Survey 2013 (BAIS) [@botswana2013botswana] were included.
 
@@
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
-Exact survey questions varied slightly between surveys (Appendix B).
-Questions captured information about if the respondent had been sexually active in the past twelve months, and if so how with many partners.
+<!-- TODO: Include example of inconsistent result. -->
+Exact survey questions varied slightly across survey types and between survey phases (Appendix B).
+Questions captured information about whether the respondent had been sexually active in the past twelve months, and if so how with many partners.
 For their three most recent partners, respondents were also asked about the type of partnership (spouse, cohabiting partner, partner not cohabiting with respondent, friend, sex worker, sex work client, and other).
 
-Some surveys included a specific question asking if the respondent had received money or gifts for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
+Some surveys included a specific question asking if the respondent had received or given money or gifts for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
 In surveys without that question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
-Because of this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who were FSW or engaged in transactional sex.
-We focused on estimating the proportion of women who reported transactional sex at a district level, and subsequently adjsuted these proportions to align to national estimates for the number of female sex workers.
+Because of this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who engaged in transactional sex.
+We focused on estimating the proportion of women who reported transactional sex at a district level, and subsequently adjusted these proportions to align to national estimates for the number of female sex workers.
 
@@
 To estimate the proportion of AGYW in each risk group we took a two-stage modelling approach.
-First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24 and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) cohabiting, and (3) either non-regular partner(s) or transactional sex.
-Combining the two highest risk groups in this way allowed data from all 47 surveys to be included in this first stage model.
-Second, we fit a spatial logistic regression model separating those who have non-regular parnter(s) from those who have had transactional sex, stratified by district, and five-year age group, and using only data from the 13 surveys with a specific transaction sex question.
-As surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in at least the high risk group was constant over time.
+First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24 and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) one cohabiting partner, and (3) either non-regular or multiple partner(s), or transactional sex.
+Combining the two highest risk groups (high and very high) in this way allowed data from all surveys to be included in this first stage model.
+Second, we fit a spatial logistic regression model separating those who have non-regular or multiple partner(s) or multiple partners from those who reported transactional sex, stratified by district, and five-year age group, and using only data from the surveys with a specific transactional sex question.
+As surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in the two highest risk groups was constant over time.
 We combined the two models using 1000 samples from each posterior distribution to produce samples from all four risk groups.
-Finally, we adjusted the samples from the transactional sex category to match age-country specific FSW population size estimates, modifying the samples from the non-regular partner(s) category such that the proportions sum to one.
-To do so, we disaggregated national 15-49 FSW population size estimates from @stevens2022estimating using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions from @kinh2021trends.
-Technical details of the model are in Appendix A.
+Finally, we adjusted the samples from the transactional sex category to match age- and country-specific FSW population size estimates.
+To ensure that after adjustment the risk group proportions still sum to one, we made appropriate modifications to the samples from the non-regular or multiple partner(s) category.
+FSW population size estimates were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@kinh2021trends].
+Technical details of the models used are in Appendix A.
 
@@
 
-We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A).
+We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.X).
 All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
@@
 Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts.
-To understand the importance of each part of the model we undertook a variance-based sensitivity analysis using the random effect variance parameters.
+To understand the importance of each part of the model we analysed the relative sizes of the variance parameters for each effect.
 
-For the logistic regression model for the proportion engaging in transactional sex among those with non-regular partner(s), we considered six specifications (Appendix A).
-Each included an intercept, age and country effects, and a spatial effect allowing district level variation.
+For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Appendix A.X).
+Each included an intercept, age and country effects, and a spatial effect allowing district-level variation.
 Both independent and spatially correlated spatial effects were considered.
-To improve estimation with sparse data, we considered model alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months, available from @hodgins2022population.
+To improve estimation with sparse data, during model selection we considered alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months [@hodgins2022population].
 
@@
 The \textsc{R} [@r] code used to implement the models and produce  results is available from `github.com/athowes/multi-agyw`.
-We used the `orderly` package [@orderly] for reproducible research.
+We used `sf` [@pebesma2018sf] for handling of spatial data, `orderly` [@orderly] for reproducible research, `ggplot2` for data visualisation [@wickham2016ggplot2] and `rticles` [@allaire2022rticles] for reporting via `rmarkdown` [@allaire2022rmarkdown].
 
@@
 
-We used the risk group proportion estimates to calculate HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified according to district, age group and risk group by disaggregating estimates from the Naomi model.
-Further details are provided in Appendix A.
+Using risk group proportion estimates, and Naomi model estimates, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
+Further details are provided in Appendix A.X.
 
@@
 
-To calculate HIV prevalence by risk group, we disaggregated on the logit scale using age-country prevalence log-odds ratios calculated from survey bio-marker data. 
-Logit scaling was used because linear scaling resulted in some strata having prevalence above 100\%.
-PLHIV were calculated by multiplying HIV prevalence by risk group population size.
+To calculate HIV prevalence by risk group, we disaggregated the district-age specific prevalence estimates from Naomi estimates to risk groups using odds ratios for the relative odds of having HIV between risk groups, calculated from a logistic regression of country-age specific household survey HIV bio-marker data.
+Prevalence disaggregation was on the logit scale to ensure that HIV prevalence in each risk group remained in the range 0\% to 100\%.
+The number of PLHIV was calculated by multiplying HIV prevalence by risk group population size.
 
-### Incidence and new infection
+### Incidence and new infections
 
-We disaggregated HIV incidence by risk group using the HIV infection risk ratios given in Table \ref{tab:risk-groups}.
+We disaggregated HIV incidence by risk group using the HIV infection risk ratios in Table \ref{tab:risk-groups}.
 The risk ratio used for the not sexually active risk group was zero, excluding incidence from non-sexual transmission which is negligible in these populations.
-For the non-regular partner(s) risk group, the risk ratio was based on analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa by @slaymaker2020croi and supported by the review of @jia2022risk.
-Risk ratios for the highest risk group vary based upon general population HIV incidence and are based on a UNAIDS analysis led by Keith Sabin.
+For the non-regular or multiple partner(s) risk group, the risk ratio was based on analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa [@slaymaker2020croi] and supported a recent systematic review [@jia2022risk].
+Risk ratios for the highest risk group vary based upon general population HIV incidence and are based on an analysis of HIV prevalence among FSW relative to population prevalence [@aidsinfo] using data from the UNAIDS Key Population Atlas [@kpatlas].
 The number of new HIV infections were calculated by multiplying HIV incidence by susceptible risk group population size.
@@
 For each possible stratification of risk, we calculated the expected number of new infections that would be found per person reached when prioritising according to incidence.
-To do so, we ordered the strata by descending incidence before cumulatively summing the expected incidence and population.
+To do so, we ordered the strata by descending incidence before cumulatively summing the expected new infections and population.
 We assumed it was possible to reach all members of every strata.
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.X), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
 Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size in these surveys of `r comma(agyw_surveyed_giftsvar)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029)` aged 25-29 years).
@@
 
-## Model selection
+## Model selection and model fit
 
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria is provided in Appendix A for all considered models.
+Model performance according to the CPO criteria is provided in Appendix A.X for all considered models.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level.
 
@@
 
-Posterior mean estimates from our final model are shown as choropleths (Fig \ref{fig:continental-map}) and dotplots (Fig \ref{fig:within-between-country-variation}).
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level.
-Posterior mean, median, upper (97.5\%) and lower (2.5\%) credible estimates for each district, age group and year from our final model are provided in the supplementary material.
-In the writing to follow, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
+Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model.
+Posterior mean, median, and 95\% credible intervals are provided in supplementary material as `estimates.csv`.
+In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
 
@@
 
-The median proportion of FSW nationally was `r fsw_age_Y015_019$median`\% (95\% CI `r fsw_age_Y015_019$lower`--`r fsw_age_Y015_019$upper`\%) for the 15-19 age group, `r fsw_age_Y020_024$median`\% (95\% CI `r fsw_age_Y020_024$lower`--`r fsw_age_Y020_024$upper`\%) for the 20-24 age group and `r fsw_age_Y025_029$median`\% (95\% CI `r fsw_age_Y025_029$lower`--`r fsw_age_Y025_029$upper`\%) for the 25-29 age group.
+The median national FSW proportion was `r fsw_age_Y015_019$median`\% (95\% CI `r fsw_age_Y015_019$lower`--`r fsw_age_Y015_019$upper`\%) for the 15-19 age group, `r fsw_age_Y020_024$median`\% (95\% CI `r fsw_age_Y020_024$lower`--`r fsw_age_Y020_024$upper`\%) for the 20-24 age group and `r fsw_age_Y025_029$median`\% (95\% CI `r fsw_age_Y025_029$lower`--`r fsw_age_Y025_029$upper`\%) for the 25-29 age group.
 
-In the 20-24 and 25-29 year age groups, the majority of women were either cohabiting or had non-regular partner(s).
-Countries in eastern and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r dividing_border_above_sexcohab$median`\% [95\% CI `r dividing_border_above_sexcohab$lower`--`r dividing_border_above_sexcohab$upper`\%] as compared with `r dividing_border_above_sexnonreg$median`\% [95\% CI `r dividing_border_above_sexnonreg$lower`--`r dividing_border_above_sexnonreg$upper`\%] with non-regular partner[s]) and countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular partner(s) (`r dividing_border_below_sexnonreg$median`\% [95\% CI `r dividing_border_below_sexnonreg$lower`--`r dividing_border_below_sexnonreg$upper`\%], as compared with `r dividing_border_below_sexcohab$median`\% [95\% CI `r dividing_border_below_sexcohab$lower`--`r dividing_border_below_sexcohab$upper`\%] cohabiting).
+<!-- I would like some more quantitive results here comparing the amount of within-country variation vs. between country variation. -->
+
+In the 20-24 and 25-29 year age groups, the majority of women were either cohabiting or had non-regular or multiple partner(s).
+Countries in eastern and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r dividing_border_above_sexcohab$median`\% [95\% CI `r dividing_border_above_sexcohab$lower`--`r dividing_border_above_sexcohab$upper`\%] as compared with `r dividing_border_above_sexnonreg$median`\% [95\% CI `r dividing_border_above_sexnonreg$lower`--`r dividing_border_above_sexnonreg$upper`\%] with non-regular partner[s]).
+In contrast, countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular or multiple partner(s) (`r dividing_border_below_sexnonreg$median`\% [95\% CI `r dividing_border_below_sexnonreg$lower`--`r dividing_border_below_sexnonreg$upper`\%], compared with `r dividing_border_below_sexcohab$median`\% [95\% CI `r dividing_border_below_sexcohab$lower`--`r dividing_border_below_sexcohab$upper`\%] cohabiting).
 This clear geographic delineation passes along the border of Mozambique, through the interior of Zimbabwe and along the border of Zambia (Fig \ref{fig:continental-map}).
@@
 Age explained `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`\%) of the variation in risk group proportions.
-Variance explained by location may be broken down into `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`\%) explained by country and `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`\%) explained by district.
-The temporal effects only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`\%) of variation, indicating very little change in risk group proportions over time.
+Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`\%) of variation and district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`\%).
+Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`\%) of variation, indicating very little change in risk group proportions over time.
 We observed similar variance decomposition results fitting each country individually, and using other model specifications.
+
+<!-- Are these results presented? (A reviewer might ask for it if referencing here; but fine to leave as this statement for now.) -->
 
@@
 
-## Infections reached
+## Expected infections reached
 
-```{r fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population reached.
+```{r fig.cap="Percentage of new infections reached across all 13 countries, taking a variety of risk stratification approaches, against the percentage of at risk population required to be reached.
 \\label{fig:infections-reached}"}
@@
 For any given fraction of AGYW prioritised, substantially more new infections were reached by strategies that included behavioural risk stratification.
-Reaching half of all new infections required reaching `r inf_half_without_behaviour`\% of the population when stratifying by area and age, but only `r inf_half_with_behaviour`\% when behavioural stratification was included (Fig \ref{fig:infections-reached}).
+Reaching half of all expected new infections required reaching `r inf_half_without_behaviour`\% of the population when stratifying by subnational area and age, but only `r inf_half_with_behaviour`\% when behavioural stratification was included (Fig \ref{fig:infections-reached}).
 The majority of this benefit came from reaching FSW, who were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all new infections.
+
+<!-- How does this vary by country / region?
+Maybe worth calling out result for West Africa vs.
+East Africa vs.
+Southern Africa here to highlight the difference.
+Also how does this compare with other estimates?
+And what does Oli think about this?
+I recognize that comparison is not straightforward because age group difference!
+-->
 
@@
 
+<!-- Are we able to add an analysis of the number who are prioritized for the 'standard' and 'enhanced' prevention packages in the Global Strategy?
+That gets a lot of emphasis in the Introduction, so would be nice to report about here.
+-->
+
 ---
@@
   The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiated intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
-  We aimed to estimate occurance of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
+  We aimed to estimate occurrence of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
 
@@
   We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 Global Fund priority countries in sub-Saharan Africa.
-  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular partner[s] and female sex workers) based on reported sexual behaviour.
+  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular or multiple partner[s] and female sex workers) based on reported sexual behaviour.
   We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
@@
   Risk group proportions varied substantially across age groups (`r variance_proportions_age$mean`\% of total variation), countries (`r variance_proportions_iso3$mean`\%), and between districts within each country (`r variance_proportions_area$mean`\%), but changed little over time (`r variance_proportions_year$mean`\%).
-  Among women aged 20-29, cohabiting (`r dividing_border_above_sexcohab$median`\%) was more common in eastern Africa than non-regular partner(s) (`r dividing_border_above_sexnonreg$median`\%), while in southern countries non-regular partner(s) (`r dividing_border_below_sexnonreg$median`\%) were more common than cohabiting (`r dividing_border_below_sexcohab$median`\%).
+  Among women aged 20-29, cohabiting (`r dividing_border_above_sexcohab$median`\%) was more common in eastern Africa than non-regular or multiple partner(s) (`r dividing_border_above_sexnonreg$median`\%), while in southern countries non-regular or multiple partner(s) (`r dividing_border_below_sexnonreg$median`\%) were more common than cohabiting (`r dividing_border_below_sexcohab$median`\%).
   Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
@@
 
+<!-- TODO: Include key conclusions in author summary. -->
+
 # Discussion
@@
 We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with pressing HIV prevention requirements.
-Our estimates will enable country and district-level planners to differentiate prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
+Our estimates support consideration of differentiated prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
 <!-- Some type of comment about how novel this would be if implemented -->
 
-By considering all possible risk stratification strategies, we showed that successful implementation of a risk-stratified approach would allow substantially more new infections to be found before they occur.
-A considerable proportion of these new infections are among FSW, supporting the case for HIV programming efforts focused on key population groups [@baral2012burden].
-We showed that there is substantial variation in the importance of prioritisation by age, location and behaviour within each country.
+By considering all possible risk stratification strategies, we showed that successful implementation of a risk-stratified approach would allow substantially more of those at risk for infections to be identified before infection occurs.
+A considerable proportion estimated new infections were among FSW, supporting the case for HIV programming efforts focused on key population groups [@baral2012burden].
+There is substantial variation in the importance of prioritisation by age, location and behaviour within each country.
 This highlights the importance of understanding and tailoring HIV prevention efforts to country-specific contexts.
@@
 The delineation does not represent a boundary between predominately Christian and Muslim populations, which is further north.
-We also note that the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique, reflecting existing concerns [@unicef].
+We also note that the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique [@unicef].
 
@@
 
-To the best of our knowledge, the only previous research to geographically map AGYW HIV risk groups is @brugh2021characterizing, who use biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups using a range of machine learning techniques.
-Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform policy.
+@brugh2021characterizing previously geographically mapped AGYW HIV risk groups using biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
+Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
 
@@
 
-Our FSW estimates do not overcome the difficulties of sampling hard to reach groups, specifically the possibility of being excluded from household sampling frames.
-As well, we did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
+Our FSW estimates do not overcome the difficulties of sampling hard to reach groups.
+We did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
 
-Our analysis of the number of infections that could be reached by each risk stratification strategy was based on simplifying assumptions and should therefore be interpreted as illustrating the potentially obtainable benefits, rather than benefits that would be accrued from any specific intervention strategy.
+The extent to which the efficiencies from risk-stratified prioritisation depends on the ability of programmes to identify and efficiently reach those in each risk category.
+In practice, this is likely to result in substantially less efficiency in the number of potential infections averted for a given proportion of the population reached compared to the 'best-case' frontier analysis in which we assumed those in each risk category could be perfectly reached.
+These results therefore be interpreted as illustrating the potential
+maximal benefits, rather than benefits that would be accrued from any
+specific intervention strategy. Factors we did not consider include the
+greater administrative burden of more complex strategies, variation in
+difficulty or feasibility of reaching individuals in each strata,
+variation in the range or effectiveness of interventions by strata, and
+changes in strata membership that may occur during the course of a year.
+Empirical evaluations of risk screening tools to stratify individual HIV infection risk have found only moderate discriminatory ability [CITE Jia et al.] and risk behaviour may change rapidly among young populations, further increasing the challenge to effectively deliver prevention packages to those at risk at the right times.
+
+The efficiency of each stratified prevention strategy depends on the ability of programmes to identify and effectively reach those in each strata.
+Our analysis assumed a "best-case" scenario where AGYW of every strata are reached perfectly, and should therefore be interpreted as illustrating the potentially obtainable benefits rather than benefits which would be obtained from any specific intervention strategy.
+In practice, stratified prevention strategies are likely to be substantially less efficient than this best-case scenario.
 Factors we did not consider include the greater administrative burden of more complex strategies, variation in difficulty or feasibility of reaching individuals in each strata, variation in the range or effectiveness of interventions by strata, and changes in strata membership that may occur during the course of a year.
+Identifying and reaching behavioural strata may be particularly challenging.
+Empirical evaluations of behavioural risk screening tools have found only moderate discriminatory ability [@jia2022risk], and risk behaviour may change rapidly among young populations, increasing the challenge to effectively deliver appropriately timed prevention packages.
 
@@
 
-Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the wider population of all adults of both sexes.
-By limiting our consideration to this group we didn't account for `r "num"`\% of all new infections [CITE: Katie, others].
-Furthermore, obtaining population size estimates for sexual risk behaviour in the general population is a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
+Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the broader population.
+By limiting our consideration to this group we did not account for `r 100 - infections_percent`\% of new infections in adults 15-49.
+Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
 
@@
 
+LZ, IW, MM and CB were supported by...
+
 ## Disclaimer

### 2022-06-17 src/docs_paper/tables-figures.Rmd
Add model direct benefits plot #128
Tables and figures in appendices A and B now have appropriate "A." or "B." prefixes to distinguish from those in the main text #128

@@
 ---
+
+\clearpage
+
+<!-- So that the tables and figures in this appendix are prefixed by "B." -->
+\setcounter{table}{0}  
+\renewcommand{\thetable}{B.\arabic{table}} 
+\setcounter{figure}{0} 
+\renewcommand{\thefigure}{B.\arabic{figure}}
+
+# Additional figures
+
+<!-- Might find a home for these. -->
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
+\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
+Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district level heterogeneity, as well as imputing any districts with missing data.}
+\label{fig:model-direct-benefits}
+\end{figure}
 

### 2022-06-17 src/docs_paper/tables-figures.Rmd
Variance proportions, prevalence plots into appendix B. Changes to captions #128

@@
 
-# Additional figures
-
-<!-- Might find a home for these. -->
-
-\begin{figure}[h]
-\centering
-\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
-\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
-Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district level heterogeneity, as well as imputing any districts with missing data.}
-\label{fig:model-direct-benefits}
-\end{figure}
-
-\newpage
-
 # The Global AIDS Strategy
@@
 \midrule
-Low & 0.3-1\% incidence AND low-risk behaviour OR $<$0.3\% incidence AND high-risk behaviour \\
-Moderate & 1-3\% incidence AND low-risk behaviour OR 0.3-1\% incidence AND high-risk behaviour \\
-High & 1-3\% incidence AND high-risk behaviour \\
-Very high & $>$3\% incidence \\
+Low & 0.3-1.0\% incidence and low-risk behaviour, or $<$0.3\% incidence and high-risk behaviour \\
+Moderate & 1.0-3.0\% incidence and low-risk behaviour, or 0.3-1.0\% incidence and high-risk behaviour \\
+High & 1.0-3.0\% incidence and high-risk behaviour \\
+Very high & $>$3.0\% incidence \\
 \bottomrule
@@
 
-# Survey data
+# Household survey data
+
+## Included surveys
 
@@
 \bottomrule
-\caption{All surveys that we used in our analysis and their sample sizes.}
+\caption{All of the surveys that we used in our analysis and their sample sizes, disaggregated by respondent age.}
 \label{tab:surveys-used}
@@
 \label{tab:surveys-excluded}
-\caption{All surveys excluded from our analysis.}
+\caption{All of that surveys that were excluded from our analysis.}
 \end{table}
+
+\clearpage
+
+## Spatial analysis levels
 
@@
 \label{tab:area-levels}
-\caption{The numer of areas and analysis levels used in our analysis.}
+\caption{The numer of areas and analysis levels for each country that were used in our analysis.}
 \end{table}
@@
 
-# Survey questions and risk group allocation
+## Survey questions
 
@@
 
+## Risk group allocation
+
 \newpage
@@
 
-# National direct and modelled estimates comparison
+# Miscellaneous figures
+
+<!-- Might find a home for these. -->
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
+\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
+Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.}
+\label{fig:model-direct-benefits}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.pdf}}
+    \caption{Proportion of variance explained by each random effect (Sobol' indices) when the multinomial regression model is fit to each country individually.
+In this setting, country-category random effects are not included in the model and year-category random effects are replaced by survey-category random effects (for countries with surveys in multiple years).
+Countries are ordered by the proportion of their variance which is explained by the area-category random effects.}
+\label{fig:aaa-variance-proportions}
+\end{figure}
+
+\clearpage
+
+# Country-specific figures
+
+## Comparison of direct and modelled risk group estimates
 
@@
 
-# Cloropleths
+## HIV prevalence
 
-## HIV prevalence
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Botswana.}
+    \label{fig:prevalence-district-sexbehav-1}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.}
+    \label{fig:prevalence-district-sexbehav-2}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Kenya.}
+    \label{fig:prevalence-district-sexbehav-3}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.}
+    \label{fig:prevalence-district-sexbehav-4}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.}
+    \label{fig:prevalence-district-sexbehav-5}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Malawi.}
+    \label{fig:prevalence-district-sexbehav-6}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Namibia.}
+    \label{fig:prevalence-district-sexbehav-7}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.}
+    \label{fig:prevalence-district-sexbehav-8}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.}
+    \label{fig:prevalence-district-sexbehav-9}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Uganda.}
+    \label{fig:prevalence-district-sexbehav-10}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in South Africa.}
+    \label{fig:prevalence-district-sexbehav-11}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zambia.}
+    \label{fig:prevalence-district-sexbehav-12}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/prev-district-sexbehav-logit.pdf}}
+    \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.}
+    \label{fig:prevalence-district-sexbehav-13}
+\end{figure}
+
+\clearpage
 
@@
     \makebox[\textwidth][c]{\includegraphics[page=1]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Botswana.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Botswana.}
     \label{fig:incidence-district-sexbehav-1}
@@
     \makebox[\textwidth][c]{\includegraphics[page=2]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Cameroon.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Cameroon.}
     \label{fig:incidence-district-sexbehav-2}
@@
     \makebox[\textwidth][c]{\includegraphics[page=3]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Kenya.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Kenya.}
     \label{fig:incidence-district-sexbehav-3}
@@
     \makebox[\textwidth][c]{\includegraphics[page=4]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Lesotho.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Lesotho.}
     \label{fig:incidence-district-sexbehav-4}
@@
     \makebox[\textwidth][c]{\includegraphics[page=5]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Mozambique.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Mozambique.}
     \label{fig:incidence-district-sexbehav-5}
@@
     \makebox[\textwidth][c]{\includegraphics[page=6]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Malawi.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Malawi.}
     \label{fig:incidence-district-sexbehav-6}
@@
     \makebox[\textwidth][c]{\includegraphics[page=7]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Namibia.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Namibia.}
     \label{fig:incidence-district-sexbehav-7}
@@
     \makebox[\textwidth][c]{\includegraphics[page=8]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Eswatini.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Eswatini.}
     \label{fig:incidence-district-sexbehav-8}
@@
     \makebox[\textwidth][c]{\includegraphics[page=9]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Tanzania.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Tanzania.}
     \label{fig:incidence-district-sexbehav-9}
@@
     \makebox[\textwidth][c]{\includegraphics[page=10]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Uganda.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Uganda.}
     \label{fig:incidence-district-sexbehav-10}
@@
     \makebox[\textwidth][c]{\includegraphics[page=11]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in South Africa.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in South Africa.}
     \label{fig:incidence-district-sexbehav-11}
@@
     \makebox[\textwidth][c]{\includegraphics[page=12]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Zambia.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Zambia.}
     \label{fig:incidence-district-sexbehav-12}
@@
     \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}}
-    \caption{District level incidence for each of the risk groups in 2018 in Zimbabwe.}
+    \caption{District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.}
     \label{fig:incidence-district-sexbehav-13}
@@
 
-# Infections reached
+## Expected new infections reached
 
@@
 \makebox[\textwidth][c]{\includegraphics[page=1]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
 \label{fig:infections-reached-country-1}
@@
 \makebox[\textwidth][c]{\includegraphics[page=2]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
 \label{fig:infections-reached-country-2}
@@
 \makebox[\textwidth][c]{\includegraphics[page=3]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
 \label{fig:infections-reached-country-3}
@@
 \makebox[\textwidth][c]{\includegraphics[page=4]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
 \label{fig:infections-reached-country-4}
@@
 \makebox[\textwidth][c]{\includegraphics[page=5]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
 \label{fig:infections-reached-country-5}
@@
 \makebox[\textwidth][c]{\includegraphics[page=6]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
 \label{fig:infections-reached-country-6}
@@
 \makebox[\textwidth][c]{\includegraphics[page=7]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
 \label{fig:infections-reached-country-7}
@@
 \makebox[\textwidth][c]{\includegraphics[page=8]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
 \label{fig:infections-reached-country-8}
@@
 \makebox[\textwidth][c]{\includegraphics[page=9]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
 \label{fig:infections-reached-country-9}
@@
 \makebox[\textwidth][c]{\includegraphics[page=10]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
 \label{fig:infections-reached-country-10}
@@
 \makebox[\textwidth][c]{\includegraphics[page=11]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
 \label{fig:infections-reached-country-11}
@@
 \makebox[\textwidth][c]{\includegraphics[page=12]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
 \label{fig:infections-reached-country-12}
@@
 \makebox[\textwidth][c]{\includegraphics[page=13]{depends/infections-reached-country.pdf}}
-\caption{Percentage of new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}
+\caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}
 \label{fig:infections-reached-country-13}

### 2022-06-18 src/docs_paper/appendix.Rmd
Tables and figures in appendices A and B now have appropriate "A." or "B." prefixes to distinguish from those in the main text #128
Add appendix section on logit scale prevalence disaggregation, and start on AFS FSW disaggregation section #128

@@
 \newpage
+
+<!-- So that the tables and figures in this appendix are prefixed by "A." -->
+\setcounter{table}{0}  
+\renewcommand{\thetable}{A.\arabic{table}} 
+\setcounter{figure}{0} 
+\renewcommand{\thefigure}{A.\arabic{figure}}
 
@@
 
-We obtained estimates of adult (15-49) FSW population size from @stevens2022estimating.
+To estimate the number of FSW by age group and country, we disaggregated country-specific estimates of adult (15-49) FSW population size from @stevens2022estimating by age.
+
+First, we calculated the total sexually debuted population in each age group, in each country.
+To descibe the distribution of age at first sex, we used skew logistic distributions [@kinh2021trends] with cumulative distribution function given by
+\begin{equation}
+F(x) = \left(1 + \exp(\kappa_c (\mu_c - x)) \right)^{- \gamma_c},
+\end{equation}
+where $\kappa_c, \mu_c, \gamma_c > 0$ are the country-specific shape, shape and skewness parameters respectively.
+
+<!-- \text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution -->
 
@@
 
-# Prevalence, incidence and new infections reached analysis {#hiv-indicators}
+# Prevalence, incidence and expected new infections reached {#hiv-indicators}
 
@@
 
-We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak} = \rho_{iak} N_{iak}$ stratified according to district, age group and risk group by disaggregation on the logit scale.
-\begin{align}
-    H_{ia} &= \sum_k H_{iak} = \sum_k \rho_{iak} N_{iak} \\
-    &= \rho_{ia1} N_{ia1} + \rho_{ia1} \text{PR}_2 N_{ia2} + \rho_{ia1} \text{PR}_3 N_{ia3} + \rho_{ia1} \text{PR}_4 N_{ia4} \\
-    &= \rho_{ia1} \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right).
-\end{align}
-Risk group specific prevalence estimates are then given by
-\begin{align}
-    \rho_{ia1} &= H_{ia} / \left(N_{ia1} + \text{PR}_2 N_{ia2} + \text{PR}_3 N_{ia3} + \text{PR}_4 N_{ia4} \right), \\
-    \rho_{ia2} &= \rho_{ia1} \text{PR}_2,\\
-    \rho_{ia3} &= \rho_{ia1} \text{PR}_3,\\
-    \rho_{ia4} &= \rho_{ia1} \text{PR}_4,
-\end{align}
-which we evaluated using Naomi model estimates of PLHIV $H_{ia} = \rho_{ia} N_{ia}$, prevalence ratios $\{\text{PR}_k\}$ as described below, and risk group population sizes $N_{iak} = p_{iak} N_{ia}$ based on our 2018 risk group estimates together with population size estimates from the Naomi model.
-To obtain the prevalence ratios, we...
+We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak}$ stratified according to district, age group and risk group by disaggregating Naomi estimates by risk group.
 
-## Calculation of incidence and number of new infections
+To do so, we estimated HIV prevalence log odds ratios relative to the general population using age, country and risk group specific HIV prevalence bio-marker survey data.
+We also included general population HIV prevalence data, allowing us to fit a logistic regression model including indicator functions for each risk group, and an indicator for being in the general population.
+The regression coefficients in this model correspond to log odds, such that log odds ratios may be easily obtained by taking the difference.
+
+To allow the log odds ratio for the highest risk group to vary based on general population prevalence we fit a linear regression of the FSW log odds against the general population log odds.
+<!-- TODO: Include the data source that was used for this. -->
+We ensured that the log odds ratio for the highest risk group was at least as large as that of the second highest risk group.
+
+Given the fitted log odds ratios $\log(\text{OR}_k)$, we disaggregated Naomi estimates of PLHIV $H_{ia}$ on the logit scale using numerically optimisation to obtain the value of $\theta$ minimising the function
+\begin{equation}
+\hat \theta = \argmin_{\theta \in [-10, 10]} \left( \sum_{k} \left( \text{logistic}(\theta + \log(\text{OR}_k)) \cdot N_{iak} \right) - H_{ia} \right)^2
+\end{equation}
+where $\text{logistic}(x) = \exp(x) / (1 + \exp(x))$ such that $\text{logistic}(\hat \theta + \log(\text{OR}_k)) = \rho_{iak}$.
+The number of PLHIV are then obtained by $H_{iak} = \rho_{iak} N_{iak}$, where $N_{iak}$ is the risk group population size.
+
+## Calculation of incidence and expected number of new infections
 
@@
 \end{align}
-Risk group specific incidence estimates are then given by
+Risk group specific HIV incidence estimates are then given by
 \begin{align}
@@
 \end{align}
-which we evaluated using Naomi model estimates of the number of new HIV infections $I_{ia} = \lambda_{ia} N_{ia}$, HIV infection risk ratios $\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}$, and 2018 risk group population sizes as above.
-The risk ratio $\text{RR}_4(\lambda_{ia})$ is defined as a function of general population incidence.
-Using these estimates $\{\lambda_{iak}\}$, the number of new HIV infections is then $I_{iak} = \lambda_{iak} N_{iak}$.
+which we evaluated using Naomi model estimates of the number of new HIV infections $I_{ia} = \lambda_{ia} N_{ia}$, HIV infection risk ratios $\{\text{RR}_3, \text{RR}_4(\lambda_{ia})\}$, and risk group population sizes as above.
+The risk ratio $\text{RR}_4(\lambda_{ia})$ was defined as a function of general population incidence.
+The number of new HIV infections are then $I_{iak} = \lambda_{iak} N_{iak}$.
 
-## Analysis of new infections reached
+## Calculation of expected new infections reached
 
@@
 Under this stratification, individuals in each age group $a$ are prioritised according to the highest HIV incidence $\lambda_a$.
-By cumulatively summing the expected infections, we calculated for each fraction of the total population reached, the fraction of total new infections that would be reached.
-This analysis was relatively simple: more involved analyses might consider prioritisation of a hypothetical interventions which has some, possibly varying, probability of preventing HIV acquistion together with the costs associated to its roll-out.
+By cumulatively summing the expected infections, for each fraction of the total population reached we calculated the fraction of total expected new infections that would be reached.
+
+This analysis was relatively simple.
+More involved analyses might consider prioritisation of a hypothetical intervention which has some, possibly varying, probability of preventing HIV acquisition, and the costs associated to its roll-out.
 

### 2022-06-18 src/docs_paper/appendix.Rmd
Kinh's paper got published! #128

@@
 First, we calculated the total sexually debuted population in each age group, in each country.
-To descibe the distribution of age at first sex, we used skew logistic distributions [@kinh2021trends] with cumulative distribution function given by
+To descibe the distribution of age at first sex, we used skew logistic distributions [@nguyen2022trends] with cumulative distribution function given by
 \begin{equation}

### 2022-06-18 src/docs_paper/paper.Rmd
Add appendix section on logit scale prevalence disaggregation, and start on AFS FSW disaggregation section #128
Kinh's paper got published! #128

@@
 To ensure that after adjustment the risk group proportions still sum to one, we made appropriate modifications to the samples from the non-regular or multiple partner(s) category.
-FSW population size estimates were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@kinh2021trends].
+FSW population size estimates were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
 Technical details of the models used are in Appendix A.
-
-<!-- \text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution -->
 
@@
 
-<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@kinh2021trends]. -->
+<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->
 
@@
 Under-reporting of higher risk sexual behaviours amongst AGYW could affect the validity of our risk group proportion estimates.
-Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive} or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @kinh2021trends].
+Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive} or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @nguyen2022trends].
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.

### 2022-06-18 src/docs_paper/appendix.Rmd
Improve MP transformation section, move constraints section, correct some indexing issues (not using K anymore), improve survey weighting section (still needs more though) #128

@@
 
-We index the four risk groups by $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
-Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts according to Table A.
-For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider the multinomial random vector
+Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, partitioned into subnational units $i \in \{1, \ldots, n\}$ according to Table B.5.
+We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
+Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
+We modelled the probability of being in each risk group $k \in \{1, 2, 3^{+}\}$ using a multinomial logisitic regression model.
+Typically, this model would be specified using a multinomial likelihood
 \begin{equation}
@@
 where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
+Following the baseline category approach with $k = 1$ say, linear predictors would then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
+Instead of taking this approach, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
+This transformation, and further details about this model, are presented in Section 1.2.
 
-To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial] of the form
-\begin{align}
-    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
-    \log(\kappa_{itak}) &= \eta_{itak}, \label{eq:linearpredictor}
-\end{align}
-for suitable choice of the linear predictor $\eta_{itak}$, which we describe in more detail in Section.
-Then, to estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
+Next, we fit a logistic regression model to estimate the proportion of those in the $k = 3^{+}$ risk group that were in the $k = 3$ and $k = 4$ risk groups respectively.
+This model was of the form
 \begin{align}
@@
 \end{align}
-again for suitable choice of the linear predictor $\eta_{ia}$, which we describe in more detail in Section.
-This approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
+for suitable choice of the linear predictor $\eta_{ia}$, described in Section 1.3.
+Taking this modular approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
 As all such surveys occurred in 2013-2018, in the logistic regresion model $q_{ia}$ was assumed to be constant over time.
 
-To allow uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+To facilitate uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
 Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.
@@
 
-The transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
+The multinomial-Poisson transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
 \begin{align}
-    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
-    \log(\kappa_{itak}) &= \eta_{itak}.
+    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
+    \log(\kappa_{itak}) &= \eta_{itak},
 \end{align}
-Category probabilities are obtained by applying the softmax function to the linear predictor as follows
+for certain choice of the linear predictor $\eta_{itak}$.
+The basis of the transformation is that, conditional on their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized] as follows
 \begin{equation}
-    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}}.
+    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{ita3^{+}}}{\kappa_{ita}} \right),
 \end{equation}
-In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random, rather than fixed as they would be in the multinomial logistic regression model, and follow a Poisson distribution
+where $\kappa_{ita} = \sum_{k = 1}^{3^{+}} \kappa_{itak}$ such that category probabilites are obtained by the softmax funciton
 \begin{equation}
-    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right),
+    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}} = \frac{\kappa_{itak}}{\kappa_{ita}}.
 \end{equation}
-where the intensity $\kappa_{ita} = \sum_k \kappa_{itak}$ is given by a sum of intensities over each category.
-The basis of the Poisson trick is that, conditional on their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized]
+In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random, rather than fixed as they would be in the multinomial logistic regression model, taking a Poisson distribution
 \begin{equation}
-    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{itaK}}{\kappa_{ita}} \right).
+    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right).
 \end{equation}
-As such, the joint distribution of $p(\mathbf{y}_{ita}, m_{ita})$ is
+In the equivalent model, the joint distribution of $p(\mathbf{y}_{ita}, m_{ita}) = p(\mathbf{y}_{ita} \, | \, m_{ita})p(m_{ita})$ is
 \begin{align}
-p(m_{ita}) p(\mathbf{y}_{ita} \, | \, m_{ita}) 
-&= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
+p(\mathbf{y}_{ita}, m_{ita}) &= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
 &= \prod_k \left( \frac{\exp(-\kappa_{itak}) \left( \kappa_{itak} \right)^{y_{itak}}}{y_{itak}!} \right) \\
@@
 \end{align}
-Equation corresponds to the product of $K$ independent Poisson likelihoods, and the joint distribution over all the data $\{\mathbf{y}_{ita}, m_{ita}\}_{i, t, a}$ is given by $\prod_{i, t, a, k} \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right)$.
-The Poisson log-linear model, which vicariously includes the sample sizes as random, is equivalent only when these normalisation constants are recovered exactly by the model.
-To ensure that this is the case, we included observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor in every model we considered.
-Multiplying each of $\{\kappa_{itak}\}_{k = 1}^K$ by $\exp(\theta_{ita})$ has no effect on the multinomial probabilities, but does provide the flexibility required for $\kappa_{ita}$ to exactly recover $m_{ita}$ as desired.
-Although in theory an improper prior $\theta_{ita} \propto 1$ should be used, in practise, by keeping $\eta_{ita}$ small so that arbitrarily large values of the observation-specific random effects $\theta_{ita}$ are not required, it is sufficient (and practically preferable for inference) to instead use a vague prior.
-As such, we set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
+corresponding to the product of independent Poisson likelihoods as in Equation \ref{eq:poisson}.
+This model, including random sample sizes, is equivalent to the multinomial logisitc regression only when these normalisation constants are recovered exactly.
+To ensure that this is the case, one approach is to include observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor.
+Multiplying each of $\{\kappa_{itak}\}_{k = 1}^{3^+}$ by $\exp(\theta_{ita})$ has no effect on the category probabilities, but does provide the necessary flexibility for $\kappa_{ita}$ to recover $m_{ita}$ exactly.
+Although in theory an improper prior $\theta_{ita} \propto 1$ should be used, in practise, by keeping $\eta_{ita}$ otherwise small using appropriate constraints, so that arbitrarily large values of $\theta_{ita}$ are not required, it is sufficient (and practically preferable for inference) to instead use a vague prior.
 
@@
 $$
-Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to allow the sample sizes $m_{ita}$ to be recovered exactly, as required for equivalency of the models.
-To capture country-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
-We allowed heterogeneity in risk group proportions by age by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
-We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects, as well as separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure.
-All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$
-where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
+As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
+To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
+We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
+We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}).
 
-To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
-For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
-Together, these were\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.}:
-\begin{enumerate}
-    \item Category $\sum_k \beta_k = 0$
-    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
-    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, k \quad \text{TODO}$,
-    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
-    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
-    \item Spatio-temporal $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
-\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
-\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
-\end{enumerate}
+All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
 
@@
 
-The specifications we considered for the space-category random effects were IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and Besag grouped by category
+The specifications we considered were IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and Besag grouped by category
 $$
-\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{1K}, \ldots \phi_{nK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
+\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{13^{+}}, \ldots \phi_{n3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
 $$
@@
 
-The specifications we considered for the survey-category random effects were IID $\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and AR1 grouped by category
+The specifications we considered were IID $\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and AR1 grouped by category
 $$
-\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{1K}, \ldots, \gamma_{T1}, \ldots, \gamma_{TK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
+\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{13^{+}}, \ldots, \gamma_{T1}, \ldots, \gamma_{T3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
 $$
@@
 
-For each model including spatio-temporal random effects we used the specification
+We used the specification
 \begin{equation}
-    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nTK})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
+    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nT3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
 \end{equation}
@@
 
+#### Constraints
+
+To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
+For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
+Together, these were:
+\begin{enumerate}
+    \item Category $\sum_k \beta_k = 0$
+    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
+    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, k \quad \text{TODO}$,
+    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
+    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
+    \item Spatio-temporal\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
+\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
+\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
+\end{enumerate}
+
 ### Survey weighted likelihood
@@
 
-The surveys we used utilise a complex design, in which each individual has an unequal probability of being included in the sample.
-For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
-To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y_{itak}$ are replaced by effective counts $y^\star_{itak}$ calculated using survey weights $w_{itak}$.
+The surveys we included use a complex design, in which each individual has an unequal probability of being included in the sample.
+For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling [@measure2012sampling].
+To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y$ are replaced by effective counts $y^\star$ calculated using the survey weights $w_j$ of all individuals $j$ in the corresponding strata.
 We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
 \begin{equation}
-    m^\star_{itak} = \left(\sum_{itak} w_{itak} \right)^2 / \sum_{itak} {w_{itak}}^2
+    m^\star = \frac{\left(\sum_j w_j \right)^2}{\sum_j {w_j}^2}
 \end{equation}
-to obtain $y^\star_{itak}$.
-As these counts may not be integers, the Poisson likelihood in Equation~\eqref{eq:poisson} is inappropriate.
-Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, as implemented by `family = "xPoisson"` in `R-INLA`, given by
+to obtain $y^\star$.
+These counts may not be integers, and the Poisson likelihood we used in Equation \ref{eq:poisson} is inappropriate.
+Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, given by
 \begin{equation}
-    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right).
+    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right),
 \end{equation}
+as implemented by `family = "xPoisson"` in `R-INLA`.
+
+### Model selection
+
+To fill.
 
@@
 
-We considered six logistic regression models (Table~\ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
 We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.

### 2022-06-18 src/docs_paper/tables-figures.Rmd
Doesn't need to be commented out anymore #128

@@
 
-<!-- \begin{figure}[h] -->
-<!-- \centering -->
-<!-- \makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}} -->
-<!-- \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
-Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.} -->
-<!-- \label{fig:temporal-interpolation-ribbon-13} -->
-<!-- \end{figure} -->
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}}
+\caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.}
+\label{fig:temporal-interpolation-ribbon-13}
+\end{figure}
 

### 2022-06-18 src/docs_paper/appendix.Rmd
More information about FSW age disaggregation #128

@@
 Scaling of the structure matrix to have generalised variance one ensures interpretable priors may be placed on the precision parameter [@sorbye2014scaling].
-We follow the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
+We followed the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
 The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with the full conditionals
@@
 
-In preliminary testing, we tried excluding spatial random effects from the model, but found that this negatively effected performance.
-We also tried using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one.
-For simplicity and to avoid numerical issues, by instead using Besag random effects we decided to fix this proportion to one, rather than learn it.
+In preliminary testing, we excluded spatial random effects from the model, but found that this negatively effected performance.
+We also tested using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one so for simplicity and to avoid numerical issues, by using Besag random effects we decided to fix this proportion to one.
 
@@
 
-To fill.
+To fill: table and figure.
 
@@
 \end{equation}
-where $\kappa_c, \mu_c, \gamma_c > 0$ are the country-specific shape, shape and skewness parameters respectively.
+where $\kappa_c, \mu_c, \gamma_c > 0$ are country-specific shape, shape and skewness parameters respectively.
 
-<!-- \text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution -->
+Next, we used the assumed $\text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] to calculate the implied ratio between the number of FSW and the sexually debuted population in each age group.
+We assumed that those ratios in South Africa were applicable to every country, and therefore calculated the number of FSW by age in all 13 countries.
+
+To fill: plots and comparisons to other data sources.
 

### 2022-06-19 src/docs_paper/appendix.Rmd
Convert .pdf to .jpeg using the shell, add age variation plot, add cor. author to appendices #128

@@
   girls and young women across 13 priority countries in sub-Saharan Africa"
+subtitle: |
+  Corresponding author: Adam Howes (`ath19@ic.ac.uk`)
 output:
@@
 
+<!-- \begin{figure} -->
+<!--   \centering -->
+<!--   \makebox[\textwidth][c]{\includegraphics{figures/coverage.jpeg}} -->
+<!--   \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the selected models.
+These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see e.g.
+\citet[Chapter 6.1]{gelman2020bayesian}.} -->
+<!--   \label{fig:coverage} -->
+<!-- \end{figure} -->
+
 ## Logistic regression model
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.jpeg}}
     \caption{Logistic regression model performance.}

### 2022-06-19 src/docs_paper/paper.Rmd
Convert .pdf to .jpeg using the shell, add age variation plot, add cor. author to appendices #128

@@
 HIV incidence amongst AGYW is `r inc_ratio` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
-AGYW have therefore been identified as a priority population for HIV primary prevention, with significant investments being been made in prevention programming [@saul2018dreams; @global2018measurement].
+AGYW have therefore been identified as a priority population for HIV primary prevention, with significant investments being made in prevention programming [@saul2018dreams; @global2018measurement].
 
-The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
-Four prioritisation strata (Table B.X) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
-The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table B.X) based upon this prioritisation strata [@unaids2021global].
+The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour, to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+Four prioritisation strata (Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
+<!-- NB: Check again about the recent STI infection aspect. -->
+The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table B.2) based upon this prioritisation strata [@unaids2021global].
 All AGYW are recommended to have access to a basic package of HIV prevention, while those with with high risk behaviours in moderate incidence settings and all AGYW in very high incidence settings are recommended to have access to enhanced intervention packages [@joint2016hiv; @birdthistle2018evaluating].
@@
 We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
-Using our estimates, we calculated the HIV prevalence, people living with HIV (PLHIV), HIV incidence, and number of new HIV infections in each risk group by disaggregating district-level estimates from the Naomi model [@eaton2021naomi].
-Finally, we quantified the increased efficiency of HIV prevention, in terms of the expected number of new infections that could be preemptively reached, by stratified prioritisation of interventions.
+Using our estimates, we calculated the HIV prevalence, people living with HIV (PLHIV), HIV incidence, and expected number of new HIV infections in each risk group by disaggregating district-level estimates from the Naomi model [@eaton2021naomi].
+Finally, we quantified the increased efficiency of HIV prevention, in terms of the expected number of new infections that could be preemptively reached, by stratified prioritisation of interventions by risk group, location and age group.
 
@@
 \centering
-\begin{tabularx}{\textwidth}{llll}
+\begin{tabularx}{\textwidth}{lp{5cm}ll}
 \toprule
@@
 High & Non-regular or multiple partner(s) & -- & 1.72 \\
-Very high & Female sex workers & $<$0.1\% & 25.0 \\
+Very high & Transactional sex & $<$0.1\% & 25.0 \\
  & & 0.1-0.3\% & 13.0 \\
@@
 The incidence rate ratio for women with non-regular or multiple sexual partner(s) was derived from analysis of ALPHA network data.
-The incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.}
+The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.
+}
 \label{tab:risk-groups}
@@
 
-Some surveys included a specific question asking if the respondent had received or given money or gifts for sex in the past twelve months; in these surveys, 2.64\% of women reported transactional sex.
-In surveys without that question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
-Because of this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who engaged in transactional sex.
+Some surveys included a specific question asking if the respondent had received or given money or gifts for sex in the past twelve months.
+In these surveys, 2.64\% of women reported transactional sex.
+In surveys without such a question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
+Due to this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who engaged in transactional sex.
 We focused on estimating the proportion of women who reported transactional sex at a district level, and subsequently adjusted these proportions to align to national estimates for the number of female sex workers.
@@
 The model synthesises data from multiple sources to produce subnational estimates of indicators of interest, and has been used by countries as a part of the HIV estimates process supported by UNAIDS.
-The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning in UNAIDS Naomi estimates, except for Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Appendix B).
+<!-- and so far has been used by X countries could be better (adds some information that it's widely used) -->
+The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning in UNAIDS Naomi estimates, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Table B.5).
 
@@
 ```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
-knitr::include_graphics("depends/available-surveys.pdf")
+knitr::include_graphics("depends/available-surveys.jpeg")
 ```
@@
 \\label{fig:continental-map}"}
-knitr::include_graphics("depends/3p1-continental-map.png")
+knitr::include_graphics("depends/3p1-continental-map.jpeg")
 ```
@@
 \\label{fig:within-between-country-variation}"}
-knitr::include_graphics("depends/3p1-within-between-country-variation.pdf")
+knitr::include_graphics("depends/3p1-within-between-country-variation.jpeg")
 ```
@@
 
-<!-- Write another paragraph here calling out some examples of the amount of variation -->
+<!-- TODO: Write another paragraph here calling out some examples of the amount of variation -->
 <!-- Awaiting additional results: https://github.com/athowes/multi-agyw/issues/95 -->
@@
 \\label{fig:infections-reached}"}
-knitr::include_graphics("depends/infections-reached.pdf")
+knitr::include_graphics("depends/infections-reached.jpeg")
 ```

### 2022-06-19 src/docs_paper/tables-figures.Rmd
Convert .pdf to .jpeg using the shell, add age variation plot, add cor. author to appendices #128

@@
 
-## Survey questions
+## Survey questions and risk group allocation
 
@@
 
-## Risk group allocation
-
-\newpage
-
-\begin{figure}[h!]
+\begin{figure}[h]
     \centering
-    \includegraphics{depends/category-flowchart.pdf}
+    \includegraphics{depends/category-flowchart.jpeg}
     \caption{Flowchart describing allocation of respondents to risk groups.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.jpeg}}
 \caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.jpeg}}
     \caption{Proportion of variance explained by each random effect (Sobol' indices) when the multinomial regression model is fit to each country individually.
@@
 \label{fig:aaa-variance-proportions}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\makebox[\textwidth][c]{\includegraphics{depends/age-variation.jpeg}}
+\caption{The posterior density of national-level risk group proportions by age, illustrating the bi-modality of the cohabiting partner and non-regular and multiple partner(s) risk groups.}
+\label{fig:age-variation}
 \end{figure}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=1]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-1.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Botswana.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=2]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-2.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Cameroon.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=3]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-3.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Kenya.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=4]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-4.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Lesotho.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=5]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-5.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Mozambique.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=6]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-6.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Malawi.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=7]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-7.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Namibia.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=8]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-8.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Eswatini.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=9]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-9.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Tanzania.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=10]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-10.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Uganda.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=11]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-11.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in South Africa.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=12]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-12.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zambia.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=13]{depends/temporal-interpolation-ribbon.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-13.jpeg}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-1.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Botswana.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-2.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-3.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Kenya.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-4.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-5.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-6.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Malawi.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-7.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Namibia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-8.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-9.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-10.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Uganda.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-11.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in South Africa.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-12.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zambia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/prev-district-sexbehav-logit.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-13.jpeg}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=1]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-1.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Botswana.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=2]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-2.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Cameroon.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=3]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-3.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Kenya.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=4]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-4.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Lesotho.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=5]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-5.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Mozambique.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=6]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-6.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Malawi.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=7]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-7.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Namibia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=8]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-8.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Eswatini.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=9]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-9.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Tanzania.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=10]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-10.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Uganda.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=11]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-11.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in South Africa.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=12]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-12.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Zambia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics[page=13]{depends/incidence-district-sexbehav.pdf}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-13.jpeg}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=1]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-1.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=2]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-2.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=3]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-3.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=4]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-4.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=5]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-5.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=6]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-6.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=7]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-7.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=8]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-8.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=9]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-9.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=10]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-10.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=11]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-11.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=12]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-12.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics[page=13]{depends/infections-reached-country.pdf}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-13.jpeg}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}

### 2022-06-19 src/docs_paper/script.R

@@ -1,6 +1,37 @@
 # orderly::orderly_develop_start("docs_paper")
 # setwd("src/docs_paper")
 
+#' Conversion of figures from .pdf to .jpeg at specified resolution
+Sys.setenv(PATH = paste(Sys.getenv("PATH"), "/opt/homebrew/bin", sep = ":"))
+
+convert_pdf_jpeg <- function(name) {
+  command <- paste0(
+    "convert -density 300 depends/", name, ".pdf -scene 1 -background white",
+    " -alpha remove -alpha off -quality 90 depends/", name, ".jpeg"
+  )
+  system(command)
+}
+
+#' For paper.Rmd
+convert_pdf_jpeg("available-surveys")
+convert_pdf_jpeg("3p1-continental-map")
+convert_pdf_jpeg("3p1-within-between-country-variation")
+convert_pdf_jpeg("infections-reached")
+
+#' For appendix.Rmd
+convert_pdf_jpeg("fsw-logit-information-criteria")
+
+#' For tables-figures.Rmd
+convert_pdf_jpeg("category-flowchart")
+convert_pdf_jpeg("model-direct-benefits")
+convert_pdf_jpeg("aaa-variance-proportions")
+convert_pdf_jpeg("age-variation")
+convert_pdf_jpeg("temporal-interpolation-ribbon")
+convert_pdf_jpeg("prev-district-sexbehav-logit")
+convert_pdf_jpeg("incidence-district-sexbehav")
+convert_pdf_jpeg("infections-reached-country")
+
+#' Render documents
 rmarkdown::render("paper.Rmd")
 rmarkdown::render("appendix.Rmd")
 rmarkdown::render("tables-figures.Rmd")

### 2022-06-19 src/plot_age-variation/script.R

@@ -4,7 +4,10 @@
 
 df <- read_csv("depends/adjust-best-3p1-multi-sexbehav-sae.csv") %>%
   multi.utils::update_naming() %>%
-  filter(age_group != "15-24")
+  filter(
+    age_group != "15-24",
+    indicator != "Nonregular partners(s) +"
+  )
 
 #' Add region column
 #' Defined based on the UN geoscheme for Africa

### 2022-06-19 src/docs_paper/paper.Rmd
Fix references to appendices, fix numbers of 25-29 surveyed about transactional sex, move some more of Katie's comment about reporting bias into the text, remove duplicated text #128

@@
 FSW population size estimates were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
-Technical details of the models used are in Appendix A.
+Technical details of the models we used are in Appendix A.1.
 
-We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.X).
+We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.1.2).
 All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
@@
 
-For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Appendix A.X).
+For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Appendix A.1.3).
 Each included an intercept, age and country effects, and a spatial effect allowing district-level variation.
@@
 Using risk group proportion estimates, and Naomi model estimates, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
-Further details are provided in Appendix A.X.
+Further details are provided in Appendix A.2.
 
@@
 #' Disaggregated by age
-#' TODO: This isn't quite right because some 25-29 are not asked FSW question in DHS surveys
+#' This isn't quite right because some 25-29 are not asked FSW question in DHS surveys, which I fix below
 agyw_surveyed_giftsvar_age <- available_surveys %>%
@@
   )
+
+#' These surveys excluded AGYW 25-29 for the transactional sex question
+#' I've quickly hard-coded this by looking at data-check.pdf from fit_fsw-logit-sae
+#' In future it could be automatically updated based on that report instead
+giftsvar_exclude_Y025_029 <- c("CMR2018DHS", "MWI2015DHS", "UGA2016DHS", "ZAF2016DHS", "ZMB2018DHS", "ZWE2015DHS")
+
+giftsvar_Y025_029_overcount <- available_surveys %>%
+  filter(
+    survey_id %in% giftsvar_exclude_Y025_029,
+  ) %>%
+  pull(Y025_029) %>%
+  sum()
 
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.X), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
-Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size in these surveys of `r comma(agyw_surveyed_giftsvar)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029)` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size of `r comma(agyw_surveyed_giftsvar - giftsvar_Y025_029_overcount)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029 - giftsvar_Y025_029_overcount)` aged 25-29 years^[There were `r length(giftsvar_exclude_Y025_029)` DHS surveys which excluded women 25-29 from the transactional sex survey question.]).
 The median number of surveys per country was four, ranging from one in Botswana and South Africa to six in Uganda.
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria is provided in Appendix A.X for all considered models.
+Model performance according to the CPO criteria is provided in Appendix A.1.2.4 for all considered models.
 Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level.
@@
   Among women aged 20-29, cohabiting (`r dividing_border_above_sexcohab$median`\%) was more common in eastern Africa than non-regular or multiple partner(s) (`r dividing_border_above_sexnonreg$median`\%), while in southern countries non-regular or multiple partner(s) (`r dividing_border_below_sexnonreg$median`\%) were more common than cohabiting (`r dividing_border_below_sexcohab$median`\%).
-  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
-  Female sex workers were `r inf_fsw$prop_population_cumulative`\% of the at risk population but `r inf_fsw$prop_infections_averted_cumulative`\% of all new infections.
+  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all expected new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
+  Female sex workers were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all expected new infections.
 
@@
   Doing so also allowed us to estimate the the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
+  We found that prioritising HIV prevention using behavioural risk groups almost halved the proportion of the population that would need to be reached to find half of all expected new infections.
 ---
-
-<!-- TODO: Include key conclusions in author summary. -->
 
@@
 
-Under-reporting of higher risk sexual behaviours amongst AGYW could affect the validity of our risk group proportion estimates.
-Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive} or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @nguyen2022trends].
+Under-reporting of higher risk sexual behaviours among AGYW could affect the validity of our risk group proportion estimates.
+Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive, @helleringer2011reliability] or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @nguyen2022trends].
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
+These reporting biases will also have distortied of our estimates of infection risk ratios and prevalence ratios, likely over-attributing risk to higher risk groups.
 
@@
 We did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
-
-The extent to which the efficiencies from risk-stratified prioritisation depends on the ability of programmes to identify and efficiently reach those in each risk category.
-In practice, this is likely to result in substantially less efficiency in the number of potential infections averted for a given proportion of the population reached compared to the 'best-case' frontier analysis in which we assumed those in each risk category could be perfectly reached.
-These results therefore be interpreted as illustrating the potential
-maximal benefits, rather than benefits that would be accrued from any
-specific intervention strategy. Factors we did not consider include the
-greater administrative burden of more complex strategies, variation in
-difficulty or feasibility of reaching individuals in each strata,
-variation in the range or effectiveness of interventions by strata, and
-changes in strata membership that may occur during the course of a year.
-Empirical evaluations of risk screening tools to stratify individual HIV infection risk have found only moderate discriminatory ability [CITE Jia et al.] and risk behaviour may change rapidly among young populations, further increasing the challenge to effectively deliver prevention packages to those at risk at the right times.
-
 The efficiency of each stratified prevention strategy depends on the ability of programmes to identify and effectively reach those in each strata.
@@
 
-<!-- I think the Nnko 2004 is a good cite. For biases in age at first sex as folks age: -->
-<!-- https://pubmed.ncbi.nlm.nih.gov/15572637/ -->
-<!-- https://pubmed.ncbi.nlm.nih.gov/19307342/ -->
-<!-- Then these are all about how methodological approaches can result in different estimates (I think): -->
-<!-- Hewett PC, Mensch BS, Erulkar AS.
-Consistency in the reporting of sexual behaviour by adolescent girls in Kenya: a comparison of interviewing methods.
-Sex Transm Infect.
-2004;80 Suppl 2:ii43-8.
--->
-<!-- Cleland J, Boerma JT, Carael M, Weir SS. Monitoring sexual behaviour in general populations: a synthesis of lessons of the past decade. Sex Transm Infect. 2004;80 Suppl 2:ii1-7. -->
-<!-- Helleringer S, Kohler HP, Kalilani-Phiri L, Mkandawire J, Armbruster B.
-The reliability of sexual partnership histories: implications for the measurement of partnership concurrency during surveys.
-AIDS.
-2011;25(4):503-11.Mensch BS, Hewett PC, Erulkar AS.
-The reporting of sensitive behavior by adolescents: a methodological experiment in Kenya.
-Demography.
-2003;40(2):247-68.
--->
-<!-- Then there’s the option of discussing validity of self-reported sexual behaviour based on biomarker validation (e.g.
-https://academic.oup.com/ofid/article/6/2/ofz010/5285444, there are more like this) but I’m not super familiar with this literature to pull a reference that would be appropriate.
--->
-
 Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the broader population.
@@
 
-<!-- Likely over-reporting of never having had sex in the past year by young women, if we apply an RR of 0 to this group, to balance out the overall incidence rate, might be over-attributing risk to the other groups.
--->
+<!-- Reasons why we didn't include condom usage: -->
 <!-- Defining condom usage is challenging, particularly for those with multiple partners, and reporting is likely biased due to social desirability. -->

### 2022-06-19 src/docs_paper/appendix.Rmd
Include coverage assessment plot in appendix #128

@@
 
-<!-- \begin{figure} -->
-<!--   \centering -->
-<!--   \makebox[\textwidth][c]{\includegraphics{figures/coverage.jpeg}} -->
-<!--   \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the selected models.
-These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see e.g.
-\citet[Chapter 6.1]{gelman2020bayesian}.} -->
-<!--   \label{fig:coverage} -->
-<!-- \end{figure} -->
-
 ## Logistic regression model
@@
 
+To fill: explanation of Table \ref{tab:logistic-model-performance} and Figure \ref{fig:logistic-model-performance}.
+
 \begin{table}[h]
@@
     \label{fig:logistic-model-performance}
+\end{figure}
+
+## Coverage assessment
+
+To fill: explanation of Figure \ref{fig:coverage}.
+
+\begin{figure}
+  \centering
+  \makebox[\textwidth][c]{\includegraphics{depends/coverage.jpeg}}
+  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models.
+These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
+  \label{fig:coverage}
 \end{figure}

### 2022-06-19 src/docs_paper/script.R

@@ -20,6 +20,7 @@ convert_pdf_jpeg("infections-reached")
 
 #' For appendix.Rmd
 convert_pdf_jpeg("fsw-logit-information-criteria")
+convert_pdf_jpeg("coverage")
 
 #' For tables-figures.Rmd
 convert_pdf_jpeg("category-flowchart")

### 2022-06-19 src/process_coverage/script.R

@@ -8,12 +8,14 @@ df <- df %>%
   multi.utils::update_naming() %>%
   filter(
     age_group %in% c("15-19", "20-24", "25-29"),
+    indicator != "Nonregular partners(s) +",
     !is.na(estimate_raw)
-  )
+  ) %>%
+  droplevels()
 
 pdf("coverage.pdf", h = 4, w = 6.25)
 
-S <- 10 #' Number of Monte Carlo samples
+S <- 100 #' Number of Monte Carlo samples
 bins <- 20
 alpha <- 0.05
 
@@ -54,7 +56,7 @@ ecdf_diff <- df %>%
   }) %>%
   purrr::map_df(~as.data.frame(.x), .id = "indicator") %>%
   ggplot(aes(x = nominal_coverage, y = ecdf_diff)) +
-  facet_grid(~factor(indicator, levels = c("No sex", "Cohabiting partner", "Nonregular partner(s)", "Nonregular partners(s) +", "FSW")),
+  facet_grid(~factor(indicator, levels = c("No sex", "Cohabiting partner", "Nonregular partner(s)", "FSW")),
              drop = TRUE, scales = "free") +
   geom_line(col = "#009E73") +
   geom_step(aes(x = nominal_coverage, y = ecdf_diff_upper), alpha = 0.7, col = "grey50") +

### 2022-06-21 src/docs_paper/paper.Rmd
TMW comments on paper.Rmd

@@
 
-Implementation of the strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group by location to determine prioritisation for stratified HIV prevention.
+Implementation of a stratified HIV prevention strategy by national HIV programmes and stakeholders requires data on the population size and HIV incidence in each risk group by location.
 We developed a multinomial Bayesian spatio-temporal model to estimate the proportion of AGYW aged 15-29 years in four behavioural risk groups, stratified by district, year, and five-year age group.
@@
 Our methodology is standardised across countries, allowing prioritisation both within and between countries.
+<!-- Note: Above sentence borrowed from TOR document. To back it up, needs more between country analysis in results section. -->
 We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
@@
 We performed inference using integrated nested Laplace approximation [@rue2009approximate] via the `R-INLA` package [@martins2013bayesian].
+It is not possible to directly fit multinomial logistic regression models in `R-INLA`, so we used the multinomial-Poisson transformation [@baker1994multinomial].
+Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to define appropriate random effects, are provided in Appendix A.1.2.
 The best performing model was selected according to the conditional predictive ordinate (CPO) criteria, a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
@@
 \\label{fig:continental-map}"}
+#' Note that the subnational borders look a bit overpowering when the quality of this is reduced
 knitr::include_graphics("depends/3p1-continental-map.jpeg")
@@
     select(prop_infections_averted_cumulative, prop_population_cumulative) %>%
-      mutate(across(prop_infections_averted_cumulative:prop_population_cumulative, ~ 100 * signif(.x, digits = 3)))
+      mutate(across(prop_infections_averted_cumulative:prop_population_cumulative, ~ 100 * round(.x, 3)))
 ) %>%
@@
 Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig).
-Third, we provide estimates in all settings, including districts without any survey clusters as well as years without surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
+Third, we provide estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
 
@@
 
-As well, this work serves as a case-study in how to use the multinomial-Poisson transformation to efficiently specify and fit multinomial spatio-temporal models in `R-INLA`.
-Specifically, we used Kronecker products over Gaussian Markov random fields to define appropriate category-specific spatio-temporal random effects.
+<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->
 
-<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->
+<!-- TWM: Consider adding a note about last data point being in 2018. There is so little change over time it shouldn't make a difference, but 2018 is starting to sound like a long time ago -->
 
@@
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
-These reporting biases will also have distortied of our estimates of infection risk ratios and prevalence ratios, likely over-attributing risk to higher risk groups.
+These reporting biases will also have distorted of our estimates of infection risk ratios and prevalence ratios, likely over-attributing risk to higher risk groups.
 

### 2022-06-22 src/docs_paper/paper.Rmd
SRF funding update and open access text #128
IW comments on paper.Rmd

@@
 
+<!-- IW notes that AGYW typically refers to 15-24 -->
+<!-- Feels clunky to me to say AGYW and women 25-29 -->
 In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r population_percent`\% of the population but `r infections_percent`\% of new HIV infections [@unaids2021update].
@@
 
-Using risk group proportion estimates, and Naomi model estimates, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
+Using risk group proportion estimates, and subnational estimates developed using the Naomi model, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
 Further details are provided in Appendix A.2.
@@
 The delineation does not represent a boundary between predominately Christian and Muslim populations, which is further north.
-We also note that the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique [@unicef].
+We also note the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique [@unicef].
 
@@
 TMW was supported by Imperial College London (President's PhD Scholarship).
-SF was supported by the EPSRC (EP/V002910/1).
+SF was supported by the EPSRC (EP/V002910/2).
 JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664). 
@@
 LZ, IW, MM and CB were supported by...
+
+For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript (AAM) version arising from this submission.
 

### 2022-06-22 src/docs_paper/appendix.Rmd
TMW comments on appendix.Rmd

@@
 corresponding to the product of independent Poisson likelihoods as in Equation \ref{eq:poisson}.
-This model, including random sample sizes, is equivalent to the multinomial logisitc regression only when these normalisation constants are recovered exactly.
+This model, including random sample sizes, is equivalent to the multinomial logistic regression only when these normalisation constants are recovered exactly.
 To ensure that this is the case, one approach is to include observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor.
@@
 $$
-\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
+\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
 $$
 As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
-To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{c[i]k} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
 Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
@@
 $$
-where the scaled structure matrix $\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}$ is given by the Kronecker product of the scaled Besag structure matrix $\mathbf{R}^\star_b$ and the identity matrix $\mathbf{I}$.
+where the scaled structure matrix $\mathbf{R}^\star_\phi = \mathbf{R}^\star_b \otimes \mathbf{I}$ is given by the Kronecker product of the scaled Besag structure matrix $\mathbf{R}^\star_b$ and the identity matrix $\mathbf{I}$, and ${-}$ denotes the generalised matrix inverse.
 Scaling of the structure matrix to have generalised variance one ensures interpretable priors may be placed on the precision parameter [@sorbye2014scaling].
@@
     \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
-    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, k \quad \text{TODO}$,
+    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, c, k$,
     \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$

### 2022-06-22 src/docs_paper/appendix.Rmd
Reword i, c[i]

@@
 
-Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, partitioned into subnational units $i \in \{1, \ldots, n\}$ according to Table B.5.
+Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
 We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$

### 2022-06-22 src/docs_paper/appendix.Rmd
Agonising over putting c or c[i]

@@
 Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
-We modelled the probability of being in each risk group $k \in \{1, 2, 3^{+}\}$ using a multinomial logisitic regression model.
+We used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
 Typically, this model would be specified using a multinomial likelihood
@@
 As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
-To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{c[i]k} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
 Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
@@
 \midrule
-Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_c$) & Spatial ($\phi_i$) & Covariates \\ 
+Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_{c}$) & Spatial ($\phi_i$) & Covariates \\ 
 \midrule
@@
 
-We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_{c} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
 We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.

### 2022-06-25 make/7_post_process.R
Fix bug with not including all countries in aaa-variance-proportions

@@ -23,7 +23,7 @@ run_commit_push("process_information-criteria") #' [/]
 run_commit_push("process_variance-proportions") #' [x]
 
 #' Posterior predictive sampling to generate coverage estimates
-run_commit_push("process_coverage") #' [ ]
+run_commit_push("process_coverage") #' [x]
 
 #' Calculate and plot HIV prevalence by risk group
 run_commit_push("process_prevalence") #' [x]

### 2022-06-25 src/process_variance-proportions/script.R

@@ -66,12 +66,12 @@ fct_reorg <- function(fac, ...) {
   fct_recode(fct_relevel(fac, ...), ...)
 }
 
-#' When there is only one survey, we want to select Model 3, and when there are multiple, we want to select Model 6
+#' When there is only one survey, we want to select Model 2, and when there are multiple, we want to select Model 4
 single_survey <- df_aaa %>%
   group_by(iso3) %>%
   summarise(max = max(model)) %>%
   select(iso3, max) %>%
-  filter(max == "Model 3") %>%
+  filter(max == "Model 2") %>%
   pull(iso3)
 
 model_selector <- function(iso3, model) {
@@ -169,114 +169,116 @@ df_aaa %>%
   arrange(desc(percentage_variance_area_idx)) %>%
   mutate(percentage_variance_area_idx = signif(100 * percentage_variance_area_idx, 3))
 
-#' Joint country fitting
-df <- read_csv("depends/variance-proportions.csv")
+#' The below is still in development
 
-#' What's the proportion of variance explained?
-df %>%
-  select(starts_with("percentage_")) %>%
-  mutate(across(everything(), ~ 100 * round(.x, 3)))
-
-#' The uncertainty on that?
-S <- 100
-full_samples <- readRDS("depends/multi-sexbehav-sae-samples.rds")
-
-#' Just the hyperparameters
-precision_samples <- lapply(full_samples, "[", "hyperpar")
-precision_samples_matrix <- matrix(unlist(precision_samples), ncol = S)
-precision_samples_df <- data.frame(t(precision_samples_matrix))
-names(precision_samples_df) <- names(precision_samples[[1]][[1]])
-variance_samples_df <- 1 / precision_samples_df
-
-variance_samples_df <- variance_samples_df %>%
-  select(starts_with("Precision")) %>%
-  rename_all(list(~ stringr::str_replace(., "Precision for ", "variance_"))) %>%
-  mutate(total_variance = rowSums(., na.rm = TRUE)) %>%
-  #' Create new columns with the percentage variance
-  mutate(
-    across(
-      .cols = starts_with("variance"),
-      .fns = list(percentage = ~ . / total_variance),
-      .names = "{fn}_{col}"
-    )
-  ) %>%
-  select(starts_with("percentage_")) %>%
[…]

### 2022-06-25 src/docs_paper/paper.Rmd
KMJ comments on paper.Rmd (includes changes to risk group labels, which will likely break things in other places, which I will fix as I come to them) #128

@@
 
-The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the UN General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour, to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour, to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
 Four prioritisation strata (Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
@@
 High & Non-regular or multiple partner(s) & -- & 1.72 \\
-Very high & Transactional sex & $<$0.1\% & 25.0 \\
+Very high & Transactional sex (adjusted to correspond to female sex workers) & $<$0.1\% & 25.0 \\
  & & 0.1-0.3\% & 13.0 \\
@@
 The incidence rate ratio for women with non-regular or multiple sexual partner(s) was derived from analysis of ALPHA network data.
+Non-regular partners are defined to be non cohabiting.
 The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.
-}
+When the local HIV incidence in the general population is higher, the incidence rate ratio is lower.}
 \label{tab:risk-groups}
@@
 For each survey, we classified female respondents aged 15-29 years into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
-These risk groups were: not sexually active, one cohabiting sexual partner, at least one non-regular sexual partner, and AGYW who report transactional sex (Table \ref{tab:risk-groups}).
+These risk groups were: not sexually active, one cohabiting sexual partner, at non-regular or multiple sexual partner(s), and AGYW who report transactional sex (Table \ref{tab:risk-groups}).
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
@@
 As surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in the two highest risk groups was constant over time.
-We combined the two models using 1000 samples from each posterior distribution to produce samples from all four risk groups.
+We combined the two models using 1000 samples from each posterior distribution to produce samples for all four risk groups.
 Finally, we adjusted the samples from the transactional sex category to match age- and country-specific FSW population size estimates.
 To ensure that after adjustment the risk group proportions still sum to one, we made appropriate modifications to the samples from the non-regular or multiple partner(s) category.
-FSW population size estimates were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
+FSW population size estimates by age were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
 Technical details of the models we used are in Appendix A.1.
@@
 To calculate HIV prevalence by risk group, we disaggregated the district-age specific prevalence estimates from Naomi estimates to risk groups using odds ratios for the relative odds of having HIV between risk groups, calculated from a logistic regression of country-age specific household survey HIV bio-marker data.
+<!-- TODO: Be more specific about the data source here. -->
 Prevalence disaggregation was on the logit scale to ensure that HIV prevalence in each risk group remained in the range 0\% to 100\%.
@@
 The risk ratio used for the not sexually active risk group was zero, excluding incidence from non-sexual transmission which is negligible in these populations.
-For the non-regular or multiple partner(s) risk group, the risk ratio was based on analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa [@slaymaker2020croi] and supported a recent systematic review [@jia2022risk].
+For the non-regular or multiple partner(s) risk group, the risk ratio was based on analyses of risk factors for incident HIV infection from studies in sub-Saharan Africa [@slaymaker2020croi] and supported by a recent systematic review [@jia2022risk].
 Risk ratios for the highest risk group vary based upon general population HIV incidence and are based on an analysis of HIV prevalence among FSW relative to population prevalence [@aidsinfo] using data from the UNAIDS Key Population Atlas [@kpatlas].
@@
 moz_Y015_019_nosex12m <- filter(moz_Y015_019, indicator == "No sex")
-moz_Y015_019_sexcohab <- filter(moz_Y015_019, indicator == "Cohabiting partner")
-moz_Y015_019_sexnonreg <- filter(moz_Y015_019, indicator == "Non regular partner(s)")
+moz_Y015_019_sexcohab <- filter(moz_Y015_019, indicator == "One cohabiting partner")
+moz_Y015_019_sexnonreg <- filter(moz_Y015_019, indicator == "Non-regular or multiple partner(s)")
 
@@
   filter(
-    indicator %in% c("Cohabiting partner", "Nonregular partner(s)"),
+    indicator %in% c("One cohabiting partner", "Non-regular or multiple partner(s)"),
     age_group %in% c("20-24", "25-29")
@@
 
-dividing_border_above_sexcohab <- filter(dividing_border, border == "Above", indicator == "Cohabiting partner")
-dividing_border_above_sexnonreg <- filter(dividing_border, border == "Above", indicator == "Nonregular partner(s)")
-dividing_border_below_sexcohab <- filter(dividing_border, border == "Below", indicator == "Cohabiting partner")
-dividing_border_below_sexnonreg <- filter(dividing_border, border == "Below", indicator == "Nonregular partner(s)")
+dividing_border_above_sexcohab <- filter(dividing_border, border == "Above", indicator == "One cohabiting partner")
+dividing_border_above_sexnonreg <- filter(dividing_border, border == "Above", indicator == "Non-regular or multiple partner(s)")
+dividing_border_below_sexcohab <- filter(dividing_border, border == "Below", indicator == "One cohabiting partner")
+dividing_border_below_sexnonreg <- filter(dividing_border, border == "Below", indicator == "Non-regular or multiple partner(s)")
 
@@
   The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiated intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
-  We aimed to estimate occurrence of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
+  We aimed to estimate prevalence of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
 
@@
   We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 Global Fund priority countries in sub-Saharan Africa.
-  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular or multiple partner[s] and female sex workers) based on reported sexual behaviour.
+  Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular or multiple partner[s] and female sex workers [FSW]) based on reported sexual behaviour.
   We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
@@
   Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all expected new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
-  Female sex workers were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all expected new infections.
+  FSW were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all expected new infections.
 
@@
   Our risk group estimates provide data for HIV programmes to set targets and implement differentiated prevention strategies outlined in the Global AIDS Strategy.
-  Successfully implementing this approach would result in more efficiently reaching substantially more at risk for infections.
+  Successfully implementing this approach would result in more efficiently reaching substantially more of those at risk for infections.
 
@@
 We also note the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique [@unicef].
+<!-- Source suggested by KJ on this: https://onlinelibrary.wiley.com/doi/10.1111/padr.12043 -->
+<!-- Widespread changes in sexual behaviour in eastern and southernAfrica: Challenges to achieving global HIV targets? Longitudinalanalyses of nationally representative surveys -->
 
@@
 Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig).
-Third, we provide estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
+Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
 
@@
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
-These reporting biases will also have distorted of our estimates of infection risk ratios and prevalence ratios, likely over-attributing risk to higher risk groups.
+These reporting biases will also have distorted the estimates of infection risk ratios and prevalence ratios we used in our analysis, likely over-attributing risk to higher risk groups.
 
@@
 Using these estimates, we performed an analysis of the number of infections that could be reached by prioritisation based upon location, age and behaviour.
-Though subject to limitations, our results quantify the crucial importance of reaching the AGYW at highest risk.
+Though subject to limitations, our results quantify the crucial importance of prioritising reaching AGYW at highest risk.
+<!-- TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
 

### 2022-06-25 src/plot_continental-map/functions.R

@@ -44,7 +44,7 @@ continental_map <- function(df, areas, national_areas) {
     geom_sf(data = filter(national_areas, area_id %in% c(priority_iso3, missing_iso3)),
             aes(geometry = geometry), fill = NA, size = 0.2) +
     scale_fill_viridis_c(option = "C", label = label_percent(), na.value = "#E6E6E6") +
-    facet_grid(age_group ~ indicator) +
+    facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
     labs(fill = "Estimated proportion") +
     theme_minimal() +
     theme(

### 2022-06-25 src/plot_within-between-country-variation/script.R

@@ -33,7 +33,7 @@ plotA <- df_3p1_subnational %>%
     geom_jitter(width = 0.1, alpha = 0.6, shape = 20) +
     geom_point(data = df_3p1_national, aes(x = fct_rev(iso3), y = estimate_smoothed),
                shape = 21, size = 2, fill = "white", col = "black", alpha = 0.9) +
-    facet_grid(age_group ~  indicator, labeller = labeller(indicator = label_wrap_gen(10))) +
+    facet_grid(age_group ~  indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
     scale_color_manual(values = multi.utils::cbpalette()) +
     scale_y_continuous(labels = function(x) paste0(100 * x, "%")) +
     coord_flip() +
@@ -67,7 +67,7 @@ df_3p1_subnational %>%
   mutate(iso3 = reorder(iso3, iso3_sort_order)) %>%
   filter(
     age_group == "15-19",
-    indicator == "Cohabiting partner"
+    indicator == "One cohabiting partner"
   ) %>%
   mutate(
     moz_indicator = factor(ifelse(iso3 == "Mozambique", 1, 0))
@@ -81,7 +81,7 @@ df_3p1_subnational %>%
   scale_y_continuous(labels = function(x) paste0(100 * x, "%")) +
   coord_flip() +
   labs(x = "", y = "Proportion of girls 15-19 cohabiting", col = "") +
-  guides(colour = FALSE) +
+  guides(colour = "none") +
   theme_minimal() +
   theme(
     panel.spacing = unit(0.5, "lines"),

### 2022-06-27 src/docs_paper/paper.Rmd
Easy fixes from KAR comments on paper.Rmd #128

@@
 
+<!-- Suggestions for other things to include in the results from Katie: -->
+<!-- * Number in different buckets of intervention strategies (caveat on not including STI past year) -->
+<!-- * Section on incidence disaggregated by risk group -->
+
 ## Data
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r agyw_surveyed_age$Y025_029` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_age$Y025_029)` aged 25-29 years).
 Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size of `r comma(agyw_surveyed_giftsvar - giftsvar_Y025_029_overcount)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029 - giftsvar_Y025_029_overcount)` aged 25-29 years^[There were `r length(giftsvar_exclude_Y025_029)` DHS surveys which excluded women 25-29 from the transactional sex survey question.]).
@@
   ungroup() %>%
-  mutate(across(lower:upper, ~signif(.x, digits = 3)))
+  mutate(across(lower:upper, ~round(.x, digits = 1)))
 
@@
   ) %>%
-  mutate(across(lower:upper, ~signif(.x, digits = 3)))
+  mutate(across(lower:upper, ~ round(.x, digits = 1)))
 
@@
   summarise(
-    max = 100 * round(max(prop_population_cumulative), 3),
-    median = 100 * round(median(prop_population_cumulative), 3),
-    min = 100 * round(min(prop_population_cumulative), 3)
+    max = round(100 * max(prop_population_cumulative), 1),
+    median = round(100 * median(prop_population_cumulative), 1),
+    min = round(100 * min(prop_population_cumulative), 1)
   )
@@
   select(prop_infections_averted_cumulative, prop_population_cumulative) %>%
-  mutate(across(everything(), ~ 100 * signif(.x, digits = 3)))
+  mutate(across(everything(), ~ round(100 * .x, digits = 1)))
 
@@
 Considering each country separately, on average, reaching half of new infections required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
-The importance of stratifying risk upon age, location and behaviour within a country varied, analogous to the varying contribution of each to the total variance (Appendix B).
+The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (Appendix B).
 For example, FSW in Kenya were estimated to be `r inf_fsw_kenya$prop_population_cumulative`\% of the population and close to a third (`r inf_fsw_kenya$prop_infections_averted_cumulative`\%) of all new infections, whereas FSW in Tanzania were just `r inf_fsw_tanzania$prop_population_cumulative`\% of the population and `r inf_fsw_tanzania$prop_infections_averted_cumulative`\% of all new infections.
@@
 
+<!-- Suggestions for other things to include in the discussion from Katie: -->
+<!-- *  Discussion of different interventions to be implemented in the different risk groups based on Global Strategy -->
+<!-- *  Possibly move section on "not including all variables" into discussion, and discuss all relevant variables, then say why we settled for the ones we did -->
+
 We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with pressing HIV prevention requirements.
@@
 
-By considering all possible risk stratification strategies, we showed that successful implementation of a risk-stratified approach would allow substantially more of those at risk for infections to be identified before infection occurs.
-A considerable proportion estimated new infections were among FSW, supporting the case for HIV programming efforts focused on key population groups [@baral2012burden].
+By considering a range of possible risk stratification strategies, we showed that successful implementation of a risk-stratified approach would allow substantially more of those at risk for infections to be identified before infection occurs.
+A considerable proportion of estimated new infections were among FSW, supporting the case for HIV programming efforts focused on key population groups [@baral2012burden].
 There is substantial variation in the importance of prioritisation by age, location and behaviour within each country.
@@
 The delineation does not represent a boundary between predominately Christian and Muslim populations, which is further north.
-We also note the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique [@unicef].
+We also note that the high numbers of adolescent girls aged 15-19 cohabiting in Mozambique is markedly different from the other countries [@unicef].
 <!-- Source suggested by KJ on this: https://onlinelibrary.wiley.com/doi/10.1111/padr.12043 -->
@@
 First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
-Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig).
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig B.2).
 Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
 
-@brugh2021characterizing previously geographically mapped AGYW HIV risk groups using biomaker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
+Brugh et al.
+[@brugh2021characterizing] previously geographically mapped AGYW HIV risk groups using biomarker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
 Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
@@
 
+<!-- Think it's a good idea to move the start of this to discussion. -->
+<!-- There are good reasons why we chose the risk groups that we did. -->
 The risk groups we analysed did not consider other important characteristics, such as condom usage or partner-specific risk, which contribute to heterogeneity within each risk group.
 Although the number of risk groups considered could be increased, capturing more of this heterogeneity, this inclination must be balanced with the benefits of parsimony.
-Our approach assumed that within risk group heterogeneity is small enough that the categories are meaningfully consistent across contexts.
-Additionally, the categories we used are not immediately actionable.
-For example, a program is designed to reach AGYW who are cohabiting, then it is not clear how to find these individuals within a community.
-It may be preferable to select risk groups based more amenable attributes, such as attendance of a particular service or facility.
+Our approach assumed that within risk group heterogeneity is small enough that the risk groups are meaningfully consistent across contexts.
+Additionally, it is not clear how to find those AGYW within the risk groups we defined in a community.
+It may be preferable to select risk groups based on other more easily observable attributes, such as attendance of a particular service or facility.
 <!-- e.g. school, healthcare -->
@@
 For guidance of resource allocation, differing rates of under-reporting by country, district, year or age group are particularly concerning to the applicability of our results; and, while it may be reasonable to assume a constant rate over space-time, the same cannot be said for age, where aspects of under-reporting have been shown to decline as respondents age [@glynn2011assessing], suggesting that the elevated risks we found faced by younger women are likely a conservative estimate.
-These reporting biases will also have distorted the estimates of infection risk ratios and prevalence ratios we used in our analysis, likely over-attributing risk to higher risk groups.
+If present, these reporting biases will also have distorted the estimates of infection risk ratios and prevalence ratios we used in our analysis, likely over-attributing risk to higher risk groups.
 
@@
 By limiting our consideration to this group we did not account for `r 100 - infections_percent`\% of new infections in adults 15-49.
-Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models of greater fidelity to reality which include stratification of individuals by sexual risk.
+Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models to include stratification of individuals by sexual risk.
 
@@
 
+<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
+
 AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).

### 2022-06-27 src/plot_continental-map/functions.R

@@ -40,7 +40,7 @@ continental_map <- function(df, areas, national_areas) {
   )
 
   ggplot(df_subnational, aes(fill = estimate_smoothed)) +
-    geom_sf(size = 0.1, colour = scales::alpha("grey", 0.25)) +
+    geom_sf(size = 0.05, colour = scales::alpha("grey", 0.1)) +
     geom_sf(data = filter(national_areas, area_id %in% c(priority_iso3, missing_iso3)),
             aes(geometry = geometry), fill = NA, size = 0.2) +
     scale_fill_viridis_c(option = "C", label = label_percent(), na.value = "#E6E6E6") +

### 2022-07-04 src/docs_paper/appendix.Rmd
Small appendix fixes SRF #128

@@
 Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
-We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
+We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
 Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
 We used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
-Typically, this model would be specified using a multinomial likelihood
+This model can be specified using a multinomial likelihood
 \begin{equation}
@@
 where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
-Following the baseline category approach with $k = 1$ say, linear predictors would then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
-Instead of taking this approach, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
+Following the baseline category approach with $k = 1$, linear predictors may then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
+To facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
 This transformation, and further details about this model, are presented in Section 1.2.
@@
 \begin{align}
-    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \\
-    q_{ia} &= p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}, \\
+    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \label{eq:logistic-regression} \\
     q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
 \end{align}
-for suitable choice of the linear predictor $\eta_{ia}$, described in Section 1.3.
-Taking this modular approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
-As all such surveys occurred in 2013-2018, in the logistic regresion model $q_{ia}$ was assumed to be constant over time.
+where $q_{ia} = p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}$ and the linear predictor $\eta_{ia}$ is chosen suitably, described in Section 1.3.
+Taking this two-step approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question in Equation \ref{eq:logistic-regression}.
+As all such surveys occurred in 2013-2018, in the logistic regression model $q_{ia}$ was assumed to be constant over time.
 
@@
 \midrule
-M1 & IID & IID & IID & IID & IID & \xmark \\
+M1 & IID & IID & IID & IID & IID & Not included \\
 M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\
-M2 & IID & IID & IID & Besag & IID & \xmark \\
+M2 & IID & IID & IID & Besag & IID & Not included \\
 M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\
-M3 & IID & IID & IID & IID & AR1 & \xmark \\
+M3 & IID & IID & IID & IID & AR1 & Not included \\
 M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\
-M4 & IID & IID & IID & Besag & AR1 & \xmark \\
+M4 & IID & IID & IID & Besag & AR1 & Not included \\
 M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\
@@
 $$
-As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).
+As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$.
 To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
@@
 \midrule
-L1 & Constant & IID & IID & IID & \xmark \\
-L2 & Constant & IID & IID & Besag & \xmark \\
+L1 & Constant & IID & IID & IID & Not included \\
+L2 & Constant & IID & IID & Besag & Not included \\
 L3 & Constant & IID & IID & IID & \texttt{cfswever} \\
@@
 As with the multinomial regression model, we used survey weighted counts $\{y_{itak}^\star\}$ and sample sizes $\{m_{itak}^\star\}$.
-We used a used a generalised binomial pseudo-likelihood $y^\star \sim \text{xBinomial}(y^\star, m^\star)$, as implemented by \texttt{family = "xBinomial"} in \texttt{R-INLA}, given by
+We used a generalised binomial pseudo-likelihood $y^\star \sim \text{xBinomial}(y^\star, m^\star)$, as implemented by \texttt{family = "xBinomial"} in \texttt{R-INLA}, given by
 \begin{equation}
@@
 \end{tabularx}
-\caption{Logistic regression model performance.}
+\caption{Logistic regression model performance. For the CPO, higher values indicate better model performance for the CPO. For the DIC and WAIC, lower values indicate better model performance.}
 \label{tab:logistic-model-performance}
@@
     \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.jpeg}}
-    \caption{Logistic regression model performance.}
+    \caption{Logistic regression model performance, with the best performing model(s) according to each criteria shown as a square.}
     \label{fig:logistic-model-performance}

### 2022-07-04 src/docs_paper/paper.Rmd
Easy fixes from VKN #128

@@
 Combining the two highest risk groups (high and very high) in this way allowed data from all surveys to be included in this first stage model.
-Second, we fit a spatial logistic regression model separating those who have non-regular or multiple partner(s) or multiple partners from those who reported transactional sex, stratified by district, and five-year age group, and using only data from the surveys with a specific transactional sex question.
+Second, we fit a spatial logistic regression model separating those who have non-regular or multiple partner(s) from those who reported transactional sex, stratified by district, and five-year age group, and using only data from the surveys with a specific transactional sex question.
 As surveys were only available in the years 2013-2018, we assumed the proportion in the very high risk group among those in the two highest risk groups was constant over time.
@@
 Finally, we adjusted the samples from the transactional sex category to match age- and country-specific FSW population size estimates.
-To ensure that after adjustment the risk group proportions still sum to one, we made appropriate modifications to the samples from the non-regular or multiple partner(s) category.
+We modified the samples from the non-regular or multiple partner(s) risk group to ensure that after adjustment the risk group proportions still summed to one.
 FSW population size estimates by age were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
-Technical details of the models we used are in Appendix A.1.
+Further technical details are in Appendix A.1.
 
@@
 
-```{r continental-map, fig.cap="Choropleths of the posterior mean proportion of AGYW in each risk group in 2018.
+```{r continental-map, fig.cap="The spatial distribution (posterior mean) of the AGYW risk group proportions in 2018.
 Countries in grey are included to show Cameroon (upper left) in relation to the other twelve spatially-contiguous countries (lower right).
@@
 
-The median national FSW proportion was `r fsw_age_Y015_019$median`\% (95\% CI `r fsw_age_Y015_019$lower`--`r fsw_age_Y015_019$upper`\%) for the 15-19 age group, `r fsw_age_Y020_024$median`\% (95\% CI `r fsw_age_Y020_024$lower`--`r fsw_age_Y020_024$upper`\%) for the 20-24 age group and `r fsw_age_Y025_029$median`\% (95\% CI `r fsw_age_Y025_029$lower`--`r fsw_age_Y025_029$upper`\%) for the 25-29 age group.
+The median national FSW proportion was `r fsw_age_Y015_019$median`\% (95\% CI `r fsw_age_Y015_019$lower`--`r fsw_age_Y015_019$upper`) for the 15-19 age group, `r fsw_age_Y020_024$median`\% (95\% CI `r fsw_age_Y020_024$lower`--`r fsw_age_Y020_024$upper`) for the 20-24 age group and `r fsw_age_Y025_029$median`\% (95\% CI `r fsw_age_Y025_029$lower`--`r fsw_age_Y025_029$upper`) for the 25-29 age group.
 
@@
 
-In most districts (`r round(district_Y015_019_nosex12m_quantiles$median, 1)`\%; 95\% credible interval [CI] `r round(district_Y015_019_nosex12m_quantiles$lower, 1)`--`r round(district_Y015_019_nosex12m_quantiles$upper, 1)`\%) adolescent girls aged 15-19 were not sexually active.
+In most districts (`r round(district_Y015_019_nosex12m_quantiles$median, 1)`\%; 95\% credible interval [CI] `r round(district_Y015_019_nosex12m_quantiles$lower, 1)`--`r round(district_Y015_019_nosex12m_quantiles$upper, 1)`) adolescent girls aged 15-19 were not sexually active.
 The exception was Mozambique, where the majority (`r 100 - round(moz_Y015_019_nosex12m$estimate_smoothed, 2)`\%) were sexually active in the past year and close to a third (`r round(moz_Y015_019_sexcohab$estimate_smoothed, 2)`\%) were cohabiting with a partner.
@@
 
-Age explained `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`\%) of the variation in risk group proportions.
-Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`\%) of variation and district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`\%).
-Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`\%) of variation, indicating very little change in risk group proportions over time.
+Age explained `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`) of the variation in risk group proportions.
+Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`) of variation and district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`).
+Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`) of variation, indicating very little change in risk group proportions over time.
 We observed similar variance decomposition results fitting each country individually, and using other model specifications.

### 2022-07-04 src/docs_paper/tables-figures.Rmd
Add GAS commitments #128

@@
 \end{tabularx}
-\caption{Prioritisation strata.}
+\caption{Prioritisation strata according to HIV incidence in the general population and behavioural risk.}
 \label{tab:unaids-strategy-prioritisation}
@@
 \centering
-\begin{tabularx}{\textwidth}{lX}
+\begin{tabularx}{\textwidth}{p{9cm}XXXX}
 \toprule
-Intervention & Details \\
+Intervention & Low & Moderate & High & Very High \\
 \midrule
-STI screening and treatment & (Remain to be filled in: describe targets and commitments in terms of each prioritisation strata) \\
-PrEP use & (As above) \\
-Access to PEP & (As above) \\
-Comprehensive sexuality education & (As above) \\
-Economic empowerment & (As above) \\
+Condoms and lube for those with non-regular partners(s) with unknown STI status and not on PrEP & 50\% & 70\% & 95\% & 95\% \\
+STI screening and treatment & 10\% & 10\% & 80\% & 80\% \\
+Access to PEP & - & - & 50\% & 90\% \\
+PrEP use & - & 5\% & 50\% & 50\% \\
+Economic empowerment & - & - & 20\% & 20\% \\
 \bottomrule
 \end{tabularx}
-\caption{Targets and commitments.}
+\caption{Commitments to be met for each intervention in terms of proportion of the prioritisation strata reached, where "-" represents no commitment.}
 \label{tab:unaids-strategy-targets}

### 2022-07-06 src/docs_paper/script.R
Add information criteria plot for multinomial to appendix #128

@@ -19,6 +19,7 @@ convert_pdf_jpeg("3p1-within-between-country-variation")
 convert_pdf_jpeg("infections-reached")
 
 #' For appendix.Rmd
+convert_pdf_jpeg("information-criteria")
 convert_pdf_jpeg("fsw-logit-information-criteria")
 convert_pdf_jpeg("coverage")
 

### 2022-07-06 src/process_information-criteria/functions.R

@@ -106,8 +106,8 @@ create_latex_table <- function(df, file_name) {
     ) %>%
     select(-contains("se")) %>%
     rename_with(~toupper(.), .cols = any_of(c("dic", "waic", "cpo"))) %>%
+    rename(country = iso3) %>%
     rename_with(~str_to_title(.), .cols = any_of(c("model", "country"))) %>%
-    select(-any_of(c("iso3"))) %>%
     pivot_longer(
       cols = c("DIC", "WAIC", "CPO"),
       names_to = "Criteria"

### 2022-07-06 src/process_information-criteria/script.R

@@ -168,7 +168,9 @@ create_latex_table(df_4, file_name = "4-model-comparison.txt")
 
 files <- paste0("depends/", tolower(unique(available_surveys$iso3)), "_3-information-criteria.csv")
 df_3 <- bind_rows(lapply(files, function(file) read_csv(file))) %>%
-  update_naming()
+  mutate(age_group = "placeholder", indicator = "placeholder") %>%
+  multi.utils::update_naming() %>%
+  select(-age_group, -indicator)
 
 #' Countries with only one survey
 iso3_3_single <- available_surveys %>%

### 2022-07-06 src/docs_paper/paper.Rmd
Reworking the discussion section #128

@@
 The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.
-When the local HIV incidence in the general population is higher, the incidence rate ratio is lower.}
+When the local HIV incidence in the general population is higher, the incidence rate ratio for FSW is lower.}
 \label{tab:risk-groups}
@@
 <!-- *  Discussion of different interventions to be implemented in the different risk groups based on Global Strategy -->
-<!-- *  Possibly move section on "not including all variables" into discussion, and discuss all relevant variables, then say why we settled for the ones we did -->
 
-We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with pressing HIV prevention requirements.
+We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with high-priority HIV prevention requirements.
 Our estimates support consideration of differentiated prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
 <!-- Some type of comment about how novel this would be if implemented -->
+
+We used risk group definitions based on individual sexual behaviour, the most proximal determinant of risk.
+Other factors, such as condom usage, could be considered for extending the risk group defintions, but the appeal of accounting for greater risk heterogenity must be balanced with the benefits of parsimony and measurement difficulties associated to any additional factors.
+<!-- Reasons why we didn't include condom usage: -->
+<!-- Defining condom usage is challenging, particularly for those with multiple partners, and reporting is likely biased due to social desirability. -->
+<!-- Additionally, consistent condom usage is rare amongst those cohabiting, and as such likely only relevant for those with non-regular sexual partners.  -->
+
+Brugh et al.
+[@brugh2021characterizing] previously geographically mapped AGYW HIV risk groups using biomarker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
+Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
 
@@
 <!-- Source suggested by KJ on this: https://onlinelibrary.wiley.com/doi/10.1111/padr.12043 -->
-<!-- Widespread changes in sexual behaviour in eastern and southernAfrica: Challenges to achieving global HIV targets? Longitudinalanalyses of nationally representative surveys -->
+<!-- Widespread changes in sexual behaviour in eastern and southern Africa: Challenges to achieving global HIV targets? Longitudinal analyses of nationally representative surveys -->
+
+The final surveys included in our risk model model were conducted in 2018.
+We plan to update our analysis with more surveys as they become available, but do not anticipate that the risk group proportions will change substantially, as we found that they did not change significantly over time.
 
@@
 
-Brugh et al.
-[@brugh2021characterizing] previously geographically mapped AGYW HIV risk groups using biomarker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
-Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
+Our analysis focused only on females aged 15-29 years, and could be extended to consider optimisation of prevention for the broader population, accounting for the `r 100 - infections_percent`\% of new infections which occur in women 29-49 and men 15-49.
+Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models to include stratification of individuals by sexual risk.
 
@@
 
-<!-- TWM: Consider adding a note about last data point being in 2018. There is so little change over time it shouldn't make a difference, but 2018 is starting to sound like a long time ago -->
-
 ## Limitations
 
-<!-- Think it's a good idea to move the start of this to discussion. -->
-<!-- There are good reasons why we chose the risk groups that we did. -->
-The risk groups we analysed did not consider other important characteristics, such as condom usage or partner-specific risk, which contribute to heterogeneity within each risk group.
-Although the number of risk groups considered could be increased, capturing more of this heterogeneity, this inclination must be balanced with the benefits of parsimony.
-Our approach assumed that within risk group heterogeneity is small enough that the risk groups are meaningfully consistent across contexts.
-Additionally, it is not clear how to find those AGYW within the risk groups we defined in a community.
-It may be preferable to select risk groups based on other more easily observable attributes, such as attendance of a particular service or facility.
-<!-- e.g. school, healthcare -->
-
-Under-reporting of higher risk sexual behaviours among AGYW could affect the validity of our risk group proportion estimates.
+Our analysis was subject to challenges shared by almost approaches to monitoring sexual behaviour in the general population [@cleland2004monitoring].
+In particular, under-reporting of higher risk sexual behaviours among AGYW could affect the validity of our risk group proportion estimates.
 Due to social stigma or disapproval, respondents may be reluctant to report non-marital partners [@nnko2004secretive, @helleringer2011reliability] or may bias their reporting of sexual debut [@zaba2004age; @wringe2009comparative; @nguyen2022trends].
@@
 We did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
+
 The efficiency of each stratified prevention strategy depends on the ability of programmes to identify and effectively reach those in each strata.
@@
 Empirical evaluations of behavioural risk screening tools have found only moderate discriminatory ability [@jia2022risk], and risk behaviour may change rapidly among young populations, increasing the challenge to effectively deliver appropriately timed prevention packages.
-
-Finally, our analysis focused only on females aged 15-29 years and therefore did not consider optimisation of prevention for the broader population.
-By limiting our consideration to this group we did not account for `r 100 - infections_percent`\% of new infections in adults 15-49.
-Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models to include stratification of individuals by sexual risk.
-
-<!-- Reasons why we didn't include condom usage: -->
-<!-- Defining condom usage is challenging, particularly for those with multiple partners, and reporting is likely biased due to social desirability. -->
-<!-- Additionally, consistent condom usage is rare amongst those cohabiting, and as such likely only relevant for those with non-regular sexual partners.  -->
+This consideration may motivate selecting risk groups based on easily observable attributes, such as attendance of a particular service or facility, rather than sexual behaviour.
 

### 2022-07-09 src/docs_paper/paper.Rmd
Note about 2022 and 2021 data (MOZ) #128
Draft of fixing comments from MM #128

@@
 In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r population_percent`\% of the population but `r infections_percent`\% of new HIV infections [@unaids2021update].
-HIV incidence amongst AGYW is `r inc_ratio` times higher than among similarly aged males due to younger age at first sex, age patterns of sexual mixing, structural vulnerability and power imbalances, and increased susceptibility to HIV infection [@joint2016hiv].
+HIV incidence amongst AGYW is `r inc_ratio` times higher than among similarly aged males, due to structural vulnerability and power imbalances, age patterns of sexual mixing, younger age at first sex, and increased susceptibility to HIV infection [@joint2016hiv].
 AGYW have therefore been identified as a priority population for HIV primary prevention, with significant investments being made in prevention programming [@saul2018dreams; @global2018measurement].
@@
 For each survey, we classified female respondents aged 15-29 years into one of four behavioural risk groups according to reported sexual risk behaviour in the past 12 months.
-These risk groups were: not sexually active, one cohabiting sexual partner, at non-regular or multiple sexual partner(s), and AGYW who report transactional sex (Table \ref{tab:risk-groups}).
+These risk groups were: not sexually active, one cohabiting sexual partner, non-regular or multiple sexual partner(s), and AGYW who report transactional sex (Table \ref{tab:risk-groups}).
 In the case of inconsistent responses, women were categorised according to the highest risk group they fell into, ensuring that the categories were mutually exclusive.
@@
 <!-- and so far has been used by X countries could be better (adds some information that it's widely used) -->
-The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning in UNAIDS Naomi estimates, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Table B.5).
+The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning by countries, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Table B.5).
+We used the most recent 2022 estimates for all countries, apart from Mozambique where, due to data accuracy concerns, we used the 2021 estimates (in which the Cabo Delgado province is excluded due to disruption by conflict).
 
@@
 ```{r continental-map, fig.cap="The spatial distribution (posterior mean) of the AGYW risk group proportions in 2018.
-Countries in grey are included to show Cameroon (upper left) in relation to the other twelve spatially-contiguous countries (lower right).
+Countries in grey were not included in our analysis.
 \\label{fig:continental-map}"}
@@
 Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model.
-Posterior mean, median, and 95\% credible intervals are provided in supplementary material as `estimates.csv`.
+Posterior mean, median, and 95\% credible intervals are provided in the supplementary material.
 In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
@@
 
-Age explained `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`) of the variation in risk group proportions.
-Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`) of variation and district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`).
+Age group was the most important factor explaining variation in risk group proportions, and accounted for `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`) of total variation.
+The primary change in risk group proportions by age group occurs between the 15-19 age group and 20-29 age group (Fig \ref{fig:within-between-country-variation}).
+The next most important factor was location.
+Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`) of variation, while district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`).
+<!-- Can I plot the country-level and district-level random effects to visualise this? -->
 Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`) of variation, indicating very little change in risk group proportions over time.
@@
   **Methods:**
-  We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 Global Fund priority countries in sub-Saharan Africa.
+  We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 high burden countries in sub-Saharan Africa.
   Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular or multiple partner[s] and female sex workers [FSW]) based on reported sexual behaviour.
   We used a Bayesian spatio-temporal multinomial regression model to estimate the proportion of AGYW in each risk group stratified by district, year, and five-year age group.
-  Using the UNAIDS district-level estimates of HIV prevalence and incidence, we estimated new HIV infections in each risk group by district and age group.
+  Using subnational estimates of HIV prevalence and incidence produced by countries with support from UNAIDS, we estimated new HIV infections in each risk group by district and age group.
   We then assessed the efficiency of prioritising interventions according to risk group.
@@
   Data consisted of `r comma(agyw_surveyed)` female survey respondents aged 15-29.
-  Risk group proportions varied substantially across age groups (`r variance_proportions_age$mean`\% of total variation), countries (`r variance_proportions_iso3$mean`\%), and between districts within each country (`r variance_proportions_area$mean`\%), but changed little over time (`r variance_proportions_year$mean`\%).
   Among women aged 20-29, cohabiting (`r dividing_border_above_sexcohab$median`\%) was more common in eastern Africa than non-regular or multiple partner(s) (`r dividing_border_above_sexnonreg$median`\%), while in southern countries non-regular or multiple partner(s) (`r dividing_border_below_sexnonreg$median`\%) were more common than cohabiting (`r dividing_border_below_sexcohab$median`\%).
-  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population that must be reached to find half of all expected new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
+    Risk group proportions varied substantially across age groups (`r variance_proportions_age$mean`\% of total variation explained), countries (`r variance_proportions_iso3$mean`\%), and between districts within each country (`r variance_proportions_area$mean`\%), but changed little over time (`r variance_proportions_year$mean`\%).
+  Prioritisation based on behavioural risk, in combination with location- and age-based prioritisation, reduced the proportion of population required to be reached in order to find half of all expected new infections from `r inf_half_without_behaviour`\% to `r inf_half_with_behaviour`\%.
   FSW were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all expected new infections.
@@
 author_summary: |
-  Exposure to HIV among adolescent girls and young women depends on individual sexual behaviour and the level of HIV in the local community among potential sexual partners.
+  Exposure to HIV among adolescent girls and young women depends on the level of unsuppresed HIV in their local community among potential partners, and their individual sexual behaviour.
   To support HIV programmes in identifying and providing services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
@@
 
-We estimated sexual risk group proportions for AGYW at a district-level in 13 sub-Saharan African countries with high-priority HIV prevention requirements.
-Our estimates support consideration of differentiated prevention programming according to risk behaviour, as outlined in the Global AIDS Strategy.
+We estimated the proportion of AGYW who fall into different risk groups at a district level in 13 sub-Saharan African countries.
+Our estimates support consideration of differentiated prevention programming according to geographic locations and risk behaviour, as outlined in the Global AIDS Strategy.
 <!-- Some type of comment about how novel this would be if implemented -->
 
-We used risk group definitions based on individual sexual behaviour, the most proximal determinant of risk.
-Other factors, such as condom usage, could be considered for extending the risk group defintions, but the appeal of accounting for greater risk heterogenity must be balanced with the benefits of parsimony and measurement difficulties associated to any additional factors.
+We defined four risk groups based on sexual behaviour, the most proximal determinant of risk.
+Other factors, such as condom usage or type of sexual act, may account for additional heterogeneity in risk from sexual behaviour.
+However, we did not include these factors in view of measurement difficulties, consistency across contexts, and the operational benefits of describing risk parsimoniously.
 <!-- Reasons why we didn't include condom usage: -->
@@
 <!-- Additionally, consistent condom usage is rare amongst those cohabiting, and as such likely only relevant for those with non-regular sexual partners.  -->
+Sexual behaviour confers risk only when AGYW reside in geographic locations where there is unsuppressed viral load among their potential partners.
+
+We did not include more distal determinants, such as school attendance, orphanhood, or gender empowerment, as we expect their effects on risk to largely be mediated by more proximal determinants.
+However, to effectively implement programming, it is crucial to understand these factors, as well as the broader structural barriers and limits to personal agency faced by AGYW.
+Importantly, programs must ensure that intervention prioritisation occurs without stigmatising or blaming AGYW.
 
@@
 [@brugh2021characterizing] previously geographically mapped AGYW HIV risk groups using biomarker and behavioural data from the most recent surveys in Eswatini, Haiti and Mozambique to define and subsequently map risk groups with a range of machine learning techniques.
-Our work builds on [@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
+Our work builds on Brugh et al.
+[@brugh2021characterizing] by including more countries, integrating a greater number of surveys, and connecting risk group proportions with HIV epidemic indicators to help inform programming.
 
@@
 
+Our modelled estimates of risk group proportions improve upon direct survey results for three reasons.
+First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig B.2).
+Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines (such as our analysis of risk group specific prevalence and incidence).
+
 The final surveys included in our risk model model were conducted in 2018.
@@
 
-Our modelled estimates improve upon direct survey results for three reasons.
-First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
-Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig B.2).
-Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines.
-
-Our analysis focused only on females aged 15-29 years, and could be extended to consider optimisation of prevention for the broader population, accounting for the `r 100 - infections_percent`\% of new infections which occur in women 29-49 and men 15-49.
-Obtaining population size estimates for sexual risk behaviour in the general population would be a crucial step toward greater understanding the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models to include stratification of individuals by sexual risk.
+Our analysis focused on females aged 15-29 years, and could be extended to consider optimisation of prevention more broadly, accounting for the `r 100 - infections_percent`\% of new infections among adults 15-49 which occur in women 30-49 and men 15-49.
+Estimating sexual risk behaviour in adults 15-49 would be a crucial step toward greater understanding of the dynamics of the HIV epidemic in sub-Saharan Africa, and would allow incidence models to include stratification of individuals by sexual risk.
 
@@
 
-Our analysis was subject to challenges shared by almost approaches to monitoring sexual behaviour in the general population [@cleland2004monitoring].
+Our analysis was subject to challenges shared by most approaches to monitoring sexual behaviour in the general population [@cleland2004monitoring].
 In particular, under-reporting of higher risk sexual behaviours among AGYW could affect the validity of our risk group proportion estimates.
@@
 
-Our FSW estimates do not overcome the difficulties of sampling hard to reach groups.
-We did not consider seasonal migration patterns, which may particularly effect FSW population sizes.
+We have the least confidence in our estimates for the FSW risk group.
+As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups.
+In adjusting our estimates of transactional sex to match national FSW estimates, we inherent their limitations. 
+Furthermore, we do not consider seasonal migration patterns, which may particularly effect FSW size.
 
 The efficiency of each stratified prevention strategy depends on the ability of programmes to identify and effectively reach those in each strata.
-Our analysis assumed a "best-case" scenario where AGYW of every strata are reached perfectly, and should therefore be interpreted as illustrating the potentially obtainable benefits rather than benefits which would be obtained from any specific intervention strategy.
+Our analysis of new infections potentially averted assumed a "best-case" scenario where AGYW of every strata can be reached perfectly, and should therefore be interpreted as illustrating the potentially obtainable benefits rather than benefits which would be obtained from any specific intervention strategy.
 In practice, stratified prevention strategies are likely to be substantially less efficient than this best-case scenario.
@@
 Using these estimates, we performed an analysis of the number of infections that could be reached by prioritisation based upon location, age and behaviour.
-Though subject to limitations, our results quantify the crucial importance of prioritising reaching AGYW at highest risk.
+Though subject to limitations, our results quantify the crucial importance of prioritising reaching AGYW in the highest risk districts and at highest behavioural risk.
 <!-- TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->

### 2022-07-09 src/docs_paper/appendix.Rmd
Add information criteria plot for multinomial to appendix #128
JWE suggests replacing .jpeg with .png #128

@@
 
-To fill: table and figure.
+\begin{figure}[h]
+    \centering
+    \makebox[\textwidth][c]{\includegraphics{depends/model-comparison.png}}
+    \caption{Multinomial regression model performance, with the best performing model(s) according to each criteria shown as a square.}
+    \label{fig:multinomial-model-performance}
+\end{figure}
+
+To fill: table.
 
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.png}}
     \caption{Logistic regression model performance, with the best performing model(s) according to each criteria shown as a square.}
@@
   \centering
-  \makebox[\textwidth][c]{\includegraphics{depends/coverage.jpeg}}
+  \makebox[\textwidth][c]{\includegraphics{depends/coverage.png}}
   \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models.

### 2022-07-09 src/docs_paper/paper.Rmd
JWE suggests replacing .jpeg with .png #128

@@
 ```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
-knitr::include_graphics("depends/available-surveys.jpeg")
+knitr::include_graphics("depends/available-surveys.png")
 ```
@@
 #' Note that the subnational borders look a bit overpowering when the quality of this is reduced
-knitr::include_graphics("depends/3p1-continental-map.jpeg")
+knitr::include_graphics("depends/3p1-continental-map.png")
 ```
@@
 \\label{fig:within-between-country-variation}"}
-knitr::include_graphics("depends/3p1-within-between-country-variation.jpeg")
+knitr::include_graphics("depends/3p1-within-between-country-variation.png")
 ```
@@
 \\label{fig:infections-reached}"}
-knitr::include_graphics("depends/infections-reached.jpeg")
+knitr::include_graphics("depends/infections-reached.png")
 ```

### 2022-07-09 src/docs_paper/tables-figures.Rmd
JWE suggests replacing .jpeg with .png #128

@@
     \centering
-    \includegraphics{depends/category-flowchart.jpeg}
+    \includegraphics{depends/category-flowchart.png}
     \caption{Flowchart describing allocation of respondents to risk groups.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.png}}
 \caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/aaa-variance-proportions.png}}
     \caption{Proportion of variance explained by each random effect (Sobol' indices) when the multinomial regression model is fit to each country individually.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/age-variation.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/age-variation.png}}
 \caption{The posterior density of national-level risk group proportions by age, illustrating the bi-modality of the cohabiting partner and non-regular and multiple partner(s) risk groups.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-1.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-1.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Botswana.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-2.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-2.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Cameroon.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-3.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-3.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Kenya.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-4.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-4.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Lesotho.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-5.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-5.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Mozambique.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-6.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-6.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Malawi.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-7.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-7.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Namibia.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-8.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-8.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Eswatini.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-9.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-9.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Tanzania.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-10.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-10.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Uganda.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-11.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-11.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in South Africa.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-12.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-12.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zambia.
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-13.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/temporal-interpolation-ribbon-13.png}}
 \caption{Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-1.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-1.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Botswana.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-2.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-2.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-3.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-3.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Kenya.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-4.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-4.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-5.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-5.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-6.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-6.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Malawi.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-7.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-7.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Namibia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-8.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-8.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-9.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-9.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-10.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-10.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Uganda.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-11.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-11.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in South Africa.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-12.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-12.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zambia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-13.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/prev-district-sexbehav-logit-13.png}}
     \caption{District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-1.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-1.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Botswana.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-2.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-2.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Cameroon.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-3.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-3.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Kenya.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-4.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-4.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Lesotho.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-5.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-5.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Mozambique.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-6.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-6.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Malawi.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-7.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-7.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Namibia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-8.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-8.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Eswatini.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-9.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-9.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Tanzania.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-10.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-10.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Uganda.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-11.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-11.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in South Africa.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-12.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-12.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Zambia.}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-13.jpeg}}
+    \makebox[\textwidth][c]{\includegraphics{depends/incidence-district-sexbehav-13.png}}
     \caption{District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-1.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-1.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-2.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-2.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-3.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-3.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-4.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-4.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-5.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-5.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-6.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-6.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-7.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-7.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-8.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-8.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-9.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-9.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-10.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-10.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-11.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-11.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-12.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-12.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.}
@@
 \centering
-\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-13.jpeg}}
+\makebox[\textwidth][c]{\includegraphics{depends/infections-reached-country-13.png}}
 \caption{Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.}

### 2022-07-09 src/docs_paper/script.R

@@ -12,26 +12,34 @@ convert_pdf_jpeg <- function(name) {
   system(command)
 }
 
+convert_pdf_png <- function(name) {
+  command <- paste0(
+    "convert -density 300 depends/", name, ".pdf -scene 1 -background white",
+    " -alpha remove -alpha off -quality 80 depends/", name, ".png"
+  )
+  system(command)
+}
+
 #' For paper.Rmd
-convert_pdf_jpeg("available-surveys")
-convert_pdf_jpeg("3p1-continental-map")
-convert_pdf_jpeg("3p1-within-between-country-variation")
-convert_pdf_jpeg("infections-reached")
+convert_pdf_png("available-surveys")
+convert_pdf_png("3p1-continental-map")
+convert_pdf_png("3p1-within-between-country-variation")
+convert_pdf_png("infections-reached")
 
 #' For appendix.Rmd
-convert_pdf_jpeg("information-criteria")
-convert_pdf_jpeg("fsw-logit-information-criteria")
-convert_pdf_jpeg("coverage")
+convert_pdf_png("model-comparison")
+convert_pdf_png("fsw-logit-information-criteria")
+convert_pdf_png("coverage")
 
 #' For tables-figures.Rmd
-convert_pdf_jpeg("category-flowchart")
-convert_pdf_jpeg("model-direct-benefits")
-convert_pdf_jpeg("aaa-variance-proportions")
-convert_pdf_jpeg("age-variation")
-convert_pdf_jpeg("temporal-interpolation-ribbon")
-convert_pdf_jpeg("prev-district-sexbehav-logit")
-convert_pdf_jpeg("incidence-district-sexbehav")
-convert_pdf_jpeg("infections-reached-country")
+convert_pdf_png("category-flowchart")
+convert_pdf_png("model-direct-benefits")
+convert_pdf_png("aaa-variance-proportions")
+convert_pdf_png("age-variation")
+convert_pdf_png("temporal-interpolation-ribbon")
+convert_pdf_png("prev-district-sexbehav-logit")
+convert_pdf_png("incidence-district-sexbehav")
+convert_pdf_png("infections-reached-country")
 
 #' Render documents
 rmarkdown::render("paper.Rmd")

### 2022-07-09 src/docs_paper/appendix.Rmd
Improving appendix (mostly some text about coverage) #128

@@
 Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
-We used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
+
+First, we used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
 This model can be specified using a multinomial likelihood
@@
 where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
-Following the baseline category approach with $k = 1$, linear predictors may then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
-To facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
+Taking $k = 1$ to be the baseline category, linear predictors may be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
+Rather than taking this approach directly, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
 This transformation, and further details about this model, are presented in Section 1.2.
@@
 \end{align}
-where $q_{ia} = p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}$ and the linear predictor $\eta_{ia}$ is chosen suitably, described in Section 1.3.
+where $q_{ia} = p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}$ and the linear predictor $\eta_{ia}$ is chosen suitably, described in more detail in Section 1.3.
 Taking this two-step approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question in Equation \ref{eq:logistic-regression}.
@@
 
-To facilitate uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+To facilitate uncertainty quantification, we took 1000 posterior samples (indexed by $s$) from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
 Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.
@@
 Our methodology for producing these estimates is described in Section \ref{fsw-population-size-estimation}.
-In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
+In making this adjustment, we assumed that subnational variation in the FSW proportions corresponds to that of the transactional sex proportions.
 
@@
 $$
-As described above, we included observation random effects in all models we considered, and set $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$.
+As described above, we included observation random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in all models we considered.
 To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
 Heterogeneity in risk group proportions by age was allowed by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
-We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
+We considered two specifications, independent and identically distributed (IID) and Besag [@besag1991bayesian], for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
 We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}).
-
 All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
 
-#### Spatial random effects \label{sec:spatial-random-effects}
+### Spatial random effects \label{sec:spatial-random-effects}
 
-The specifications we considered were IID $\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and Besag grouped by category
+The specifications we considered were IID
 $$
-\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{13^{+}}, \ldots \phi_{n3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-})
+\phi_{ik} \sim \mathcal{N}(0, \tau_\phi^{-1}),
+$$
+and Besag grouped by category
+$$
+\bphi = (\phi_{11}, \ldots, \phi_{n1}, \ldots, \phi_{13^{+}}, \ldots \phi_{n3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\phi)^{-}),
 $$
@@
 We followed the further recommendations of @freni2018note with regard to disconnected adjacency graphs, singletons and constraints.
-The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with the full conditionals
+The Besag structure matrix $\mathbf{R}_b$ is obtained by the precision matrix of the random effects $\mathbf{b} = (b_1, \ldots, b_n)^\top$ with full conditionals
 \begin{equation}
@@
 In preliminary testing, we excluded spatial random effects from the model, but found that this negatively effected performance.
-We also tested using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one so for simplicity and to avoid numerical issues, by using Besag random effects we decided to fix this proportion to one.
+We also tested using the BYM2 model [@simpson2017penalising] in place of the Besag, but found that the proportion parameter posteriors tended to be highly peaked at the value one.
+For simplicity and to avoid numerical issues, by using Besag random effects we decided to fix this proportion to one.
 
-#### Temporal random effects \label{sec:temporal-random-effects}
+### Temporal random effects \label{sec:temporal-random-effects}
 
-The specifications we considered were IID $\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1})$ and AR1 grouped by category
+The specifications we considered were IID
 $$
-\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{13^{+}}, \ldots, \gamma_{T1}, \ldots, \gamma_{T3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-})
+\phi_{tk} \sim \mathcal{N}(0, \tau_\phi^{-1}),
+$$
+and AR1 grouped by category
+$$
+\bm{\gamma} = (\gamma_{11}, \ldots, \gamma_{13^{+}}, \ldots, \gamma_{T1}, \ldots, \gamma_{T3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\phi \mathbf{R}^\star_\gamma)^{-}),
 $$
@@
 For the lag-one correlation parameter $\rho$, we used the PC prior, as derived by @sorbye2017penalised, with base model $\rho = 1$ and condition $\mathbb{P}(\rho > 0 = 0.75)$.
-We chose a base model corresponding to no change in behaviour over time, rather than the alternative $\rho = 0$ corresponding to no correlation in behaviour over time, as we judged the former to be more plausible a priori.
+We chose the base model $\rho = 1$ corresponding to no change in behaviour over time, rather than the alternative $\rho = 0$ corresponding to no correlation in behaviour over time, as we judged the former to be more plausible a priori.
 
-#### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}
+### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}
 
@@
 In particular, for each of the four models including spatio-temporal interactions, these matrices are
-\begin{itemize}
-\item
-1x: No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
-\item
-2x: Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
-\item
-3x: Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
-\item
-4x: Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
-\\
-\end{itemize}
-where the first, second and third elements of the product represent space, time and category respectively, and the interaction type provided in brackets is given according to the @knorr2000bayesian framework.
 
-#### Constraints
+1. No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
+2. Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
+3. Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
+4. Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
 
-To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
-For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
+where the first, second and third elements of the Kronecker product represent space, time and category strucutre matrices respectively.
+The interaction type in brackets (e.g. Type I) is given according to the @knorr2000bayesian framework.
+
+### Constraints
+
+To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that none of the category interaction random effects altered overall category probabilities.
+For the space-year-category random effects, we applied analogous sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
 Together, these were:
-\begin{enumerate}
-    \item Category $\sum_k \beta_k = 0$
-    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
-    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, c, k$,
-    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
-    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
-    \item Spatio-temporal\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
+
+1. Category $\sum_k \beta_k = 0$
+2. Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
+3. Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, c, k$,
+4. Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
+5. Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
+6.
+Spatio-temporal\footnote{It was not possible to fully implement these constraints in \texttt{R-INLA}.
+This only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
 \quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
 \quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
-\end{enumerate}
 
@@
 The surveys we included use a complex design, in which each individual has an unequal probability of being included in the sample.
-For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling [@measure2012sampling].
-To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y$ are replaced by effective counts $y^\star$ calculated using the survey weights $w_j$ of all individuals $j$ in the corresponding strata.
+The DHS [@measure2012sampling], for example, often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
+
+To account for this aspect of survey design, we use a weighted pseudo-likelihood where the observed counts $y$ are replaced by effective counts $y^\star$ calculated using the survey weights $w_j$ of all individuals $j$ in the corresponding strata.
 We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
@@
 to obtain $y^\star$.
-These counts may not be integers, and the Poisson likelihood we used in Equation \ref{eq:poisson} is inappropriate.
+These counts may not be integers, and as such the Poisson likelihood we used in Equation \ref{eq:poisson} is not appropriate.
 Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, given by
@@
 \end{equation}
-as implemented by `family = "xPoisson"` in `R-INLA`.
+as implemented by `family = "xPoisson"` in `R-INLA`, which accepts non-integer input.
 
@@
 
-To fill: explanation of Figure \ref{fig:coverage}.
+To assess the calibration of our fitted model, we calculated the quantile $q$ of each observation within the posterior predictive distribution (that is, within the collection of samples generated from the posterior predictive distribution).
+For calibrated models, these quantiles, known as probability integral transform (PIT) values [@dawid1984present; @bosse2022scoringutils], should follow a uniform distribution $q \sim \mathcal{U}[0, 1]$.
+
+Using the PIT values, it is possible to calculate the empirical coverage of all $(1 - \alpha)100$\% (equal-tailed) posterior predictive credible intervals.
+These empirical coverages can be compared to the nominal coverage $(1 - \alpha)$ for each value of $\alpha \in [0, 1]$ to give empirical cumulative distribution function (ECDF) difference values.
+This approach has the advantage of considering all possible confidence values at once.
+@sailynoja2021graphical develop binomial distribution-based simultaneous confidence bands for ECDF difference values which test uniformity.
+
+Figure \ref{fig:coverage} shows the PIT histogram and ECDF difference plots for our final model, faceted by risk group.
+<!-- Comment on the results. -->
+<!-- What is going on with the cohabiting partner group towards one? -->
 
@@
   \makebox[\textwidth][c]{\includegraphics{depends/coverage.png}}
-  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected models.
-These plots are adapted from \citet{sailynoja2021graphical} and are an example of posterior predictive checks, see for example \citet[Chapter 6.1]{gelman2020bayesian}.}
+  \caption{Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected model.}
   \label{fig:coverage}

### 2022-07-09 src/docs_paper/appendix.Rmd
Add age-disagg-fsw-line plot #128

@@
 
-To estimate the number of FSW by age group and country, we disaggregated country-specific estimates of adult (15-49) FSW population size from @stevens2022estimating by age.
+To estimate the number of FSW by age group and country, we disaggregated country-specific estimates of adult (15-49) FSW population size from @stevens2022estimating by age group.
 
 First, we calculated the total sexually debuted population in each age group, in each country.
-To descibe the distribution of age at first sex, we used skew logistic distributions [@nguyen2022trends] with cumulative distribution function given by
+To describe the distribution of age at first sex, we used skew logistic distributions [@nguyen2022trends] with cumulative distribution function given by
 \begin{equation}
@@
 Next, we used the assumed $\text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] to calculate the implied ratio between the number of FSW and the sexually debuted population in each age group.
-We assumed that those ratios in South Africa were applicable to every country, and therefore calculated the number of FSW by age in all 13 countries.
+We assumed that those ratios in South Africa were applicable to every country, and thereby calculated the number of FSW by age group in all 13 countries (Figure \ref{fig:age-disagg-fsw-line}).
 
-To fill: plots and comparisons to other data sources.
+\begin{figure}
+  \centering
+  \makebox[\textwidth][c]{\includegraphics{depends/age-disagg-fsw-line.png}}
+  \caption{Proportion of FSW by age group (including the age groups 30-34, 35-39, 40-44 and 45-49) as produced by our disaggregation procedure.}
+  \label{fig:age-disagg-fsw-line}
+\end{figure}
 

### 2022-07-09 src/docs_paper/script.R

@@ -30,6 +30,7 @@ convert_pdf_png("infections-reached")
 convert_pdf_png("model-comparison")
 convert_pdf_png("fsw-logit-information-criteria")
 convert_pdf_png("coverage")
+convert_pdf_png("age-disagg-fsw-line")
 
 #' For tables-figures.Rmd
 convert_pdf_png("category-flowchart")

### 2022-07-09 src/process_age-disagg-fsw/script.R

@@ -140,12 +140,13 @@ df %>%
 
 dev.off()
 
-pdf("age-disagg-fsw-line.pdf", h = 5, w = 6.25)
+pdf("age-disagg-fsw-line.pdf", h = 4, w = 6.25)
 
 df %>%
   filter(age_group != "Y015_049") %>%
   ggplot(aes(x = age_group, y = fsw_prop, group = area_id, col = area_id)) +
   geom_line() +
+  labs(x = "Age group", y = "FSW proportion", col = "ISO3") +
   theme_minimal()
 
 dev.off()

### 2022-07-10 src/docs_paper/appendix.Rmd
Remove interactions from the text until I can get them all to run #128 #138

@@
 M1 & IID & IID & IID & IID & IID & Not included \\
-M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\
+<!-- M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\ -->
 M2 & IID & IID & IID & Besag & IID & Not included \\
-M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\
+<!-- M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\ -->
 M3 & IID & IID & IID & IID & AR1 & Not included \\
-M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\
+<!-- M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\ -->
 M4 & IID & IID & IID & Besag & AR1 & Not included \\
-M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\
+<!-- M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\ -->
 \midrule
@@
 We considered two specifications, independent and identically distributed (IID) and Besag [@besag1991bayesian], for the space-category $\phi_{ik}$ random effects (Section \ref{sec:spatial-random-effects}) and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects (Section \ref{sec:temporal-random-effects}).
-We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}).
-All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
+<!-- We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}). -->
+All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma \}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
+<!-- \tau_\delta -->
 
@@
 
-### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects}
+<!-- ### Spatio-temporal random effects \label{sec:spatio-temporal-random-effects} -->
 
-We used the specification
-\begin{equation}
-    \bm{\delta} = (\delta_{111}, \ldots, \delta_{nT3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}),
-\end{equation}
-where $\mathbf{R}^\star_\delta$ is a Kronecker product of the relevant space, time and category structure matrices.
-In particular, for each of the four models including spatio-temporal interactions, these matrices are
+<!-- We used the specification -->
+<!-- \begin{equation} -->
+<!--     \bm{\delta} = (\delta_{111}, \ldots, \delta_{nT3^{+}})^\top \sim \mathcal{N}(\mathbf{0}, (\tau_\delta \mathbf{R}^\star_\delta)^{-}), -->
+<!-- \end{equation} -->
+<!-- where $\mathbf{R}^\star_\delta$ is a Kronecker product of the relevant space, time and category structure matrices. -->
+<!-- In particular, for each of the four models including spatio-temporal interactions, these matrices are -->
 
-1. No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$,
-2. Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$,
-3. Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
-4. Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$,
+<!-- 1. No spatial or temporal structure (Type I) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{I} \otimes \mathbf{I}$, -->
+<!-- 2. Structured spatial and unstructured temporal (Type II) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{I} \otimes \mathbf{I}$, -->
+<!-- 3. Unstructured spatial and structured temporal (Type III) $\mathbf{R}^\star_\delta = \mathbf{I} \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$, -->
+<!-- 4. Structured spatial and temporal (Type IV) $\mathbf{R}^\star_\delta = \mathbf{R}^\star_b \otimes \mathbf{R}^\star_a \otimes \mathbf{I}$, -->
 
-where the first, second and third elements of the Kronecker product represent space, time and category strucutre matrices respectively.
-The interaction type in brackets (e.g. Type I) is given according to the @knorr2000bayesian framework.
+<!-- where the first, second and third elements of the Kronecker product represent space, time and category strucutre matrices respectively. -->
+<!-- The interaction type in brackets (e.g. Type I) is given according to the @knorr2000bayesian framework. -->
 
@@
 5. Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
-6.
+<!-- 6.
 Spatio-temporal\footnote{It was not possible to fully implement these constraints in \texttt{R-INLA}.
-This only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
-\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
-\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
+This only effects the variance components interpretation.} $\sum_i \delta_{itk} = 0, \, \forall \, t, k; -->
+<!-- \quad \sum_t \delta_{itk} = 0, \, \forall \, i, k; -->
+<!-- \quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$ -->
 

### 2022-07-10 src/docs_paper/paper.Rmd
Remove interactions from the text until I can get them all to run #128 #138

@@
 Alternative models varied the specification for the spatial effect between independent spatial effects versus spatially correlated effects and independent temporal effects versus first-order auto-regressive temporal effects.
-Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts.
+<!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
 To understand the importance of each part of the model we analysed the relative sizes of the variance parameters for each effect.
@@
 
-The best fitting multinomial regression model included correlated spatial effects and first-order autoregressive temporal effects, but not spatio-temporal interactions.
+The best fitting multinomial regression model included correlated spatial effects and first-order autoregressive temporal effects.
+<!-- but not spatio-temporal interactions. -->
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.

### 2022-07-10 src/docs_paper/appendix.Rmd
Collection of final fixes incl. remove interaction text, add multinomial model performance, add model performance text, text linking to figures, alter colours for FSW age disaggregation figure, move FSW logistic model comparison to correct report #135 #128 #138

@@
 M1 & IID & IID & IID & IID & IID & Not included \\
-<!-- M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\ -->
 M2 & IID & IID & IID & Besag & IID & Not included \\
-<!-- M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\ -->
 M3 & IID & IID & IID & IID & AR1 & Not included \\
-<!-- M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\ -->
 M4 & IID & IID & IID & Besag & AR1 & Not included \\
-<!-- M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\ -->
 \midrule
@@
 
-We considered eight models (Table \ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
+<!-- To add once they work: -->
+<!-- M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\ -->
+<!-- M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\ -->
+<!-- M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\ -->
+<!-- M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\ -->
+
+We considered four models (Table \ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
 $$
-\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
+\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk}.
 $$
+<!-- + \delta_{itk} -->
 As described above, we included observation random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in all models we considered.
@@
 
+We performed model selection on the basis of the conditional predictive ordinate (CPO) criterion [@pettit1990conditional].
+For comparison, we also calculated the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely].
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{0.65\textwidth}{lllll}
+\toprule
+ & M1 & M2 & M3 & M4 \\ 
+\midrule
+DIC & 100780 (300) & 101588 (317) & 100781 (300) & 101589 (317) \\ 
+WAIC & 103763 (358) & 105008 (383) & 103763 (358) & 105009 (383) \\ 
+CPO & 5573 (36) & 5772 (36) & 5574 (36) & 5771 (36) \\ 
+\bottomrule
+\end{tabularx}
+\caption{Multinomial regression model performance. For the CPO, higher values indicate better model performance. For the DIC and WAIC, lower values indicate better model performance.}
+\label{tab:multinomial-model-performance}
+\end{table}
+
 \begin{figure}[h]
@@
     \makebox[\textwidth][c]{\includegraphics{depends/model-comparison.png}}
-    \caption{Multinomial regression model performance, with the best performing model(s) according to each criteria shown as a square.}
+    \caption{Multinomial regression model performance, with the best performing model(s) according to each criterion shown as a square.
+For the CPO, higher values indicate better model performance for the CPO.
+For the DIC and WAIC, lower values indicate better model performance.}
     \label{fig:multinomial-model-performance}
 \end{figure}
-
-To fill: table.
 
@@
 We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_{c} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+The prior on $\beta_0$ placed 95\% prior probability on the range `r 100 * round(plogis(-4), 2)`-`r 100 * round(plogis(0), 2)`\% for the percentage of those with non-regular or multiple partners who report transactional sex.
 We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.
@@
 
-To fill: explanation of Table \ref{tab:logistic-model-performance} and Figure \ref{fig:logistic-model-performance}.
+We selected the best model according to the CPO statistic, which was model L6.
+CPO values, along with DIC and WAIC values for reference, are presented in Table \ref{tab:logistic-model-performance} and Figure \ref{fig:logistic-model-performance}.
+Inclusion of Besag spatial random effects, rather than IID, consistently improved performance.
+Benefits from inclusion of covariates were more marginal.
+That said, as some countries had no suitable surveys, we preferred to include covariate information such that the estimates in these countries are based on some country-specific data.
 
@@
 \toprule
- & Model 1 & Model 2 & Model 3 & Model 4 & Model 5 & Model 6 \\ 
+ & L1 & L2 & L3 & L4 & L5 & L6 \\ 
 \midrule
@@
 \end{tabularx}
-\caption{Logistic regression model performance. For the CPO, higher values indicate better model performance for the CPO. For the DIC and WAIC, lower values indicate better model performance.}
+\caption{Logistic regression model performance. For the CPO, higher values indicate better model performance. For the DIC and WAIC, lower values indicate better model performance.}
 \label{tab:logistic-model-performance}
@@
     \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.png}}
-    \caption{Logistic regression model performance, with the best performing model(s) according to each criteria shown as a square.}
+    \caption{Logistic regression model performance, with the best performing model(s) according to each criterion shown as a square.}
     \label{fig:logistic-model-performance}
@@
 
-To assess the calibration of our fitted model, we calculated the quantile $q$ of each observation within the posterior predictive distribution (that is, within the collection of samples generated from the posterior predictive distribution).
+To assess the calibration of our fitted model, we calculated the quantile $q$ of each observation within the posterior predictive distribution.
 For calibrated models, these quantiles, known as probability integral transform (PIT) values [@dawid1984present; @bosse2022scoringutils], should follow a uniform distribution $q \sim \mathcal{U}[0, 1]$.
+To generate samples from the posterior predictive distribution, we applied the multinomial likelihood to samples from the latent field, setting the sample size to be the floor of the Kish effective sample size.
 
@@
 where $\text{logistic}(x) = \exp(x) / (1 + \exp(x))$ such that $\text{logistic}(\hat \theta + \log(\text{OR}_k)) = \rho_{iak}$.
+Figures B.18 - B.30 show the resulting HIV prevalence estimates by risk group in each country.
 The number of PLHIV are then obtained by $H_{iak} = \rho_{iak} N_{iak}$, where $N_{iak}$ is the risk group population size.
@@
 The risk ratio $\text{RR}_4(\lambda_{ia})$ was defined as a function of general population incidence.
+Figures B.31 - B.43 show the resulting HIV incidence estimates by risk group in each country.
 The number of new HIV infections are then $I_{iak} = \lambda_{iak} N_{iak}$.
@@
 By cumulatively summing the expected infections, for each fraction of the total population reached we calculated the fraction of total expected new infections that would be reached.
+Figures B.44 - B.56 show the percentage of new infections that would be reached prioritising according to each possible stratification within each country.
 
 This analysis was relatively simple.
-More involved analyses might consider prioritisation of a hypothetical intervention which has some, possibly varying, probability of preventing HIV acquisition, and the costs associated to its roll-out.
+More involved analyses might consider prioritisation of a hypothetical intervention which has some, possibly varying, probability of preventing HIV acquisition, as well as the costs associated to its roll-out.
 

### 2022-07-10 src/docs_paper/paper.Rmd
Collection of final fixes incl. remove interaction text, add multinomial model performance, add model performance text, text linking to figures, alter colours for FSW age disaggregation figure, move FSW logistic model comparison to correct report #135 #128 #138

@@
 Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to define appropriate random effects, are provided in Appendix A.1.2.
-The best performing model was selected according to the conditional predictive ordinate (CPO) criteria, a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
+The best performing model was selected according to the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
 The \textsc{R} [@r] code used to implement the models and produce  results is available from `github.com/athowes/multi-agyw`.
@@
 
-The best fitting multinomial regression model included correlated spatial effects and first-order autoregressive temporal effects.
+The best fitting multinomial regression model included correlated spatial effects and independent and identically distributed temporal effects.
 <!-- but not spatio-temporal interactions. -->
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criteria is provided in Appendix A.1.2.4 for all considered models.
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level.
+Model performance according to the CPO criterion is provided in Appendix A.1 for all models we considered.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Fig B.5 - B.17).
 
@@
 Other factors, such as condom usage or type of sexual act, may account for additional heterogeneity in risk from sexual behaviour.
-However, we did not include these factors in view of measurement difficulties, consistency across contexts, and the operational benefits of describing risk parsimoniously.
+However, we did not include these factors in view of measurement difficulties, concerns about consistency across contexts, and the operational benefits of describing risk parsimoniously.
 <!-- Reasons why we didn't include condom usage: -->
@@
 As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups.
-In adjusting our estimates of transactional sex to match national FSW estimates, we inherent their limitations. 
+We inherent any limitations of the national FSW estimates [@stevens2022estimating] which we adjust our estimates of transactional sex to match.
+<!-- (As presented by Oli's paper) -->
 Furthermore, we do not consider seasonal migration patterns, which may particularly effect FSW size.

### 2022-07-10 src/fit_fsw-logit-sae/script.R

@@ -388,68 +388,6 @@ ic_df <- sapply(res_fit, function(fit) {
     .before = dic
   )
 
-pdf("fsw-logit-information-criteria.pdf", h = 3, w = 6.25)
-
-ic_df %>%
-  rename("dic_mean" = "dic", "waic_mean" = "waic", "cpo_mean" = "cpo") %>%
-  pivot_longer(
-    cols = starts_with(c("dic", "waic", "cpo")),
-    names_to = "name",
-    values_to = "value"
-  ) %>%
-  separate(name, into = c("metric", "type"), extra = "merge", fill = "left") %>%
-  pivot_wider(
-    names_from = "type",
-    values_from = "value"
-  ) %>%
-  mutate(
-    metric = fct_recode(metric,
-      "DIC" = "dic",
-      "WAIC" = "waic",
-      "CPO" = "cpo"
-    ),
-    model = fct_recode(model,
-      "L1: IID spatial" = "Model 1",
-      "L2: Besag spatial" = "Model 2",
-      "L3: IID spatial, cfswever" = "Model 3",
-      "L4: Besag spatial, cfswever" = "Model 4",
-      "L5: IID spatial, cfswrecent" = "Model 5",
-      "L6: Besag spatial, cfswrecent" = "Model 6",
-    )
-  ) %>%
-  split(.$metric) %>%
-  lapply(function(x)
-    x %>%
-      mutate(
-        min_idx = (mean == min(mean, na.rm = TRUE)),
-        max_idx = (mean == max(mean, na.rm = TRUE)),
-        best_idx = ifelse(metric %in% c("WAIC", "DIC"), min_idx, max_idx)
-      )
-  ) %>%
-  bind_rows() %>%
-  ggplot(aes(x = model, y = mean, col = model, shape = best_idx)) +
-    geom_point(size = 3) +
-    geom_errorbar(
-      aes(ymin = mean - se, ymax = mean + se),
-      stat = "identity", position = "dodge", alpha = 0.4, col = "black", width = 0
-    ) +
-    facet_wrap(~metric, scales = "free") +
-    scale_color_manual(values = multi.utils::cbpalette()) +
-    scale_shape_manual(values = c(16, 15)) +
-    guides(shape = "none") +
-    labs(y = "Value", x = "", col = "") +
-    theme_minimal() +
-    theme(
-      legend.position = "bottom",
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
[…]

### 2022-07-10 src/fit_multi-sexbehav-sae/script.R

@@ -340,8 +340,8 @@ if(include_interactions) {
 #' If low on computational resources i.e. not on the cluster
 #' Just fit one model
 if(lightweight) {
-  formulas <- list(formula4)
-  models <- list("Model 4")
+  formulas <- list(formula2)
+  models <- list("Model 2")
 }
 
 #' tryCatch version for safety
@@ -362,7 +362,8 @@ res_df <- lapply(res, "[[", 1) %>% bind_rows()
 res_fit <- lapply(res, "[[", 2)
 names(res_fit) <- models
 
-best <- "Model 4"
+#' Which model has the highest CPO?
+best <- paste0("Model ", which.max(ic_df$cpo))
 
 #' Artefact: Fitted model objects
 saveRDS(res_fit, "multi-sexbehav-sae-fits.rds")

### 2022-07-10 src/process_age-disagg-fsw/script.R

@@ -140,14 +140,25 @@ df %>%
 
 dev.off()
 
+extended_cbpalette <- colorRampPalette(multi.utils::cbpalette())
+
 pdf("age-disagg-fsw-line.pdf", h = 4, w = 6.25)
 
 df %>%
   filter(age_group != "Y015_049") %>%
   ggplot(aes(x = age_group, y = fsw_prop, group = area_id, col = area_id)) +
   geom_line() +
+  scale_color_manual(values = extended_cbpalette(n = 13)) +
   labs(x = "Age group", y = "FSW proportion", col = "ISO3") +
   theme_minimal()
+
+dev.off()
+
+pdf("palette-extension.pdf", h = 4, w = 4)
+
+scales::show_col(multi.utils::cbpalette())
+
+scales::show_col(extended_cbpalette(n = 13))
 
 dev.off()
 

### 2022-07-10 src/process_information-criteria/script.R

@@ -8,7 +8,9 @@ available_surveys <- read_csv("depends/available-surveys.csv")
 
 #' Multinomial model
 
-df <- read_csv("depends/information-criteria.csv")
+df <- read_csv("depends/information-criteria.csv") %>%
+  #' Round these to the nearest integer
+  mutate_at(2:7, round, 0)
 
 pdf("model-comparison.pdf", h = 3, w = 6.25)
 
@@ -75,9 +77,106 @@ df %>%
 
 dev.off()
 
+df %>%
+  mutate(
+    dic = paste0(dic, " (", dic_se, ")"),
+    waic = paste0(waic, " (", waic_se, ")"),
+    cpo = paste0(cpo, " (", cpo_se, ")"),
+  ) %>%
+  select(-contains("se")) %>%
+  mutate(
+    model = fct_recode(model,
+                       "M1" = "Model 1", "M2" = "Model 2",
+                       "M3" = "Model 3", "M4" = "Model 4")
+  ) %>%
+  rename_with(~toupper(.), .cols = any_of(c("dic", "waic", "cpo"))) %>%
+  rename_with(~str_to_title(.), .cols = any_of(c("model", "country"))) %>%
+  select(-any_of(c("iso3"))) %>%
+  pivot_longer(
+    cols = c("DIC", "WAIC", "CPO"),
+    names_to = "Criteria"
+  ) %>%
+  pivot_wider(
+    names_from = "Model",
+    values_from = "value"
+  ) %>%
+  gt() %>%
+  fmt_missing(columns = everything(), rows = everything(), missing_text = "-") %>%
+  #' It's clear from context that these are the criteria
+  #' (such that the label is not required)
+  cols_label(
+    Criteria = "",
+  ) %>%
+  tab_stubhead(label = "") %>%
+  as_latex() %>%
+  as.character() %>%
+  cat(file = "model-comparison.txt")
+
 #' Logistic model
 
 df_prop <- read_csv("depends/fsw-logit-information-criteria.csv")
+
+pdf("fsw-logit-model-comparison.pdf", h = 3, w = 6.25)
+
+df_prop %>%
+  rename("dic_mean" = "dic", "waic_mean" = "waic", "cpo_mean" = "cpo") %>%
+  pivot_longer(
+    cols = starts_with(c("dic", "waic", "cpo")),
+    names_to = "name",
+    values_to = "value"
+  ) %>%
+  separate(name, into = c("metric", "type"), extra = "merge", fill = "left") %>%
+  pivot_wider(
[…]

### 2022-07-10 src/docs_paper/paper.Rmd
Fix to bugs with MOZ population (noticed by MM) #128

@@
 
-<!-- IW notes that AGYW typically refers to 15-24 -->
-<!-- Feels clunky to me to say AGYW and women 25-29 -->
+<!-- IW notes that AGYW typically refers to 15-24, but it feels clunky to me to say AGYW and women 25-29 -->
 In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are `r population_percent`\% of the population but `r infections_percent`\% of new HIV infections [@unaids2021update].
@@
 All AGYW are recommended to have access to a basic package of HIV prevention, while those with with high risk behaviours in moderate incidence settings and all AGYW in very high incidence settings are recommended to have access to enhanced intervention packages [@joint2016hiv; @birdthistle2018evaluating].
-<!-- TODO: Add "basic package of HIV prevention consisting of... -->
+<!-- Could add "basic package of HIV prevention consisting of... -->
 These interventions may include STI screening and treatment, access to pre-exposure prophylaxis (PrEP), access to post-exposure prophylaxis (PEP), comprehensive sexuality education, and economic empowerment.
@@
 Our methodology is standardised across countries, allowing prioritisation both within and between countries.
-<!-- Note: Above sentence borrowed from TOR document. To back it up, needs more between country analysis in results section. -->
+<!-- Above is borrowed from TOR document. To back it up more, needs between country analysis in results section. -->
 We analysed the extent to which the risk group proportions varied across districts, age groups, between countries, and over time.
@@
 
-We considered eight model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.1.2).
+We considered four model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.1.2).
 All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
@@
 It is not possible to directly fit multinomial logistic regression models in `R-INLA`, so we used the multinomial-Poisson transformation [@baker1994multinomial].
-Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to define appropriate random effects, are provided in Appendix A.1.2.
+Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to appropriately define random effects, are provided in Appendix A.1.2.
 The best performing model was selected according to the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
@@
 
-district_Y015_019_nosex12m_quantiles <- filter(district_age_quantiles, indicator == "No sex", age_group == "15-19")
+district_Y015_019_nosex12m_quantiles <- filter(district_age_quantiles, indicator == "Not sexually active", age_group == "15-19")
 
@@
 
-moz_Y015_019_nosex12m <- filter(moz_Y015_019, indicator == "No sex")
+moz_Y015_019_nosex12m <- filter(moz_Y015_019, indicator == "Not sexually active")
 moz_Y015_019_sexcohab <- filter(moz_Y015_019, indicator == "One cohabiting partner")
@@
 
-<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
-
 AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).
@@
 
-LZ, IW, MM and CB were supported by...
+<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
+<!-- LZ, IW, MM and CB were supported by... -->
 

### 2022-07-10 make/2_pull_naomi.R

@@ -8,6 +8,11 @@ url <- "sites/HIVInferenceGroup-WP/Shared Documents/Data/Spectrum files/2022 nao
 path <- sharepoint$download(URLencode(url))
 naomi_output <- readRDS(path)
 
+naomi_output %>%
+  filter(iso3 == "MOZ") %>%
+  pull(calendar_quarter) %>%
+  unique()
+
 naomi_extract <- naomi_output %>%
   filter(
     iso3 %in% priority_iso3,
@@ -17,7 +22,11 @@ naomi_extract <- naomi_output %>%
     #' Only female
     sex == "female",
     #' Value being used in the global report (there is no CY2021Q4 in ZAF)
-    ifelse(iso3 != "ZAF", calendar_quarter == "CY2021Q4", calendar_quarter == "CY2021Q3")
+    case_when(
+      iso3 == "ZAF" ~ calendar_quarter == "CY2021Q3",
+      iso3 == "MOZ" ~ calendar_quarter == "CY2020Q4",
+      TRUE ~ calendar_quarter == "CY2021Q4"
+    )
   ) %>%
   left_join(
     as.data.frame(analysis_level) %>%

### 2022-07-11 src/docs_paper/paper.Rmd
Add author contributions #128

@@
 
+## Author contributions
+
+* Conceptualisation: JWE, KAR, CB
+* Data curation: AH, KAR, VKN, RE, OS, JWE
+* Formal analysis: AH
+* Funding acquisition: JWE
+* Investigation: AH
+* Methodology: AH, KAR, VKN, TMW, SRF, JWE
+* Project administration: JWE, KAR, CB
+* Software: AH, KAR
+* Supervision: JWE, SRF
+* Visualisation: AH
+* Writing - Original draft: AH
+* Writing - Review and Editing: AH, KAR, VKN, OS, KMJ, RE, LZ, IW, MM, CB, SRF, JWE
+
+\clearpage
+
 # References {#references .unnumbered}

### 2022-07-11 src/docs_paper/paper.Rmd
CB UNAIDS employment statement and change to plot caption #128

@@
 JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664). 
+LZ, IW, MM and CB are employed by UNAIDS.
+<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
 This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
-
-<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
-<!-- LZ, IW, MM and CB were supported by... -->
 

### 2022-07-11 src/plot_available-surveys/script.R

@@ -85,7 +85,7 @@ plotA <- df %>%
   ) %>%
   ggplot(aes(x = year, y = fct_rev(country), col = type, size = sample_size_factor, shape = giftsvar)) +
   geom_point(alpha = 0.7) +
-  labs(x = "", y = "", col = "Survey type", shape = "Does the survey include\na specific transactional question?", size = "Sample size") +
+  labs(x = "", y = "", col = "Survey type", shape = "Does the survey include a specific\nquestion about transactional sex?", size = "Sample size") +
   scale_color_manual(values = multi.utils::cbpalette()[c(3, 7, 1, 2)]) +
   scale_x_continuous(breaks = min(df$year):max(df$year)) +
   scale_size_discrete(range = c(2, 5)) +

### 2022-07-12 src/docs_paper/appendix.Rmd
Model selection note #128

@@
 
-We performed model selection on the basis of the conditional predictive ordinate (CPO) criterion [@pettit1990conditional].
-For comparison, we also calculated the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely].
+We performed model selection on the basis of the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], selecting model M2.
+This model included Besag spatial random effects and IID temporal random effects.
+The deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] are included for reference (Table \ref{tab:multinomial-model-performance} and Figure \ref{fig:multinomial-model-performance}).
 

### 2022-07-12 src/plot_age-variation/script.R
Update labels on these plots (and fix bug with Cabo Delgado introduced by MOZ data change) #128

@@ -6,7 +6,7 @@ df <- read_csv("depends/adjust-best-3p1-multi-sexbehav-sae.csv") %>%
   multi.utils::update_naming() %>%
   filter(
     age_group != "15-24",
-    indicator != "Nonregular partners(s) +"
+    indicator != "Non-regular or multiple partners(s) +"
   )
 
 #' Add region column
@@ -51,7 +51,8 @@ plotA <- ggplot(df_age_country, aes(y = age_group, x = estimate_smoothed, fill =
   theme_minimal() +
   scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
   scale_y_discrete(expand = expansion(mult = c(0.05, 0))) +
-  labs(y = "Age group", x = "Proportion", fill = "Category") +
+  labs(y = "Age group", x = "Proportion", fill = "Risk group") +
+  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
   theme(
     legend.position = "bottom",
     legend.key.width = unit(1, "lines"),

### 2022-07-12 src/process_incidence/script.R

@@ -51,7 +51,13 @@ df <- df_3p1 %>%
   left_join(
     select(prev, "area_id", "age_group", starts_with("prev_")),
     by = c("area_id", "age_group")
-  )
+  ) %>%
+  #' Cabo Delgado Province in MOZ disrupted due to conflict, so no population data from Naomi
+  filter(!is.na(population))
+
+# df %>% filter(is.na(population)) %>%
+#   pull(area_id) %>%
+#   unique()
 
 rr_sexcohab <- 1
 rr_sexnonreg <- 1.72
@@ -131,7 +137,7 @@ plotsA <- df_plot %>%
       geom_sf(size = 0.1, colour = scales::alpha("grey", 0.25)) +
       coord_sf(lims_method = "geometry_bbox") +
       scale_fill_viridis_c(option = "C", label = label_percent()) +
-      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(10))) +
+      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
       theme_minimal() +
       labs(
         title = paste0(x$iso3[1]),
@@ -174,7 +180,7 @@ df %>%
       geom_sf(size = 0.1, colour = scales::alpha("grey", 0.25)) +
       coord_sf(lims_method = "geometry_bbox") +
       scale_fill_viridis_c(option = "C") +
-      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(10))) +
+      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
       theme_minimal() +
       labs(
         title = paste0(x$iso3[1]),

### 2022-07-12 src/process_prevalence/script.R

@@ -354,7 +354,7 @@ plotsA <- df_3p1_linear_plot %>%
       geom_sf(size = 0.1, colour = scales::alpha("grey", 0.25)) +
       coord_sf(lims_method = "geometry_bbox") +
       scale_fill_viridis_c(option = "C", label = label_percent()) +
-      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(10))) +
+      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
       theme_minimal() +
       labs(
         title = paste0(x$iso3[1]),
@@ -399,7 +399,7 @@ plotsB <- df_3p1_logit_plot %>%
       geom_sf(size = 0.1, colour = scales::alpha("grey", 0.25)) +
       coord_sf(lims_method = "geometry_bbox") +
       scale_fill_viridis_c(option = "C", label = label_percent()) +
-      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(10))) +
+      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
       theme_minimal() +
       labs(
         title = paste0(x$iso3[1]),

### 2022-07-12 src/docs_paper/script.R
Final fixes (capitalisation of citations, correct naming of depends) #128

@@ -21,7 +21,7 @@ convert_pdf_png <- function(name) {
 
 #' For appendix.Rmd
 convert_pdf_png("model-comparison")
-convert_pdf_png("fsw-logit-information-criteria")
+convert_pdf_png("fsw-logit-model-comparison")
 convert_pdf_png("coverage")
 convert_pdf_png("age-disagg-fsw-line")
 

### 2022-07-12 src/plot_temporal-variation/script.R

@@ -65,7 +65,7 @@ plotsA <- df_3p1_ribbon %>%
         data = filter(df_3p1_raw, iso3 == x$iso3[1]),
         aes(x = year, y = mean_raw, col = type, shape = raw_replaced)
       ) +
-      facet_grid(age_group ~ indicator) +
+      facet_grid(age_group ~ indicator, labeller = labeller(indicator = label_wrap_gen(20))) +
       scale_color_manual(values = match_available_surveys_plot_palette) +
       scale_shape_manual(values = c(19, 1)) +
       lims(x = c(2000L, 2018L)) +
@@ -99,7 +99,7 @@ dev.off()
 pdf("uga-check.pdf", h = 7, w = 6.25)
 
 df_3p1 %>%
-  filter(iso3 == "Uganda", indicator == "Cohabiting partner") %>%
+  filter(iso3 == "Uganda", indicator == "One cohabiting partner") %>%
   select(year, age_group, estimate_raw, estimate_smoothed) %>%
   pivot_longer(
     cols = starts_with("estimate"),

### 2022-07-14 src/docs_paper/cover.Rmd
Write cover letter; close #139

---
title: "Cover letter"
author: "Adam Howes"
output:
  pagedown::html_letter:
    self_contained: false
links-to-footnotes: true
paged-footnotes: true
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

::: from
Adam Howes    
Email: ath19@ic.ac.uk     
:::

::: date
13th July, 2022
:::

Dear editor,

Please find attached our manuscript, entitled “Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa” for consideration for publication in PLOS Global Public Health.

Adolescent girls and young women (AGYW) are at elevated risk of HIV acquisition.
To inform implementation of HIV prevention for AGYW, we used a Bayesian statistical model to geographically map HIV risk group proportions defined based on sexual behaviour.
We used these estimates to disaggregate HIV prevalence and HIV incidence by risk group, as well as calculating the expected number of new infections which could be reached according to different prioritisation strategies.
Our approach is aligned with the Global AIDS Strategy 2021-2026, which recommends differentiating HIV prevention according to location and behavioural risk.

All authors have approved this version of the manuscript for submission and the content of the manuscript has not been published or submitted elsewhere.

With kind regards, on behalf of all the co-authors,

Adam Howes

### 2022-07-14 src/docs_paper/script.R

@@ -39,3 +39,5 @@ convert_pdf_png("infections-reached-country")
 rmarkdown::render("paper.Rmd")
 rmarkdown::render("appendix.Rmd")
 rmarkdown::render("tables-figures.Rmd")
+rmarkdown::render("cover.Rmd")
+pagedown::chrome_print("cover.html")

### 2022-07-14 src/docs_aids22-poster/aids22-poster.Rmd
Poster draft out #111

@@
     affil: 1, 2
+  - name: "Rachel Esra"
+    affil: 2
   - name: "Lycias Zembe"
@@
 main_findings:
-  - "Successful **targeting of HIV prevention** using **risk behaviour** would **greatly increase** expected new infections preemptively reached."
+  - "Successful **priorisation of HIV prevention** using **risk behaviour** would **greatly increase** expected new infections preemptively reached."
 logoleft_name: "IMP_ML_W_N.png"
-logoright_name: "UNAIDS-reverse-EN.gif"
+# logoright_name: "UNAIDS-reverse-EN.gif"
 # Style & formatting
@@
 
-* Adolescent girls and young women (AGYW) 15-29 **face disproportionately high risk** of HIV infection, and have been identified as a **priority population** for prevention efforts
-* The UNAIDS Global AIDS Strategy 2021-2026 **recommends differentiating services** for AGYW geographically based both on individual risk behaviour and epidemic indicators
-* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** $k = 1:4$ in 13 priority countries at a district level in the years 1999-2018
+* Adolescent girls and young women (AGYW) 15-29 face disproportionately high risk of HIV infection, and are a priority population for prevention efforts
+* The Global AIDS Strategy 2021-2026 recommends differentiating services for AGYW geographically based both on individual risk behaviour and epidemic indicators
+* We used a spatio-temporal model to estimate the proportion of AGYW in four behavioural risk categories in 13 priority countries at a district level in the years 1999-2018
 
-|$k$|Category                 | Risk ratio|
+|$k$|Risk group               | Risk ratio|
 |:--|:------------------------|----------:|
@@
 |2  |One cohabiting partner   |          1|
-|3  |Non-regular partner(s)   |       1.72|
+|3  |Non-regular or multiple partner(s)   |       1.72|
 |4  |Female sex workers (FSW) |         13|
@@
 
-* We analyzed 47 national household surveys (AIS, BAIS, DHS, PHIA)
-* For the categories $k \in \{1, 2, 3^{+}\}$ we fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
-\begin{align}
-    &y_{itak}^\star \sim \text{Poisson}(\kappa_{itak}), \\
-    &\log(\kappa_{itak}) 
-    = \underbrace{\theta_{ita}}_{\text{Observation (IID)}}
-    + \underbrace{\beta_k}_{\text{Category (IID)}}
-    + \underbrace{\alpha_{ak}}_{\text{Age (IID)}} \\
-    &+ \underbrace{\zeta_{ck}}_{\text{Country (IID)}} 
-    + \underbrace{\phi_{ik}}_{\text{Spatial (Besag)}} 
-    + \underbrace{\gamma_{tk}}_{\text{Temporal (AR1)}}
-\end{align}
-where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
-* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
-* To estimate the FSW proportion we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
-\begin{align}
-    &y_{ia4}^\star \sim \text{Binomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
-    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4}))
-    = \beta_0
-    + \beta_\texttt{cfswever} x_c \\
-    &+ \underbrace{\alpha_a}_{\text{Age (IID)}}
-    + \underbrace{\zeta_c}_{\text{Country (IID)}}
-    + \underbrace{\phi_i}_{\text{Spatial (Besag)}}
-\end{align}
-where $x_c$ is the proportion of men in each country who are clients of FSW [@hodgins2021cfsw]
-* We aligned our FSW estimates to the national-level UNAIDS Key Populations Atlas [@johnston2022deriving]
-* We estimated incidence and number of expected new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates
+* We analyzed 46 national household surveys, including AIS, BAIS, DHS and PHIA
+* We took a two-stage modelling approach:
+1.
+We fit a survey-weighted multinomial logistic regression to estimate the proportion of AGYW each risk group, with the non-regular or multiple partner(s) and FSW risk groups combined together, using age (IID), country (IID), spatial (ICAR) and temporal (IID) random effects
+2.
+To estimate the FSW proportion we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression using age (IID), country (IID) and spatial (ICAR) random effects, as well as covariates for the proportion of men who are clients of FSW [@hodgins2022population]
+* We aligned our FSW estimates to national-level estimates obtained by disaggregating @stevens2022estimating by age group
+* We disaggregated Naomi model [@eaton2021naomi] general population incidence and prevalence estimates by risk group using incidence risk ratios and prevalence ratios
+* We estimated the new infections that could be reached prioritisting according to different strategies
+
+\newpage
 
@@
 
-```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Dotplots showing the posterior mean of our district level estimates (in colour) and national estimates (in white) in 2018.'}
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='District level estimates (in colour) and national estimates (in white) in 2018.'}
 knitr::include_graphics("depends/3p1-within-between-country-variation.png")
@@
 
-```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Cloropleths showing the posterior mean of our district level estimates in 2018.'}
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Spatial distribution of our 2018 estimates.'}
 knitr::include_graphics("depends/3p1-continental-map.png")
@@
 
-* There is **significant variation** in risk group proportions **within and between countries**, as well as **between age groups** (but close to no change over time)
-* We found a geographic delineation, with **cohabiting more common in the east** and **non-regular partner(s) more common in the south**
-* Large numbers of 15-19 in Mozambique have early sexual debut and are already cohabiting
+* Risk group proportions varied substantially across age groups (65.9% of total variation explained), countries (20.9%), and between districts within each country (11.3%), but changed little over time (0.9%)
+* Among women aged 20-29, cohabiting (63.1%) was more common in eastern Africa than non-regular or multiple partner(s) (21.4%), while in southern countries non-regular or multiple partner(s) (58.5%) were more common than cohabiting (23.4%)
+* Large numbers of 15-19 in Mozambique have early sexual debut (64.2%) and close to a third (34.2%) are already cohabiting
 
-```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of targeting strategies'}
+```{r echo=FALSE, fig.align='center', out.width='100%', fig.cap='Comparison of prioritisation strategies'}
 knitr::include_graphics("depends/infections-reached.png")
@@
 
-* Using location, age and behavioral risk stratification, **25% of expected new infections can be found by reaching 3% of the population**, compared with 8% of the population when behaviour is excluded
-* Majority of this benefit comes from reaching FSW, who are **3.5% of the at risk population but 21.0% of all expected new infections**
+* Using location, age and behavioral risk prioritisation, 50% of expected new infections can be found by reaching 10.6% of the population, compared with 19.3% of the population when behaviour is excluded
+* The majority of this benefit comes from reaching FSW, who are 1.4% of the at risk population but 10.9% of all expected new infections
 
@@
 
-* Using a **modular approach** allowed us to integrate all data from non-conformable surveys
-* **Spatio-temporal smoothing** can be used to overcome high variance from the small sample sizes that result when further stratifying districts
-* Individual behaviour is a **key determinant** of risk and providing prevention services on the basis of behavior would allow many more expected new infections to be reached, **especially among FSW**
+* Providing prevention services on the basis of behavior would allow many more expected new infections to be reached, especially among FSW
+* Programs should ensure that behavioural prioritisation occurs without stigmatising or blaming AGYW
+* We focused on the most proximal determinants of risk, based on location and behaviour, rather than more distal determinants
+* Using a two-stage approach allowed us to include all surveys, even those without a specific transactional sex question
+* We overcome the small sample sizes created by multiple stratifications by using spatio-temporal smoothing
 
@@
 
-* No assessment of **practicalities or costs** of risk stratification approaches, or efficacy of available interventions
-* No adjustment for **reporting bias**
-* **Risk category definitions** could be disputed
-  * What constitutes sex work?
-  * Is within-group risk heterogeneity small enough?
+* No adjustment for under-reporting biases, which likely vary by age group
+* Choosing appropriate risk group definitions that succinctly capture variation in risk consistently across contexts is challenging
+* We are least confident in our FSW estimates, which face particular measurement difficulties
+* We did not assess the practicalities or costs of the risk prioritisation strategies we considered
 
@@
 
-* Inclusion of **more surveys** e.g. VACS
-* Extension to **general population**: men and women 15-49
+* Inclusion of more surveys e.g. VACS
+* Extension to general population (adults 15-49)
+
+<font size="6"> **Interested to read more?** Manuscript and R code available are available from `github.com/athowes/multi-agyw`. </font>
 

### 2022-09-16 docs/waterloo.Rmd
Abstract for Waterloo

---
title: "Waterloo student conference abstract submission"
author: "Adam Howes, Imperial College London"
date: "16th September 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

**Title**:
A Bayesian multinomial spatio-temporal for HIV risk group proportions.

**Abstract**:
The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios according to local HIV incidence, and individual risk behaviour.
To help countries implement the strategy, we developed a Bayesian multinomial spatio-temporal model to estimate district-level HIV risk group proportions for AGYW across 13 high burden countries in sub-Saharan Africa.
We used the multinomial-Poisson transformation to enable fast and accruate inference for the model via integrated nested Laplace approximations.
Using our risk group proportions we estimated additional policy-relevant indicators including HIV prevalence and HIV incidence by risk group, as well as numbers of infections that could be averted using different intervention strategies.
For more information, see [`athowes/multi-agyw`](https://github.com/athowes/multi-agyw).

### 2022-09-17 utils/archive_to_docs.R
new-cohort presentation upload

@@ -17,4 +17,5 @@ archive_to_docs <- function(report) {
 
 #' Names of the reports to move
 archive_to_docs("docs_30-11-21-coverage")
+archive_to_docs("docs_24-09-21-new-cohort")
 archive_to_docs("docs_paper")

### 2022-09-17 src/docs_09-09-21-three-category/09-09-21-three-category.Rmd
three-category presentation upload

@@
 2. The raw proportions don't add up to one
-  * This is illustrated in the next slide
-
-##
-
-:::: columns
-
-::: column
-
-```{r echo=FALSE}
-knitr::include_graphics("page1-check100.pdf")
-```
-
-:::
-
-::: column
-
-```{r echo=FALSE}
-knitr::include_graphics("page2-check100.pdf")
-```
-
-:::
-
-::::
 
@@
 
-##
-
-:::: columns
-
-::: column
-
-```{r echo=FALSE}
-knitr::include_graphics("page-multi-sexbehav-sae.pdf")
-```
-
-:::
-
-::: column
-
-* A (difficult to see) example of what this looks like
-* Model 9 has BYM2 and AR1
-* Other notes
-  * Quantiles produced by manipulating `inla.posterior.sample`s
-  * Same samples used in combination with Naomi population data to produce aggregates (i.e. 15-24 age category)
-
-:::
-
-::::
-
 ## Data issues for `sexpaid12m` category
@@
     * Not all "gifts of money in exchange for sex" is sex work
-
-##
-
-```{r echo=FALSE}
-knitr::include_graphics("depends/sexpaid-survey-question.pdf")
-```
 

### 2022-09-17 make/8_docs.R

@@ -1,8 +1,9 @@
 run_commit_push("plot-tikz_category-flowchart")
 
 #' Presentations
-run_commit_push("docs_30-11-21-coverage")
+run_commit_push("docs_09-09-21-three-category")
 run_commit_push("docs_24-09-21-new-cohort")
+run_commit_push("docs_30-11-21-coverage")
 
 #' Posters
 run_commit_push("docs_amazon-poster")

### 2022-09-17 utils/archive_to_docs.R

@@ -16,6 +16,7 @@ archive_to_docs <- function(report) {
 }
 
 #' Names of the reports to move
-archive_to_docs("docs_30-11-21-coverage")
 archive_to_docs("docs_24-09-21-new-cohort")
+archive_to_docs("docs_09-09-21-three-category")
+archive_to_docs("docs_30-11-21-coverage")
 archive_to_docs("docs_paper")

### 2022-09-17 src/docs_04-01-22-update/04-01-22-update.Rmd
update upload

@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/3-rank-comparison.pdf")
-```
-
-##
-
-```{r echo=FALSE}
 knitr::include_graphics("depends/model-direct-benefits.pdf")
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/continental-map.pdf")
+knitr::include_graphics("depends/3-continental-map.png.pdf")
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/within-between-country-variation.pdf")
-```
-
-##
-
-```{r echo=FALSE}
-knitr::include_graphics("depends/variance-proportions.pdf")
+knitr::include_graphics("depends/aaa-variance-proportions.pdf")
 ```

### 2022-09-17 utils/archive_to_docs.R

@@ -19,4 +19,6 @@ archive_to_docs <- function(report) {
 archive_to_docs("docs_24-09-21-new-cohort")
 archive_to_docs("docs_09-09-21-three-category")
 archive_to_docs("docs_30-11-21-coverage")
+archive_to_docs("docs_04-01-22-update")
+archive_to_docs("docs_amazon-poster")
 archive_to_docs("docs_paper")

### 2022-09-19 src/docs_19-01-22-stats-epi-group/19-01-22-stats-epi-group.Rmd
stats-epi-group upload

--- 2022-01-19 src/docs_19-01-22-seth-sam/19-01-22-seth-sam.Rmd
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/continental-map.pdf")
+knitr::include_graphics("depends/3-continental-map.pdf")
 ```

### 2022-09-19 make/8_docs.R

@@ -8,6 +8,7 @@ run_commit_push("docs_04-01-22-update")
 run_commit_push("docs_19-01-22-stats-epi-group")
 run_commit_push("docs_03-02-22-ea-talk")
 run_commit_push("docs_12-05-22-mrc-gida")
+run_commit_push("docs_28-09-22-toronto")
 
 #' Posters
 run_commit_push("docs_amazon-poster")

### 2022-09-19 utils/archive_to_docs.R

@@ -20,5 +20,6 @@ archive_to_docs("docs_24-09-21-new-cohort")
 archive_to_docs("docs_09-09-21-three-category")
 archive_to_docs("docs_30-11-21-coverage")
 archive_to_docs("docs_04-01-22-update")
+archive_to_docs("docs_19-01-22-stats-epi-group")
 archive_to_docs("docs_amazon-poster")
 archive_to_docs("docs_paper")

### 2022-09-19 src/docs_03-02-22-ea-talk/03-02-22-ea-talk.Rmd
ea-talk upload

@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/model-direct-benefits-h.pdf")
+knitr::include_graphics("depends/model-direct-benefits.pdf")
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("geometry-graph-zwe.pdf")
+library(bsae)
+plot_graph(zw, add_geography = TRUE)
 ```
@@
 ```{r echo=FALSE}
-knitr::include_graphics("depends/infections-averted-country.pdf")
+knitr::include_graphics("depends/infections-reached-country.pdf")
 ```

### 2022-09-19 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
mrc-gida upload

@@
   pivot_wider(
-    id_cols = c("area_id", "age_group", "indicator", "category"),
+    id_cols = c("area_id", "age_group", "category"),
     names_from = "indicator",
@@
 ```{r echo=FALSE, out.width = "350px", fig.cap = "New infections reached prioritising according to different stratifications."}
-knitr::include_graphics("depends/infections-reached.png")
-```
-
-##
-
-```{r echo=FALSE, out.width = "350px", fig.cap = "As previous slide but specific to Mozambique."}
-knitr::include_graphics("depends/infections-reached-moz.png")
+knitr::include_graphics("depends/infections-reached.pdf")
 ```

### 2022-09-19 make/8_docs.R

@@ -9,6 +9,8 @@ run_commit_push("docs_19-01-22-stats-epi-group")
 run_commit_push("docs_03-02-22-ea-talk")
 run_commit_push("docs_12-05-22-mrc-gida")
 run_commit_push("docs_28-09-22-toronto")
+run_commit_push("docs_09-22-hdsl")
+run_commit_push("docs_14-10-22-waterloo")
 
 #' Posters
 run_commit_push("docs_amazon-poster")

### 2022-09-19 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Upcoming presentation templates

--- 2022-09-19 src/docs_12-05-22-mrc-gida/12-05-22-mrc-gida.Rmd
@@
 title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
-subtitle: MRC Centre for Global Infectious Disease Analysis Seminars
+subtitle: Centre for Global Health Research, UToronto
 author: Adam Howes

### 2022-09-19 src/docs_28-09-22-toronto/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_28-09-22-toronto")
+# setwd("src/docs_28-09-22-toronto")
+
+rmarkdown::render("28-09-22-toronto.Rmd")

### 2022-09-19 src/docs_paper/paper.Rmd
RE comment for future discussion #128
Add cover letter for journal submission

@@
     affiliation: [A, B]
-    corresponding: ath19@ic.ac.uk
+    corresponding: \texttt{ath19@ic.ac.uk}
   - name: Kathryn A. Risher 
@@
   **Background:**
-  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiated intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
+  The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
   We aimed to estimate prevalence of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
@@
 
+<!-- RE notes that it could be worth talking about the age patterns of sexual mixing, that we didn't consider them, and how they might effect intervention planning. -->
+
 ## Conclusion

### 2022-09-19 src/docs_paper/script.R

@@ -40,6 +40,4 @@ rmarkdown::render("paper.Rmd")
 rmarkdown::render("appendix.Rmd")
 rmarkdown::render("tables-figures.Rmd")
 rmarkdown::render("cover.Rmd")
-
-# There is a chrome error with this, commenting out for now
-# pagedown::chrome_print("cover.html")
+pagedown::chrome_print("cover.html")

### 2022-09-21 src/docs_paper/paper.Rmd
Add T middle name and remove "the the" typo

@@
     affiliation: [A, B]
-  - name: Rachel Esra
+  - name: Rachel T. Esra
     affiliation: B    
@@
   To support HIV programmes in identifying and providing services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
-  Doing so also allowed us to estimate the the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
+  Doing so also allowed us to estimate the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
   We found that prioritising HIV prevention using behavioural risk groups almost halved the proportion of the population that would need to be reached to find half of all expected new infections.

### 2022-09-27 src/docs_paper/appendix.Rmd
Final fixes (capitalisation of citations, correct naming of depends) #128
Spotted some notation errors while making slides

@@
 \midrule
-Model ID & Category ($\beta_k$) & Age ($\alpha_{ak}$) & Country ($\zeta_{ck}$) & Spatial ($\phi_{ik}$) & Temporal ($\gamma_{tk}$) & Spatio-temporal ($\delta{itk}$) \\
+Model ID & Category ($\beta_k$) & Country ($\zeta_{ck}$) & Age ($\alpha_{ack}$) & Spatial ($\phi_{ik}$) & Temporal ($\gamma_{tk}$) & Spatio-temporal ($\delta{itk}$) \\
 \midrule
@@
 $$
-\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{c[i]k} + \phi_{ik} + \gamma_{tk}.
+\eta_{ita} = \theta_{ita} + \beta_k + \zeta_{c[i]k} + \alpha_{ac[i]k} + \phi_{ik} + \gamma_{tk}.
 $$
@@
 <!-- We also considered separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure (Section \ref{sec:spatio-temporal-random-effects}). -->
-All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma \}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
+All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\zeta, \tau_\alpha, \tau_\phi, \tau_\gamma\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$ where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.
 <!-- \tau_\delta -->
@@
 As with the multinomial regression model, we used survey weighted counts $\{y_{itak}^\star\}$ and sample sizes $\{m_{itak}^\star\}$.
-We used a generalised binomial pseudo-likelihood $y^\star \sim \text{xBinomial}(y^\star, m^\star)$, as implemented by \texttt{family = "xBinomial"} in \texttt{R-INLA}, given by
+We used a generalised binomial pseudo-likelihood $y^\star \sim \text{xBinomial}(m^\star, q)$, as implemented by \texttt{family = "xBinomial"} in \texttt{R-INLA}, given by
 \begin{equation}
-    p(y^\star \, | \, m^\star) =  \binom{\lfloor m^\star \rfloor}{\lfloor y^\star \rfloor} q^{y^\star} (1 - q)^{m^\star - y^\star}.
+    p(y^\star \, | \, m^\star, q) =  \binom{\lfloor m^\star \rfloor}{\lfloor y^\star \rfloor} q^{y^\star} (1 - q)^{m^\star - y^\star}.
 \end{equation}
@@
     \centering
-    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.png}}
+    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-model-comparison.png}}
     \caption{Logistic regression model performance, with the best performing model(s) according to each criterion shown as a square.}

### 2022-09-27 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Iterate Toronto presentation forward

@@
 institute: Imperial College London
-date: May 2022
+date: September 2022
 bibliography: citations.bib
@@
 
-* Prevention
-  * Core package
-  * Intensified interventions
-* It's important to priorisite intensified interventions to those at highest risk
+* Prevention options can be divided into two:
+  1. Core package
+  2. Intensified interventions
+* There are not enough resources to offer the more costly intensified interventions to all AGYW, so it's important to prioritise those at highest risk
 
@@
 
-The Global AIDS strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
-
+* The Global AIDS strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
   1. Population-level HIV incidence
   2. Individual-level sexual risk behaviour
+* Takes into account the two most proximal drivers of sexual transmission
 
@@
 1. Enable implementation of prevention stratified by incidence and behaviour
-2. Assess the benefits of such approaches
+2. Assess the benefits of such approaches: is it worth it?
 
@@
 1. Estimate the proportion of AGYW in four behavioural risk groups at a district level (in 13 countries identified as priority by The Global Fund)
-2. Analyze numbers of new infections reached by stratified prevention strategies
+2. Analyze the new infections which could be reached by different stratified prevention strategies
 
@@
 
-* We used sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys to place respondents into four risk groups:
-  1. Not sexually active
-  2. One cohabiting sexual partner
-  3. Non-regular sexual partner(s)
-  4. Female sex workers
+* We used sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys to place respondents into $K = 4$ risk groups:
+  1. $k = 1$ Not sexually active
+  2. $k = 2$ One cohabiting sexual partner
+  3. $k = 3$ Non-regular sexual partner(s)
+  4. $k = 4$ Female sex workers
 * District-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
@@
 
-### Stage 1: $k = 1, 2, 3^{+}$
+* Only some of the surveys included a transactional sex question, required to differentiate between the $k = 3$ and $k = 4$ risk groups
+* Our approach was to fit a two-stage model
+  1. Spatio-temporal multinomial logistic regression model for the proportion of AGYW in the $k = 1, 2, 3^{+}$ risk groups, using all 47 surveys
+  2.
+Spatial logistic regression model for the proportion of those in the $k = 3^{+} = \{3, 4\}$ risk groups who are in the $k = 4$ risk group, using only the 13 surveys with a specific transactional sex question
 
-* Multinomial logistic regression model for the proportion of AGYW in the $k = 1, 2, 3^{+}$ risk groups, using all 47 surveys
-* Selected model (by CPO) included:
-  * Age country effects (IID)
-  * Country effects (IID)
-  * Correlated spatial effects (ICAR)
-  * Correlated temporal effects (AR1) 
-* Multinomial-Poisson transformation allowed use of `R-INLA` for inference
+## Notation
 
-## Two-stage model for risk group proportions
+* $k \in \{1, \ldots, 4\}$: risk groups
+* $i \in \{1, \ldots, n\}$: districts
+* $c[i] \in \{\text{Botswana}, \ldots, \text{Zimbabwe}\}$: country containing district $i$
+* $t \in \{1999, \ldots, 2018\}$: years
+* $a \in \{\text{15-19}, \text{20-24}, \text{25-29}\}$: age groups
+* $y_{ita}^\star = (y_{ita1}^\star, y_{ita2}^\star, y_{ita3}^\star, y_{ita4}^\star)$: survey weighted multinomial observations
+* $m_{ita}^\star$: survey weighted multinomial sample size
 
-### Stage 2: $k = 3, 4$
+## Multinomial logistic regression model
 
-* Logistic regression model for the proportion of those in the $k = 3^{+} = \{3, 4\}$ risk groups who are in the $k = 4$ risk group, using only the 13 surveys with a specific transactional sex question
-* Selected model (by CPO) included:
-  * Age country effects (IID)
-  * Country effects (IID)
-  * Correlated spatial effects (ICAR)
-  * Clients of FSW covariates [@hodgins2022population]
-* Used `R-INLA` for inference
+* Would like to use integrated nested Laplace approximations for fast, accurate inference, but `R-INLA` is not compatible with multinomial likelihoods because they depend on multiple elements of the latent field
+* Instead, use that multinomial logistic regression models can be recast as a Poisson log-linear models using the Poisson trick
+* Include observation-specific random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in any linear predictor $\eta_{itak} = \theta_{ita} + \cdots$ to ensure exact reproduction of $m_{ita}^\star$
 
-## Two-stage model for risk group proportions
+## Multinomial logistic regression model
 
-### Combination and FSW adjustment
+* Consider models of the form
+\begin{align}
+    y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
+    \log(\lambda_{itak}) &= \theta_{ita} + \beta_k + \zeta_{c[i]k} + \alpha_{ac[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
+\end{align}
+* With the following random effects
+  * $\theta_{ita}$: observation (IID)
+  * $\beta_k$: category (IID)
+  * $\zeta_{ck}$: country-category (IID x IID) 
+  * $\alpha_{ack}$: age-country-category (IID x IID x IID)
+  * $\phi_{ik}$: space-category ({IID, **Besag**} x IID)
+  * $\gamma_{tk}$: year-category ({**IID**, AR1} x IID)
+  * $\delta_{itk}$: space-year-category (Implemented but crashing on cluster at the moment...)
+
+## Multinomial logistic regression model
+
+* Independent penalised complexity [@simpson2017penalising] priors on all standard deviation parameters with $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$
+  * Sidenote, I'm interested as to if joint priors might be more suitable
+* Possible (but tricky) to define all these interactions in `R-INLA` by combination of the `group` and `replicate` options
+* Used sum-to-zero constraints to make posterior inferences interpretable
+  * Because we're interested in the contribution of each random effect to total variance
+* Model comparison via CPO statistic
+
+## Logistic regression model
+
+* Consider models of the form
+\begin{align}
+    y_{ia4}^\star &\sim \text{Binomial} \left( y_{ia3}^\star + y_{ia4}^\star, q_{ia} \right), \label{eq:logistic-regression} \\
+    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), \\
+    \eta_{ia} &= \beta_0 +  \zeta_{c[i]} + \alpha_{ac[i]} + \phi_i + \beta_{\texttt{cfsw}} \texttt{cfsw}_{c[i]}.
+\end{align}
+* With the following terms:
+  * $\beta_0$: intercept
+  * $\zeta_{c[i]}$: country effects (IID)
+  * $\alpha_{ac[i]}$ age-country effects (IID)
+  * $\phi_i$: spatial effects (IID, **Besag**)
+  * Clients of FSW covariates ($\texttt{cfswever}$, $\texttt{cfswrecent}$) [@hodgins2022population]
+
+## Combination and FSW adjustment
 
 * Take 1000 samples from each model, then multiply suitably to generate estimates for all four risk groups
-* We adjusted the $k = 4$ risk group to match national FSW estimates from @johnston2022deriving
+* We adjusted the $k = 4$ risk group to match age-country FSW estimates
+  * Obtained these by disaggregating @stevens2022estimating by age using estimates of sexually active population from @nguyen2022trends
 

### 2022-09-27 src/docs_paper/appendix.Rmd
More notation fixes

@@
 \midrule
-Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_{c}$) & Spatial ($\phi_i$) & Covariates \\ 
+Model ID & Intercept ($\beta_0$) & Country ($\zeta_{c}$) & Age ($\alpha_ca$) & Spatial ($\phi_i$) & Covariates \\ 
 \midrule
@@
 
-We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_{c} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
+We considered six logistic regression models (Table \ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, country random effects $\zeta_{c} \sim \mathcal{N}(0, \tau_\zeta^{-1})$, and age-country random effects $\alpha_{ac} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
 The prior on $\beta_0$ placed 95\% prior probability on the range `r 100 * round(plogis(-4), 2)`-`r 100 * round(plogis(0), 2)`\% for the percentage of those with non-regular or multiple partners who report transactional sex.

### 2022-09-28 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Iterate Toronto talk

@@
 * Consider models of the form
-\begin{align}
+\begin{align*}
     y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\
     \log(\lambda_{itak}) &= \theta_{ita} + \beta_k + \zeta_{c[i]k} + \alpha_{ac[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
-\end{align}
-* With the following random effects
+\end{align*}
+* The terms are
   * $\theta_{ita}$: observation (IID)
@@
 * Consider models of the form
-\begin{align}
+\begin{align*}
     y_{ia4}^\star &\sim \text{Binomial} \left( y_{ia3}^\star + y_{ia4}^\star, q_{ia} \right), \label{eq:logistic-regression} \\
@@
     \eta_{ia} &= \beta_0 +  \zeta_{c[i]} + \alpha_{ac[i]} + \phi_i + \beta_{\texttt{cfsw}} \texttt{cfsw}_{c[i]}.
-\end{align}
-* With the following terms:
+\end{align*}
+* The terms are
   * $\beta_0$: intercept
@@
   * $\phi_i$: spatial effects (IID, **Besag**)
-  * Clients of FSW covariates ($\texttt{cfswever}$, $\texttt{cfswrecent}$) [@hodgins2022population]
+  * Clients of FSW covariates (`cfswever`, **`cfswrecent`**) [@hodgins2022population]
 
@@
 
-* Take 1000 samples from each model, then multiply suitably to generate estimates for all four risk groups
-* We adjusted the $k = 4$ risk group to match age-country FSW estimates
+* Take 1000 samples from each model, then manipulate suitably to generate estimates for all four risk groups
+* We adjusted the samples from the $k = 4$ risk group to match age-country FSW estimates, reallocating into non-regular partner(s)
   * Obtained these by disaggregating @stevens2022estimating by age using estimates of sexually active population from @nguyen2022trends
@@
 
+```{r echo=FALSE, out.width="350px", fig.cap = "Results of FSW age disaggregation."}
+knitr::include_graphics("depends/age-disagg-fsw-line.pdf")
+```
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "PIT histograms and ECDF difference plots."}
+knitr::include_graphics("depends/coverage.pdf")
+```
+
+##
+
 ```{r echo=FALSE, out.width="350px", fig.cap = "We found a geographic discontinuity in behaviour between Southern and Eastern Africa."}
@@
 
-```{r echo=FALSE, out.width="350px", fig.cap = "Here is another view of the discontinuity."}
+```{r echo=FALSE, out.width="350px", fig.cap = "Viewing the discontinuity another way."}
 knitr::include_graphics("depends/aids-abstract-B.pdf")
+```
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "Proportions of variance explained."}
+knitr::include_graphics("depends/aaa-variance-proportions.pdf")
 ```
@@
 * Integration of all relevant surveys
-  <!-- * Modular approach allowed estimating FSW proportion even for surveys without a specific transactional sex question -->
+  * Two-stage approach allowed estimating FSW proportion even for surveys without a specific transactional sex question
 * Alleivating small-sample sizes by borrowing information
-  <!-- * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity -->
+  * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity
 * Estimates where there isn't direct data
-  <!-- * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model) -->
-  <!-- * Uncertainty should be higher in regions with infilling: important to transparently communicate this -->
+  * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model)
+  * Uncertainty should be higher in regions with infilling: important to transparently communicate this
 
@@
 
-## HIV incidence by risk group
+## HIV prevalence and incidence by risk group
 
-* Risk group proportion estimates plus relative risk ratio estimates to disaggregate general population HIV incidence estimates
-\begin{align*}
-I_{ia} &= \sum_k \lambda_{iak} N_{iak} \\
-&= \sum_k \lambda_{ia2} \text{RR}_k N_{iak}.
-\end{align*}
+* We used our risk group proportion estimates together with incidence relative risk ratios and prevalence ratios to disaggregate general population HIV estimates in the most recent year
+* Disaggregated number of new infections on a linear scale, and people living with HIV (PLHIV) on a logit scale
+  * Using a linear scale for PLHIV resulted in prevalences outside $[0, 1]$
 
@@
 \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ Estimates of HIV incidence $\lambda_{iak}$ and number of new HIV infections $I_{iak}$ by district, age group and risk group
+$\implies$ Estimates of HIV incidence $\lambda_{iak}$, number of new HIV infections $I_{iak}$, HIV prevalence $\rho_{iak}$ and PLHIV $H_{iak}$ by district, age group and risk group
 \end{tcolorbox}
@@
 
-##
-
-```{r echo=FALSE, out.width = "300px", fig.cap = "Mozambique stands out."}
-knitr::include_graphics("depends/cohabiting-girls.pdf")
-```
-
 ## Limitations
@@
 * Simplistic infections reached analysis
-  <!-- * No accounting for difficulty in reaching each strata -->
-  <!-- * Variable intervention effectiveness -->
-  <!-- * Change in strata membership -->
+  * No accounting for difficulty in reaching each strata
+  * Variable intervention effectiveness
+  * Change in strata membership
 * Under-reporting of high risk sexual behaviours
-  <!-- * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning -->
+  * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning
 * Risk groups definition justification not clear
-  <!-- * Didn't consider other important characteristics that may determine risk e.g. condom usage -->
+  * Didn't consider other important characteristics that may determine risk e.g. condom usage
 * Only focused on AGYW 15-29
-  <!-- * Could be extended to adults of both sexes aged 15-49 -->
+  * Could be extended to adults of both sexes aged 15-49
 
@@
 
-* Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being prepared!
+* Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being rolled out!
 * Importance of reaching FSW

### 2022-09-28 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
Spotted typos during talk

@@
 
-* The Global AIDS strategy 2021-2016 proposed stratifying HIV prevention for AGYW based upon
+* The Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based upon
   1. Population-level HIV incidence
@@
 \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ Estimates of risk group proportions $\rho_{itak}$ by district, year and age group
+$\implies$ Estimates of risk group proportions $p_{itak}$ by district, year and age group
 \end{tcolorbox}

### 2022-09-28 src/docs_06-10-22-hdsl/06-10-22-hdsl.Rmd
HDSL template up

--- 2022-09-28 src/docs_28-09-22-toronto/28-09-22-toronto.Rmd
@@
 title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
-subtitle: Centre for Global Health Research, UToronto
+subtitle: Health Data Science Lab, UWaterloo
 author: Adam Howes
 institute: Imperial College London
-date: September 2022
+date: October 2022
 bibliography: citations.bib

### 2022-09-28 make/8_docs.R

@@ -9,7 +9,7 @@ run_commit_push("docs_19-01-22-stats-epi-group")
 run_commit_push("docs_03-02-22-ea-talk")
 run_commit_push("docs_12-05-22-mrc-gida")
 run_commit_push("docs_28-09-22-toronto")
-run_commit_push("docs_09-22-hdsl")
+run_commit_push("docs_06-10-22-hdsl")
 run_commit_push("docs_14-10-22-waterloo")
 
 #' Posters

### 2022-09-28 src/docs_06-10-22-hdsl/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_06-10-22-hdsl")
+# setwd("src/docs_06-10-22-hdsl")
+
+rmarkdown::render("06-10-22-hdsl.Rmd")

### 2022-10-06 src/docs_06-10-22-hdsl/06-10-22-hdsl.Rmd
Update HDSL talk

@@
 
+::: columns
+
+:::: column
+
 * In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are disproportionately at risk of HIV infection
+  * 28% of population and 44% of new infections
 * This disparity is because of:
@@
   4. Increased susceptibility to HIV infection
+
+::::
+
+:::: column
+
+```{r echo=FALSE, out.width = "125px", fig.cap="Tweet from UNAIDS"}
+knitr::include_graphics("tweet.png")
+```
+
+::::
+
+:::
 
@@
 * District-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi]
+  * Combines survey and programmatic data to estimate indicators in the general population
 * Risk ratios from ALPHA network analysis [@slaymaker2020croi] and UNAIDS analysis led by Keith Sabin
+  * 10 longitudinal studies: https://alpha.lshtm.ac.uk/
 
@@
 * Instead, use that multinomial logistic regression models can be recast as a Poisson log-linear models using the Poisson trick
-* Include observation-specific random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in any linear predictor $\eta_{itak} = \theta_{ita} + \cdots$ to ensure exact reproduction of $m_{ita}^\star$
+* This works because conditional on their sum, Poisson counts are jointly multinomially distributed
+* If you include observation-specific random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in the linear predictor $\eta_{itak} = \theta_{ita} + \cdots$ then the sample sizes $m_{ita}^\star$ can be exactly recovered, ensuring the models are actually the same
 

### 2022-10-06 src/plot_aids-abstract/script.R

@@ -93,7 +93,7 @@ plotB <- df_3p1_subnational %>%
   geom_point(
     data = df_3p1_national %>%
       filter(
-        indicator %in% c("Cohabiting partner", "Nonregular partner(s)")
+        indicator %in% c("One cohabiting partner", "Non-regular or multiple partner(s)")
       ),
     aes(x = fct_rev(iso3), y = estimate_smoothed),
     shape = 21,

### 2022-10-13 src/docs_14-10-22-waterloo/14-10-22-waterloo.Rmd
Basic version of WSSAF slides (need to slim them down a bit)

--- 2022-10-06 src/docs_06-10-22-hdsl/06-10-22-hdsl.Rmd
@@
 title: Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
-subtitle: Health Data Science Lab, UWaterloo
+subtitle: 3rd Waterloo Student Conference in Statistics, Actuarial Science and Finance
 author: Adam Howes

### 2022-10-13 src/docs_14-10-22-waterloo/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_14-10-22-waterloo")
+# setwd("src/docs_14-10-22-waterloo")
+
+rmarkdown::render("14-10-22-waterloo.Rmd")

### 2022-10-14 src/docs_14-10-22-waterloo/14-10-22-waterloo.Rmd
Update slides

@@
   2. Intensified interventions
-* There are not enough resources to offer the more costly intensified interventions to all AGYW, so it's important to prioritise those at highest risk
+* Insufficient resources to offer the more costly intensified interventions to all AGYW
+
+\begin{center}
+\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
+$\implies$ How should interventions be prioritised to have the greatest impact?
+\end{tcolorbox}
+\end{center}
 
@@
 
-* The Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based upon
+* Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based on
   1. Population-level HIV incidence
   2. Individual-level sexual risk behaviour
-* Takes into account the two most proximal drivers of sexual transmission
+* The two most proximal drivers of sexual transmission
 
@@
 
-* We used sexual behaviour data from AIS, BAIS, DHS and PHIA household surveys to place respondents into $K = 4$ risk groups:
+* Sexual behaviour data from household surveys to place respondents into $K = 4$ risk groups:
   1. $k = 1$ Not sexually active
@@
 
-* Only some of the surveys included a transactional sex question, required to differentiate between the $k = 3$ and $k = 4$ risk groups
+\begin{center}
+\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
+How do we deal with the fact that only some of the surveys included a transactional sex question? This question is required to differentiate between the $k = 3$ and $k = 4$ risk groups
+\end{tcolorbox}
+\end{center}
+
 * Our approach was to fit a two-stage model
@@
 
-* Consider models of the form
 \begin{align*}
@@
 \end{align*}
+
 * The terms are
@@
   * $\delta_{itk}$: space-year-category (Implemented but crashing on cluster at the moment...)
+* Without category interactions, any effect will be washed out when we apply softmax to get the probabilities!
+
+##
+
+```{r echo=FALSE, warning =FALSE, out.width="350px", fig.cap = "The Besag model, $\\phi_i \\, | \\, \\phi_{-i} \\sim \\mathcal{N} \\left(\\frac{1}{n_{\\delta i}} \\sum_{j: j \\sim i} \\phi_j, \\frac{1}{n_{\\delta i}\\tau_\\phi} \\right)$, operates on the neighbourhood graph."}
+areas <- sf::read_sf("depends/zwe_areas.geojson")
+
+areas %>%
+  filter(area_level == 2) %>%
+  bsae::plot_graph(add_geography = TRUE)
+```
 
@@
 * Possible (but tricky) to define all these interactions in `R-INLA` by combination of the `group` and `replicate` options
+  * Check out the `aaa_fit_multi-sexbehav-sae` report if you're interested!
 * Used sum-to-zero constraints to make posterior inferences interpretable
@@
 \end{center}
-
-##
-
-```{r echo=FALSE, out.width="350px", fig.cap = "Results of FSW age disaggregation."}
-knitr::include_graphics("depends/age-disagg-fsw-line.pdf")
-```
-
-##
-
-```{r echo=FALSE, out.width="350px", fig.cap = "PIT histograms and ECDF difference plots."}
-knitr::include_graphics("depends/coverage.pdf")
-```
 
@@
 ```{r include=FALSE}
-df <- readr::read_csv("depends/incidence-district-sexbehav.csv")
+twdf <- readr::read_csv("depends/incidence-district-sexbehav.csv")
 
@@
 
-* Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being rolled out!
-* Importance of reaching FSW
-* Countries have different epidemic profiles
+1. Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being rolled out!
+2. Importance of reaching FSW
+3. Countries have different epidemic profiles
 
-## Thanks for listening!
+## Acknowledgements
 
@@
 * The code for this project is at `github.com/athowes/multi-agyw`
+
+## About me
+
+* At Waterloo this term to work with Alex Stringer on improving the approximate inference method we use for the Naomi model
+* Interested in Bayesian statistics, and applications in global health and biosecurity
+* Recently worked on early detection of biological threats with metagenomic sequencing at the Nucleic Acid Observatory
 * You can find me online at `athowes.github.io`
+* Come say hi if you have any similar interests!
+
+# Supplement
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "Results of FSW age disaggregation."}
+knitr::include_graphics("depends/age-disagg-fsw-line.pdf")
+```
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "PIT histograms and ECDF difference plots."}
+knitr::include_graphics("depends/coverage.pdf")
+```
 

### 2022-11-14 src/docs_09-09-21-three-category/09-09-21-three-category.Rmd
Remove half sentence

@@
   * By "observation" I mean observation of the multinomial e.g. a vector `c(2, 5, 3, 0)`
-  * These variables correspond to $\log(\delta)$ from before. So we're just having a free parameter which can 
+  * These variables correspond to $\log(\delta)$ from before
 * Then you put whatever mixed model things you'd like in

### 2022-12-17 src/docs_paper/appendix.Rmd
A few small appendix edits

@@
 Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
-We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
+We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$, and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
 Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
@@
 First, we used a multinomial logistic regression model to infer the proportion of AGYW in the risk groups $k \in \{1, 2, 3^{+}\}$.
-This model can be specified using a multinomial likelihood
+One way to specify this model is using a multinomial likelihood
 \begin{equation}
@@
 \end{equation}
-where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
-Taking $k = 1$ to be the baseline category, linear predictors may be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
-Rather than taking this approach directly, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
+where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$, and taking $k = 1$ to be the baseline category, linear predictors may be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
+To facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
 This transformation, and further details about this model, are presented in Section 1.2.
@@
 Taking this two-step approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question in Equation \ref{eq:logistic-regression}.
-As all such surveys occurred in 2013-2018, in the logistic regression model $q_{ia}$ was assumed to be constant over time.
+As all such surveys occurred in 2013-2018, in the logistic regression model we assumed $q_{ia}$ to be constant over time.
 
-To facilitate uncertainty quantification, we took 1000 posterior samples (indexed by $s$) from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
-Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.
+To facilitate uncertainty quantification, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
+Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by $p_{ita3}^s = (1 - q_{ia}^s)p_{ita{3^+}^s}$ and $p_{ita4}^s = q_{ia}^s p_{ita{3^+}}^s$.
 
-As transactional sex does not directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match FSW population size estimates at a national level by age.
+As transactional sex does not directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match FSW population size estimates by age.
 Our methodology for producing these estimates is described in Section \ref{fsw-population-size-estimation}.
@@
 
-We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using the adjusted samples.
+We calculated the mean, median, and 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using the adjusted samples.
 To produce aggregated estimates, such as the age category 15-24 or any national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].
@@
 \end{tabularx}
-\caption{The multinomial regression models that we considered. Observation random effects $\theta_{ita}$ are omitted from this table.}
+\caption{The multinomial regression models that we considered. Observation random effects $\theta_{ita}$, included in all models, are omitted from this table.}
 \label{tab:multinomial-models}
@@
 <!-- + \delta_{itk} -->
-As described above, we included observation random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in all models we considered.
+Observation random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ were included in all models we considered.
 To capture country-specific proportion estimates for each category, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
@@
 
-The surveys we included use a complex design, in which each individual has an unequal probability of being included in the sample.
-The DHS [@measure2012sampling], for example, often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
+We included surveys which use a complex design, in which each individual has an unequal probability of being included in the sample.
+For example the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling [@measure2012sampling].
 
@@
 This model included Besag spatial random effects and IID temporal random effects.
-The deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] are included for reference (Table \ref{tab:multinomial-model-performance} and Figure \ref{fig:multinomial-model-performance}).
+For reference, we also computed the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] (Table \ref{tab:multinomial-model-performance} and Figure \ref{fig:multinomial-model-performance}).
 
@@
 Next, we used the assumed $\text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] to calculate the implied ratio between the number of FSW and the sexually debuted population in each age group.
-We assumed that those ratios in South Africa were applicable to every country, and thereby calculated the number of FSW by age group in all 13 countries (Figure \ref{fig:age-disagg-fsw-line}).
+We assumed these ratios in South Africa were applicable to every country to calculate the number of FSW by age group in all 13 countries (Figure \ref{fig:age-disagg-fsw-line}).
 
@@
 
-We calculated HIV prevalence $\rho_{iak}$ and number of people living with HIV (PLHIV) $H_{iak}$ stratified according to district, age group and risk group by disaggregating Naomi estimates by risk group.
+We calculated HIV prevalence $\rho_{iak}$ and the number of people living with HIV (PLHIV) $H_{iak}$ stratified according to district, age group and risk group by disaggregating Naomi estimates by risk group.
 

### 2022-12-17 src/docs_review/review.Rmd
Template for (first) response to reviewers

---
title: Response to reviewers for "Spatio-temporal estimates of HIV risk group proportions for adolescent
  girls and young women across 13 priority countries in sub-Saharan Africa"
subtitle: |
  Corresponding author: Adam Howes (`ath19@ic.ac.uk`)
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: true
    includes:
      in_header: preamble.tex
bibliography: citations.bib
---

\newpage

# Reviewer 1 {-}

We thank the reviewer for...

> Comment

Reply, perhaps some code

```{r}
2 + 2
```

\newpage

# Reviewer 2 {-}

We thank the reviewer for...

> Comment

Reply, perhaps some code

```{r}
2 + 2
```

\newpage

# References {#references .unnumbered}

### 2022-12-17 make/8_docs.R

@@ -18,3 +18,6 @@ run_commit_push("docs_aids22-poster")
 
 #' Paper and appendices
 run_commit_push("docs_paper")
+
+#' Reviews
+run_commit_push("docs_review")

### 2022-12-17 src/docs_review/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_review")
+# setwd("src/docs_review")
+
+rmarkdown::render("review.Rmd")

### 2022-12-17 utils/archive_to_docs.R

@@ -28,3 +28,4 @@ archive_to_docs("docs_06-10-22-hdsl")
 archive_to_docs("docs_14-10-22-waterloo")
 archive_to_docs("docs_amazon-poster")
 archive_to_docs("docs_paper")
+archive_to_docs("docs_review")

### 2022-12-19 src/docs_review/review.Rmd
Quick review responses

@@
 
-We thank the reviewer for...
+We thank the reviewer for their helpful comments regarding the statistical modelling.
 
-> Comment
+> 1. In the manuscript, explain why you use the INLA not WINBUGS coding? The multinomial regression could be modeled in WINBUGS directly.
 
-Reply, perhaps some code
+The reviewer is right to note that multinomial logistic regression models can be implemented in probabilistic programming languages like `WinBUGS` directly.
+However, for this application, Markov chain Monte Carlo approaches would be prohibitively expensive.
+For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, non-asymptotic regime.
+We have added the following text to the manuscript to clarify this point:
+*Insert added text here*.
 
-```{r}
-2 + 2
-```
+> 2. Is there no other potential covariate that could be used for better modeling?
+
+Many of the covariates which would be most predictive of risk group proportions are themselves difficult to accuracy measure, and make only modest at best improvements to model performance.
+For example, despite the case for their being a clear link between the "proportion clients of FSW" covariate and the "proportion FSW" outcome we found only marginal benefits to inclusion.
+
+> 3. Please explain sub-national effect more clearly. Why and how you used it?
+
+Using district-level spatial random effects allowed us to account for subnational variation in risk group proportions.
+We considered both spatially unstructured (IID) and spatially structured (Besag) random effects, which can be implemented in `R-INLA` by setting `model = "iid"` or `model = "besag"` respectively.
+
+> 4. Why the interaction term for spatiotemporal effect didn't consider in the modeling framework?
+
+We found that the spatiotemporal interaction terms substantially increased the computational burden of the model, so decided to exclude them.
 
@@
 
-We thank the reviewer for...
+We thank the reviewer for their kind comments.
 
-> Comment
+> My little concern is about using different data from UNAIDS Key Population Atlas apart from the DHS, which is the may source data for the analyses.
+I believe the two variants of data are based on different designs, and combining them may not result in dependable results.
+It would have been more attainable if the UNAIDS data had been used in their sensitivity analysis to confirm the results from the DHS data.
 
-Reply, perhaps some code
+The UNAIDS KP Atlas data and household survey data are different in their design.
+We believe the household data to be more biased.
 
-```{r}
-2 + 2
-```
+> Figure 1 is not clear. I recommend that the authors use a table as an alternative visualization.
+
+Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
+We are unsure how Figure 1 might be made clearer.
+*Look for other papers which have similar plots. Is there anything they do that we could add to make it clearer*.
 

### 2022-12-20 src/docs_review/cover.Rmd
Add cover to editor and update response based on feedback from Katie

--- 2022-07-14 src/docs_paper/cover.Rmd
@@
 ::: date
-13th July, 2022
+19th December, 2022
 :::
@@
 
-Please find attached our manuscript, entitled “Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa” for consideration for publication in PLOS Global Public Health.
-
-Adolescent girls and young women (AGYW) are at elevated risk of HIV acquisition.
-To inform implementation of HIV prevention for AGYW, we used a Bayesian statistical model to geographically map HIV risk group proportions defined based on sexual behaviour.
-We used these estimates to disaggregate HIV prevalence and HIV incidence by risk group, as well as calculating the expected number of new infections which could be reached according to different prioritisation strategies.
-Our approach is aligned with the Global AIDS Strategy 2021-2026, which recommends differentiating HIV prevention according to location and behavioural risk.
-
-All authors have approved this version of the manuscript for submission and the content of the manuscript has not been published or submitted elsewhere.
+Thank you for the opportunity to submit a revised version of our manuscript.
+We appreciate the time you and the reviewers have given to providing helpful feedback.
+Enclosed is a point-by-point response to all points raised.
 

### 2022-12-20 src/docs_review/review.Rmd
Add cover to editor and update response based on feedback from Katie

@@
 
-Many of the covariates which would be most predictive of risk group proportions are themselves difficult to accuracy measure, and make only modest at best improvements to model performance.
+Many of the covariates which one might expect to be most predictive of risk group proportions are themselves difficult to accurately measure, and can only lead to modest at best improvements in model performance.
 For example, despite the case for their being a clear link between the "proportion clients of FSW" covariate and the "proportion FSW" outcome we found only marginal benefits to inclusion.
@@
 
-We found that the spatiotemporal interaction terms substantially increased the computational burden of the model, so decided to exclude them.
+```{r}
+#' TODO Calculate the average Sobol index for survey random effects
+sobol <- 1
+```
+
+Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Figure B.3).
+This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Figure A.1).
+
+We had wanted to include the spatiotemporal interaction terms regardless, first for statistical completeness, and second to demonstrate how complex three-way^[As all random effects in the model are interacted with category.] interactions can be specified in `R-INLA` by careful use of the `group` and `replicate` options.
+However, we found that including these terms substantially increased the computational burden of the model when fitting all countries jointly, so in the end decided to exclude them.
 
@@
 
-The UNAIDS KP Atlas data and household survey data are different in their design.
-We believe the household data to be more biased.
+For the FSW risk group, we used age-disaggregated (Figure A.4) national-level estimates from @stevens2022estimating to inform the level, and household survey data to inform subnational variation.
+Estimates of hidden populations like FSW from household surveys have significant limitations due in part to stigma around disclosing membership, as well as potential for not being included in the sampling frame [@abdul2014estimating].
+For this reason, we believe it is more appropriate to calibrate our estimates to @stevens2022estimating, who as well as including the KP Atlas data integrate data from other FSW population size estimates using a Bayesian mixed effects model.
 
@@
 Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
-We are unsure how Figure 1 might be made clearer.
-*Look for other papers which have similar plots. Is there anything they do that we could add to make it clearer*.
+We are unsure on how to make Figure 1 might clearer.
+Other examples of similar figures in published papers include @giguere2021trends (Figure 1), ...
 

### 2022-12-20 src/docs_review/script.R

@@ -2,3 +2,5 @@
 # setwd("src/docs_review")
 
 rmarkdown::render("review.Rmd")
+rmarkdown::render("cover.Rmd")
+pagedown::chrome_print("cover.html")

### 2023-01-16 src/docs_paper/paper.Rmd
First pass over Jeff's edits

@@
   - code: A
-    address: Department of Mathematics, Imperial College London
+    address: Department of Mathematics, Imperial College London, London, United Kingdom
   - code: B
-    address: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London
+    address: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London, London, United Kingdom
   - code: C
-    address: Department of Medical Social Sciences, Feinberg School of Medicine, Northwestern University
+    address: Department of Public Health Sciences, Penn State College of Medicine, Pennsylvania State University, Hershey, PA, USA
   - code: D
-    address: Harvard T. H. Chan School of Public Health, Harvard University
+    address: Department of Epidemiology, Harvard T. H. Chan School of Public Health, Harvard University, Boston, MA, USA
   - code: E
@@
   - code: F
-    address: Department of Computer Science, University of Oxford
+    address: Department of Computer Science, University of Oxford, Oxford, United Kingdom
 bibliography: citations.bib
@@
 
-The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour, to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
-Four prioritisation strata (Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
+The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+Four prioritisation strata (Supplementary Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
 <!-- NB: Check again about the recent STI infection aspect. -->
-The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table B.2) based upon this prioritisation strata [@unaids2021global].
+The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Supplementary Table B.2) based upon this prioritisation strata [@unaids2021global].
 All AGYW are recommended to have access to a basic package of HIV prevention, while those with with high risk behaviours in moderate incidence settings and all AGYW in very high incidence settings are recommended to have access to enhanced intervention packages [@joint2016hiv; @birdthistle2018evaluating].
@@
 We analysed nationally-representative household survey data from 13 countries: Botswana, Cameroon, Kenya, Lesotho, Malawi, Mozambique, Namibia, South Africa, Eswatini, Tanzania, Uganda, Zambia and Zimbabwe.
-We included surveys conducted in these countries in the years 1999-2018 in which women were interviewed about their sexual behaviour and sufficient geographic information was available to locate survey clusters to districts.
+We included surveys conducted in these countries between 1999 and 2018 in which women were interviewed about their sexual behaviour and sufficient geographic information was available to locate survey clusters to health districts.
 Demographic and Health Surveys (DHS) [@measure2012sampling], AIDS Indicator Surveys (AIS) [@ais], Population-based HIV Impact Assessment (PHIA) [@phia] surveys, and the Botswana AIDS Impact Survey 2013 (BAIS) [@botswana2013botswana] were included.
@@
 <!-- TODO: Include example of inconsistent result. -->
-Exact survey questions varied slightly across survey types and between survey phases (Appendix B).
+Exact survey questions varied slightly across survey types and between survey phases (Supplementary Appendix B).
 Questions captured information about whether the respondent had been sexually active in the past twelve months, and if so how with many partners.
@@
 In surveys without such a question, women almost never (0.01\%) answered that one of their three most recent partners was a sex work client.
-Due to this incomparably across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who engaged in transactional sex.
+Due to this incomparability across surveys, we did not include surveys without a specific transactional sex question when estimating the proportion of the population who engaged in transactional sex.
 We focused on estimating the proportion of women who reported transactional sex at a district level, and subsequently adjusted these proportions to align to national estimates for the number of female sex workers.
@@
 <!-- and so far has been used by X countries could be better (adds some information that it's widely used) -->
-The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning by countries, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Table B.5).
+The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning by countries, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Supplementary Table B.5).
 We used the most recent 2022 estimates for all countries, apart from Mozambique where, due to data accuracy concerns, we used the 2021 estimates (in which the Cabo Delgado province is excluded due to disruption by conflict).
@@
 
-To estimate the proportion of AGYW in each risk group we took a two-stage modelling approach.
-First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24 and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) one cohabiting partner, and (3) either non-regular or multiple partner(s), or transactional sex.
+To estimate the proportion of AGYW in each risk group, we took a two-stage modelling approach.
+First, we fit a spatio-temporal multinomial model stratified by district, year (1999-2018) and five-year age group (15-19, 20-24, and 25-29) for the proportion of AGYW in three categories: (1) not sexually active, (2) one cohabiting partner, and (3) either non-regular or multiple partner(s), or transactional sex.
 Combining the two highest risk groups (high and very high) in this way allowed data from all surveys to be included in this first stage model.
@@
 FSW population size estimates by age were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
-Further technical details are in Appendix A.1.
+Further technical details are in Supplementary Appendix A.1.
 
-We considered four model specifications for the space-age-time multinomial model for the three risk groups (Appendix A.1.2).
-All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation by district, and a temporal effect allowing variation over time.
-Alternative models varied the specification for the spatial effect between independent spatial effects versus spatially correlated effects and independent temporal effects versus first-order auto-regressive temporal effects.
+We considered four model specifications for the space-age-time multinomial model for the three risk groups (Supplementary Appendix A.1.2).
+All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation in risk group proportions by district, and a temporal effect allowing variation over time.
+The specification for the spatial random effects was varied in alternative models between independent spatial effects for each district versus spatially correlated effects, where information is borrowed more between neighboring districts.
+Temporal effects were varied as independent temporal effects versus first-order auto-regressive temporal effects, where a smooth temporal trend is assumed. 
 <!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
@@
 
-For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Appendix A.1.3).
+For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Supplementary Appendix A.1.3).
 Each included an intercept, age and country effects, and a spatial effect allowing district-level variation.
@@
 
-We performed inference using integrated nested Laplace approximation [@rue2009approximate] via the `R-INLA` package [@martins2013bayesian].
+```{r results='hide', warning=FALSE, message=FALSE}
+df_3p1_subnational <- read_csv("depends/df_3p1_subnational.csv")
+
+#' For justifying how big the model is!
+n_district <- length(unique(df_3p1_subnational$area_id))
+n_year <- length(1999:2018)
+n_age <- length(unique(df_3p1_subnational$age_group))
+n_group <- length(unique(df_3p1_subnational$indicator))
+```
+
+We performed inference using the integrated nested Laplace approximation (INLA) [@rue2009approximate] algorithm via the `R-INLA` package [@martins2013bayesian].
+For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo in the realistic, pre-asymptotic regime, and is substantially more computationally tractable for high dimensional models like ours, which has `r n_district` districts, `r n_year` years, `r n_age` age groups, and `r n_group` risk groups.
 It is not possible to directly fit multinomial logistic regression models in `R-INLA`, so we used the multinomial-Poisson transformation [@baker1994multinomial].
-Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to appropriately define random effects, are provided in Appendix A.1.2.
+Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to appropriately define random effects, are provided in Supplementary Appendix A.1.2.
 The best performing model was selected according to the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
@@
 
-```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex. \\label{fig:available-surveys}"}
+```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex.
+Details of included surveys are in Supplementary Table B.3.
+\\label{fig:available-surveys}"}
 knitr::include_graphics("depends/available-surveys.png")
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_age$Y025_029)` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Supplementary Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_age$Y025_029)` aged 25-29 years).
 Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size of `r comma(agyw_surveyed_giftsvar - giftsvar_Y025_029_overcount)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029 - giftsvar_Y025_029_overcount)` aged 25-29 years^[There were `r length(giftsvar_exclude_Y025_029)` DHS surveys which excluded women 25-29 from the transactional sex survey question.]).
@@
 The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criterion is provided in Appendix A.1 for all models we considered.
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Fig B.5 - B.17).
+Model performance according to the CPO criterion is provided in Supplementary Appendix A.1 for all models we considered.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Supplementary Fig B.5 - B.17).
 
@@
 ```{r continental-map, fig.cap="The spatial distribution (posterior mean) of the AGYW risk group proportions in 2018.
+Estimates are stratified by risk group (columns) and five-year age group (rows).
 Countries in grey were not included in our analysis.
@@
 ```{r within-between-country-variation, fig.cap="National (in white) and subnational (in color) posterior means of the risk group proportions.
-We used regions of sub-Saharan Africa defined according to the UN geocode (M49).
+Estimates are stratified by risk group (columns) and five-year age group (rows).
+Regions of sub-Saharan Africa were defined according to the UN geocode (M49 standard).
 \\label{fig:within-between-country-variation}"}
@@
 ```{r results=FALSE}
-df_3p1_subnational <- read_csv("depends/df_3p1_subnational.csv")
 df_3p1_national <- read_csv("depends/df_3p1_national.csv")
@@
 In the 20-24 and 25-29 year age groups, the majority of women were either cohabiting or had non-regular or multiple partner(s).
-Countries in eastern and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r dividing_border_above_sexcohab$median`\% [95\% CI `r dividing_border_above_sexcohab$lower`--`r dividing_border_above_sexcohab$upper`\%] as compared with `r dividing_border_above_sexnonreg$median`\% [95\% CI `r dividing_border_above_sexnonreg$lower`--`r dividing_border_above_sexnonreg$upper`\%] with non-regular partner[s]).
+Countries in eastern and central Africa (Cameroon, Kenya, Malawi, Mozambique, Tanzania, Uganda, Zambia and Zimbabwe) had a higher proportion of women in these age groups cohabiting (`r dividing_border_above_sexcohab$median`\% [95\% CI `r dividing_border_above_sexcohab$lower`--`r dividing_border_above_sexcohab$upper`\%] compared with `r dividing_border_above_sexnonreg$median`\% [95\% CI `r dividing_border_above_sexnonreg$lower`--`r dividing_border_above_sexnonreg$upper`\%] with non-regular partner[s]).
 In contrast, countries in southern Africa (Botswana, Eswatini, Lesotho, Namibia and South Africa) had a higher proportion with non-regular or multiple partner(s) (`r dividing_border_below_sexnonreg$median`\% [95\% CI `r dividing_border_below_sexnonreg$lower`--`r dividing_border_below_sexnonreg$upper`\%], compared with `r dividing_border_below_sexcohab$median`\% [95\% CI `r dividing_border_below_sexcohab$lower`--`r dividing_border_below_sexcohab$upper`\%] cohabiting).
@@
 
-Age group was the most important factor explaining variation in risk group proportions, and accounted for `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`) of total variation.
+Age group was the most important factor explaining variation in risk group proportions, accounting for `r variance_proportions_age$mean`\% (95\% CI `r variance_proportions_age$lower`--`r variance_proportions_age$upper`\%) of total variation.
 The primary change in risk group proportions by age group occurs between the 15-19 age group and 20-29 age group (Fig \ref{fig:within-between-country-variation}).
 The next most important factor was location.
-Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`) of variation, while district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`).
+Country-level differences explained `r variance_proportions_iso3$mean`\% (95\% CI `r variance_proportions_iso3$lower`--`r variance_proportions_iso3$upper`\%) of variation, while district-level variation within countries explained `r variance_proportions_area$mean`\% (95\% CI `r variance_proportions_area$lower`--`r variance_proportions_area$upper`\%).
 <!-- Can I plot the country-level and district-level random effects to visualise this? -->
-Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`) of variation, indicating very little change in risk group proportions over time.
+Temporal changes only explained `r variance_proportions_year$mean`\% (95\% CI `r variance_proportions_year$lower`--`r variance_proportions_year$upper`\%) of variation, indicating very little change in risk group proportions over time.
 We observed similar variance decomposition results fitting each country individually, and using other model specifications.
@@
 
-Considering each country separately, on average, reaching half of new infections required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
-The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (Appendix B).
+Considering each country separately, on average, reaching half of new infections in each country required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
+The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (Supplementary Appendix B).
 For example, FSW in Kenya were estimated to be `r inf_fsw_kenya$prop_population_cumulative`\% of the population and close to a third (`r inf_fsw_kenya$prop_infections_averted_cumulative`\%) of all new infections, whereas FSW in Tanzania were just `r inf_fsw_tanzania$prop_population_cumulative`\% of the population and `r inf_fsw_tanzania$prop_infections_averted_cumulative`\% of all new infections.
@@
   The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
-  We aimed to estimate prevalence of HIV risk behaviours and associated HIV incidence at a small spatial scale among AGYW living in 13 countries in sub-Saharan Africa.
+  We estimated prevalence of HIV risk behaviours and associated HIV incidence at health district level among AGYW living in 13 countries in sub-Saharan Africa.
 
   **Methods:**
-  We analysed `r total_surveys` geospatially referenced national household surveys conducted between 1999-2018 across 13 high burden countries in sub-Saharan Africa.
+  We analysed `r total_surveys` geospatially-referenced national household surveys conducted between 1999-2018 across 13 high HIV burden countries in sub-Saharan Africa.
   Female survey respondents aged 15-29 years were classified into four risk groups (not sexually active, cohabiting, non-regular or multiple partner[s] and female sex workers [FSW]) based on reported sexual behaviour.
@@
   Exposure to HIV among adolescent girls and young women depends on the level of unsuppresed HIV in their local community among potential partners, and their individual sexual behaviour.
-  To support HIV programmes in identifying and providing services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
-  Doing so also allowed us to estimate the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
+  To support HIV programmes in identifying and providing prevention services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
+  This produced estimates of the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
   We found that prioritising HIV prevention using behavioural risk groups almost halved the proportion of the population that would need to be reached to find half of all expected new infections.
@@
 Our estimates support consideration of differentiated prevention programming according to geographic locations and risk behaviour, as outlined in the Global AIDS Strategy.
+Systematic differences in risk by age groups, and variation within and between countries, explained the large majority of variation in risk group proportions.
+Changes over time were negligible in the overall variation in risk group proportions.
+The proportion of 15-19 year olds who are sexually active, and among women aged 20-29 years, norms around cohabitation especially varied across districts and countries.
+This variation underscores the need for these granular data to implement HIV prevention options aligned to local norms and risk behaviours.
 <!-- Some type of comment about how novel this would be if implemented -->
@@
 
-We found a geographic delineation in the proportion of women cohabiting between southern and eastern Africa, calling attention to a divide attributable to many cultural, social and economic factors.
+We found a geographic delineation in the proportion of women cohabiting between southern and eastern Africa, calling attention to a divide attributable to many cultural, social, and economic factors.
 The delineation does not represent a boundary between predominately Christian and Muslim populations, which is further north.
@@
 First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
-Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig B.2).
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Supplementary Fig B.2).
 Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines (such as our analysis of risk group specific prevalence and incidence).
@@
 <!-- (As presented by Oli's paper) -->
-Furthermore, we do not consider seasonal migration patterns, which may particularly effect FSW size.
+Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.
+More generally, we did not aim to include predictive covariates.
 
@@
 
-We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk categories at a district-level in 13 priority countries.
-Using these estimates, we performed an analysis of the number of infections that could be reached by prioritisation based upon location, age and behaviour.
-Though subject to limitations, our results quantify the crucial importance of prioritising reaching AGYW in the highest risk districts and at highest behavioural risk.
+We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk categories at a district-level in 13 priority countries and analyzed the number of infections that could be reached by prioritisation based upon location, age and behaviour.
+Though subject to limitations, these estimates provide data that national HIV programmes can use to set targets and implement differentiated HIV prevention strategies as outlined in the Global AIDS Strategy.
+Successfully implementing this approach would result in more efficientlt reaching a greater number of those at risk of infection.
+
 <!-- TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
@@
 
-**Appendix A**: Statistical modelling \newline
-**Appendix B**: Supplementary tables and figures
+**Supplementary Appendix A**: Statistical modelling \newline
+**Supplementary Appendix B**: Supplementary tables and figures
 

### 2023-01-16 src/docs_review/cover.Rmd
First pass over Jeff's edits

@@
 
-Thank you for the opportunity to submit a revised version of our manuscript.
-We appreciate the time you and the reviewers have given to providing helpful feedback.
-Enclosed is a point-by-point response to all points raised.
+Many thanks for your consideration of our manuscript "Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa".
+We appreciate the thoughtful comments from the reviewers and the opportunity to submit a revised version of our manuscript which incorperates the feedback.
+Please find enclosed a point-by-point response to each of the reviewer's comments, and the editorial comments on journal requirements.
 

### 2023-01-16 src/docs_review/review.Rmd
More edits to review response

@@
 ---
-title: Response to reviewers for "Spatio-temporal estimates of HIV risk group proportions for adolescent
+title: Response to reviewers and editorial comments for "Spatio-temporal estimates of HIV risk group proportions for adolescent
   girls and young women across 13 priority countries in sub-Saharan Africa"
@@
 
-> 1. In the manuscript, explain why you use the INLA not WINBUGS coding? The multinomial regression could be modeled in WINBUGS directly.
+> *1. In the manuscript, explain why you use the INLA not WINBUGS coding? The multinomial regression could be modeled in WINBUGS directly.*
 
@@
 However, for this application, Markov chain Monte Carlo approaches would be prohibitively expensive.
-For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, non-asymptotic regime.
-We have added the following text to the manuscript to clarify this point:
-*Insert added text here*.
+For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, pre-asymptotic regime.
+We have added the following text to the methods section of the manuscript to clarify this point:
 
-> 2. Is there no other potential covariate that could be used for better modeling?
+> For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo in the realistic, pre-asymptotic regime, and is substantially more computationally tractable for high dimensional models like ours, which has 940 districts, 20 years, 3 age groups, and 4 risk groups.
+
+> *2. Is there no other potential covariate that could be used for better modeling?*
 
@@
 
-> 3. Please explain sub-national effect more clearly. Why and how you used it?
+We agree that identifying predictive and measureable predictors of risk group proportions, or high risk locations, is an important area for further research.
+We have commented on this in the discussion section:
+
+> Comment here.
+
+> *3. Please explain sub-national effect more clearly. Why and how you used it?*
 
@@
 
-> 4. Why the interaction term for spatiotemporal effect didn't consider in the modeling framework?
+> *4. Why the interaction term for spatiotemporal effect didn't consider in the modeling framework?*
 
@@
 
-Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Figure B.3).
-This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Figure A.1).
+Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Supplementary Figure B.3).
+This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).
 
@@
 
+> *This is a well-crafted manuscript investigating the spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa.
+Their analyses identify specific age groups at the district level that should be targeted for HIV intervention in SSA.
+This is critical in reducing the HIV epidemic in the southern region of SSA.
+In addition to the main figures, the supplementary Tables and Figures show country-by-country risk, mostly among female sex workers for all age groups.
+With the help of their models, specific resources can target at-risk populations with a moderate assurance of how many people to reach and where these resources should go.*
+
 We thank the reviewer for their kind comments.
 
-> My little concern is about using different data from UNAIDS Key Population Atlas apart from the DHS, which is the may source data for the analyses.
+> *My little concern is about using different data from UNAIDS Key Population Atlas apart from the DHS, which is the may source data for the analyses.
 I believe the two variants of data are based on different designs, and combining them may not result in dependable results.
-It would have been more attainable if the UNAIDS data had been used in their sensitivity analysis to confirm the results from the DHS data.
+It would have been more attainable if the UNAIDS data had been used in their sensitivity analysis to confirm the results from the DHS data.*
 
-For the FSW risk group, we used age-disaggregated (Figure A.4) national-level estimates from @stevens2022estimating to inform the level, and household survey data to inform subnational variation.
+For the FSW risk group, we used age-disaggregated (Supplementary Figure A.4) national-level estimates from @stevens2022estimating to inform the national risk group population size within each age group, and household survey data to inform subnational variation.
 Estimates of hidden populations like FSW from household surveys have significant limitations due in part to stigma around disclosing membership, as well as potential for not being included in the sampling frame [@abdul2014estimating].
-For this reason, we believe it is more appropriate to calibrate our estimates to @stevens2022estimating, who as well as including the KP Atlas data integrate data from other FSW population size estimates using a Bayesian mixed effects model.
+For this reason, we believe it is more appropriate to calibrate our estimates to @stevens2022estimating, who as well as including the KP Atlas data, integrate data from other FSW population size estimates using a Bayesian mixed effects model.
 
-> Figure 1 is not clear. I recommend that the authors use a table as an alternative visualization.
+Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
+We have noted this in the limitations section of the discussion.
+
+> *Figure 1 is not clear. I recommend that the authors use a table as an alternative visualization.*
 
@@
 
+# Editorial comments {-}
+
+> *Please send a completed Competing Interests' statement, including any COIs declared by your co-authors.
+If you have no competing interests to declare, please state: "The authors have declared that no competing interests exist".
+Otherwise please declare all competing interests beginning with the statement ``I have read the journal's policy and the authors of this manuscript have the following competing interests:*
+
+Response here.
+
+> *Please amend your detailed Financial Disclosure statement.
+This is published with the article.
+It must therefore be completed in full sentences and contain the exact wording you wish to be published.
+State what role the funders took in the study.
+If the funders had no role in your study, please state: "The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript." If any authors received a salary from any of your funders, please state which authors and which funders.
+If you did not receive any funding for this study, please simply state: "The authors received no specific funding for this work."*
+
+Response here.
+
+> *Please ensure that the funders and grant numbers match between the Financial Disclosure field and the Funding Information tab in your submission form.
+Note that the funders must be provided in the same order in both places as well.*
+
+Response here.
+
+> *Please provide separate figure files in .tif or .eps format only and remove any figures embedded in your manuscript file.
+Please also ensure that all files are under our size limit of 10MB.
+For more information about figure files please see our guidelines: https://journals.plos.org/globalpublichealth/s/figures, https://journals.plos.org/globalpublichealth/s/figures#loc-file-requirements*
+
+Response here.
+
+> *Figure 2: please (a) provide a direct link to the base layer of the map (i.e., the country or region border shape) and ensure this is also included in the figure legend; and (b) provide a link to the terms of use / license information for the base layer image or shapefile.
+We cannot publish proprietary or copyrighted maps (e.g.
+Google Maps, Mapquest) and the terms of use for your map base layer must be compatible with our CC-BY 4.0 license.
+Note: if you created the map in a software program like R or ArcGIS, please locate and indicate the source of the basemap shapefile onto which data has been plotted.
+If your map was obtained from a copyrighted source please amend the figure so that the base map used is from an openly available source.
+Alternatively, please provide explicit written permission from the copyright holder granting you the right to publish the material under our CC-BY 4.0 license.
+Please note that the following CC BY licenses are compatible with PLOS license: CC BY 4.0, CC BY 2.0 and CC BY 3.0, meanwhile such licenses as CC BY-ND 3.0 and others are not compatible due to additional restrictions.
+If you are unsure whether you can use a map or not, please do reach out and we will be able to help you.
+The following websites are good examples of where you can source open access or public domain maps: U.S.
+Geological Survey (USGS) - All maps are in the public domain.
+(http://www.usgs.gov), PlaniGlobe - All maps are published under a Creative Commons license so please cite “PlaniGlobe, http://www.planiglobe.com, CC BY 2.0” in the image credit after the caption.
+(http://www.planiglobe.com/?lang=enl), Natural Earth - All maps are public domain.
+(http://www.naturalearthdata.com/about/terms-of-use/)*
+
+Response here.
+
+\newpage
+
 # References {#references .unnumbered}

### 2023-01-16 src/docs_paper/paper.Rmd
Update Katie and Katherine affiliations

@@
   - code: C
-    address: Department of Public Health Sciences, Penn State College of Medicine, Pennsylvania State University, Hershey, PA, USA
+    address: Department of Public Health Sciences, Penn State College of Medicine, Hershey, PA, USA
   - code: D
-    address: Department of Epidemiology, Harvard T. H. Chan School of Public Health, Harvard University, Boston, MA, USA
+    address: Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, MA, USA
   - code: E

### 2023-01-16 src/docs_paper/paper.Rmd
Reference for the accuracy of INLA (though in Rue 2017 it's still mostly just claimed rather than demonstrated..)

@@
 We performed inference using the integrated nested Laplace approximation (INLA) [@rue2009approximate] algorithm via the `R-INLA` package [@martins2013bayesian].
-For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo in the realistic, pre-asymptotic regime, and is substantially more computationally tractable for high dimensional models like ours, which has `r n_district` districts, `r n_year` years, `r n_age` age groups, and `r n_group` risk groups.
+For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo with realistic, finite samples [@rue2017bayesian], and is substantially more computationally tractable for high dimensional models like ours, which has `r n_district` districts, `r n_year` years, `r n_age` age groups, and `r n_group` risk groups.
 It is not possible to directly fit multinomial logistic regression models in `R-INLA`, so we used the multinomial-Poisson transformation [@baker1994multinomial].

### 2023-01-17 src/docs_paper/paper.Rmd
Table fix, spatial effect explain, M49 geocode reference

@@
 \centering
-\begin{tabularx}{\textwidth}{lp{5cm}ll}
+\begin{tabularx}{\textwidth}{lp{6cm}ll}
 \toprule
-Risk group & Description & Local HIV incidence & Incidence ratio \\
+Risk group & Description & Local HIV & Incidence ratio \\
+ & & incidence & \\
 \midrule
@@
 High & Non-regular or multiple partner(s) & -- & 1.72 \\
-Very high & Transactional sex (adjusted to correspond to female sex workers) & $<$0.1\% & 25.0 \\
+ & & $<$0.1\% & 25.0 \\
  & & 0.1-0.3\% & 13.0 \\
- & & 0.3-1.0\% & 9.0 \\
- & & 1.0-3.0\% & 6.0 \\
+ Very high & Transactional sex (adjusted to correspond & 0.3-1.0\% & 9.0 \\
+ & to female sex workers) & 1.0-3.0\% & 6.0 \\
  & & $>$3.0\% & 3.0 \\
@@
 We considered four model specifications for the space-age-time multinomial model for the three risk groups (Supplementary Appendix A.1.2).
-All models included intercepts for each risk group, age, country, and age-country effects, a spatial effect allowing variation in risk group proportions by district, and a temporal effect allowing variation over time.
-The specification for the spatial random effects was varied in alternative models between independent spatial effects for each district versus spatially correlated effects, where information is borrowed more between neighboring districts.
-Temporal effects were varied as independent temporal effects versus first-order auto-regressive temporal effects, where a smooth temporal trend is assumed. 
+All models included intercepts for each risk group, as well as age, country, and age-country random effects.
+We used spatial effects to allow variation in risk group proportions by district, and considered alternative model specifications with either independent spatial effects or spatially correlated effects which share information more between neighboring districts than those far apart.
+Similary, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent temporal effects versus first-order auto-regressive temporal effects where a smooth temporal trend is assumed.
 <!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
@@
 Estimates are stratified by risk group (columns) and five-year age group (rows).
-Regions of sub-Saharan Africa were defined according to the UN geocode (M49 standard).
+Regions of sub-Saharan Africa were defined according to the UN M49 geocode [@un2020statistics].
 \\label{fig:within-between-country-variation}"}

### 2023-01-17 src/docs_paper/paper.Rmd
Spatial effects clarification and response, Sobol calculation and no interactions response, FSW limiation, Figure 1 response

@@
 All models included intercepts for each risk group, as well as age, country, and age-country random effects.
-We used spatial effects to allow variation in risk group proportions by district, and considered alternative model specifications with either independent spatial effects or spatially correlated effects which share information more between neighboring districts than those far apart.
-Similary, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent temporal effects versus first-order auto-regressive temporal effects where a smooth temporal trend is assumed.
+To account for district-level variation we used spatial random effects consisting of a parameter for each district. 
+We considered alternative model specifications in which the spatial random effects were either independent or spatially correlated such that more information was shared between neighboring districts than those far apart.
+Similarly, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent versus first-order auto-regressive where a smooth temporal trend is assumed.
 <!-- Each alternative was considered with an additional spatio-temporal interaction term allowing the temporal trend to vary across districts. -->
@@
 For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Supplementary Appendix A.1.3).
-Each included an intercept, age and country effects, and a spatial effect allowing district-level variation.
-Both independent and spatially correlated spatial effects were considered.
+Each included an intercept, age and country random effects, and a spatial random effect allowing district-level variation.
+Both independent and spatially correlated spatial random effects were considered.
 To improve estimation with sparse data, during model selection we considered alternatives with national-level covariates for either the proportion of men who reported ever having paid for sex or having paid for sex in the last twelve months [@hodgins2022population].
@@
 
-The best fitting multinomial regression model included correlated spatial effects and independent and identically distributed temporal effects.
+The best fitting multinomial regression model included correlated spatial random effects and independent and identically distributed temporal random effects.
 <!-- but not spatio-temporal interactions. -->
-The best logistic regression model for transactional sex included correlated spatial effects and the proportion of men who reported ever paying for sex covariate.
+The best logistic regression model for transactional sex included correlated spatial random effects and the proportion of men who reported ever paying for sex covariate.
 Model performance according to the CPO criterion is provided in Supplementary Appendix A.1 for all models we considered.

### 2023-01-17 src/docs_review/review.Rmd
Spatial effects clarification and response, Sobol calculation and no interactions response, FSW limiation, Figure 1 response

@@
 
-Using district-level spatial random effects allowed us to account for subnational variation in risk group proportions.
-We considered both spatially unstructured (IID) and spatially structured (Besag) random effects, which can be implemented in `R-INLA` by setting `model = "iid"` or `model = "besag"` respectively.
+We did not use the specific term "sub-national effect" in the manuscript.
+We believe the reviewer is referring to the term "spatial effect", which we use to describe district-specific effects that allow the model to capture district-level variation in risk group proportions, primarily informed by survey data in each district.
+
+Thank you to the reviewer for highlighting the omission of specific definition for this term.
+Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of spatial random effect where it first appears in the methods section as follows:
+
+> All models included intercepts for each risk group, as well as age, country, and age-country random effects.
+To account for district-level variation we used spatial random effects consisting of a parameter for each district.
+We considered alternative model specifications in which the spatial random effects were either independent or spatially correlated such that more information was shared between neighboring districts than those far apart.
+Similarly, we used temporal random effects to allow variation in risk group proportions over time, and considered alternative model specifications as independent versus first-order auto-regressive where a smooth temporal trend is assumed.
 
@@
 ```{r}
-#' TODO Calculate the average Sobol index for survey random effects
-sobol <- 1
+df <- read_csv("depends/aaa-variance-proportions.csv")
+sobol <- 100 * mean(df$percentage_variance_sur_idx, na.rm = TRUE)
 ```
 
-Fitting each country individually, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects was on average `r sobol`/% (Supplementary Figure B.3).
+We share the reviewer's interest in the spatiotemporal interaction in risk group proportions, which would allow variation in temporal trend by country.
+However, we found that these interactions made the model computationally intractable to estimate given the large number of districts, years, age groups and risk groups involved.
+This is a limitation of our analysis, but, in practice, we do not believe this has a large impact on our results because overall we found that risk group proportions were very stable over time, while they varied substantially spatially.
+More specifically, when we fit the model to each country individually, which can be considered as an extreme version of country-specific spatiotemporal interactions, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects^[For those countries where such a random effect could be meaningfully defined.] was on average `r sobol`/% (Supplementary Figure B.3).
 This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).
-
-We had wanted to include the spatiotemporal interaction terms regardless, first for statistical completeness, and second to demonstrate how complex three-way^[As all random effects in the model are interacted with category.] interactions can be specified in `R-INLA` by careful use of the `group` and `replicate` options.
-However, we found that including these terms substantially increased the computational burden of the model when fitting all countries jointly, so in the end decided to exclude them.
 
@@
 Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
-We have noted this in the limitations section of the discussion.
+We have noted this in the limitations section of the discussion:
+
+> We have the least confidence in our estimates for the FSW risk group.
+As well as having the smallest sample sizes, our transactional sex estimates do not overcome the difficulties of sampling hard to reach groups.
+We inherent any limitations of the national FSW estimates which we adjust our estimates of transactional sex to match.
+Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.
 
@@
 
-Table B.3 in the appendix provides an alternative tabulation of the surveys we used, with sample size further broken down by age group.
-We are unsure on how to make Figure 1 might clearer.
-Other examples of similar figures in published papers include @giguere2021trends (Figure 1), ...
+In our and other previous work, figures similar to Figure 1 have been effective at concisely visualising inclusion of a large number of surveys across several countries and types (see, for example, Figure 1 of @giguere2021trends), and we prefer to retain this figure.
+Supplementary Table B.3 provides an alternative tabular summary of the surveys analysed, with sample size broken down by age group. 
+We have extended the caption of Figure 1 to draw attention to this alternative presentation:
+
+> **Fig 1.** Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex.
+Details of included surveys are in Supplementary Table B.3.
 

### 2023-01-17 src/docs_paper/paper.Rmd
Covariates text and refresh online copies

@@
 More generally, we did not aim to include predictive covariates.
+Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance.
+Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.
 

### 2023-01-17 src/docs_review/review.Rmd
Covariates text and refresh online copies

@@
 
-> Comment here.
+> More generally, we did not aim to include predictive covariates.
+Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance.
+Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.
 
@@
 
-```{r}
+```{r echo=FALSE, results='hide', warning=FALSE, message=FALSE}
 df <- read_csv("depends/aaa-variance-proportions.csv")
@@
 More specifically, when we fit the model to each country individually, which can be considered as an extreme version of country-specific spatiotemporal interactions, the proportion of variance (Sobol' index) attributable to the temporal (survey) random effects^[For those countries where such a random effect could be meaningfully defined.] was on average `r sobol`/% (Supplementary Figure B.3).
-This is corroborated by the lack of temporal trends in Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).
+This is corroborated by the lack of temporal trends in Supplementary Figures B.5 through B.17 which show the modelled and direct estimates for each country individually, as well as the fact that unstructured (IID) rather than structured (AR1) temporal random effects were preferred in the model selection (Supplementary Figure A.1).
 
@@
 Response here.
+Requested that coauthors send their COIs.
 

### 2023-01-19 src/docs_review/review.Rmd
Update COI statement

@@
 
-Response here.
-Requested that coauthors send their COIs.
+The competing interests' statement has been updated to the following:
+
+> I have read the journal's policy and the authors of this manuscript have the following competing interests: KAR was supported through a consultancy via UNAIDS to conduct an early version of this work;  LZ, IW, MM, and CB are employees of UNAIDS; JWE is a member of the editorial board for PLOS GPH; other authors have declared that no competing interests exist.
 

### 2023-01-22 src/docs_paper/paper.Rmd
SRF not SF for Seth
Update funding statement

@@
 TMW was supported by Imperial College London (President's PhD Scholarship).
-SF was supported by the EPSRC (EP/V002910/2).
+SRF was supported by the EPSRC (EP/V002910/2).
 JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664). 
 LZ, IW, MM and CB are employed by UNAIDS.
-<!-- A first version of this work was funded by the Global Fund (###) via UNAIDS -->
+A first version of this work was funded by UNAIDS.
 This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.

### 2023-01-25 src/docs_paper/paper.Rmd
Prospective final conclusion update

@@
 
-<!-- TODO: Follow up with Clemens r.e. FSW group name: -->
+<!-- Possible TODO: Follow up with Clemens r.e. FSW group name: -->
 <!-- There are a couple of options: female sex workers, young women from key populations (and clarify in the text that you mean sex work), AGYW who sell sex.
@@
 To calculate HIV prevalence by risk group, we disaggregated the district-age specific prevalence estimates from Naomi estimates to risk groups using odds ratios for the relative odds of having HIV between risk groups, calculated from a logistic regression of country-age specific household survey HIV bio-marker data.
-<!-- TODO: Be more specific about the data source here. -->
+<!-- Possible TODO: Be more specific about the data source here. -->
 Prevalence disaggregation was on the logit scale to ensure that HIV prevalence in each risk group remained in the range 0\% to 100\%.
@@
 
-<!-- How does this vary by country / region?
+<!-- Possible TODO: How does this vary by country / region?
 Maybe worth calling out result for West Africa vs.
@@
 
-<!-- Are we able to add an analysis of the number who are prioritized for the 'standard' and 'enhanced' prevention packages in the Global Strategy?
+<!-- Possible TODO: Are we able to add an analysis of the number who are prioritized for the 'standard' and 'enhanced' prevention packages in the Global Strategy?
 That gets a lot of emphasis in the Introduction, so would be nice to report about here.
@@
 This variation underscores the need for these granular data to implement HIV prevention options aligned to local norms and risk behaviours.
-<!-- Some type of comment about how novel this would be if implemented -->
+<!-- Possible TODO: Some type of comment about how novel this would be if implemented -->
 
@@
 
-<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->
+<!-- Possible paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->
 
@@
 
-We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk categories at a district-level in 13 priority countries and analyzed the number of infections that could be reached by prioritisation based upon location, age and behaviour.
+We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk groups at a district-level in 13 priority countries and analyzed the number of infections that could be reached by prioritisation based upon location, age and behaviour.
 Though subject to limitations, these estimates provide data that national HIV programmes can use to set targets and implement differentiated HIV prevention strategies as outlined in the Global AIDS Strategy.
-Successfully implementing this approach would result in more efficientlt reaching a greater number of those at risk of infection.
+Successfully implementing this approach would result in more efficiently reaching a greater number of those at risk of infection.
 
-<!-- TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
+Among AGYW, there was systematic variation by age group in risk group proportions, primary attributable to sexual debut typically occurring during the ages 15-24.
+There was also large amounts of spatial variation, particularly between those who reported one cohabiting partner versus non-regular or multiple partners.
+Risk group proportions did not change substantially over time, indicating that norms relating to sexual behaviour are relatively static.
+These findings underscore the importance of providing effective HIV prevention options tailored to the needs of particular age groups, as well as local sexual norms.
+
+<!-- Possible TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
 

### 2023-01-26 src/docs_paper/paper.Rmd
Rework final paragraph

@@
 
-Among AGYW, there was systematic variation by age group in risk group proportions, primary attributable to sexual debut typically occurring during the ages 15-24.
-There was also large amounts of spatial variation, particularly between those who reported one cohabiting partner versus non-regular or multiple partners.
+Among AGYW, there was systematic variation in sexual behaviour by age and location, but not over time.
+Age group variation was primarily attributable to age of sexual debut (ages 15-24).
+Spatial variation was particularly present between those who reported one cohabiting partner versus non-regular or multiple partners.
 Risk group proportions did not change substantially over time, indicating that norms relating to sexual behaviour are relatively static.
-These findings underscore the importance of providing effective HIV prevention options tailored to the needs of particular age groups, as well as local sexual norms.
-
-<!-- Possible TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
+These findings underscore the importance of providing effective HIV prevention options tailored to the needs of particular age groups, as well as local norms around sexual partnerships.
 

### 2023-01-31 src/docs_paper/paper.Rmd
Final updates to review response

@@
 
-The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient priorisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
+The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient prioritisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
 Four prioritisation strata (Supplementary Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
@@
 Furthermore, we do not consider seasonal migration patterns, which may particularly affect FSW size.
-More generally, we did not aim to include predictive covariates.
-Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance.
-Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.
+More generally, we did not consider covariates potentially predictive of risk group proportions (such as sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes), which are typically difficult to measure spatially.
+Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk prioritisation and precision HIV programme delivery.
 
@@
 
-## Funding
+<!-- ## Funding and disclaimer -->
 
-AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).
-AH, VKN, KAR, JWE were supported by the Bill and Melinda Gates Foundation (OPP1190661, OPP1164897).
-TMW was supported by Imperial College London (President's PhD Scholarship).
-SRF was supported by the EPSRC (EP/V002910/2).
-JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664). 
-LZ, IW, MM and CB are employed by UNAIDS.
-A first version of this work was funded by UNAIDS.
-This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
+<!-- AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1). -->
+<!-- AH, VKN, KAR, JWE were supported by the Bill and Melinda Gates Foundation (OPP1190661, OPP1164897). -->
+<!-- TMW was supported by Imperial College London (President's PhD Scholarship). -->
+<!-- SRF was supported by the EPSRC (EP/V002910/2). -->
+<!-- JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664).  -->
+<!-- This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth \& Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
+-->
 
-For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript (AAM) version arising from this submission.
+<!-- LZ, IW, MM, and CB are employed by UNAIDS, who also partially funded this study. -->
+<!-- LZ, IW, MM, and CB contributed to the design of the study, revision of the manuscript, and approved the final manuscript for submission. -->
+<!-- Findings and conclusions in this manuscript are those of the authors and do not necessarily represent the official position of the funding agencies. -->
 
-## Disclaimer
+<!-- ## Author contributions -->
 
-The findings and conclusions in this manuscript are those of the authors and do not necessarily represent the official position of the funding agencies.
-
-## Author contributions
-
-* Conceptualisation: JWE, KAR, CB
-* Data curation: AH, KAR, VKN, RE, OS, JWE
-* Formal analysis: AH
-* Funding acquisition: JWE
-* Investigation: AH
-* Methodology: AH, KAR, VKN, TMW, SRF, JWE
-* Project administration: JWE, KAR, CB
-* Software: AH, KAR
-* Supervision: JWE, SRF
-* Visualisation: AH
-* Writing - Original draft: AH
-* Writing - Review and Editing: AH, KAR, VKN, OS, KMJ, RE, LZ, IW, MM, CB, SRF, JWE
+<!-- * Conceptualisation: JWE, KAR, CB -->
+<!-- * Data curation: AH, KAR, VKN, RE, OS, JWE -->
+<!-- * Formal analysis: AH -->
+<!-- * Funding acquisition: JWE -->
+<!-- * Investigation: AH -->
+<!-- * Methodology: AH, KAR, VKN, TMW, SRF, JWE -->
+<!-- * Project administration: JWE, KAR, CB -->
+<!-- * Software: AH, KAR -->
+<!-- * Supervision: JWE, SRF -->
+<!-- * Visualisation: AH -->
+<!-- * Writing - Original draft: AH -->
+<!-- * Writing - Review and Editing: AH, KAR, VKN, OS, KMJ, RE, LZ, IW, MM, CB, SRF, JWE -->
 

### 2023-01-31 src/docs_review/review.Rmd
Final updates to review response

--- 2023-01-17 src/docs_review/review.Rmd
@@
 
-We agree that identifying predictive and measureable predictors of risk group proportions, or high risk locations, is an important area for further research.
+We agree that identifying predictive and measurable predictors of risk group proportions, or high risk locations, is an important area for further research.
 We have commented on this in the discussion section:
 
-> More generally, we did not aim to include predictive covariates.
-Many covariates that might be predictive of risk group proportions (for example sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes) are themselves difficult to measure spatially, and previous efforts have only led to modest improvements in model performance.
-Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk priorisation and precision HIV programme delivery.
+> More generally, we did not consider covariates potentially predictive of risk group proportions (such as sociodemographic characteristics, education, local economic activity, cultural and religious norms and attitudes), which are typically difficult to measure spatially.
+Identifying measurable correlates of risk, or particular settings in which time-concentrated HIV risk occurs, is an important area for further research to improve risk prioritisation and precision HIV programme delivery.
 
@@
 
-Response here.
-Requested that coauthors send their COIs.
+The competing interests' statement has been updated to the following:
+
+> I have read the journal's policy and the authors of this manuscript have the following competing interests: KAR was supported through a consultancy via UNAIDS to conduct an early version of this work;  LZ, IW, MM, and CB are employees of UNAIDS; JWE is a member of the editorial board for PLOS Global Public Health; other authors have declared that no competing interests exist.
 
@@
 
-Response here.
+The financial disclosure statement has been amended to clarify the role of the funders as following:
+
+> AH was supported by the EPSRC Centre for Doctoral Training in Modern Statistics and Statistical Machine Learning (EP/S023151/1).
+AH, VKN, KAR, JWE were supported by the Bill and Melinda Gates Foundation (OPP1190661, OPP1164897).
+TMW was supported by Imperial College London (President's PhD Scholarship).
+SF was supported by the EPSRC (EP/V002910/2).
+JWE was supported by UNAIDS and National Institute of Allergy and Infectious Disease of the National Institutes of Health (R01AI136664).
+LZ, IW, MM and CB are employed by UNAIDS.
+This research was supported by the MRC Centre for Global Infectious Disease Analysis (MR/R015600/1), jointly funded by the UK Medical Research Council (MRC) and the UK Foreign, Commonwealth & Development Office (FCDO), under the MRC/FCDO Concordat program and is also part of the EDCTP2 programme supported by the European Union.
+
+> LZ, IW, MM, and CB are employed by UNAIDS, who also partially funded this study.
+LZ, IW, MM, and CB contributed to the design of the study, revision of the manuscript, and approved the final manuscript for submission.
+Findings and conclusions in this manuscript are those of the authors and do not necessarily represent the official position of the funding agencies.
 
@@
 
-Response here.
+The financial disclosure fields and funding information tab have now been aligned.
 
@@
 
-Response here.
+Separate figure files have been provided as requested.
 
@@
 
-Response here.
+We attach an email from UNAIDS confirming approval for use of these subnational boundary shapefiles.
 

### 2023-01-31 src/docs_review/review.Rmd
Add line numbers for changed review text

@@
 For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, pre-asymptotic regime.
-We have added the following text to the methods section of the manuscript to clarify this point:
+We have added the following text to the methods section of the manuscript (lines 126-129) to clarify this point:
 
-> For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo in the realistic, pre-asymptotic regime, and is substantially more computationally tractable for high dimensional models like ours, which has 940 districts, 20 years, 3 age groups, and 4 risk groups.
+> For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo with realistic, finite samples, and is substantially more computationally tractable for high dimensional models like ours, which has 940 districts, 20 years, 3 age groups, and 4 risk groups.
 
@@
 We agree that identifying predictive and measurable predictors of risk group proportions, or high risk locations, is an important area for further research.
-We have commented on this in the discussion section:
+We have commented on this in the discussion section (lines 316-321):
 
@@
 Thank you to the reviewer for highlighting the omission of specific definition for this term.
-Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of spatial random effect where it first appears in the methods section as follows:
+Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of the term spatial random effect where it first appears in the methods section (lines 108-114) as follows:
 
@@
 Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
-We have noted this in the limitations section of the discussion:
+We have noted this in the limitations section of the discussion (lines 311-316):
 
@@
 Supplementary Table B.3 provides an alternative tabular summary of the surveys analysed, with sample size broken down by age group. 
-We have extended the caption of Figure 1 to draw attention to this alternative presentation:
+We have extended the caption of Figure 1 (proceeding line 170) to draw attention to this alternative presentation:
 

### 2023-03-01 src/docs_paper/appendix.Rmd
Journal formatting requirements

@@
 ---
-title: Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent
-  girls and young women across 13 priority countries in sub-Saharan Africa"
+title: Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa"
 subtitle: |
@@
 
-<!-- So that the tables and figures in this appendix are prefixed by "A." -->
+<!-- So that the tables and figures in this appendix are numbered alphabetically --->
 \setcounter{table}{0}  
-\renewcommand{\thetable}{A.\arabic{table}} 
+\renewcommand{\thetable}{\Alph{table}} 
 \setcounter{figure}{0} 
-\renewcommand{\thefigure}{A.\arabic{figure}}
+\renewcommand{\thefigure}{\Alph{figure}}
 
@@
 
-Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
+Let $i \in \{1, \ldots, n\}$ denote subnational units (Table E in S2 Text) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
 We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$, and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$.
@@
 This model included Besag spatial random effects and IID temporal random effects.
-For reference, we also computed the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] (Table \ref{tab:multinomial-model-performance} and Figure \ref{fig:multinomial-model-performance}).
+For reference, we also computed the deviance information criterion (DIC) [@spiegelhalter2002bayesian] and widely applicable information criterion (WAIC) [@watanabe2013widely] (Table \ref{tab:multinomial-model-performance} and Fig \ref{fig:multinomial-model-performance}).
 
@@
 We selected the best model according to the CPO statistic, which was model L6.
-CPO values, along with DIC and WAIC values for reference, are presented in Table \ref{tab:logistic-model-performance} and Figure \ref{fig:logistic-model-performance}.
+CPO values, along with DIC and WAIC values for reference, are presented in Table \ref{tab:logistic-model-performance} and Fig \ref{fig:logistic-model-performance}.
 Inclusion of Besag spatial random effects, rather than IID, consistently improved performance.
@@
 
-Figure \ref{fig:coverage} shows the PIT histogram and ECDF difference plots for our final model, faceted by risk group.
+Fig \ref{fig:coverage} shows the PIT histogram and ECDF difference plots for our final model, faceted by risk group.
 <!-- Comment on the results. -->
@@
 Next, we used the assumed $\text{Gamma}(\alpha = 10.4, \beta = 0.36)$ FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] to calculate the implied ratio between the number of FSW and the sexually debuted population in each age group.
-We assumed these ratios in South Africa were applicable to every country to calculate the number of FSW by age group in all 13 countries (Figure \ref{fig:age-disagg-fsw-line}).
+We assumed these ratios in South Africa were applicable to every country to calculate the number of FSW by age group in all 13 countries (Fig \ref{fig:age-disagg-fsw-line}).
 
@@
 where $\text{logistic}(x) = \exp(x) / (1 + \exp(x))$ such that $\text{logistic}(\hat \theta + \log(\text{OR}_k)) = \rho_{iak}$.
-Figures B.18 - B.30 show the resulting HIV prevalence estimates by risk group in each country.
+Fig R - AD in S2 Text show the resulting HIV prevalence estimates by risk group in each country.
 The number of PLHIV are then obtained by $H_{iak} = \rho_{iak} N_{iak}$, where $N_{iak}$ is the risk group population size.
@@
 The risk ratio $\text{RR}_4(\lambda_{ia})$ was defined as a function of general population incidence.
-Figures B.31 - B.43 show the resulting HIV incidence estimates by risk group in each country.
+Fig AE - AQ in S2 Text show the resulting HIV incidence estimates by risk group in each country.
 The number of new HIV infections are then $I_{iak} = \lambda_{iak} N_{iak}$.
@@
 By cumulatively summing the expected infections, for each fraction of the total population reached we calculated the fraction of total expected new infections that would be reached.
-Figures B.44 - B.56 show the percentage of new infections that would be reached prioritising according to each possible stratification within each country.
+Fig AR - BD in S2 Text show the percentage of new infections that would be reached prioritising according to each possible stratification within each country.
 

### 2023-03-01 src/docs_paper/paper.Rmd
Journal formatting requirements

@@
   - name: Van Kính Nguyen
-    affiliation: B
+    affiliation: [D, B]
   - name: Oliver Stevens
@@
   - name: Katherine M. Jia
-    affiliation: D
+    affiliation: E
   - name: Timothy M. Wolock
@@
   - name: Lycias Zembe
-    affiliation: E
+    affiliation: F
   - name: Ian Wanyeki
-    affiliation: E
+    affiliation: F
   - name: Mary Mahy
-    affiliation: E
+    affiliation: F
   - name: Clemens Benedikt
-    affiliation: E
+    affiliation: F
   - name: Seth R. Flaxman
-    affiliation: F
+    affiliation: G
   - name: Jeffrey W. Eaton
@@
   - code: C
+    address: Heidelberg Institute for Global Health, Faculty of Medicine, Heidelberg University, Germany
+  - code: D
     address: Department of Public Health Sciences, Penn State College of Medicine, Hershey, PA, USA
-  - code: D
+  - code: E
     address: Center for Communicable Disease Dynamics, Department of Epidemiology, Harvard T.H. Chan School of Public Health, Boston, MA, USA
-  - code: E
+  - code: F
     address: Joint United Nations Programme on HIV/AIDS, Geneva, Switzerland
-  - code: F
+  - code: G
     address: Department of Computer Science, University of Oxford, Oxford, United Kingdom
@@
 The Global AIDS Strategy 2021-2026 [@unaids2021global], adopted by the United Nations (UN) General Assembly in June 2021, proposed stratifying packages of HIV prevention provided to AGYW based on both local population-level HIV incidence and individual-level sexual risk behaviour to promote more efficient prioritisation of prevention services [@anderson2014maximising; @mcgillen2016optimum; @kelly2018global; @jia2022risk].
-Four prioritisation strata (Supplementary Table B.1) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
+Four prioritisation strata (Table A in S2 Text) were defined based on: (1) subnational annual incidence (<0.3\%, 0.3-1.0\%, 1.0-3.0\% and >3.0\%), and (2) self-reported high-risk behaviour or recent STI infection.
 <!-- NB: Check again about the recent STI infection aspect. -->
-The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Supplementary Table B.2) based upon this prioritisation strata [@unaids2021global].
+The strategy encourages programmes to  define targets for the proportion of AGYW to be reached with a range of interventions (Table B in S2 Text) based upon this prioritisation strata [@unaids2021global].
 All AGYW are recommended to have access to a basic package of HIV prevention, while those with with high risk behaviours in moderate incidence settings and all AGYW in very high incidence settings are recommended to have access to enhanced intervention packages [@joint2016hiv; @birdthistle2018evaluating].
@@
 <!-- TODO: Include example of inconsistent result. -->
-Exact survey questions varied slightly across survey types and between survey phases (Supplementary Appendix B).
+Exact survey questions varied slightly across survey types and between survey phases (S2 Text).
 Questions captured information about whether the respondent had been sexually active in the past twelve months, and if so how with many partners.
@@
 <!-- and so far has been used by X countries could be better (adds some information that it's widely used) -->
-The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning by countries, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Supplementary Table B.5).
+The administrative area hierarchy and geographic boundaries we used correspond to those used for health service planning by countries, exceptions being Cameroon and Kenya where we conducted analysis one level higher at the department and county levels, respectively (Table E in S2 Text).
 We used the most recent 2022 estimates for all countries, apart from Mozambique where, due to data accuracy concerns, we used the 2021 estimates (in which the Cabo Delgado province is excluded due to disruption by conflict).
@@
 FSW population size estimates by age were obtained by disaggregating national 15-49 FSW population size estimates [@stevens2022estimating] using the FSW age distribution in South Africa from the Thembisa model [@johnson2020thembisa] in combination with country-specific age at first sex distributions [@nguyen2022trends].
-Further technical details are in Supplementary Appendix A.1.
+Further technical details are in Section 1 of S1 Text.
 
-We considered four model specifications for the space-age-time multinomial model for the three risk groups (Supplementary Appendix A.1.2).
+We considered four model specifications for the space-age-time multinomial model for the three risk groups.
 All models included intercepts for each risk group, as well as age, country, and age-country random effects.
@@
 
-For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications (Supplementary Appendix A.1.3).
+For the logistic regression model of the proportion engaging in transactional sex among those with non-regular or multiple partner(s), we considered six specifications.
 Each included an intercept, age and country random effects, and a spatial random effect allowing district-level variation.
@@
 It is not possible to directly fit multinomial logistic regression models in `R-INLA`, so we used the multinomial-Poisson transformation [@baker1994multinomial].
-Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to appropriately define random effects, are provided in Supplementary Appendix A.1.2.
+Details of this approach, including how we used Kronecker products over Gaussian Markov random fields to appropriately define random effects, are provided in Section 1.2 of S1 Text.
 The best performing model was selected according to the conditional predictive ordinate (CPO) criterion [@pettit1990conditional], a measure of leave-one-out model performance that can be calculated directly in `R-INLA` without explicit model refitting [@held2010posterior].
@@
 ```{r fig.cap="Surveys used in our analysis by year, survey type, sample size, and whether the survey included a question about transactional sex.
-Details of included surveys are in Supplementary Table B.3.
+Details of included surveys are in Table C in S2 Text.
 \\label{fig:available-surveys}"}
@@
 
-We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Supplementary Table B.3), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_age$Y025_029)` aged 25-29 years).
+We included `r total_surveys` surveys in our analysis (Fig \ref{fig:available-surveys}, Table C in S2 Text), with a total sample size of `r comma(agyw_surveyed)` women aged 15-29 years (`r comma(agyw_surveyed_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_age$Y025_029)` aged 25-29 years).
 Of these, `r length(giftsvar_surveys)` surveys included a specific transactional sex question, with a total sample size of `r comma(agyw_surveyed_giftsvar - giftsvar_Y025_029_overcount)` (`r comma(agyw_surveyed_giftsvar_age$Y015_019)` aged 15-19 years, `r comma(agyw_surveyed_giftsvar_age$Y020_024)` aged 20-24 years, and `r comma(agyw_surveyed_giftsvar_age$Y025_029 - giftsvar_Y025_029_overcount)` aged 25-29 years^[There were `r length(giftsvar_exclude_Y025_029)` DHS surveys which excluded women 25-29 from the transactional sex survey question.]).
@@
 The best logistic regression model for transactional sex included correlated spatial random effects and the proportion of men who reported ever paying for sex covariate.
-Model performance according to the CPO criterion is provided in Supplementary Appendix A.1 for all models we considered.
-Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Supplementary Fig B.5 - B.17).
+Model performance according to the CPO criterion is provided in S1 Text for all models we considered.
+Direct estimates of the four risk group proportions from these surveys were highly correlated with our modelled estimates at a national-level (Fig E - Q in S2 Text).
 
@@
 Considering each country separately, on average, reaching half of new infections in each country required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
-The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (Supplementary Appendix B).
+The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (S2 Text).
 For example, FSW in Kenya were estimated to be `r inf_fsw_kenya$prop_population_cumulative`\% of the population and close to a third (`r inf_fsw_kenya$prop_infections_averted_cumulative`\%) of all new infections, whereas FSW in Tanzania were just `r inf_fsw_tanzania$prop_population_cumulative`\% of the population and `r inf_fsw_tanzania$prop_infections_averted_cumulative`\% of all new infections.
@@
 
+<!-- Structured abstract no longer required -->
+<!-- **Background:** -->
+<!-- **Methods:** -->
+<!-- **Results:** -->
+<!-- **Conclusions:** -->
+
 ---
 abstract: |
-  **Background:**
   The Global AIDS Strategy 2021-2026 identifies adolescent girls and young women (AGYW) as a priority population for HIV prevention, and recommends differentiating intervention portfolios geographically based on local HIV incidence and individual risk behaviours.
   We estimated prevalence of HIV risk behaviours and associated HIV incidence at health district level among AGYW living in 13 countries in sub-Saharan Africa.
-
-  **Methods:**
   We analysed `r total_surveys` geospatially-referenced national household surveys conducted between 1999-2018 across 13 high HIV burden countries in sub-Saharan Africa.
@@
   We then assessed the efficiency of prioritising interventions according to risk group.
-
-  **Results:**
   Data consisted of `r comma(agyw_surveyed)` female survey respondents aged 15-29.
@@
   FSW were `r inf_fsw$prop_population_cumulative`\% of the population but `r inf_fsw$prop_infections_averted_cumulative`\% of all expected new infections.
-
-  **Conclusions:**
   Our risk group estimates provide data for HIV programmes to set targets and implement differentiated prevention strategies outlined in the Global AIDS Strategy.
   Successfully implementing this approach would result in more efficiently reaching substantially more of those at risk for infections.
+---
 
-author_summary: |
-  Exposure to HIV among adolescent girls and young women depends on the level of unsuppresed HIV in their local community among potential partners, and their individual sexual behaviour.
-  To support HIV programmes in identifying and providing prevention services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
-  This produced estimates of the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group.
-  We found that prioritising HIV prevention using behavioural risk groups almost halved the proportion of the population that would need to be reached to find half of all expected new infections.
----
+<!-- Journal no longer requires author summary -->
+<!-- author_summary: | -->
+<!--   Exposure to HIV among adolescent girls and young women depends on the level of unsuppresed HIV in their local community among potential partners, and their individual sexual behaviour. -->
+<!--   To support HIV programmes in identifying and providing prevention services to those at highest risk, we geographically mapped HIV risk groups using sexual risk behaviour data from household surveys and estimated the proportion of people living with HIV in each risk group, and the rate of infections in each risk group.
+-->
+<!--   This produced estimates of the proportion of people living with HIV in each risk group, as well as the rate of new infections in each risk group. -->
+<!--   We found that prioritising HIV prevention using behavioural risk groups almost halved the proportion of the population that would need to be reached to find half of all expected new infections.
+-->
 
@@
 First, by taking a modular modelling approach, we integrated all relevant survey information from multiple years, allowing estimation of the FSW proportion for surveys without a specific transactional sex question.
-Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Supplementary Fig B.2).
+Second, whereas direct estimates exhibit large sampling variability at a district level, we alleviated this issue using spatio-temporal smoothing (Fig B in S2 Text).
 Third, we provided estimates in all district-years, including those not directly sampled by surveys, allowing estimates to be consistently fed into further analysis and planning pipelines (such as our analysis of risk group specific prevalence and incidence).
@@
 
-**Supplementary Appendix A**: Statistical modelling \newline
-**Supplementary Appendix B**: Supplementary tables and figures
+**S1 Text**: Mathematical appendix, including for: the risk group model, FSW population size estimation, and calculation of HIV prevalence, HIV incidence and expected new HIV infections reached.
+\newline
+**S2 Text**: Supplementary tables and figures, including for: the Global AIDS strategy, the household survey data used, and plots of country-specific comparisons between direct and modelled estimates, HIV prevalence estimates, HIV incidence estimates, and expected new HIV infections reached.
 
@@
 <!-- * Conceptualisation: JWE, KAR, CB -->
-<!-- * Data curation: AH, KAR, VKN, RE, OS, JWE -->
+<!-- * Data curation: AH, KAR, VKN, RE, OS, IW, MM, JWE -->
 <!-- * Formal analysis: AH -->

### 2023-03-01 src/docs_paper/paper.Rmd
Couple of changes

@@
 Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model.
-Posterior mean, median, and 95\% credible intervals are provided in the supplementary material.
+Posterior mean, median, and 95\% credible intervals are provided in S1 Data.
 In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.
@@
 Considering each country separately, on average, reaching half of new infections in each country required reaching `r inf_country_half_without_behaviour$median`\% (range `r inf_country_half_without_behaviour$min`-`r inf_country_half_without_behaviour$max`\%) of the population when stratifying by area and age, reducing to `r inf_country_half_with_behaviour$median`\% (range `r inf_country_half_with_behaviour$min`-`r inf_country_half_with_behaviour$max`\%) when behaviour was included.
-The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (S2 Text).
+The relative importance of stratifying by age, location and behaviour varied between countries, analogous to the varying contribution of each to the total variance (Fig C in S2 Text).
 For example, FSW in Kenya were estimated to be `r inf_fsw_kenya$prop_population_cumulative`\% of the population and close to a third (`r inf_fsw_kenya$prop_infections_averted_cumulative`\%) of all new infections, whereas FSW in Tanzania were just `r inf_fsw_tanzania$prop_population_cumulative`\% of the population and `r inf_fsw_tanzania$prop_infections_averted_cumulative`\% of all new infections.
@@
 **S2 Text**: Supplementary tables and figures, including for: the Global AIDS strategy, the household survey data used, and plots of country-specific comparisons between direct and modelled estimates, HIV prevalence estimates, HIV incidence estimates, and expected new HIV infections reached.
+\newline
+**S1 Data**: Estimates of risk group proportions.
 

### 2023-03-09 src/docs_paper/paper.Rmd
Very long list of legends

@@
 
+## List of legends
+
+### S1 Text
+
+#### Tables
+
+* Table A: The multinomial regression models that we considered. Observation random effects $\theta_{ita}$, included in all models, are omitted from this table.
+* Table B: Multinomial regression model performance, with the best performing model(s) according to each criterion shown as a square.
+For the CPO, higher values indicate better model performance for the CPO.
+For the
+DIC and WAIC, lower values indicate better model performance.
+* Table C: The logistic regression models that were considered.
+\texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months.
+* Table D: Logistic regression model performance. For the CPO, higher values indicate better model performance. For the DIC and WAIC, lower values indicate better model performance.
+
+#### Figures
+
+* Figure A: Multinomial regression model performance, with the best performing model(s) according to each criterion shown as a square.
+For the CPO, higher values indicate better model performance for the CPO.
+For the DIC and WAIC, lower values indicate better model performance.
+* Figure B: Logistic regression model performance, with the best performing model(s) according to each criterion shown as a square.
+* Figure C: Probability integral transform (PIT) histograms (top row) and empirical cumulative distribution function (ECDF) difference plots (bottom row) for the final selected model.
+* Figure D: Proportion of FSW by age group (including the age groups 30-34, 35-39, 40-44 and 45-49) as produced by our disaggregation procedure.
+
+### S2 Text
+
+#### Tables
+
+* Table A: Prioritisation strata according to HIV incidence in the general population and behavioural risk.
+* Table B: Commitments to be met for each intervention in terms of proportion of the prioritisation strata reached, where "-" represents no commitment.
+* Table C: All of the surveys that we used in our analysis and their sample sizes, disaggregated by respondent age.
+* Table D: All of that surveys that were excluded from our analysis.
+* Table E: The numer of areas and analysis levels for each country that were used in our analysis.
+* Table F: AIS, BAIS and DHS survey questions.
+* Table G: PHIA survey questions.
+
+#### Figures
+
+* Figure A: Flowchart describing allocation of respondents to risk groups.
+* Figure B: Illustration of our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
+Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.
+* Figure C: Proportion of variance explained by each random effect (Sobol’ indices) when the multinomial regression model is fit to each country individually.
+In this setting, country-category random effects are not included in the model and year-category random effects are replaced by survey-category random effects (for countries with surveys in multiple years).
+Countries are ordered by the proportion of their variance which is explained by the area-category random effects.
+* Figure D: The posterior density of national-level risk group proportions by age, illustrating the bi-modality of the cohabiting partner and non-regular and multiple partner(s) risk groups.
+* Figure E: Comparison of modelled and direct national-level estimates in 1999-2018 in Botswana.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure F: Comparison of modelled and direct national-level estimates in 1999-2018 in Cameroon.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure G: Comparison of modelled and direct national-level estimates in 1999-2018 in Kenya.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure H: Comparison of modelled and direct national-level estimates in 1999-2018 in Lesotho.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure I: Comparison of modelled and direct national-level estimates in 1999-2018 in Mozambique.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure J: Comparison of modelled and direct national-level estimates in 1999-2018 in Malawi.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure K: Comparison of modelled and direct national-level estimates in 1999-2018 in Namibia.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure L: Comparison of modelled and direct national-level estimates in 1999-2018 in Eswatini.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure M: Comparison of modelled and direct national-level estimates in 1999-2018 in Tanzania.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure M: Comparison of modelled and direct national-level estimates in 1999-2018 in Uganda.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure O: Comparison of modelled and direct national-level estimates in 1999-2018 in South Africa.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure P: Comparison of modelled and direct national-level estimates in 1999-2018 in Zambia.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure Q: Comparison of modelled and direct national-level estimates in 1999-2018 in Zimbabwe.
+Estimates are described as "partially direct" when there are no surveys containing a transactional sex question in a country-age-group and we instead used modelled logistic regression estimates to differentiate the direct estimates.
+* Figure R: District-level HIV prevalence for each of the risk groups in 2018 in Botswana.
+* Figure S: District-level HIV prevalence for each of the risk groups in 2018 in Cameroon.
+* Figure T: District-level HIV prevalence for each of the risk groups in 2018 in Kenya.
+* Figure U: District-level HIV prevalence for each of the risk groups in 2018 in Lesotho.
+* Figure V: District-level HIV prevalence for each of the risk groups in 2018 in Mozambique.
+* Figure W: District-level HIV prevalence for each of the risk groups in 2018 in Malawi.
+* Figure X: District-level HIV prevalence for each of the risk groups in 2018 in Namibia.
+* Figure Y: District-level HIV prevalence for each of the risk groups in 2018 in Eswatini.
+* Figure Z: District-level HIV prevalence for each of the risk groups in 2018 in Tanzania.
+* Figure AA: District-level HIV prevalence for each of the risk groups in 2018 in Uganda.
+* Figure AB: District-level HIV prevalence for each of the risk groups in 2018 in South Africa.
+* Figure AC: District-level HIV prevalence for each of the risk groups in 2018 in Zambia.
+* Figure AD: District-level HIV prevalence for each of the risk groups in 2018 in Zimbabwe.
+* Figure AE: District-level HIV incidence for each of the risk groups in 2018 in Botswana.
+* Figure AF: District-level HIV incidence for each of the risk groups in 2018 in Cameroon.
+* Figure AG: District-level HIV incidence for each of the risk groups in 2018 in Kenya.
+* Figure AH: District-level HIV incidence for each of the risk groups in 2018 in Lesotho.
+* Figure AI: District-level HIV incidence for each of the risk groups in 2018 in Mozambique.
+* Figure AJ: District-level HIV incidence for each of the risk groups in 2018 in Malawi.
+* Figure AK: District-level HIV incidence for each of the risk groups in 2018 in Namibia.
+* Figure AL: District-level HIV incidence for each of the risk groups in 2018 in Eswatini.
+* Figure AM: District-level HIV incidence for each of the risk groups in 2018 in Tanzania.
+* Figure AN: District-level HIV incidence for each of the risk groups in 2018 in Uganda.
+* Figure AO: District-level HIV incidence for each of the risk groups in 2018 in South Africa.
+* Figure AP: District-level HIV incidence for each of the risk groups in 2018 in Zambia.
+* Figure AQ: District-level HIV incidence for each of the risk groups in 2018 in Zimbabwe.
+* Figure AR: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Botswana.
+* Figure AS: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Cameroon.
+* Figure AT: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Kenya.
+* Figure AU: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Lesotho.
+* Figure AV: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Mozambique.
+* Figure AW: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Malawi.
+* Figure AX: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Namibia.
+* Figure AY: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Eswatini.
+* Figure AZ: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Tanzania.
+* Figure BA: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Uganda.
+* Figure BB: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in South Africa.
+* Figure BC: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zambia.
+* Figure BD: Percentage of expected new infections reached taking a variety of risk stratification approaches against the percentage of at risk population reached in Zimbabwe.
+
 <!-- ## Funding and disclaimer -->

### 2023-03-09 src/docs_paper/tables-figures.Rmd
Journal formatting requirements
Very long list of legends

@@
 
-<!-- So that the tables and figures in this appendix are prefixed by "B." -->
+<!-- So that the tables and figures in this appendix are numbered alphabetically --->
 \setcounter{table}{0}  
-\renewcommand{\thetable}{B.\arabic{table}} 
+\renewcommand{\thetable}{\AlphAlph{\value{table}}} 
 \setcounter{figure}{0} 
-\renewcommand{\thefigure}{B.\arabic{figure}}
+\renewcommand{\thefigure}{\AlphAlph{\value{figure}}}
 
@@
 \makebox[\textwidth][c]{\includegraphics{depends/model-direct-benefits.png}}
-\caption{Illustration our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
+\caption{Illustration of our model results for AGYW 20-24 in Tanzania in 2010 in the cohabiting risk group.
 Compared to the direct survey results, our spatio-temporally smoothed estimates more plausibly represent district-level heterogeneity, as well as imputing any districts with missing data.}

### 2023-03-09 src/docs_paper/paper.Rmd
S1 Data description and remove mention of Appendix (now S1 Text)

@@
 Using risk group proportion estimates, and subnational estimates developed using the Naomi model, we calculated HIV prevalence, PLHIV, HIV incidence and number of new HIV infections stratified by district, age group and risk group.
-Further details are provided in Appendix A.2.
+Further details are provided in S1 Text.
 
@@
 
-Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model.
-Posterior mean, median, and 95\% credible intervals are provided in S1 Data.
+Fig \ref{fig:continental-map} and Fig \ref{fig:within-between-country-variation} show posterior mean estimates for the proportion in each risk group from our final model (provided in S1 Data).
 In subsequent results, all estimates refer to 2018, the most recent year included in our analysis, unless otherwise indicated.

### 2023-03-09 src/docs_paper/paper.Rmd
Two typos (maybe the last ones?)

@@
 Non-regular partners are defined to be non cohabiting.
-The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were dervied based on patterns of relative HIV prevalence among FSW compared to general population prevalence.
+The transactional sex risk group is adjusted during analysis to correspond to female sex worker, and incidence rate ratios among FSW were derived based on patterns of relative HIV prevalence among FSW compared to general population prevalence.
 When the local HIV incidence in the general population is higher, the incidence rate ratio for FSW is lower.}
@@
 Estimates are stratified by risk group (columns) and five-year age group (rows).
-Regions of sub-Saharan Africa were defined according to the UN M49 geocode [@un2020statistics].
 \\label{fig:within-between-country-variation}"}

### 2023-04-08 src/docs_xx-05-23-hi-med/xx-05-23-hi-med.Rmd
Template for Hi-Med talk

---
title: Using statistics to respond to the HIV epidemic
subtitle: High Impact Medicine
author: Adam Howes
institute: Imperial College London
date: May 2023
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

## About me

* Maths undergraduate $\to$ statistics masters $\to$ statistics PhD
* Interested in impactful applications in global health and biosecurity
* Limited knowledge about epidemiology or biology

##

<!-- ## Background -->

<!-- ::: columns -->

<!-- :::: column -->

<!-- * In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are disproportionately at risk of HIV infection -->
<!--   * 28% of population and 44% of new infections -->
<!-- * This disparity is because of: -->
<!--   1. Younger age at first sex -->
<!--   2. Age patterns of sexual mixing -->
<!--   3. Structural vulnerabilities and power imbalances -->
<!--   4. Increased susceptibility to HIV infection -->

<!-- :::: -->

<!-- :::: column -->

<!-- ```{r echo=FALSE, out.width = "125px", fig.cap="Tweet from UNAIDS"} -->
<!-- knitr::include_graphics("tweet.png") -->
<!-- ``` -->

<!-- :::: -->

<!-- ::: -->

<!-- ## Prevention packages -->

<!-- * Prevention options can be divided into two: -->
<!--   1. Core package -->
<!--   2. Intensified interventions -->
<!-- * Insufficient resources to offer the more costly intensified interventions to all AGYW -->

<!-- \begin{center} -->
<!-- \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}] -->
<!-- $\implies$ How should interventions be prioritised to have the greatest impact? -->
<!-- \end{tcolorbox} -->
<!-- \end{center} -->

<!-- ## Stratified prevention -->

<!-- ::: columns -->

<!-- :::: column -->

<!-- * Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based on -->
<!--   1. Population-level HIV incidence -->
<!--   2. Individual-level sexual risk behaviour -->
<!-- * The two most proximal drivers of sexual transmission -->

<!-- :::: -->

<!-- :::: column -->

<!-- ```{r echo=FALSE, out.width = "125px", fig.cap="Global AIDS strategy"} -->
<!-- knitr::include_graphics("global-aids-strategy.png") -->
<!-- ``` -->

<!-- :::: -->

<!-- ::: -->

<!-- ## Scope for our work -->

<!-- ### Goals -->

<!-- 1. Enable implementation of prevention stratified by incidence and behaviour -->
<!-- 2. Assess the benefits of such approaches: is it worth it? -->

<!-- ### Approach -->

<!-- 1. Estimate the proportion of AGYW in four behavioural risk groups at a district level (in 13 countries identified as priority by The Global Fund) -->
<!-- 2. Analyze the new infections which could be reached by different stratified prevention strategies -->

<!-- ## Data -->

<!-- * Sexual behaviour data from household surveys to place respondents into $K = 4$ risk groups: -->
<!--   1. $k = 1$ Not sexually active -->
<!--   2. $k = 2$ One cohabiting sexual partner -->
<!--   3. $k = 3$ Non-regular sexual partner(s) -->
<!--   4. $k = 4$ Female sex workers -->
<!-- * District-level HIV incidence, prevalence, population size estimates from the Naomi model [@eaton2021naomi] -->
<!--   * Combines survey and programmatic data to estimate indicators in the general population -->
<!-- * Risk ratios from ALPHA network analysis [@slaymaker2020croi] and UNAIDS analysis led by Keith Sabin -->
<!--   * 10 longitudinal studies: https://alpha.lshtm.ac.uk/ -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width = "400px"} -->
<!-- knitr::include_graphics("depends/category-flowchart.pdf") -->
<!-- ``` -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width = "400px"} -->
<!-- knitr::include_graphics("depends/available-surveys.png") -->
<!-- ``` -->

<!-- ## Two-stage model for risk group proportions -->

<!-- \begin{center} -->
<!-- \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}] -->
<!-- How do we deal with the fact that only some of the surveys included a transactional sex question? This question is required to differentiate between the $k = 3$ and $k = 4$ risk groups -->
<!-- \end{tcolorbox} -->
<!-- \end{center} -->

<!-- * Our approach was to fit a two-stage model -->
<!--   1. Spatio-temporal multinomial logistic regression model for the proportion of AGYW in the $k = 1, 2, 3^{+}$ risk groups, using all 47 surveys -->
<!--   2. Spatial logistic regression model for the proportion of those in the $k = 3^{+} = \{3, 4\}$ risk groups who are in the $k = 4$ risk group, using only the 13 surveys with a specific transactional sex question -->

<!-- ## Notation -->

<!-- * $k \in \{1, \ldots, 4\}$: risk groups -->
<!-- * $i \in \{1, \ldots, n\}$: districts -->
<!-- * $c[i] \in \{\text{Botswana}, \ldots, \text{Zimbabwe}\}$: country containing district $i$ -->
<!-- * $t \in \{1999, \ldots, 2018\}$: years -->
<!-- * $a \in \{\text{15-19}, \text{20-24}, \text{25-29}\}$: age groups -->
<!-- * $y_{ita}^\star = (y_{ita1}^\star, y_{ita2}^\star, y_{ita3}^\star, y_{ita4}^\star)$: survey weighted multinomial observations -->
<!-- * $m_{ita}^\star$: survey weighted multinomial sample size -->

<!-- ## Multinomial logistic regression model -->

<!-- * Would like to use integrated nested Laplace approximations for fast, accurate inference, but `R-INLA` is not compatible with multinomial likelihoods because they depend on multiple elements of the latent field -->
<!-- * Instead, use that multinomial logistic regression models can be recast as a Poisson log-linear models using the Poisson trick -->
<!-- * This works because conditional on their sum, Poisson counts are jointly multinomially distributed -->
<!-- * If you include observation-specific random effects $\theta_{ita} \sim \mathcal{N}(0, 1000^2)$ in the linear predictor $\eta_{itak} = \theta_{ita} + \cdots$ then the sample sizes $m_{ita}^\star$ can be exactly recovered, ensuring the models are actually the same -->

<!-- ## Multinomial logistic regression model -->

<!-- \begin{align*} -->
<!--     y_{itak}^\star &\sim \text{xPoisson}(\lambda_{itak}) \\ -->
<!--     \log(\lambda_{itak}) &= \theta_{ita} + \beta_k + \zeta_{c[i]k} + \alpha_{ac[i]k} + \phi_{ik} + \gamma_{tk} + \delta_{itk}. -->
<!-- \end{align*} -->

<!-- * The terms are -->
<!--   * $\theta_{ita}$: observation (IID) -->
<!--   * $\beta_k$: category (IID) -->
<!--   * $\zeta_{ck}$: country-category (IID x IID) -->
<!--   * $\alpha_{ack}$: age-country-category (IID x IID x IID) -->
<!--   * $\phi_{ik}$: space-category ({IID, **Besag**} x IID) -->
<!--   * $\gamma_{tk}$: year-category ({**IID**, AR1} x IID) -->
<!--   * $\delta_{itk}$: space-year-category (Implemented but crashing on cluster at the moment...) -->
<!-- * Without category interactions, any effect will be washed out when we apply softmax to get the probabilities! -->

<!-- ##  -->

<!-- ```{r echo=FALSE, warning =FALSE, out.width="350px", fig.cap = "The Besag model, $\\phi_i \\, | \\, \\phi_{-i} \\sim \\mathcal{N} \\left(\\frac{1}{n_{\\delta i}} \\sum_{j: j \\sim i} \\phi_j, \\frac{1}{n_{\\delta i}\\tau_\\phi} \\right)$, operates on the neighbourhood graph."} -->
<!-- areas <- sf::read_sf("depends/zwe_areas.geojson") -->

<!-- areas %>% -->
<!--   filter(area_level == 2) %>% -->
<!--   bsae::plot_graph(add_geography = TRUE) -->
<!-- ``` -->

<!-- ## Multinomial logistic regression model -->

<!-- * Independent penalised complexity [@simpson2017penalising] priors on all standard deviation parameters with $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$ -->
<!--   * Sidenote, I'm interested as to if joint priors might be more suitable -->
<!-- * Possible (but tricky) to define all these interactions in `R-INLA` by combination of the `group` and `replicate` options -->
<!--   * Check out the `aaa_fit_multi-sexbehav-sae` report if you're interested! -->
<!-- * Used sum-to-zero constraints to make posterior inferences interpretable -->
<!--   * Because we're interested in the contribution of each random effect to total variance -->
<!-- * Model comparison via CPO statistic -->

<!-- ## Logistic regression model -->

<!-- \begin{align*} -->
<!--     y_{ia4}^\star &\sim \text{Binomial} \left( y_{ia3}^\star + y_{ia4}^\star, q_{ia} \right), \label{eq:logistic-regression} \\ -->
<!--     q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), \\ -->
<!--     \eta_{ia} &= \beta_0 +  \zeta_{c[i]} + \alpha_{ac[i]} + \phi_i + \beta_{\texttt{cfsw}} \texttt{cfsw}_{c[i]}. -->
<!-- \end{align*} -->

<!-- * The terms are -->
<!--   * $\beta_0$: intercept -->
<!--   * $\zeta_{c[i]}$: country effects (IID) -->
<!--   * $\alpha_{ac[i]}$ age-country effects (IID) -->
<!--   * $\phi_i$: spatial effects (IID, **Besag**) -->
<!--   * Clients of FSW covariates (`cfswever`, **`cfswrecent`**) [@hodgins2022population] -->

<!-- ## Combination and FSW adjustment -->

<!-- * Take 1000 samples from each model, then manipulate suitably to generate estimates for all four risk groups -->
<!-- * We adjusted the samples from the $k = 4$ risk group to match age-country FSW estimates, reallocating into non-regular partner(s) -->
<!--   * Obtained these by disaggregating @stevens2022estimating by age using estimates of sexually active population from @nguyen2022trends -->

<!-- \begin{center} -->
<!-- \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}] -->
<!-- $\implies$ Estimates of risk group proportions $p_{itak}$ by district, year and age group -->
<!-- \end{tcolorbox} -->
<!-- \end{center} -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width="350px", fig.cap = "We found a geographic discontinuity in behaviour between Southern and Eastern Africa."} -->
<!-- knitr::include_graphics("depends/aids-abstract-A.pdf") -->
<!-- ``` -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width="350px", fig.cap = "Viewing the discontinuity another way."} -->
<!-- knitr::include_graphics("depends/aids-abstract-B.pdf") -->
<!-- ``` -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width="350px", fig.cap = "Proportions of variance explained."} -->
<!-- knitr::include_graphics("depends/aaa-variance-proportions.pdf") -->
<!-- ``` -->

<!-- ## Benefits of our modelled risk group estimates -->

<!-- * Integration of all relevant surveys -->
<!--   * Two-stage approach allowed estimating FSW proportion even for surveys without a specific transactional sex question -->
<!-- * Alleivating small-sample sizes by borrowing information -->
<!--   * We borrowed information across space, between countries and over surveys so that our estimates more plausibly reflect spatial heterogeneity -->
<!-- * Estimates where there isn't direct data -->
<!--   * Although some people think of this as "making up data", the data almost never "speak for themselves" (everything is a model) -->
<!--   * Uncertainty should be higher in regions with infilling: important to transparently communicate this -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width = "350px", fig.cap = "Illustration of the problem with direct survey estimates."} -->
<!-- knitr::include_graphics("depends/model-direct-benefits.png") -->
<!-- ``` -->

<!-- ## HIV prevalence and incidence by risk group -->

<!-- * We used our risk group proportion estimates together with incidence relative risk ratios and prevalence ratios to disaggregate general population HIV estimates in the most recent year -->
<!-- * Disaggregated number of new infections on a linear scale, and people living with HIV (PLHIV) on a logit scale -->
<!--   * Using a linear scale for PLHIV resulted in prevalences outside $[0, 1]$ -->

<!-- \begin{center} -->
<!-- \begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}] -->
<!-- $\implies$ Estimates of HIV incidence $\lambda_{iak}$, number of new HIV infections $I_{iak}$, HIV prevalence $\rho_{iak}$ and PLHIV $H_{iak}$ by district, age group and risk group -->
<!-- \end{tcolorbox} -->
<!-- \end{center} -->

<!-- ## Prioritisation with risk group information -->

<!-- * Suppose we have all of the information (district, age, and risk group) -->
<!-- * Which are the strata with highest incidence? -->

<!-- ```{r include=FALSE} -->
<!-- df <- readr::read_csv("depends/incidence-district-sexbehav.csv") -->

<!-- df_area_age_behav <- df %>% -->
<!--   select(area_id, age_group, population_nosex12m, incidence_nosex12m, starts_with("population_sex"), starts_with("incidence_sex")) %>% -->
<!--   pivot_longer( -->
<!--     cols = starts_with("population") | starts_with("incidence"), -->
<!--     names_to = c("indicator", "category"), -->
<!--     names_sep = "_" -->
<!--   ) %>% -->
<!--   pivot_wider( -->
<!--     id_cols = c("area_id", "age_group", "category"), -->
<!--     names_from = "indicator", -->
<!--     values_from = "value" -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r echo=FALSE} -->
<!-- df_area_age_behav %>% -->
<!--   arrange(desc(incidence)) %>% -->
<!--   head() %>% -->
<!--   knitr::kable(digits = 2) -->
<!-- ``` -->

<!-- ## Prioritisation without risk group information -->

<!-- * What about if we lost the risk group information? Now what are the strata with the highest incidence? -->

<!-- ```{r include=FALSE} -->
<!-- df_area_age <- df_area_age_behav %>% -->
<!--   group_by(area_id, age_group) %>% -->
<!--   summarise( -->
<!--     incidence = sum(incidence * population, na.rm = TRUE) / sum(population, na.rm = TRUE), -->
<!--     population = sum(population, na.rm = TRUE) -->
<!--   ) %>% -->
<!--   ungroup() -->
<!-- ``` -->

<!-- ```{r echo=FALSE} -->
<!-- df_area_age %>% -->
<!--   select(area_id, age_group, population, incidence) %>% -->
<!--   arrange(desc(incidence)) %>% -->
<!--   head() %>% -->
<!--   knitr::kable(digits = 2) -->
<!-- ``` -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width = "350px", fig.cap = "New infections reached prioritising according to different stratifications."} -->
<!-- knitr::include_graphics("depends/infections-reached.pdf") -->
<!-- ``` -->

<!-- ## Limitations -->

<!-- * Simplistic infections reached analysis -->
<!--   * No accounting for difficulty in reaching each strata -->
<!--   * Variable intervention effectiveness -->
<!--   * Change in strata membership -->
<!-- * Under-reporting of high risk sexual behaviours -->
<!--   * Variation in under-reporting (likely by age, foremost, and location, less so) particularly concerning -->
<!-- * Risk groups definition justification not clear -->
<!--   * Didn't consider other important characteristics that may determine risk e.g. condom usage -->
<!-- * Only focused on AGYW 15-29 -->
<!--   * Could be extended to adults of both sexes aged 15-49 -->

<!-- ## Takeaways -->

<!-- 1. Risk group estimates can help implement the Global AIDS Strategy; tool and user guide currently being rolled out! -->
<!-- 2. Importance of reaching FSW -->
<!-- 3. Countries have different epidemic profiles -->

<!-- ## Acknowledgements -->

<!-- * Joint work with members of the HIV inference group (`hiv-inference.org`) particularly Katie Risher and Jeff Eaton -->
<!-- * The code for this project is at `github.com/athowes/multi-agyw` -->

<!-- ## About me -->

<!-- * At Waterloo this term to work with Alex Stringer on improving the approximate inference method we use for the Naomi model -->
<!-- * Interested in Bayesian statistics, and applications in global health and biosecurity -->
<!-- * Recently worked on early detection of biological threats with metagenomic sequencing at the Nucleic Acid Observatory -->
<!-- * You can find me online at `athowes.github.io` -->
<!-- * Come say hi if you have any similar interests! -->

<!-- # Supplement -->

<!-- ## -->

<!-- ```{r echo=FALSE, out.width="350px", fig.cap = "Results of FSW age disaggregation."} -->
<!-- knitr::include_graphics("depends/age-disagg-fsw-line.pdf") -->
<!-- ``` -->

<!-- ##  -->

<!-- ```{r echo=FALSE, out.width="350px", fig.cap = "PIT histograms and ECDF difference plots."} -->
<!-- knitr::include_graphics("depends/coverage.pdf") -->
<!-- ``` -->

## Bibliography {.allowframebreaks}

### 2023-04-08 src/docs_xx-05-23-hi-med/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_xx-05-23-hi-med")
+# setwd("src/docs_xx-05-23-hi-med")
+
+rmarkdown::render("xx-05-23-hi-med.Rmd")

### 2023-04-17 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Start sketching out slides for #144

---
title: Using statistics to guide response to the HIV epidemic
subtitle: High Impact Medicine
author: Adam Howes
institute: Imperial College London
date: May 2023
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

## Outline

1. Background on small-area estimation of HIV indicators
2. Estimating HIV risk group proportions
3. Is this something you might want to work on?

# 1. Background on small-area estimation of HIV indicators

# 2. Estimating HIV risk group proportions

## Background

::: columns

:::: column

* In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are 28% of the population but 44% of new infections
* This disparity is because of:
  1. Younger age at first sex
  2. Age patterns of sexual mixing
  3. Structural vulnerabilities and power imbalances
  4. Increased susceptibility to HIV infection

::::

:::: column

```{r echo=FALSE, out.width = "125px", fig.cap="Tweet from UNAIDS"}
knitr::include_graphics("tweet.png")
```

::::

:::

## Prevention packages

* There are some prevention options ("core package") cheap enough they should be provided to all AGYW 
* Other options ("intensified interventions") are more costly, and there are insufficient resources to offer to all AGYW

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
$\implies$ How to prioritise interventions to have the greatest impact?
\end{tcolorbox}
\end{center}

## Stratified prevention

::: columns

:::: column

* Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based on
  1. Population-level HIV incidence
  2. Individual-level sexual risk behaviour
* These are the two most proximal drivers of sexual transmission

::::

:::: column

```{r echo=FALSE, out.width = "125px", fig.cap="Global AIDS strategy"}
knitr::include_graphics("global-aids-strategy.png")
```

::::

:::

# 3. Is this something you might want to work on?

## About me

* Maths undergraduate $\to$ statistics masters $\to$ statistics PhD
* Interested in impactful applications of statistics
* Limited domain knowledge in any given area! Need to collaborate!

## Many skills are required

* Mathematics and statistics
* Computer science and software engineering
* Epidemiology and public health
* Health economics and behavioural science
* Implementation science
* ...

## Thanks for listening!

* More information about me on my website `athowes.github.io`
* Feel free to get in contact if I can be useful at `ath19@ic.ac.uk`
* My PhD is supervised by Seth Flaxman and Jeff Eaton, and the risk group work is in collaboration with Imperial's HIV Inference Group and UNAIDS

```{r echo=FALSE, out.width = "300px", fig.align='center'}
knitr::include_graphics("mrc-gida-icl-mlgh.png")
```

## Bibliography {.allowframebreaks}

### 2023-04-17 make/8_docs.R

@@ -11,6 +11,7 @@ run_commit_push("docs_12-05-22-mrc-gida")
 run_commit_push("docs_28-09-22-toronto")
 run_commit_push("docs_06-10-22-hdsl")
 run_commit_push("docs_14-10-22-waterloo")
+run_commit_push("docs_17-05-23-hi-med")
 
 #' Posters
 run_commit_push("docs_amazon-poster")

### 2023-04-17 src/docs_17-05-23-hi-med/script.R

@@ -1,0 +1,4 @@
+# orderly::orderly_develop_start("docs_xx-05-23-hi-med")
+# setwd("src/docs_17-05-23-hi-med")
+
+rmarkdown::render("17-05-23-hi-med.Rmd")

### 2023-04-17 src/docs_xx-05-23-hi-med/script.R

@@ -1,4 +1,0 @@
-# orderly::orderly_develop_start("docs_xx-05-23-hi-med")
-# setwd("src/docs_xx-05-23-hi-med")
-
-rmarkdown::render("xx-05-23-hi-med.Rmd")

### 2023-04-17 utils/archive_to_docs.R

@@ -26,6 +26,7 @@ archive_to_docs("docs_12-05-22-mrc-gida")
 archive_to_docs("docs_28-09-22-toronto")
 archive_to_docs("docs_06-10-22-hdsl")
 archive_to_docs("docs_14-10-22-waterloo")
+archive_to_docs("docs_17-05-23-hi-med")
 archive_to_docs("docs_amazon-poster")
 archive_to_docs("docs_paper")
 archive_to_docs("docs_review")

### 2023-04-21 src/docs_paper/paper.Rmd
Correct Heidelberg and Penn ordering

@@
   - code: C
+    address: Department of Public Health Sciences, Penn State College of Medicine, Hershey, PA, USA
+  - code: D
     address: Heidelberg Institute for Global Health, Faculty of Medicine, Heidelberg University, Germany
-  - code: D
-    address: Department of Public Health Sciences, Penn State College of Medicine, Hershey, PA, USA
   - code: E

### 2023-05-15 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Full outline draft of HiMed slides #144

@@
 
-1. Background on small-area estimation of HIV indicators
-2. Estimating HIV risk group proportions
-3. Is this something you might want to work on?
+1. Precision public health for HIV
+2. Estimating risk group proportions
+3. Might you want to do similar work?
 
-# 1. Background on small-area estimation of HIV indicators
+# 1. Precision public health for HIV
 
-# 2. Estimating HIV risk group proportions
+## What is precision public health
 
-## Background
+* Precision medicine: the right intervention, at the right time, to the right **individual**
+* Precision public health: the right intervention, at the right time, to the right **population**
 
-::: columns
+## How can statistics help?
 
-:::: column
+* Requires granular estimates of relevant quantities
+* Disaggregated by age group, location, behaviour
 
-* In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are 28% of the population but 44% of new infections
-* This disparity is because of:
+## What should we estimate
+
+* HIV prevalence: proportion of people who are infected
+* HIV incidence: rate of new infections
+* Antiretroviral therapy (ART) coverage: proportion of people living with HIV who take ART
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.cap="Population health goals."}
+knitr::include_graphics("fast-track.png")
+```
+
+# 2. Estimating risk group proportions
+
+##
+
+```{r echo=FALSE}
+cbpalette <- c("#56B4E9", "#009E73", "#E69F00", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
+
+data.frame(
+  x = c("Population", "New infections"),
+  y = c(0.28, 0.44)
+) %>%
+  ggplot(aes(x = x, y = y, fill = x)) +
+    geom_col() +
+    coord_flip() +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(values = cbpalette) +
+    labs(x = "", y = "", title = bquote("AGYW*" ~ bold("over-represented") ~ "in numbers of new infections"), caption = "*Adolescent girls and young women, 15-29") +
+    guides(fill = "none") +
+    theme_minimal()
+```
+
+## Why?
+
 1. Younger age at first sex
@@
 
-::::
+##
 
-:::: column
-
-```{r echo=FALSE, out.width = "125px", fig.cap="Tweet from UNAIDS"}
-knitr::include_graphics("tweet.png")
+```{r echo=FALSE, out.width = "325px", fig.cap="HIV is a gender equality issue."}
+knitr::include_graphics("rec5.png")
 ```
 
-::::
+##
 
-:::
-
-## Prevention packages
-
-* There are some prevention options ("core package") cheap enough they should be provided to all AGYW 
-* Other options ("intensified interventions") are more costly, and there are insufficient resources to offer to all AGYW
-
-\begin{center}
-\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ How to prioritise interventions to have the greatest impact?
-\end{tcolorbox}
-\end{center}
-
-## Stratified prevention
-
-::: columns
-
-:::: column
-
-* Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based on
-  1. Population-level HIV incidence
-  2. Individual-level sexual risk behaviour
-* These are the two most proximal drivers of sexual transmission
-
-::::
-
-:::: column
-
-```{r echo=FALSE, out.width = "125px", fig.cap="Global AIDS strategy"}
-knitr::include_graphics("global-aids-strategy.png")
+```{r echo=FALSE}
+data.frame(
+  price = 10,
+  effectiveness = 40,
+  name = "Condoms"
+) %>%
+  ggplot(aes(x = price, y = effectiveness, label = name)) +
+    geom_text() +
+    labs(x = "Price", y = "Effectiveness", title = "Not all interventions can* be provided to everyone", caption = "*Or should") +
+    scale_x_continuous(breaks = c(10, 90), labels = c("Cheap", "Expensive"), limits = c(0, 100)) +
+    scale_y_continuous(breaks = c(10, 90), labels = c("Works poorly", "Works well"), limits = c(0, 100)) +
+    theme_minimal() +
+    theme(
+      panel.border = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
+    )
 ```
 
-::::
+## How to prioritise interventions?
 
-:::
+The **most proximal** drivers of transmission are
+$$
+\mathbb{P}(\text{transmission}) \propto \text{sexual partnerships} \times \mathbb{P}(\text{each partner can transmit})
+$$
 
-# 3. Is this something you might want to work on?
+##
 
-## About me
+```{r echo=FALSE}
+x <- y <- c(1:4)
+
+expand.grid(x, y) %>%
+  mutate(risk = ifelse(Var2 > 1, Var1 * Var2, 0)) %>%
+  ggplot(aes(x = Var1, y = Var2)) +
+  geom_tile(aes(fill = risk)) +
+  scale_fill_gradientn(
+    colours = c("white", "#E69F00"),
+    breaks = c(2, 14),
+    labels = c("Less risk", "More risk") 
+  ) +
+  scale_x_continuous(breaks = c(1:4), labels = c("<0.3%", "0.3-1%", "1-3%", ">3%")) +
+  scale_y_continuous(breaks = c(1:4), labels = c("None", "Low", "High", "Very\n high")) +
+  labs(x = "Population-level HIV incidence", y = "Individual-level risk behaviour", title = bquote("Important we consider" ~ bold("both") ~ "population setting and individual behaviour"), fill = "") +
+  theme_minimal() +
+  theme(
+    panel.border = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
+  )
+```
+
+## Population-level HIV incidence
+
+| Level       | District-level HIV incidence rate  |
+|-------------|------------------------------------|
+| Low         | <0.3%                              |
+| Moderate    | 0.3% - 1.0%                        |
+| High        | 1.0% - 3.0%                        |
+| Very High   | >3.0%                              |
+
+## Individual-level behavioural risk
+
+| Level       | Behavioural risk group             | Risk ratio^[From...] |
+|-------------|------------------------------------|------------|
+| None        | Not sexually active                | 0          |
+| Low         | One cohabiting partner             | 1          |
+| High        | Multiple or non-regular partner(s) | 1.72       |
+| Very High   | Female sex workers                 | 13         |
+
+##
+
+* Goal: enable prioritisation of HIV programming for AGYW
+* Audience: programme managers, service providers and policy makers 
+* Plan: estimate district-age behavioural risk group proportions, prevalences and incidences
+
+##
+
+* Describe data
+* Describe model
+* Spatio-temporal smoothing
+
+##
+
+```{r echo=FALSE, out.width = "350px", fig.cap = "Direct survey estimates are too noisy to work with, but our modelled estimates don't have the same issue."}
+knitr::include_graphics("depends/model-direct-benefits.png")
+```
+
+##
+
+* Results: geographic discontinuitiy
+
+##
+
+* Results: impact of prioritisation
+
+##
+
+* Where might this work go
+* Yearly generation of estimates by country teams
+* Extending to adults 15-49
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "Example of user interface for estimates generation."}
+knitr::include_graphics("naomi_user.png")
+```
+
+# 3. Might you want to do similar work?
+
+##
+
+Possible influence on health outcomes for many people **but** a part of a complex theory of change
+
+\begin{align*}
+\mathbb{P}(\text{impact}) = &\mathbb{P}(\text{relevant people interact with your work}) \\
+&\times \mathbb{P}(\text{what you've done is useful}) \\
+&\times \mathbb{P}(\text{message correctly conveyed}) \times \cdots \\
+&\times \mathbb{P}(\text{intervention technically works}) \\
+&\times \mathbb{P}(\text{intervention correctly implemented}) \times \cdots
+\end{align*}
+
+... hopefully you get the point
+
+##
 
 * Maths undergraduate $\to$ statistics masters $\to$ statistics PhD
-* Interested in impactful applications of statistics
-* Limited domain knowledge in any given area! Need to collaborate!
+* Involved with Effective Altruism during my masters, and since then I've been interested in impactful applications of statistics
 
-## Many skills are required
+##
 
-* Mathematics and statistics
-* Computer science and software engineering
-* Epidemiology and public health
-* Health economics and behavioural science
-* Implementation science
-* ...
+* I have very limited domain knowledge! Important to collaborate
+* Broad range of required skills: epidemiology, public health, health economics, behavioural science, implementation science, mathematics, statistics, computer science, software engineering
+
+##
+
+* How might the skills of medics fit in here?
+* Need to think about this!
 
@@
 
-* More information about me on my website `athowes.github.io`
-* Feel free to get in contact if I can be useful at `ath19@ic.ac.uk`
-* My PhD is supervised by Seth Flaxman and Jeff Eaton, and the risk group work is in collaboration with Imperial's HIV Inference Group and UNAIDS
+* More information on my website: `athowes.github.io/about`
+* Feel free to get in contact if I can be useful: `ath19@ic.ac.uk`
+* My PhD is supervised by Seth Flaxman and Jeff Eaton, and the risk group work is in collaboration with Imperial's HIV Inference Group, within the MRC Centre for Global Infectious Disease Analysis, and UNAIDS
 
@@
 
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website`"}
+knitr::include_graphics("blog-post-updated.png")
+```
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (formal!) take a look at the paper."}
+knitr::include_graphics("plos-gph.png")
+```
+
 ## Bibliography {.allowframebreaks}

### 2023-05-15 src/docs_17-05-23-hi-med/script.R

@@ -1,4 +1,4 @@
-# orderly::orderly_develop_start("docs_xx-05-23-hi-med")
+# orderly::orderly_develop_start("docs_17-05-23-hi-med")
 # setwd("src/docs_17-05-23-hi-med")
 
 rmarkdown::render("17-05-23-hi-med.Rmd")

### 2023-05-16 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Upload HiMed draft for review #144

@@
 data.frame(
-  price = 10,
-  effectiveness = 40,
-  name = "Condoms"
+  price = c(20, 50, 50, 80, 70, 70, 50),
+  effectiveness = c(80, 50, 60, 60, 50, 30, 40),
+  name = c("Condoms and lube", "STI screening", "Male partner testing", "Access to PrEP", "Access to PEP", "Cash transfers and incentives", "Keep girls in school")
 ) %>%
@@
     geom_text() +
-    labs(x = "Price", y = "Effectiveness", title = "Not all interventions can* be provided to everyone", caption = "*Or should") +
+    labs(x = "Price", y = "Effectiveness", title = "Not all interventions can, or should, be provided to everyone", caption = "Possible interventions for reducing HIV incidence in AGYW.
+Positions on plot depend\n on setting, and is subject to uncertainty, so should not be interpreted too precisely.") +
     scale_x_continuous(breaks = c(10, 90), labels = c("Cheap", "Expensive"), limits = c(0, 100)) +

### 2023-05-17 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Almost finished with slides #144

--- 2023-04-17 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
@@
 
-1. Background on small-area estimation of HIV indicators
-2. Estimating HIV risk group proportions
-3. Is this something you might want to work on?
+1. Precision public health for HIV
+2. Estimating risk group proportions
+3. Some broader thoughts on careers
 
-# 1. Background on small-area estimation of HIV indicators
+# 1. Precision public health for HIV
 
-# 2. Estimating HIV risk group proportions
+## What is precision public health
 
-## Background
+* In medicine, we want to deliver the right intervention, at the right time
+* \textcolor{hilit}{Precision medicine} seeks to do that at the individual-level
+* \textcolor{hilit}{Precision public health} seeks to do it at the population-level
+
+##
 
@@
 
-* In sub-Saharan Africa, adolescent girls and young women (AGYW) aged 15-29 are 28% of the population but 44% of new infections
-* This disparity is because of:
-  1. Younger age at first sex
-  2. Age patterns of sexual mixing
-  3. Structural vulnerabilities and power imbalances
-  4. Increased susceptibility to HIV infection
+> Recognizing that **"one size does not fit all"**, the Strategy prioritizes tailoring of differentiated service packages and service delivery approaches to the **unique needs of people, communities and locations**, using granular data to focus programmes most effectively.
 
@@
 
-```{r echo=FALSE, out.width = "125px", fig.cap="Tweet from UNAIDS"}
-knitr::include_graphics("tweet.png")
-```
-
-::::
-
-:::
-
-## Prevention packages
-
-* There are some prevention options ("core package") cheap enough they should be provided to all AGYW 
-* Other options ("intensified interventions") are more costly, and there are insufficient resources to offer to all AGYW
-
-\begin{center}
-\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
-$\implies$ How to prioritise interventions to have the greatest impact?
-\end{tcolorbox}
-\end{center}
-
-## Stratified prevention
-
-::: columns
-
-:::: column
-
-* Global AIDS strategy 2021-2026 proposed stratifying HIV prevention for AGYW based on
-  1. Population-level HIV incidence
-  2. Individual-level sexual risk behaviour
-* These are the two most proximal drivers of sexual transmission
-
-::::
-
-:::: column
-
-```{r echo=FALSE, out.width = "125px", fig.cap="Global AIDS strategy"}
+```{r echo=FALSE, out.width = "125px", fig.cap="A key feature of the HIV response, both historically and into the future."}
 knitr::include_graphics("global-aids-strategy.png")
@@
 
-# 3. Is this something you might want to work on?
+## How can statistics help?
+
+* \textcolor{hilit}{Granular estimates} of relevant quantities are required
+* Disaggregation by \textcolor{hilit}{geography, sex, age, and behaviour}
+
+\begin{center}
+\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
+
+\begin{itemize}
+\item HIV prevalence: proportion of people who are infected
+\item HIV incidence: rate of new infections
+\item Antiretroviral therapy (ART) coverage: proportion of people living with HIV who take ART
+\end{itemize}
+
+\end{tcolorbox}
+\end{center}
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.cap="Example population health goals."}
+knitr::include_graphics("fast-track.png")
+```
+
+# 2. Estimating risk group proportions
+
+##
+
+```{r warning=FALSE, echo=FALSE}
+cbpalette <- c("#56B4E9", "#009E73", "#E69F00", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
+
+data.frame(
+  x = c("28% of the population", "44% of new infections"),
+  y = c(0.28, 0.44),
+  level = c(2, 1)
+) %>%
+  ggplot(aes(x = level, y = y, fill = x)) +
+    geom_col() +
+    coord_flip() +
+    geom_text(aes(label = x, y = 0.1), colour = "white", position = "dodge", size = 5) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(values = cbpalette) +
+    labs(x = "", y = "", title = "Adolescent girls and young women (AGYW) 15-29 are", caption = "(Across 13 AGYW priority countries in sub-Saharan Africa)") +
+    guides(fill = "none") +
+    theme_minimal() +
+    theme(
+      axis.title.y = element_blank(),
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank()
+    ) 
+```
+
+## Why?
+
+1. Younger age at first sex
+2. Age patterns of sexual mixing
+3. Structural vulnerabilities and power imbalances
+4. Increased susceptibility to HIV infection
+
+##
+
+```{r echo=FALSE, out.width = "250px", fig.cap="Convergence of marginal utility with equity and human rights."}
+knitr::include_graphics("rec5.png")
+```
+
+##
+
+```{r echo=FALSE}
+data.frame(
+  price = c(20, 40, 50, 80, 70, 70, 50),
+  effectiveness = c(80, 50, 60, 60, 50, 30, 40),
+  name = c("Condoms and lube", "STI screening", "Male partner testing", "Access to PrEP", "Access to PEP", "Cash transfers and incentives", "Keep girls in school"),
+  uncertainty = factor(c("More sure", rep("Less sure", times = 6)))
+) %>%
+  ggplot(aes(x = price, y = effectiveness, label = name, col = uncertainty)) +
+    geom_text() +
+    labs(x = "Price", y = "Real world effectiveness", title = bquote(bold("Insufficient resources") ~ "to provide all interventions to everyone"), caption = "Positions on plot depend on setting and should not be interpreted too precisely.\n Some interventions do not only have the effect of reducing HIV incidence.", col = "") +
+    scale_color_manual(values = c("black", "#CC79A7")) +
+    scale_x_continuous(breaks = c(10, 90), labels = c("Cheap", "Expensive"), limits = c(0, 100)) +
+    scale_y_continuous(breaks = c(10, 90), labels = c("Works poorly", "Works well"), limits = c(0, 100)) +
+    theme_minimal() +
+    theme(
+      panel.border = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
+    )
+```
+
+## How to prioritise interventions?
+
+* The \textcolor{hilit}{most proximal drivers} of transmission are
+$$
+\mathbb{P}(\text{transmission}) \propto \text{sexual partnerships} \times \mathbb{P}(\text{each partner can transmit})
+$$
+
+##
+
+```{r echo=FALSE}
+x <- y <- c(1:4)
+
+expand.grid(x, y) %>%
+  mutate(risk = ifelse(Var2 > 1, Var1 * Var2, 0)) %>%
+  ggplot(aes(x = Var1, y = Var2)) +
+  geom_tile(aes(fill = risk)) +
+  scale_fill_gradientn(
+    colours = c("white", "#E69F00"),
+    breaks = c(2, 14),
+    labels = c("Less risk", "More risk") 
+  ) +
+  scale_x_continuous(breaks = c(1:4), labels = c("Low: <0.3%", "Moderate: 0.3-1%", "High: 1-3%", "Very high: >3%")) +
+  scale_y_continuous(breaks = c(1:4), labels = c("None", "Low", "High", "Very\n high")) +
+  labs(x = "Population-level HIV incidence", y = "Individual-level risk behaviour", title = bquote("Important we consider" ~ bold("both") ~ "population setting and individual behaviour"), fill = "") +
+  theme_minimal() +
+  theme(
+    panel.border = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
+  )
+```
+
+## Individual-level behavioural risk
+
+| Level       | Behavioural risk group             | Risk ratio |
+|-------------|------------------------------------|------------|
+| None        | Not sexually active                | 0          |
+| Low         | One cohabiting partner             | 1          |
+| High        | Multiple or non-regular partner(s) | 1.72       |
+| Very High   | Female sex workers                 | 13         |
+
+## What have we done
+
+* Goal: enable \textcolor{hilit}{prioritisation} of HIV programming for AGYW
+* Audience: programme managers, service providers and policy makers 
+* Plan: estimate district-age-behavioural risk group proportions, HIV prevalences and HIV incidences across 13 high priority countries in sub-Saharan Africa
+* Method: a Bayesian spatio-temporal model of survey data
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "A total of 46 surveys: importantance of good data processing code!"}
+knitr::include_graphics("depends/available-surveys.png")
+```
+
+##
+
+```{r echo=FALSE, warning=FALSE, out.width="350px", fig.cap = "Example of model structure: we assume that neighbouring districts are similar."}
+areas <- sf::read_sf("depends/zwe_areas.geojson")
+
+areas %>%
+  filter(area_level == 2) %>%
+  arealutils::plot_graph(add_geography = TRUE)
+```
+
+##
+
+```{r echo=FALSE, out.width="80%", fig.cap = "Direct survey estimates are too noisy to work with due to low sample sizes, but our modelled estimates don't have the same issue."}
+knitr::include_graphics("depends/model-direct-benefits.png")
+```
+
+##
+
+```{r echo=FALSE, out.width="80%", fig.cap = "We found a prominent geographic discontinuity between eastern and southen Africa in risk group membership for women 20-29."}
+knitr::include_graphics("depends/aids-abstract-A.pdf")
+```
+
+##
+
+```{r echo=FALSE, out.width="80%", fig.cap = "Supposing you prioritised those in the highest incidence strata, what percent of new infections could you find per percent of the population reached?"}
+knitr::include_graphics("depends/infections-reached.pdf")
+```
+
+## Where might this work go
+
+* Extension to adults 15-49 and further countries
+* Generation of estimates led by country teams as a part of a yearly process: data ownership, data use, and data quality
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "Example of user interface for estimates generation."}
+knitr::include_graphics("naomi_user.png")
+```
+
+# 3. Some broader thoughts on careers
+
+##
+
+* Upside: could \textcolor{hilit}{influence health outcomes for many people}
+* Downside: part of a (more?) complex theory of change
+
+\begin{align*}
+\mathbb{P}(\text{impact}) = &\mathbb{P}(\text{relevant people interact with your work}) \\
+&\times \mathbb{P}(\text{what you've done is useful}) \\
+&\times \mathbb{P}(\text{message correctly conveyed}) \times \cdots \\
+&\times \mathbb{P}(\text{intervention technically works}) \\
+&\times \mathbb{P}(\text{intervention correctly implemented}) \times \cdots
+\end{align*}
+
+* How does this balance out?
 
@@
 
-* Maths undergraduate $\to$ statistics masters $\to$ statistics PhD
-* Interested in impactful applications of statistics
-* Limited domain knowledge in any given area! Need to collaborate!
+* Maths undergraduate $\to$ statistics masters $\to$ statistics (and machine learning, sort of) PhD
+* Involved with Effective Altruism during my masters, and since then I've been interested in impactful applications of statistics
 
-## Many skills are required
+## Applied methodology
 
-* Mathematics and statistics
-* Computer science and software engineering
-* Epidemiology and public health
-* Health economics and behavioural science
-* Implementation science
-* ...
+* Being good (perhaps not great) at a useful enough collection of things
+* Feeling like no one care about the application at methods conferences, and no one cares about the methods at application conferences
+
+## Team science
+
+* A lot of disciplines required: Epidemiology, public health, health economics, behavioural science, implementation science, mathematics, statistics, computer science, software engineering
+* Academia pushes against this by wanting every contribution to be marginally interesting in each field
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "Alternative structures for science."}
+knitr::include_graphics("fro.png")
+```
 
@@
 
-## Bibliography {.allowframebreaks}
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website`"}
+knitr::include_graphics("blog-post-updated.png")
+```
+
+##
+
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (formal!) take a look at the paper."}
+knitr::include_graphics("plos-gph.png")
+```

### 2023-05-17 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Slides up #144

@@
 * In medicine, we want to deliver the right intervention, at the right time
-* \textcolor{hilit}{Precision medicine} seeks to do that at the individual-level
+* \textcolor{hilit}{Precision medicine} seeks to do it at the individual-level
 * \textcolor{hilit}{Precision public health} seeks to do it at the population-level
@@
 
-## What have we done
+## The work we've done
 
@@
 
-```{r echo=FALSE, warning=FALSE, out.width="350px", fig.cap = "Example of model structure: we assume that neighbouring districts are similar."}
-areas <- sf::read_sf("depends/zwe_areas.geojson")
+```{r echo=FALSE, out.width="350px", fig.cap = "Example DHS questionnaire."}
+knitr::include_graphics("dhs.png")
+```
+
+##
+
+```{r echo=FALSE, out.width="350px", fig.cap = "How we allocated survey respondents to risk groups based on the questionnaire."}
+knitr::include_graphics("depends/category-flowchart.pdf")
+```
+
+## What do you mean by model?
+
+* Translation of scientific knowledge into a mathematical \textcolor{hilit}{data generating process}. If we wanted to, we could simulate fake data
+* Given observed data, we use Bayes theorem to update our beliefs about the parameters of the model
+
+##
+
+```{r echo=FALSE, warning=FALSE, out.width="350px", fig.cap = "An example of scientific knowledge included in the model is that we assume that neighbouring districts are similar.
+This is Tobler's first law of geography.
+The pictured country is Tanzania."}
+areas <- sf::read_sf("depends/tza_areas.geojson")
 
@@
 * Extension to adults 15-49 and further countries
-* Generation of estimates led by country teams as a part of a yearly process: data ownership, data use, and data quality
+* Generation of estimates led by country teams as a part of a yearly process
+* Virtuous cycle of data \textcolor{hilit}{ownership}, data \textcolor{hilit}{use}, and data \textcolor{hilit}{quality}
 
@@
 * Being good (perhaps not great) at a useful enough collection of things
-* Feeling like no one care about the application at methods conferences, and no one cares about the methods at application conferences
+* Feeling like no one cares about the application at methods conferences, and no one cares about the methods at application conferences
 
@@
 * Academia pushes against this by wanting every contribution to be marginally interesting in each field
+* MRC GIDA at Imperial does a good job here, in my opinion
 
@@
 
-```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website`"}
+```{r echo=FALSE, out.width = "300px", fig.align='center', fig.cap = "For more (informal!) take a look at the blog post on my website."}
 knitr::include_graphics("blog-post-updated.png")

### 2023-05-18 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Correct typo #144

@@
 
-```{r echo=FALSE, out.width="350px", fig.cap = "A total of 46 surveys: importantance of good data processing code!"}
+```{r echo=FALSE, out.width="350px", fig.cap = "A total of 46 surveys: importance of good data processing code!"}
 knitr::include_graphics("depends/available-surveys.png")
